### 2020-01-31 main.tex
Initial Overleaf Import

%%
%% This is file `sample-xelatex.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-xelatex.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

% new commands and shortcuts
\def\bs{\textit{\textbf{s}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textrm{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
%\acmConference[ Kalamata, Messinia, Greece '20]{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation}{July 20--23, 2020}{ Kalamata, Messinia, Greece}
\acmBooktitle{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation,  July 20--23, 2020,  Kalamata, Messinia, Greece}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.

%\usepackage[options ]{algorithm2e}
\usepackage[ruled,vlined]{algorithm2e}

\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Bit Complexity for Computation of one Point in each Connected Component of a Smooth Real Hypersurface}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Jesse Elliott}
\affiliation{%
  \institution{Cheriton School of Computer Science}
  \city{University of Waterloo}
}
\email{jakellio@uwaterloo.ca}

\author{Mark Giesbrecht}
\affiliation{%
  \institution{Cheriton School of Computer Science}
  \city{University of Waterloo}
}
\email{mwg@uwaterloo.ca}

\author{Eric Schost}
\affiliation{%
  \institution{Cheriton School of Computer Science}
  \city{University of Waterloo}
}
\email{eschost@uwaterloo.ca}
%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Elliott, Giesbrecht, and Schost.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
We provide bit complexity estimates for the computation of at least one point in each connected component of a smooth real hypersurface. This problem is a basic and important subroutine used in semi-algebraic geometry. For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface. The algorithm requires some genericity properties, which we ensure through random changes of variables that produce generic coordinate systems. In order to ensure these properties with arbitrarily high probability, we developed a new quantitative extension of Thom's weak transversality theorem, and a quantitative Noether normalization statement for polar varieties. These statements enable us to give a precise probability analysis of a modular algorithm, where the algorithm is monte carlo and we can guarantee correctness with arbitrarily high probability. 
\par
Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{a,b,c,d}. However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work.  Our results therefore begin to fill a missing gap in the research. 
%Furthermore, as bit complexity provides a far more realistic model of computation compared to arithmetic complexity, which only counts each operation at unit cost whereas bit complexity provide more information for both time and space resources that are needed in practice, it is important that this missing gap is filled. 
%As bit complexity provides a far more realistic model of computation compared to arithmetic complexity, which only counts each operation at unit cost, our contribution is necessary and important. Indeed, bit estimates provide more information for both time and space resources that are needed in practice. 
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Real algebraic geometry, weak transversality, Noether position, bit complexity}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
%
%
%
%
%%%%%% Introduction
%
\section{Introduction}
%
%
%%%%%% Problem statement
%
\subsection{Problem statement}
Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth. We provide bit-complexity estimates for computing one point in each connected component of $V(f)\cap \R^n.$ Its boolean complexity is $\hdots$.
%
%
%
%%%%%% Motivation
%
\subsection{Motivation}
\subsubsection{Applications}
Computing one point in each connected component of the real part of a hypersurface is a basic and important subroutine used in semi-algebraic geometry. For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface, and it is used in determining whether or not a complex hypersurface has real solutions. 
\subsubsection{Bit-complexity}
Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{a,b,c,d}. However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work. As bit complexity provides a far more realistic model of computation compared to arithmetic complexity,  which only counts each operation at unit cost, our results therefore begin to fill an important missing gap in the research. 
%Indeed, bit estimates provide more information for both time and space resources that are needed in practice.  
\subsubsection{Quantitative genericity statements}
%
%
%
%%%%%% Main result
%
\subsection{Main result}
\begin{theorem}
Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $\hdots$. Otherwise the algorithm either produces a subset of the critical points or FAIL. In any case, the algorithm uses 
\[
\hdots  
\]
boolean operations.
\end{theorem}
%
The algorithm is Monte Carlo and can error on one side by producing a proper subset of the points. Running the algorithm $k$ times gives a list of outputs among which the highest cardinality set includes at least one point in each connected component with probability at least $\hdots.$
%
%
%
%
%%%%%% Notation and Preliminaries
%
\section{Notation and preliminaries}
%
%
%%%%%% Algebraic Sets
%
\subsection{Algebraic sets}
An \textit{algebraic set} $V \subset \C^n$ is the set of common zeros of a set of polynomials $\textit{\textbf{f}}=(f_1,\hdots,f_s)$ in $\C[X_1,\hdots,X_n].$
\subsubsection{Dimension and degree}
The \textit{dimension} of an algebraic set $V \subset \C^n$, denoted $\dim V,$ can be defined in the following ways:
\begin{enumerate}
    \item The number of generic hyperplanes needed to intersect with $V$ to obtain a finite set. 
    \item The Krull Dimension of $\C[X_1,\hdots,X_n]/I(V)$.
\end{enumerate}
The \textit{codimension} of $V$ is $n - \dim V$. An algebraic set is \textit{equidimensional} if each irreducible component has the same dimension.  If each component has dimension $d$ then we say it is $d-$equidimensional. 
The \textit{degree} of an algebraic set is the number of intersection points between itself and $\dim V$ generic hyperplanes.
\begin{example} 
An algebraic set of dimension zero is a finite set, with degree equal to its cardinality.
\end{example}
\begin{example}
An algebraic set of dimension 1 is a curve, with degree equal to the number of intersection points with a generic hyperplane.
\end{example}
%
%
%
%%%%%% Bit-size, height and degree
%
\subsection{Bit-size, height and degree}
For $r \leq n,$ $\textit{\textbf{X}}_{\leq r}$ denotes $[X_1,\hdots,X_r]$ and $\textit{\textbf{X}}$ denotes $[X_1,\hdots,X_n]$. 
\par 
For $a=\frac{u}{v}$ in $\mathbb{Q}-\{0\},$ the  \textit{height} of $a,$ $\htt(a),$ is the maximum of $\log(|u|)$ and $\log(|v|),$ where $u \in \mathbb{Z}$ and $v \in \mathbb{N}$ are coprime. If $v$ is the minimal common denominator of all non zero coefficients of $f$, then the \textit{height} of $f, \htt(f),$ is defined as the maximum of the logarithms of $v$ and of the absolute values of the coefficients of $vf$. 
%
\par
We write $\htt(\textit{\textbf{f}})=(\htt(f_1),\hdots,\htt(f_N))$ and assume that $\htt(\textit{\textbf{f}}) \leq \textit{\textbf{s}} = (S_1,\hdots,s_N),$  with $\htt(f_i) \leq s_i$ for all $i \in \{ 1,\hdots,N\}.$
%
%
%%%%%% Data structures
\subsection{Data structures}
\subsubsection{Strait-line programs}
\subsubsection{Zero-dimensional parameterizations}
%
%
%
%%%%%% Regular and singular points
%
\subsection{Critical / singular points}
\subsubsection{Regular and singular points of varieties}
Let $V \subset \C^n$ be a $d$-equidimensional algebraic set. 
The point $x \in V$ is a \textit{regular point} if $\dim (T_xV) = d.$ Otherwise $x$ is a \textit{singular point}. We let $\reg(V)$ and $\sing(V)$ respectively denote the regular and singular points of $V$. 
%
\par 
We assume that $V$ is smooth so that $V=\reg(V).$
%
%
%
%
%
%%%%%%%%%%%%%%%% Critical points of polynomial mappings
%
\subsubsection{Critical points of polynomial mappings}
Let $\phi : V \rightarrow \C^m$ be a polynomial mapping. A \textit{critical point} of $\phi$ is a regular point of $V$ with $d_x \phi(T_xV) \not = \C^m,$ where $d_x \phi$ is the differential of $\phi$ at $x.$ A \textit{critical} value of $\phi$ is the image of a critical point by $\phi$.
%
%
%%%%%% The zariski-tangent space
%
\subsection{The zariski-tangent space}
Denote by $\grad_{\xb}(f)$ the evaluation of the gradient vector of $f$ in $\C[X_1,\hdots,X_n]$ at $\textit{\textbf{x}}$ in $\C$.
The \textit{Zariski-tangent space} to $V$ at $\textit{\textbf{x}} \in V$ is the vector space $T_{\xb}V$ defined by the equations $\grad_{\xb}(f) \cdot \textit{\textbf{v}}=0$ for all polynomials $f$ that vanish on $V$. For a polynomial system $\textit{\textbf{f}}=(f_1,\hdots,f_N)$ in $\C[X_1,\hdots,X_n]$, denote by $\jac(\textit{\textbf{f}})$ the Jacobian matrix.
%and $\jac(\textit{\textbf{f}},i)$ the truncated Jacobian matrix
%\[ 
%\bbm 
%\frac{\partial f_1}{\partial X_{i+1}} \hdots \frac{\partial f_1}{\partial X_n} \\
%\frac{\partial f_N}{\partial X_{i+1}} \hdots \frac{\partial f_N}{\partial X_n}
%\ebm,~\textrm{for }i \in \{1,\hdots,n-1\}.\]
The following is a direct consequence of \cite[Corollary 16.20]{ECA}.
\begin{proposition}
If $V \subset \C^n$ is a $d$-equidimensional algebraic set with ideal $I(V)=\langle f_1,\hdots,f_N \rangle$, then at any point $\textbf{x}$ of $\reg(V),$ $\jac_\textbf{x}(\textbf{f})$ has full rank $n - \dim(V)$ and the kernel of $\jac_\textbf{x}(\textbf{f})$ is equal to $T_\textbf{x}V.$ 
\end{proposition}
%
%
%%%%%% Polar Varieties
%
\subsection{Polar varieties}
%
Let $V\subset \C^n$ be a smooth $d$-equidimensional variety. For $i \in \{1,\hdots,d\},$ denote by $\pi_i:\C^n \rightarrow \C^i$ the projection
$(x_1,\hdots,x_n) \mapsto  (x_1,\hdots,x_i)$. A \textit{critical point} $\textit{\textbf{x}}$ in $V$ is a singular point on $\pi_i.$ In other words, the point $\textit{\textbf{x}} \in V$ is a critical point if $\dim \pi_i( T_\textit{\textbf{x}}V) < i$. The $i$-th  \textit{polar variety} \[W(\pi_i,V) := \{\textit{\textbf{x}} \in V~|~\dim \pi_i(T_xV) < i\}\] is the set of critical points of $\pi_i$ on $V$. Denote by $\I$ the ideal \[\frak{I}(\pi_i,V) := I(W(\pi_i,V)).\] 
%
%
\begin{proposition} 
Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ squarefree with $V(f)$ smooth. Then, for $i \in \{1,\hdots,n\}$, the polar variety $W(\pi_i,V)$ is defined by the vanishing of \[f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.\]
\end{proposition}
\begin{proof}
We have a proof but maybe we should reference it?
\end{proof}
%
%
%
%
%
%%%%%% Changes of Variables
%
\subsection{Changes of variables}
Consider $A \in \C^{n^2}, f \in \C[X_1,\hdots,X_n], \textit{\textbf{x}} \in \mathbb{C}^n,$ and $V \subset \C^n$. We denote by 
$V^A$ the set $\{x^A~|~\xb \in V\}, f^A$ the polynomial $f(A \xb)$ and $\xb^A$ denotes $A^{-1}\xb$. Notice $f^A(\xb^A) = f(A A^{-1}\xb)=f(\xb).$
%
%
%
%%%%%% Main Algorithm 
%
\section{The Main Algorithm}
\begin{algorithm}
\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $D=\deg(f)$}
\KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq $?\;
\nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
\nl Use \cite{4} to compute the partial derivatives $\frac{\pa f^A}{\pr X_{i+1}},\hdots,\frac{\pa f^A}{\pr X_n}$\;
    \caption{{Main Algorithm} \label{}}
\nl \For{$i\gets1$ \KwTo $n$}{
Apply the symbolic homotopy algorithm from \cite{SH} with input $\{X_1,\hdots,X_i,f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$ and $D$ to obtain a zero dimensional parameterization of $W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(0)$.;
} 
\nl \Return $\cup_{i=1}^n W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(0)$;
\end{algorithm}
%
%
%
%
%
%
%%%%%% Genericity Properties
%
\section{Genericity properties}
%
Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ squarefree with total degree $D$ and $V(f)$ smooth. We say that $V$ is in \textit{Noether position} for $\pi_D$ when the extension \[\C[X_1,\hdots,X_D] \rightarrow \C[X_1,\hdots,X_n]/I(V)\] is injective and integral.  Then, for any $\xb \in \C^D,$ the fiber 
$V \cap \pi_D^{-1}(\xb)$ has dimension zero. 
We say that $f$ satisfies $\textbf{H}$ if 
\begin{enumerate}
    \item $f$ is squarefree;
    \item $V(f)$ is smooth.
\end{enumerate}
For $i\in\{1,\hdots,n\}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
\begin{enumerate}
\item $\I(\pi_i,V)$ is radical;
\item either $W(\pi_i,V)$ is empty or $(i-1)$-equidimensional;
\item $W(\pi_i,V)$ is smooth;
\item $\langle X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
\item $V(X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ has dimension $0$;
\item $V(X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
\item either $W(\pi_i,V)$ is empty or in Noether position for $\pi_{i-1}$.
\end{enumerate}
%
\begin{theorem}
Suppose that $f$ satisfies \textbf{H}. Then there exists a Zariski closed set $\frak{X} \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{?}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\frak{X}$ then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
\end{theorem}
\begin{corollary} 
Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{?}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
\end{corollary}
%
%
%
%
%
%%%%%% A Quantitative Extension of Thom's Weak Transversality
%
\section{Weak Transversality}
Write more about transversality? Provide an example?
%
%
\subsection{Extending Thom's weak transversality}
%
We prove a quantitative extension of Thom's weak transversality \cite{TWT} specialized to the particular case of transversality to a point, which can be rephrased entirely in terms of critical / regular values.
\par 
Denote by $\Phi :\C^n \times \C^{\dt} ~ \rightarrow \C^{m}$
a polynomial mapping, where $n,\dt,$ and $m$ are positive integers (assume $m \leq n$?). Assume the total degree of $\Phi$ is bounded by an integer $d$. For $\vt$ in $\C^{\dt}$, let $\Phi_{\vt} : \C^n \rightarrow \C^{m}$ be the induced mapping $x\mapsto \Phi(x,\vt)$.
\begin{theorem} (Weak transversality)
Suppose that $0$ is a regular value of $\Phi$. Then there exists a hypersurface $\Delta \subset \C^{\dt}$ of degree at most $d^n$ for which, if $\vt \in \C^{\dt}-\Delta$ then $0$ is a regular value of $\Phi_{\vt}$. 
\end{theorem}
%
%
\subsection{Genericity and Sard's lemma}
It will sometimes be useful for us to let the matrix $A$ represent new indeterminates: let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ It follows from Proposition 4.2 that for a generic $A \in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.  The proof of \cite[Theorem B.3]{NO}, which shows the existence of $\Delta \subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the critical values of a polynomial mapping are contained in a hypersurface. It follows from Sard's lemma that for the matrix of indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise it could not be that $0$ is a regular value of $\Phi_A,$ for a generic $A\in \C^{n^2}.$ Therefore,
\[
\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(x),\frac{\pa f^{\A}(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(x)}{\pa X_n}\right)
\]
has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$. We will rely on this fact in Section 5. 
%
%
\subsection{Proof of Proposition 5.1}
% 
The proof of \cite[Theorem B.3]{TWT} shows the existence of $\Delta.$ We extend the theorem by showing that the degree of $\Delta$ is upper bounded by $d^n.$ 
\subsubsection{More notation and setup}
Put $X = \Phi^{-1}(0)$ and consider the projection $\pi:(x, \vt) \in \C^n \times \C^{\dt} \mapsto \vt \in\C^{\dt}$. The proof of \cite[Theorem B.3]{NO} also shows that $X$ is $(n+ \dt -m)$-equidimensional, and that if $\vt \in \C^{\dt}$
is such that $0$ is a critical value of $\Phi_{\vt}$, then $\vt$ is a critical value of the restriction of $\pi$ to $X.$ We show that the critical points of $\pi|_X$ are contained in an algebraic set
$\Delta^{'}$. We then show that 
\[\deg \Delta \leq \deg \Delta^{'} \leq d^n.
\] 
%
\subsubsection{Explicitly characterizing $\Delta^{'}$.} 
We will use \cite[Lemma B.4]{NO}:
\begin{lemma}
Let $A=\bbm A_1 \\ A_2 \ebm$ be a matrix. Then, 
\[ 
\textup{rank}(A) = 
\textup{rank}(A_1) + \textup{rank}(A_2|\ker(A_1)),
\]
where $A_2|\ker(A_1)$ is the restriction of the linear map defined by $A_2$ to the kernel of $A_1$. 
\end{lemma}
Let $M$ denote the matrix
\begin{align*}M(\xb,\vt)&:= \jac_{(\xb,\vt)}(\Phi;X)\\
&= 
\bbm 
\jac_{(\xb,\vt)}(\pi)\\
\jac_{(\xb,\vt)}(\Phi) 
\ebm 
=
\bbm 
\textbf{0}_{\dt \times n}\hspace{5mm}\textbf{I}_{\dt} \\
\jac_{(\xb,\vt)}(\Phi)
\ebm.\end{align*}
%
%
\begin{proposition} 
$M(\xb,\vt)$ has full rank $m+\dt$ if and only if $(\xb,\vt)$ is a regular point on $\pi|_X.$ 
\end{proposition}
\begin{proof}
The dimension of the source $\pi|_X$ is $\dim X = n + \dt - m.$ The dimension of the target space is $\dim \C^{\dt} = \dt.$ Now, if $(\xb,\vt)$ is a regular point of $\pi|_{X}$ then $\dim \textrm{Im}(d\pi|_X(T_{\xb}X)) = \dt$. When $\xb$ is regular on $X$, by Proposition 2.3, $\jac_{(\xb,\vt)} (\Phi) = T_{(\xb,\vt)}X$ and has full $\rk n + \dt - \dim X = n + \dt - (n + \dt - m) = m$. By applying Lemma 4.3 we have
\begin{align*}
\rank ~M(\xb,\vartheta) &= 
\rank ~
\bbm 
\jac_{(\xb,\vartheta)}(\pi|_X)\\
\jac_{(\xb,\vartheta)}(\Phi) 
\ebm \\
&= \rank~ \jac_{(\xb,\vartheta)}(\pi|_X) + \rank ~\jac_{(\xb,\vartheta)}(\Phi)|_{T_{(x,\vartheta)}X} \\
&= m + \dim \textrm{Im}(d\pi|_{\Xb}(T_xX)) \\
&= m + \dt 
\end{align*}
Otherwise, if $(\xb,\vt)$ is not a regular point of $\pi|_X,$ then \[\dim \textrm{Im}(d\pi|_X(T_{\xb}X)) < \dt\]  and therefore $\rank ~M(\xb,\dt) < m+\dt.$ 
\end{proof}
%
Therefore if $M(x,\vt)$ does not have full rank $\dt+m$ then $(x,\vt)$ is a critical point of $\pi|_X$. Since the minors of order $\dt+m$ vanish when $(x,\vt)$ is a critical point, the algebraic set defined by the vanishing of the minors of $M$ of order $\dt + m$ describe the critical points:
\[
\Delta^{'} = V(\textrm{minors of }M\textrm{ of order }\dt + m).
\]
Furthermore, we can characterize $\Delta^{'}$ with fewer equations by discarding those that evaluate to zero. Indeed, the first $\dt$ rows of $M(x,\vt)$ is the Jacobian matrix of the projection mapping $\pi|_X,$ which consists of a sub-matrix of zeros followed by an identity sub-matrix. Hence, we can discard several minors that evaluate to zero. Let $J$ denote the sub-matrix of the Jacobian of $\Phi$ consisting of the first $n$ columns:
 \[J := \jac_{(\xb,\vt)}(\Phi)[-;1,n].\]
\begin{proposition} 
$J(\xb,\vt)$ has full rank $\min\{m,n\}$ if and only if $M(\xb,\vt)$ has full rank $\dt+m.$ 
\end{proposition}
\begin{proof}
Notice 
\begin{align*}
M(\xb,\vt)&= 
\bbm 
\jac_{(\xb,\vt)}(\pi)\\
\jac_{(\xb,\vt)}(\Phi) 
\ebm \\
&=
\bbm 
\textbf{0}_{\dt \times n}\hspace{5mm}\textbf{I}_{\dt} \\
\jac_{(\xb,\vt)}(\Phi)
\ebm\\
&=
\bbm 
\textbf{0}_{\dt \times n} &\textbf{I}_{\dt} \\
J(\xb,\vt)     &\jac_{(\xb,\vt)}(\Phi)[-;n+1,\dt]
\ebm.
\end{align*}
The first $n$ columns of $M(\xb,\vt)$ must all be different from the remaining $\dt$ columns. Therefore $J(\xb,\vt)$ has full rank $\min\{n,m\}$ if and only if $M(\xb,\vt)$ has full rank $\dt+m.$
\end{proof}
Therefore $\Delta^{'} = V(\textrm{minors of }J\textrm{ of order }\min\{m,n\}).$
%
%
%
%
\subsubsection{Bounding the degree of $\Delta^{'}$.}
% 
Let $\textit{\textbf{L}}=[L_1,\hdots,L_m]$ be Lagrange multipliers, and consider the Lagrange system 
\[
\textit{\textbf{L}}\cdot J(x,A)=[\mathscr{L}_1,\hdots,\mathscr{L}_{n}]=[0,\hdots,0].
\] 
Denote by $\frak{Z}$ the algebraic set defined by the vanishing of $\mathscr{L}_1,\hdots,\mathscr{L}_{n},$ and consider the projection 
\begin{align*} 
\pi_{n+\dt} :~ \C^{n+\dt+m} &\rightarrow \C^{n+\dt}\\
(\textit{\textbf{x}},\vt,\textit{\textbf{L}})~ &\mapsto (\textit{\textbf{x}},\vt).
\end{align*}
Denote by $\frak{Z}^{'}$ the algebraic set
\[
\frak{Z}^{'} := \overline{\frak{Z} - \{(\textit{\textbf{x}},\vt,0,\hdots,0) \in \C^{n+\dt+m}~|~(\textit{\textbf{x}},\vt,0\hdots,0) \in \frak{Z}\}}.
\]
\begin{proposition}  
The projection $\pi_{n+\dt}$ on $\frak{Z}^{'}$ is equal to $\Delta^{'}$.
\end{proposition}
%
We will use the following lemma to prove Proposition 4.6.
%
%
\begin{lemma} 
For an irreducible component $Z$ of $\Z^{'},$ there exists a Zariski open subset $Z^o \subset Z$ with \[\pi_{n+\dt}~(Z^{o}) \subset \D^{'}~(\textrm{why?})\]
and
\[\overline{\pi_{n+\dt}~(\overline{Z^o})} = \overline{\pi_{n+\dt}~(Z^o)}.\] 
\end{lemma} 
\begin{proof}
There exists a Zariski open subset $Z^o \subset Z$ with 
%
\[\pi_{n+\dt}~(Z^{o}) \subset \D^{'}~(\textrm{why?}).\] 
%
Since $Z^o \subset \overline{Z^o}$, we have $\pi_{n+\dt}~(Z^o) \subset \pi_{n+\dt}~(\overline{Z^o})$ and thus 
\[\overline{\pi_{n+\dt}~(Z^o)} \subset \overline{\pi_{n+\dt}~(\overline{Z^o})}.
\]   
Since closed sets are by definition varieties in the Zariski topology, \[\overline{\pi_{n+\dt}~(\overline{Z^o})} = V\left( I(\overline{Z^o}) \cap \mathbb{C}[\textit{\textbf{X}},\vt]\right),
\] 
so let 
\[\overline{\pi_{n+\dt}~(\overline{Z^o})} = V(\mathscr{I}),
\] 
for some ideal $\mathscr{I} \subset \C[\Xb,\vt].$ Take $f$ in $\mathscr{I}$ so that $f$ vanishes on 
\[
\overline{\pi_{n+\dt}~(Z^o)}\subset \overline{\pi_{n+\dt}~(\overline{Z^o})}
\]
Then $f$ must also vanish on the subset 
\[
\pi_{n+\dt}~(Z^o)\subset \overline{\pi_{n+\dt}~(Z^o)}\subset \overline{\pi_{n+\dt}~(\overline{Z^o})}
\]
and $Z^o,$ and hence also on $\overline{Z^o}.$ Therefore, 
\[
f \in I(\overline{Z^o}) \cap \mathbb{}[\textit{\textbf{X}},\vt]
\]
and  $\mathscr{I} \subset I(\overline{Z^o}) \cap \mathbb{Q}[\textit{\textbf{X}},\vt]$ (why?), and it then follows that 
\begin{align*}
\overline{\pi_{n+\dt}~(\overline{Z^o})}&=V\left(I(\overline{Z^o})\cap \mathbb{C}[\textit{\textbf{X}},\vt]\right) \\&\subset V(\mathscr{I})\\&\subset \overline{\pi_{n + \dt}~(Z^o)}\textrm{ (why?)}.
\end{align*}
\end{proof}
%
%
Now we prove Proposition 4.7.
\begin{proof}
For all $(\textit{\textbf{x}},\vt) \in \D^{'}, $ there exists $\textit{\textbf{L}}^{'} \not = (0,\hdots,0)$ with $(\textit{\textbf{x}},\vt,\textit{\textbf{L}}^{'}) \in \Z.$ Thus, $(\textit{\textbf{x}},\vt,\textit{\textbf{L}}^{'})$ is in
\[
     \Z - \left\{(x,\vt,0,\hdots,0) \in \C^{n+\dt+m}~|~(x,\vt,0\hdots,0) \in \Z\right\}, 
\]
which implies that $(x,\vt,\textit{\textbf{L}}^{'}) \in \Z^{'}$, which then in turn implies that
\[
    (x,\vt) \in \Pi_{n + \dt}~(\Z^{'}).
\]
Therefore $\D^{'} \subset \pi_{n+\dt}~(\Z^{'}).$
\newline \indent 
Now let $Z$ be an irreducible component of $\Z^{'}.$ By Lemma 4.7 there exists a Zariski open subset $Z^o \subset Z$ with $\pi_{n+\dt}~(Z^{o}) \subset \D^{'}$, and
\begin{align*}
 \Pi_{n+\dt}~(Z) = 
  \Pi_{n+\dt}~(\overline{Z^o})
  &\subset 
  \overline{\pi_{n+\dt}~(\overline{Z^o})}\\
  &=
  \overline{\Pi_{n+\dt}~(Z^o)}, &\textrm{by Lemma 4.7,}\\
  &\subset \overline{\D^{'}}=\D^{'}.
\end{align*}
   Therefore $\Pi_{n+\dt}~(\Z^{'}) \subset \D^{'}.$
\end{proof}
%
%
\begin{proposition} 
The degree of $\D^{'}$ is at most $d^n.$
\end{proposition} 
\begin{proof}
It follows from B\'ezout's Theorem that 
\[
\deg \frak{Z} \leq (d-1+1)^n=d^n.
\]
From \cite[Lemma 2]{H} we have 
\[
\deg(\pi_{n+\dt}(\Z^{'})) \leq \deg(\Z^{'}).
\]
Therefore 
\begin{align*}
\deg(\D^{'}) &= \deg(\pi_{n+\dt}~(\Z^{'})),&\textrm{by Proposition 4.6,}\\ 
            &\leq \deg(\Z^{'}),\\ 
            &\leq \deg(\Z), &\textrm{by ?,}\\ 
            &\leq d^n.
\end{align*}
\end{proof}
%
%
%
\section{Proof of $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$}
%
%
We assume our input polynomial $f$ satisfies \textbf{H} so that $f$ is squarefree with $V(f) \cap \mathbb{R}^n$ smooth. Thus, by Proposition 2.4,  $W(\pi_i,V(f))$ is defined by the vanishing of \[\fb := \left(f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right).\]
If the Jacobian of $\fb$ has full rank at all $x \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion [4, Theorem 16.19] that $f$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$. 
%
\begin{theorem}
There exists a Zariski closed set $\Delta \subset \C^{n^2}$ of degree at most $D^n$ with the property that, if $A \in \C^{n^2} - \Delta$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
\end{theorem}
\subsection{Sketch of the proof of Theorem 6.1}
We will let $\Phi$ be the mapping 
\[
(\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),
\] 
so that 
\[
\Phi_A^{-1}(0)= W(\pi_i,V^A).
\]
Then we show that $0$ is a regular value of $\Phi$, so that, by Proposition 4.2, $\Delta \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta$ then $0$ is a regular value of $\Phi_A.$ It then follows that 
\[
\jac_{\xb}(\Phi_A) = \jac_{\xb}\left(f^A(x),\frac{\pa f^A(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(x)}{\pa X_n}\right)
\]
has full rank for all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
\subsection{Proof of Theorem 6.1}
Now, with $i \in \{1,\hdots,n\}$, let $\Phi$ be the mapping \[(\xb,A) \mapsto (f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,
\frac{\partial f^A}{\partial X_n}(\xb))\] so that 
\[
\Phi^{-1}(0)= W(\pi_i,V^A).
\]
\begin{proposition} 
0 is a regular value of $\Phi$.
\end{proposition}
\begin{proof}
Put
\[
G_0 = f(Ax), 
G_1 = \frac{\partial (f(Ax))}{\partial X_{i+1}},\hdots,G_{n-i} = \frac{\partial (f(Ax))}{\partial X_n},
\] 
and assume that $G_0(\xb,A)=G_1(\xb,A)=\hdots =G_{n-i}(\xb,A)=0.$ We can simplify by removing $Ax$ from the system because  
\[(f(Ax),(\grad(f)\cdot 
\bbm 
a_{i+1,1} \\
\vdots \\
a_{i+1,n} 
\ebm)(Ax),\hdots, 
(\grad(f)\cdot 
\bbm 
a_{n,1} \\
\vdots \\
a_{n,n} 
\ebm)(Ax)
\] 
defines a radical ideal of dimension ? whose variety is smooth if and only if 
\[(f,\grad(f)\cdot 
\bbm 
a_{i+1,1} \\
\vdots \\
a_{i+1,n} 
\ebm),\hdots, 
\grad(f)\cdot 
\bbm 
a_{n1} \\
\vdots \\
a_{nn} 
\ebm)
\]
defines a radical ideal of dimension ? whose variety is smooth. Now, let $g$ be the following:
%
%
\begin{align*}
    g: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
       (\xb,A) &\mapsto 
       \left(f(\xb),\grad(f(\xb))\cdot 
A_{i+1},\hdots, 
\grad(f(\xb))\cdot 
A_{n}
\right)
\end{align*}
%
%
I claim that for all $(\xb,A) \in g^{-1}(0),$ the Jacobian matrix of $g$ at $(\xb,A)$ has full rank $n-i+1$ (i.e. $g$ is transverse to $\{0\}).$ The Jacobian of 
\begin{align*}
       & \left(f,\grad(f)\cdot 
\bbm 
a_{i+1,1} \\
\vdots \\
a_{i+1,n} 
\ebm,\hdots, 
\grad(f)\cdot 
\bbm 
a_{n,1} \\
\vdots \\
a_{n,n} 
\ebm\right) \\
&= \left(f, \frac{\pa f}{\pa X_1} a_{i+1,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+1,n}, \hdots, \frac{\pa f}{\pa X_1} a_{n,1} + \hdots + \frac{\pa f}{\pa X_n}a_{n,n}\right) \\
&= (f,F_{1},\hdots,F_{n-i}),  
\end{align*} where 
\[
F_j = \frac{\pa f}{\pa X_1} a_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+j,n}, 1 \leq j \leq n-i,\]
is
\[
\left[ 
\begin{array}{cccccc}
\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
\frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
\ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
\frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
\end{array}
\right]. 
\] 
Since $f$ is square-free, \[I(V(f)) = \langle f \rangle,\]  and thus for all $\xb \in V(f)$, 
\[
T_{\xb} V(f) = \textrm{Nullspace}(\grad_{\xb} f).
\]
Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes. At least one partial of $f$ must be non-zero. Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i$ rows, the matrix has full rank $n-i$.

\end{proof}
Since $\deg \Phi \leq D,$ it follows by Theorem 4.2 that a hypersurface $\Delta \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta,$ then $0$ is a regular value of $\Phi_{A}$, which means that 
\[
\jac_\textit{\textbf{x}} \Phi_A 
= \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
\] has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). Therefore, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$, for each $i \in \{1,\hdots,n\}.$
%
%
%
%
%
%%%%%%% Proof of $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$
\section{Proof of $\textbf{H}_i^{'}(4),\textbf{H}_i^{'}(5)$ and $\textbf{H}_i^{'}(6)$}
%
\begin{theorem}
There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $D^{\textrm{?}}$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(4),\textbf{H}_i^{'}(5)$ and $\textbf{H}_i^{'}(6)$.
\end{theorem}
%
\subsection{Sketch of the proof of Theorem 7.1}
%
Let 
\[
Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
\]
where $b_i$ is the i-th row of $A^{-1}$. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
\[
Y_1(\xb),\hdots,Y_{i-1}(\xb), f(\xb),  \frac{\pa f(A\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(A\xb)}{\pa X_n}
\]
has full rank, at all points $\xb \in \C^n$ with 
\[
X_1(\xb)=\hdots,X_{i-1}(\xb)=f(\xb)= \frac{\pa f(xb)}{\pa X_{i+1}}=\hdots = \frac{\pa f(\xb)}{\pa X_{n}}=0.
\]
Then we could use Theorem 5.1 to obtain a hypersurface with the desired properties. Let $\Phi$ be the mapping 
\begin{align*}
    \Phi: \C^n \times \C^{n^2} &\rightarrow \C^{n+1} \\
           (\xb,A) &\mapsto 
       (Y_1,\hdots,Y_i,f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots \\
       \hdots&~,\grad(f(\xb))\cdot A_{n}\right)),
\end{align*}
We cannot directly define the appropriate polynomial mapping, as $Y_j(A\xb)$ is rational in $A^{-1}.$ To circumvent this issue, we can alternativly define a polynomial mapping $\Psi$ as  
\begin{align*}
    \Psi: \C^n \times \C^{n^2} \times \C &\rightarrow \C^{n+2} \\
           (\xb,A,T) &\mapsto 
       (\Yt_1,\hdots,\Yt_i,f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots \\
\hdots,\grad(f(\xb))\cdot A_{n}\right),&~T\cdot \det (A) - 1),
\end{align*}
where $\Yt_j=TY_j$ with denominators cleared. Now, look at the points in $\Psi^{-1}(0).$ Here, $\det A \not = 0$ and therefore invertible, and therefore at all points in $\Psi^{-1}(0)$ the Jacobian matrix has full rank? 
\begin{proposition}
For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank (i.e. $\Psi$ is transverse to $\{0\}).$
\end{proposition}
\begin{proof}

\end{proof}
Thus, by Theorem 5.1, there exists a hypersurface $\Delta_2 \subset \C^{n^2}$, of degree at most $D^{n+1}$ with the property that if $A \in \C^{n^2}-\Delta_2$ then $\jac_{\xb}\Psi_A$ has full rank. $\hdots$ It then follows that for all $A \in \C^{n^2}-\Delta_2, \jac_{\xb}\Phi_A$ also has full rank. Therefore, by the Jacobian criterion, $f^A$ satisfies  $\textbf{H}_i^{'}(4),\textbf{H}_i^{'}(5)$ and $\textbf{H}_i^{'}(6)$. 
%
%
%
%
%%%%%% Quantitative Noether Position
%
\section{Proof of $\textbf{H}_i^{'}(7)$}
%
Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To increase readability and simplify notation, we often do not specify $i$, as it is fixed.   
\subsection{Sketch of the proof}
Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth. For $i \in \{1,\hdots,n\}$, recall $\textbf{H}_i^{'}(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension  
\[
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
\]
injective and  integral.
%
%
%%%%% Theorem
%
\begin{theorem}
There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $D^{?}$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i^{'}(7)$.
\end{theorem}
%
%
%%%%% Proposition
%
\begin{proposition} 
The ring extension \[\mathbb{Q}(\frak{A})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textbf{X}]/\I^{\A}\] is integral.
\end{proposition}
%
\begin{proof}
Let $(\frak{P}_l)_{l \leq L}$ be the prime components of the radical ideal $\I^\A$. By \cite[Proposition 1]{EMP}, 
\[
\mathbb{Q}(\frak{A})[\textit{\textbf{X}}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textit{\textbf{X}}]/\fp_l^{\A}
\] 
is integral. Therefore polynomials $p_{l,j}\in\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ exist, monic in $T$, with $p_{l,j}(X_j)\in \frak{P}_l$ for each $j\in \{i,\hdots,n\}.$ Thence, 
\begin{align*}
&P_{j}(X_j) := \prod_l p_{l,j}(X_j)\in\I^\A, 
\end{align*}
for each $j \in \{i,\hdots,n\},$ and therefore 
\[
\mathbb{Q}(\frak{A})[\textit{\textbf{X}}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textit{\textbf{X}}]/\I^{\A}
\] 
is integral.
\end{proof}
%
%
Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 8.2. Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$
 we can write
\[
P_{j}(X_j) = a_j f^{\A} + \sum_{l=1}^{n-i}b_{j,l} \frac{\partial f^\A}{\partial X_{i+l}}, ~a_j,b_{j,l} \in \mathbb{Q}(\A)[\textbf{X}].
\]
For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $A \in \Gamma_j$,
then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$. Define 
\[
\Xi_j:=V(h_j), 
\]
where $h_j$ is the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$, so that when $A \not \in \Xi_j$ then $A$ cancels none of the denominators $a_{j}$ or $b_{j,l}$ which provide the integral dependence relation. For each $j$, we want a bound on the degree of $\Xi_j$. We can obtain bounds by applying an effective Nullstellensatz theorem. However, the theorem requires $P_{j}$ to be a polynomial. We can obtain a polynomial from $P_{j}$ by clearing denominators. We can multiply $P_{j}$ by $d_j \in \Q[\A_{i,j}]$ equal to the least common multiple of the denominators of $P_{j}.$ Put 
\[
\overline{P_{j}} := dP_{j}\in \Q[\A][\textit{\textbf{X}}],
\]
and note that $\pjb(X_j) \in \I^{\A}$ with 
\[
\pjb(X_j) = \ajb f^{\A} + \sum_{l=1}^{n-i}\bjb \frac{\partial f^\A}{\partial X_{i+l}}, ~\ajb,\bjb \in \mathbb{Q}[\A][\textbf{X}].
\]
\begin{proposition} 
$\deg \pjb\leq (D+1)^{n-i+1}.$ 
\end{proposition} 
\begin{proof}
Let $\Is \subset \Q[\A,\Xb]$ be the extension of $\I$ in  $\Q[\A,\Xb],$ and consider the finite field extension
\begin{align*}
    \Q(\A,\Xb_{i-1}) &\rightarrow \Q(\A,\Xb_{i-1})[X_i,\hdots,X_n]/\Is.
\end{align*}
%
As $\pjb$ is monic (it is not....), the minimal polynomial of the linear mapping defined by multiplication by $X_j$ in $\Q(\A,\Xb_{i-1})$ is equal to $\pjb$. It therefore follows by \cite[Proposition 1]{CGR} that
\begin{align*}
&\deg \pjb \leq (D+1)^{n-i+1}.&(2D)^{n-i+1}\textrm{?} 
\end{align*}
\end{proof}
Note that 
\[
\deg d \leq \deg \pjb \leq (D+1)^{n-i+1}.
\]
%
%
%
\subsection{Applying the effective Nullstellensatz}
We have
\[
\deg_{\Xb}\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}\leq D,
\]
\[
\deg_{\A}  
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\} \leq D,
\]
\[
\deg_{\Xb}(1-T\pjb) \leq \deg \pjb +1 \leq (D+1)^{n-i+1}+1
\]
and
\[
\deg_{\A}(1-T\pjb) \leq \deg \pjb\leq (D+1)^{n-i+1}.
\]
For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, there exists $\alpha_j \in \mathbb{Q}[\A]\setminus\{0\}$ with 
\begin{align*}
\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\textit{\textbf{X}},T)g_l + B_j(\textit{\textbf{X}},T)(1-\pjb T), \\ g_l \in 
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T]
\end{align*}
with the degree of $\alpha_j$ upper bounded by
\begin{align*}
    &\left(\prod_{l=1}^{n-i+1} \deg_{\Xb,T} g_l\right)\deg_{\A} (1-T\pjb)\\ 
    + ~~~~~&(n-i+1)\left(\deg_{\Xb,T}\pjb\right)\left(\prod_{l=1}^{n-i+1}\deg_{\Xb,T} g_l \right)\deg_{\A} g_l\\
    \leq ~~~~~&D^{n-i+1}\left( (D+1)^{n-i+1}\right)\\
    +~~~~~&(n-i+1)\left( (D+1)^{n-i+1}+1\right)D^{n-i+2}.
\end{align*}
Now substitute $T \leftarrow 1/\pjb$ so that 
\[
\alpha_i = \sum_{l=1}^{n-i+1} A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb)g_l + 0
\]
and 
\begin{align*}
A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb) &= \sum_{i=1}^{n_l} A_{l,i}(\A_{i,j},\Xb,1/\pjb)\\
&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_l}}\right)\At_{l,i}(\A_{i,j},\textit{\textbf{X}}), ~k_l \in \mathbb{Z}.
\end{align*}
Now let $k := \max\{k_l\}$ so that 
\begin{align*}
    \pjb^k \alpha &= \pjb^k\left(\sum_{l=1}^{n-i+1} A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb)g_l\right)\\
    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{k-k_{n_l}}\right)\At_l(\A_{i,j},\Xb) \right)g_l \in \Q[\A_{i,j}][\Xb],
\end{align*}
which shows that $\alpha$ is the only remaining denominator. We know that $\alpha$ is not zero, we know the leading coefficient of $\overline{P_j}$ is not zero, we have an upper bound for the degree of $\alpha$, and we know $\deg d \leq \deg P_j = (D+1)^{n-i+1}$, where $\pjb=dP_j.$ By making $\pjb$ monic, the integrality of 
\begin{align*}\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}]/\I_i^{\A}
\end{align*}
holds with $\pjb(X_j)\in \I_i^{\A}.$
%
\subsection{Proof of Theorem 5.1?}
%
There is a Zariski-open subset $\Gamma \subset \GL(n,\C)$ such that for $A \in \Gamma$, the entries of $A$ cancel none of the denominators of the coefficients of the generators of $\I(\pi_i,V^{A}).$ Thus, we set
\[
\Xi := \C^{n^2} - \Gamma = V(h),
\]
with $h \in \Q[\A_{i,j}]$ defined as the least common multiple of the denominators of the generators of $\I^\A.$ Since $\pjb^k \in \I^\A$ and since
\[
\pjb^k = \frac{1}{\alpha}\left( Q(\A_{i,j},\Xb) \right), Q \in \Q[\A_{i,j}][\Xb],
\]
it follows that 
\[
\deg \Xi = \deg h \leq \deg \alpha \leq D^{\frac{3}{2} n \ln n+1}.
\]
Furthermore, since $\pjb^k \in \I^\A,$ it follows from by proposition 5.2 that, if $A \in \C^{n^2} - \Xi$ then the extension  
\[
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}^\A
\]
is integral, and thus $V(\I^A)=W^\A$ is in Noether position for $\pi_{i-1}.$ Therefore, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i^{'}(4)$.
%
%
%
%
%
%%%%%% Proof of Theorem 3.1
%
\section{Proof of Theorem 3.1}
%
Assume that $f\in \Q[X_1,\hdots,X_n]$ satisfies $\textbf{H}.$
%
%
%
%%%%%% Bit-complexity
%
\section{Proof of Theorem 1.1}
%
%
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}
%%
\end{document}
\endinput
%%
%% End of file `sample-xelatex.tex'.

### 2020-01-31 main.tex
Improved code readability

@@
 The algorithm requires some genericity properties, which we ensure through random changes of variables that produce generic coordinate systems.
-In order to ensure these properties with arbitrarily high probability, we developed a new quantitative extension of Thom's weak transversality theorem, and a quantitative Noether normalization statement for polar varieties.
-These statements enable us to give a precise probability analysis of a modular algorithm, where the algorithm is monte carlo and we can guarantee correctness with arbitrarily high probability.
+In order to ensure these properties with arbitrarily high probability, we developed a new quantitative extension of Thom's weak transversality theorem, and a new quantitative Noether normalization statement for polar varieties.
+These statements enable us to give a precise probability analysis of a monte carlo algorithm, where we can guarantee correctness with arbitrarily high probability.
 \par
 Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{a,b,c,d}.
-However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work.
+However, these algorithms are based in the arithmetic complexity model, and bit complexity questions were left for future work.
 Our results therefore begin to fill a missing gap in the research.
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Real algebraic geometry, weak transversality, Noether position, bit complexity}
+\keywords{Real algebraic geometry, transversality, Noether normalization, bit complexity}
 %% A "teaser" image appears between the author and affiliation
@@
 %
-%%%%%% Introduction
-%
 \section{Introduction}
 %
-%
-%%%%%% Problem statement
-%
 \subsection{Problem statement}
+%
 Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
@@
 %
-%
-%
-%%%%%% Motivation
-%
 \subsection{Motivation}
+%
 \subsubsection{Applications}
+%
 Computing one point in each connected component of the real part of a hypersurface is a basic and important subroutine used in semi-algebraic geometry.
@@
 As bit complexity provides a far more realistic model of computation compared to arithmetic complexity,  which only counts each operation at unit cost, our results therefore begin to fill an important missing gap in the research.
-%Indeed, bit estimates provide more information for both time and space resources that are needed in practice.  
 \subsubsection{Quantitative genericity statements}
 %
-%
-%
-%%%%%% Main result
-%
 \subsection{Main result}
+%
 \begin{theorem}
@@
 %
-%%%%%% Notation and Preliminaries
-%
 \section{Notation and preliminaries}
 %
-%
-%%%%%% Algebraic Sets
-%
 \subsection{Algebraic sets}
+%
 An \textit{algebraic set} $V \subset \C^n$ is the set of common zeros of a set of polynomials $\textit{\textbf{f}}=(f_1,\hdots,f_s)$ in $\C[X_1,\hdots,X_n].$
@@
 The \textit{dimension} of an algebraic set $V \subset \C^n$, denoted $\dim V,$ can be defined in the following ways:
+%
 \begin{enumerate}
@@
 \end{enumerate}
+%
 The \textit{codimension} of $V$ is $n - \dim V$.
@@
 The \textit{degree} of an algebraic set is the number of intersection points between itself and $\dim V$ generic hyperplanes.
+%
 \begin{example} 
@@
 \end{example}
+%
 \begin{example}
@@
 %
-%
-%
-%%%%%% Bit-size, height and degree
-%
 \subsection{Bit-size, height and degree}
+%
 For $r \leq n,$ $\textit{\textbf{X}}_{\leq r}$ denotes $[X_1,\hdots,X_r]$ and $\textit{\textbf{X}}$ denotes $[X_1,\hdots,X_n]$. 
@@
 %
-%
-%%%%%% Data structures
 \subsection{Data structures}
+%
 \subsubsection{Strait-line programs}
+%
 \subsubsection{Zero-dimensional parameterizations}
 %
-%
-%
-%%%%%% Regular and singular points
-%
 \subsection{Critical / singular points}
+%
 \subsubsection{Regular and singular points of varieties}
+%
 Let $V \subset \C^n$ be a $d$-equidimensional algebraic set. 
@@
 We let $\reg(V)$ and $\sing(V)$ respectively denote the regular and singular points of $V$.
-%
 \par 
@@
 %
-%
-%
-%
-%
-%%%%%%%%%%%%%%%% Critical points of polynomial mappings
-%
 \subsubsection{Critical points of polynomial mappings}
+%
 Let $\phi : V \rightarrow \C^m$ be a polynomial mapping.
@@
 %
-%
-%%%%%% The zariski-tangent space
-%
 \subsection{The zariski-tangent space}
+%
 Denote by $\grad_{\xb}(f)$ the evaluation of the gradient vector of $f$ in $\C[X_1,\hdots,X_n]$ at $\textit{\textbf{x}}$ in $\C$.
@@
 For a polynomial system $\textit{\textbf{f}}=(f_1,\hdots,f_N)$ in $\C[X_1,\hdots,X_n]$, denote by $\jac(\textit{\textbf{f}})$ the Jacobian matrix.
-%and $\jac(\textit{\textbf{f}},i)$ the truncated Jacobian matrix
-%\[ 
-%\bbm 
-%\frac{\partial f_1}{\partial X_{i+1}} \hdots \frac{\partial f_1}{\partial X_n} \\
-%\frac{\partial f_N}{\partial X_{i+1}} \hdots \frac{\partial f_N}{\partial X_n}
-%\ebm,~\textrm{for }i \in \{1,\hdots,n-1\}.\]
 The following is a direct consequence of \cite[Corollary 16.20]{ECA}.
+%
 \begin{proposition}
@@
 \end{proposition}
-%
-%
-%%%%%% Polar Varieties
 %
@@
 %
-%
 \begin{proposition} 
@@
 \end{proposition}
+%
 \begin{proof}
@@
 %
-%
-%
-%
-%
-%%%%%% Changes of Variables
-%
 \subsection{Changes of variables}
+%
 Consider $A \in \C^{n^2}, f \in \C[X_1,\hdots,X_n], \textit{\textbf{x}} \in \mathbb{C}^n,$ and $V \subset \C^n$. We denote by 
@@
 %
-%%%%%% Main Algorithm 
 %
 \section{The Main Algorithm}
+%
 \begin{algorithm}
@@
 \nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
-\nl Use \cite{4} to compute the partial derivatives $\frac{\pa f^A}{\pr X_{i+1}},\hdots,\frac{\pa f^A}{\pr X_n}$\;
+\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\pr X_{i+1}},\hdots,\frac{\pa f^A}{\pr X_n}$\;
     \caption{{Main Algorithm} \label{}}
@@
 %
-%
-%
-%%%%%% Genericity Properties
-%
 \section{Genericity properties}
 %
-Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ squarefree with total degree $D$ and $V(f)$ smooth.
-We say that $V$ is in \textit{Noether position} for $\pi_D$ when the extension \[\C[X_1,\hdots,X_D] \rightarrow \C[X_1,\hdots,X_n]/I(V)\] is injective and integral.
-Then, for any $\xb \in \C^D,$ the fiber
+Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ squarefree with total degree $D$ and $V(f)$ smooth. We say that $V$ is in \textit{Noether position} for $\pi_D$ when the extension 
+\[
+\C[X_1,\hdots,X_D] \rightarrow \C[X_1,\hdots,X_n]/I(V)
+\] 
+is injective and integral.  Then, for any $\xb \in \C^D,$ the fiber 
 $V \cap \pi_D^{-1}(\xb)$ has dimension zero. 
 We say that $f$ satisfies $\textbf{H}$ if 
+%
 \begin{enumerate}
@@
 \end{enumerate}
+%
 For $i\in\{1,\hdots,n\}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
+%
 \begin{enumerate}
@@
 \end{theorem}
+%
 \begin{corollary} 
@@
 %
-%
-%%%%%% A Quantitative Extension of Thom's Weak Transversality
-%
 \section{Weak Transversality}
 Write more about transversality? Provide an example?
-%
 %
@@
 For $\vt$ in $\C^{\dt}$, let $\Phi_{\vt} : \C^n \rightarrow \C^{m}$ be the induced mapping $x\mapsto \Phi(x,\vt)$.
+%
 \begin{theorem} (Weak transversality)
@@
 %
-%
 \subsection{Genericity and Sard's lemma}
+%
 It will sometimes be useful for us to let the matrix $A$ represent new indeterminates: let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ It follows from Proposition 4.2 that for a generic $A \in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.
@@
 %
-%
 \subsection{Proof of Proposition 5.1}
@@
 The proof of \cite[Theorem B.3]{TWT} shows the existence of $\Delta.$ We extend the theorem by showing that the degree of $\Delta$ is upper bounded by $d^n.$ 
+%
 \subsubsection{More notation and setup}
+%
 Put $X = \Phi^{-1}(0)$ and consider the projection $\pi:(x, \vt) \in \C^n \times \C^{\dt} \mapsto \vt \in\C^{\dt}$.
@@
 $\Delta^{'}$. We then show that 
-\[\deg \Delta \leq \deg \Delta^{'} \leq d^n.
+\[
+\deg \Delta \leq \deg \Delta^{'} \leq d^n.
 \] 
@@
 \subsubsection{Explicitly characterizing $\Delta^{'}$.} 
+%
 We will use \cite[Lemma B.4]{NO}:
@@
 Let $M$ denote the matrix
-\begin{align*}M(\xb,\vt)&:= \jac_{(\xb,\vt)}(\Phi;X)\\
+%
+\begin{align*}
+M(\xb,\vt)&:= \jac_{(\xb,\vt)}(\Phi;X)\\
 &= 
@@
 \jac_{(\xb,\vt)}(\Phi)
-\ebm.\end{align*}
-%
+\ebm.
+\end{align*}
 %
@@
 By applying Lemma 4.3 we have
+%
 \begin{align*}
@@
 \end{align*}
+%
 Otherwise, if $(\xb,\vt)$ is not a regular point of $\pi|_X,$ then \[\dim \textrm{Im}(d\pi|_X(T_{\xb}X)) < \dt\]  and therefore $\rank ~M(\xb,\dt) < m+\dt.$ 
 \end{proof}
-%
 Therefore if $M(x,\vt)$ does not have full rank $\dt+m$ then $(x,\vt)$ is a critical point of $\pi|_X$.
@@
 Let $J$ denote the sub-matrix of the Jacobian of $\Phi$ consisting of the first $n$ columns:
- \[J := \jac_{(\xb,\vt)}(\Phi)[-;1,n].\]
+ \[
+ J := \jac_{(\xb,\vt)}(\Phi)[-;1,n].
+ \]
+%
 \begin{proposition} 
@@
 \end{proposition}
+%
 \begin{proof}
 Notice 
+%
 \begin{align*}
@@
 \end{align*}
+%
 The first $n$ columns of $M(\xb,\vt)$ must all be different from the remaining $\dt$ columns. Therefore $J(\xb,\vt)$ has full rank $\min\{n,m\}$ if and only if $M(\xb,\vt)$ has full rank $\dt+m.$
 \end{proof}
+%
 Therefore $\Delta^{'} = V(\textrm{minors of }J\textrm{ of order }\min\{m,n\}).$
 %
-%
-%
-%
 \subsubsection{Bounding the degree of $\Delta^{'}$.}
@@
 Denote by $\frak{Z}$ the algebraic set defined by the vanishing of $\mathscr{L}_1,\hdots,\mathscr{L}_{n},$ and consider the projection 
+%
 \begin{align*} 
@@
 \end{align*}
+%
 Denote by $\frak{Z}^{'}$ the algebraic set
@@
 \]
+%
 \begin{proposition}  
@@
 %
-%
 \begin{lemma} 
@@
 and
-\[\overline{\pi_{n+\dt}~(\overline{Z^o})} = \overline{\pi_{n+\dt}~(Z^o)}.\] 
+\[
+\overline{\pi_{n+\dt}~(\overline{Z^o})} = \overline{\pi_{n+\dt}~(Z^o)}.
+\] 
 \end{lemma} 
+%
 \begin{proof}
 There exists a Zariski open subset $Z^o \subset Z$ with 
-%
-\[\pi_{n+\dt}~(Z^{o}) \subset \D^{'}~(\textrm{why?}).\] 
-%
+\[
+\pi_{n+\dt}~(Z^{o}) \subset \D^{'}~(\textrm{why?}).
+\] 
 Since $Z^o \subset \overline{Z^o}$, we have $\pi_{n+\dt}~(Z^o) \subset \pi_{n+\dt}~(\overline{Z^o})$ and thus 
-\[\overline{\pi_{n+\dt}~(Z^o)} \subset \overline{\pi_{n+\dt}~(\overline{Z^o})}.
+\[
+\overline{\pi_{n+\dt}~(Z^o)} \subset \overline{\pi_{n+\dt}~(\overline{Z^o})}.
 \]   
@@
 so let 
-\[\overline{\pi_{n+\dt}~(\overline{Z^o})} = V(\mathscr{I}),
+\[
+\overline{\pi_{n+\dt}~(\overline{Z^o})} = V(\mathscr{I}),
 \] 
@@
 and  $\mathscr{I} \subset I(\overline{Z^o}) \cap \mathbb{Q}[\textit{\textbf{X}},\vt]$ (why?), and it then follows that 
+%
 \begin{align*}
@@
 \end{align*}
+%
 \end{proof}
 %
-%
 Now we prove Proposition 4.7.
+%
 \begin{proof}
@@
 Now let $Z$ be an irreducible component of $\Z^{'}.$ By Lemma 4.7 there exists a Zariski open subset $Z^o \subset Z$ with $\pi_{n+\dt}~(Z^{o}) \subset \D^{'}$, and
+%
 \begin{align*}
@@
 \end{align*}
+%
    Therefore $\Pi_{n+\dt}~(\Z^{'}) \subset \D^{'}.$
 \end{proof}
-%
 %
@@
 \end{proposition} 
+%
 \begin{proof}
@@
 Therefore 
+%
 \begin{align*}
@@
 \end{align*}
+%
 \end{proof}
@@
 %
+%
 \section{Proof of $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$}
-%
 %
@@
 \end{theorem}
+%
 \subsection{Sketch of the proof of Theorem 6.1}
+%
 We will let $\Phi$ be the mapping 
@@
 \]
+%
 \begin{proposition} 
@@
 and assume that $G_0(\xb,A)=G_1(\xb,A)=\hdots =G_{n-i}(\xb,A)=0.$ We can simplify by removing $Ax$ from the system because  
-\[(f(Ax),(\grad(f)\cdot 
+\[
+(f(Ax),(\grad(f)\cdot 
 \bbm 
@@
 defines a radical ideal of dimension ? whose variety is smooth if and only if 
-\[(f,\grad(f)\cdot 
+\[
+(f,\grad(f)\cdot 
 \bbm 
@@
 defines a radical ideal of dimension ? whose variety is smooth. Now, let $g$ be the following:
-%
 %
@@
 %
-%
 I claim that for all $(\xb,A) \in g^{-1}(0),$ the Jacobian matrix of $g$ at $(\xb,A)$ has full rank $n-i+1$ (i.e. $g$ is transverse to $\{0\}).$ The Jacobian of 
+%
 \begin{align*}
@@
 &= (f,F_{1},\hdots,F_{n-i}),  
-\end{align*} where 
+\end{align*} 
+%
+where 
 \[
@@
 Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i$ rows, the matrix has full rank $n-i$.
-
 \end{proof}
+%
 Since $\deg \Phi \leq D,$ it follows by Theorem 4.2 that a hypersurface $\Delta \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta,$ then $0$ is a regular value of $\Phi_{A}$, which means that
@@
 = \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
-\] has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
+\] 
+has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
 Therefore, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$, for each $i \in \{1,\hdots,n\}.$
@@
 %
-%
-%%%%%%% Proof of $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$
 \section{Proof of $\textbf{H}_i^{'}(4),\textbf{H}_i^{'}(5)$ and $\textbf{H}_i^{'}(6)$}
@@
 Then we could use Theorem 5.1 to obtain a hypersurface with the desired properties. Let $\Phi$ be the mapping 
+%
 \begin{align*}
@@
        (Y_1,\hdots,Y_i,f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots \\
-       \hdots&~,\grad(f(\xb))\cdot A_{n}\right)),
-\end{align*}
+       \hdots&~,\grad(f(\xb))\cdot A_{n})),
+\end{align*}
+%
 We cannot directly define the appropriate polynomial mapping, as $Y_j(A\xb)$ is rational in $A^{-1}.$ To circumvent this issue, we can alternativly define a polynomial mapping $\Psi$ as  
+%
 \begin{align*}
@@
        (\Yt_1,\hdots,\Yt_i,f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots \\
-\hdots,\grad(f(\xb))\cdot A_{n}\right),&~T\cdot \det (A) - 1),
-\end{align*}
+\hdots,\grad(f(\xb))\cdot A_{n}),&~T\cdot \det (A) - 1),
+\end{align*}
+%
 where $\Yt_j=TY_j$ with denominators cleared.
 Now, look at the points in $\Psi^{-1}(0).$ Here, $\det A \not = 0$ and therefore invertible, and therefore at all points in $\Psi^{-1}(0)$ the Jacobian matrix has full rank?
+%
 \begin{proposition}
@@
 \end{proposition}
+%
 \begin{proof}
-
 \end{proof}
+%
 Thus, by Theorem 5.1, there exists a hypersurface $\Delta_2 \subset \C^{n^2}$, of degree at most $D^{n+1}$ with the property that if $A \in \C^{n^2}-\Delta_2$ then $\jac_{\xb}\Psi_A$ has full rank.
@@
 %
-%
-%%%%%% Quantitative Noether Position
 %
@@
 %
-%
-%%%%% Theorem
-%
 \begin{theorem}
@@
 %
-%
-%%%%% Proposition
-%
 \begin{proposition} 
@@
 is integral. Therefore polynomials $p_{l,j}\in\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ exist, monic in $T$, with $p_{l,j}(X_j)\in \frak{P}_l$ for each $j\in \{i,\hdots,n\}.$ Thence, 
+%
 \begin{align*}
@@
 \end{align*}
+%
 for each $j \in \{i,\hdots,n\},$ and therefore 
@@
 \end{proof}
-%
 %
@@
 \end{proposition} 
+%
 \begin{proof}
 Let $\Is \subset \Q[\A,\Xb]$ be the extension of $\I$ in  $\Q[\A,\Xb],$ and consider the finite field extension
+%
 \begin{align*}
@@
 It therefore follows by \cite[Proposition 1]{CGR} that
+%
 \begin{align*}
@@
 \end{align*}
+%
 \end{proof}
+%
 Note that 
@@
 %
+%
 \subsection{Applying the effective Nullstellensatz}
+%
 We have
@@
 For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, there exists $\alpha_j \in \mathbb{Q}[\A]\setminus\{0\}$ with 
+%
 \begin{align*}
@@
 \end{align*}
+%
 with the degree of $\alpha_j$ upper bounded by
+%
 \begin{align*}
@@
 \end{align*}
+%
 Now substitute $T \leftarrow 1/\pjb$ so that 
@@
 and
+%
 \begin{align*}
@@
 \end{align*}
+%
 Now let $k := \max\{k_l\}$ so that 
+%
 \begin{align*}
@@
 \end{align*}
+%
 which shows that $\alpha$ is the only remaining denominator.
@@
 %
-%
-%%%%%% Proof of Theorem 3.1
-%
 \section{Proof of Theorem 3.1}
@@
 %
-%%%%%% Bit-complexity
 %
@@
 %
+
 %%

### 2020-02-01 main.tex
Minor edits

@@
 
+\usepackage{mathrsfs}
 % new commands and shortcuts
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Bit Complexity for Computation of one Point in each Connected Component of a Smooth Real Hypersurface}
+%\title{Bit Complexity for Computation of one Point in each Connected
+%Component of a Smooth Real Hypersurface}
+\title{On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface}
 
@@
 \begin{abstract}
-We provide bit complexity estimates for the computation of at least one point in each connected component of a smooth real hypersurface.
-This problem is a basic and important subroutine used in semi-algebraic geometry.
-For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface.
-The algorithm requires some genericity properties, which we ensure through random changes of variables that produce generic coordinate systems.
-In order to ensure these properties with arbitrarily high probability, we developed a new quantitative extension of Thom's weak transversality theorem, and a new quantitative Noether normalization statement for polar varieties.
-These statements enable us to give a precise probability analysis of a monte carlo algorithm, where we can guarantee correctness with arbitrarily high probability.
-\par
-Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{a,b,c,d}.
-However, these algorithms are based in the arithmetic complexity model, and bit complexity questions were left for future work.
-Our results therefore begin to fill a missing gap in the research.
-%Furthermore, as bit complexity provides a far more realistic model of computation compared to arithmetic complexity, which only counts each operation at unit cost whereas bit complexity provide more information for both time and space resources that are needed in practice, it is important that this missing gap is filled.
-%As bit complexity provides a far more realistic model of computation compared to arithmetic complexity, which only counts each operation at unit cost, our contribution is necessary and important.
-Indeed, bit estimates provide more information for both time and space resources that are needed in practice.
+  We present a full analysis of an efficient algorithm for the
+  computation of at least one point in each connected component of a
+  smooth real hypersurface, taking into account bit complexity and
+  all coefficient growth.  This problem is a basic and important
+  subroutine used in semi-algebraic geometry. For instance, it is used
+  in determining an upper bound on the number of connected components
+  of a real hypersurface. The algorithm requires some genericity
+  properties, which we ensure through random changes of variables that
+  produce generic coordinate systems. In order to ensure these
+  properties with arbitrarily high probability, we developed a new
+  quantitative extension of Thom's weak transversality theorem, and a
+  new quantitative Noether normalization statement for polar
+  varieties. These statements enable us to give a precise probability
+  analysis of a monte carlo algorithm, where we can guarantee
+  correctness with arbitrarily high probability.
+
+  Algorithms for deciding connectivity queries in real algebraic
+  geometry have been developed in a series of papers
+  \cite{a,b,c,d}. However, these algorithms are based in the
+  arithmetic complexity model, and analyses of the bit complexity
+  questions were left for future work.  Our results are an important
+  first step in this analysis.
+
+  % Furthermore, as bit complexity provides a far more realistic model
+  % of computation compared to arithmetic complexity, which only
+  % counts each operation at unit cost whereas bit complexity provide
+  % more information for both time and space resources that are needed
+  % in practice, it is important that this missing gap is filled.
+  % As bit complexity provides a far more realistic model of
+  % computation compared to arithmetic complexity, which only counts
+  % each operation at unit cost, our contribution is necessary and
+  % important. Indeed, bit estimates provide more information for both
+  % time and space resources that are needed in practice.
 \end{abstract}
@@
 \nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
-\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\pr X_{i+1}},\hdots,\frac{\pa f^A}{\pr X_n}$\;
+\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\Pr X_{i+1}},\hdots,\frac{\pa f^A}{\Pr X_n}$\;
     \caption{{Main Algorithm} \label{}}
@@
 %% End of file `sample-xelatex.tex'.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2020-02-01 main.tex
Update main.tex
Updates from Overleaf

@@
 %% allowing the author to define a "short title" to be used in page headers.
-%\title{Bit Complexity for Computation of one Point in each Connected
-%Component of a Smooth Real Hypersurface}
-\title{On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface}
+\title{Bit Complexity for Computation of one Point in each Connected Component of a Smooth Real Hypersurface}
 
@@
 correctness with arbitrarily high probability.
-
+\par 
   Algorithms for deciding connectivity queries in real algebraic
@@
   first step in this analysis.
-
-  % Furthermore, as bit complexity provides a far more realistic model
-  % of computation compared to arithmetic complexity, which only
-  % counts each operation at unit cost whereas bit complexity provide
-  % more information for both time and space resources that are needed
-  % in practice, it is important that this missing gap is filled.
-  % As bit complexity provides a far more realistic model of
-  % computation compared to arithmetic complexity, which only counts
-  % each operation at unit cost, our contribution is necessary and
-  % important. Indeed, bit estimates provide more information for both
-  % time and space resources that are needed in practice.
 \end{abstract}
@@
 \nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
-\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\Pr X_{i+1}},\hdots,\frac{\pa f^A}{\Pr X_n}$\;
+\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
     \caption{{Main Algorithm} \label{}}
@@
 %
-Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To increase readability and simplify notation, we often do not specify $i$, as it is fixed.
+Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To simplify notation, we will let $i \in \{1,\hdots,\}$ be fixed, and we wil avoid writing $i$ where the context is clear.
+%
 \subsection{Sketch of the proof}
 Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
-For $i \in \{1,\hdots,n\}$, recall $\textbf{H}_i^{'}(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
+Recall $\textbf{H}_i^{'}(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
 \[
@@
 %
+Section 8 is devoted to proving Theorem 8.1.
+The majority of work is in upper bounding the degree of $\Delta_3,$ as in \cite{EMP} it was shown that $f^A$ satisfies $\textbf{H}_i^{'}$ for a generic change of variables $A\in\C^{n^2}.$
+%
 \begin{proposition} 
@@
 For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $A \in \Gamma_j$,
-then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$. Define 
-\[
-\Xi_j:=V(h_j), 
-\]
-where $h_j$ is the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$, so that when $A \not \in \Xi_j$ then $A$ cancels none of the denominators $a_{j}$ or $b_{j,l}$ which provide the integral dependence relation.
-For each $j$, we want a bound on the degree of $\Xi_j$.
-We can obtain bounds by applying an effective Nullstellensatz theorem.
+then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$.
+Define $h_j \in \Q[\A]$ to be the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$.
+Hence, if $A \not \in V(h_j)$ then $A$ cancels none of the denominators $a_{j}$ or $b_{j,l}$ which are providing the integral dependence relation.
+Define
+\[
+\Xi_i := V(h_i,\hdots,h_n).
+\]
+For each $j \in \{i,\hdots,n\}$, we want a bound on the degree of $h_j$.
+Then by applying Bezout's theorem we can obtain a bound on the degrees of $\Xi_i$.
+We can obtain bounds for $h_j$ by applying an effective Nullstellensatz theorem.
 However, the theorem requires $P_{j}$ to be a polynomial.
@@
 \[
-\overline{P_{j}} := dP_{j}\in \Q[\A][\textit{\textbf{X}}],
+\overline{P_{j}} := d_jP_{j}\in \Q[\A][\textit{\textbf{X}}],
 \]
@@
 \begin{proposition} 
-$\deg \pjb\leq (D+1)^{n-i+1}.$ 
+$\deg \pjb\leq (D+1)^{n-i+1}.$ (The same for all $j$?)
 \end{proposition} 
@@
 \[
-\deg d \leq \deg \pjb \leq (D+1)^{n-i+1}.
-\]
-%
-%
-%
+\deg d_j \leq \deg \pjb \leq (D+1)^{n-i+1}.
+\]
 %
@@
 \[
-\alpha_i = \sum_{l=1}^{n-i+1} A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb)g_l + 0
+\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},1/\pjb)g_l + 0
 \]
@@
 \begin{align*}
-A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb) &= \sum_{i=1}^{n_l} A_{l,i}(\A_{i,j},\Xb,1/\pjb)\\
-&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_l}}\right)\At_{l,i}(\A_{i,j},\textit{\textbf{X}}), ~k_l \in \mathbb{Z}.
-\end{align*}
-%
-Now let $k := \max\{k_l\}$ so that 
-%
-\begin{align*}
-    \pjb^k \alpha &= \pjb^k\left(\sum_{l=1}^{n-i+1} A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb)g_l\right)\\
-    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{k-k_{n_l}}\right)\At_l(\A_{i,j},\Xb) \right)g_l \in \Q[\A_{i,j}][\Xb],
-\end{align*}
-%
-which shows that $\alpha$ is the only remaining denominator.
-We know that $\alpha$ is not zero, we know the leading coefficient of $\overline{P_j}$ is not zero, we have an upper bound for the degree of $\alpha$, and we know $\deg d \leq \deg P_j = (D+1)^{n-i+1}$, where $\pjb=dP_j.$ By making $\pjb$ monic, the integrality of
-\begin{align*}\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}]/\I_i^{\A}
-\end{align*}
-holds with $\pjb(X_j)\in \I_i^{\A}.$
+A_{j,l}(\A,\textit{\textbf{X}},1/\pjb) 
+&= \sum_{i=1}^{n_l} A(\A,\Xb,1/\pjb)\\
+&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_l}}\right)\At_{j,l,i}(\A,\textit{\textbf{X}}), ~k_l \in \mathbb{Z}.
+\end{align*}
+%
+Now let $K := \max\{k_l\}$ so that 
+%
+\begin{align*}
+    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},1/\pjb)g_l\right)\\
+    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{n_l}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb],
+\end{align*}
+%
+which shows that $\alpha_j$ is the only remaining denominator (i.e.\ the only denominators are $d_j$ and $\alpha_j$).
+We know that $\alpha_j$ is not zero, we know the leading coefficient of $\overline{P_j}$ is $d_j$ which is not zero, we have an upper bound for the degrees of $\alpha_j$, and we know $\deg d \leq \deg P_j = (D+1)^{n-i+1}$, where $\pjb=d_jP_j.$ By making $\pjb$ monic (this is just $P_j$?), the integrality of
+%
+\begin{align*}
+\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}]/\I^{\A}
+\end{align*}
+%
+holds with $\pjb(X_j)\in \I^{\A}.$
 %
@@
 %% End of file `sample-xelatex.tex'.
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2020-02-01 main.tex
Update main.tex
Updated Section 8: Proof of H'_i(7), quantitative Noether Normalization 
- I still do not understand (fully) how to apply Cayley H. However, I think I have everything else done in this section.

@@
 
+% test 
 \usepackage{mathrsfs}
@@
   correctness with arbitrarily high probability.
-\par 
+
   Algorithms for deciding connectivity queries in real algebraic
@@
   first step in this analysis.
+
 \end{abstract}
@@
 %
-Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To simplify notation, we will let $i \in \{1,\hdots,\}$ be fixed, and we wil avoid writing $i$ where the context is clear.
+Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, to simplify notation, let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore, throughout this section, consider that $i \in \{1,\hdots,n\}$ is fixed.
+We will avoid writing $i$ where the context is clear.
 %
 \subsection{Sketch of the proof}
-Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
-Recall $\textbf{H}_i^{'}(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
-\[
-\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
+%
+Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ have total degree $D$.
+Assume $f$ satisfies \textbf{H}, so that $f$ is squarefree with $V(f)$ smooth.
+Recall $\textbf{H}_i^{'}(7):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
+\[
+\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
 \]
@@
 Section 8 is devoted to proving Theorem 8.1.
-The majority of work is in upper bounding the degree of $\Delta_3,$ as in \cite{EMP} it was shown that $f^A$ satisfies $\textbf{H}_i^{'}$ for a generic change of variables $A\in\C^{n^2}.$
+It has already been shown in \cite{EMP} that $f^A$ satisfies $\textbf{H}_i^{'}$ for a generic change of variables.
+The new contribution is in upper bounding the degree of $\Delta_3.$
 %
@@
 Define $h_j \in \Q[\A]$ to be the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$.
-Hence, if $A \not \in V(h_j)$ then $A$ cancels none of the denominators $a_{j}$ or $b_{j,l}$ which are providing the integral dependence relation.
-Define
-\[
-\Xi_i := V(h_i,\hdots,h_n).
-\]
-For each $j \in \{i,\hdots,n\}$, we want a bound on the degree of $h_j$.
-Then by applying Bezout's theorem we can obtain a bound on the degrees of $\Xi_i$.
+Hence, if $A \in \Q^{n^2}-V(h_j)$ then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l},$ which are providing the integral dependence relation.
+Now we define
+\[
+\Xi_i := V(h_i,\hdots,h_n), 
+\]
+and we obtain a bound on the degree of $\Xi_i$ by applying Bezout's theorem. Hence, if $A\in \Q^{n^2}-\Xi_i$ then
+\[
+P_j(X_j) \in \I^A,  
+\]
+for each $j \in \{i,\hdots,n\},$ and therefore the extension 
+\[
+\mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{A})
+\]
+is integral.
 We can obtain bounds for $h_j$ by applying an effective Nullstellensatz theorem.
@@
 We can obtain a polynomial from $P_{j}$ by clearing denominators.
-We can multiply $P_{j}$ by $d_j \in \Q[\A_{i,j}]$ equal to the least common multiple of the denominators of $P_{j}.$ Put
+We can multiply $P_{j}$ by the least common multiple of its denominators, which we will denote by $d_j \in \Q[\A_{i,j}]$.
+Put
 \[
@@
 \begin{proposition} 
-$\deg \pjb\leq (D+1)^{n-i+1}.$ (The same for all $j$?)
+$\deg \pjb\leq (D+1)^{n-i+1}.$ 
 \end{proposition} 
@@
 \begin{proof}
-Let $\Is \subset \Q[\A,\Xb]$ be the extension of $\I$ in  $\Q[\A,\Xb],$ and consider the finite field extension
+\textbf{Eric and Mark}: I am unsure of how to do this part correctly, so I will assume 
+\[
+\deg \pjb\leq \Dt_j.
+\]
+Let $\Is \subset \Q[\A,\Xb]$ be the extension of $\I^{\A}$ in  $\Q[\A,\Xb],$ and consider the finite field extension
 %
@@
 %
-As $\pjb$ is monic (it is not....), the minimal polynomial of the linear mapping defined by multiplication by $X_j$ in $\Q(\A,\Xb_{i-1})$ is equal to $\pjb$.
+The minimal polynomial of the linear mapping defined by multiplication by $X_j$ in $\Q(\A,\Xb_{i-1})$ is \textbf{almost}(?) equal to $\pjb$ (the leading coefficient of $\pjb$ is $d_j$).
 It therefore follows by \cite[Proposition 1]{CGR} that
@@
 \[
-\deg d_j \leq \deg \pjb \leq (D+1)^{n-i+1}.
+\deg d_j \leq \deg \pjb \leq \Dt_j.
 \]
@@
 %
-We have
+To apply the effective Nullstellensatz theorem, we first need to determine degree bounds, separately in $\Xb$ and $\A,$ of the polynomials in the membership relationship. We have
 \[
@@
 \[
-\deg_{\Xb}(1-T\pjb) \leq \deg \pjb +1 \leq (D+1)^{n-i+1}+1
+\deg_{\Xb,T}(1-T\pjb) \leq \Dt_j +1 
 \]
@@
 \[
-\deg_{\A}(1-T\pjb) \leq \deg \pjb\leq (D+1)^{n-i+1}.
+\deg_{\A}(1-T\pjb) \leq \Dt_j.
 \]
@@
 \begin{align*}
-\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\textit{\textbf{X}},T)g_l + B_j(\textit{\textbf{X}},T)(1-\pjb T), \\ g_l \in 
+\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},T)g_l + B_j(\A,\textit{\textbf{X}},T)(1-\pjb T), \\ g_l \in 
 \left\{ 
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T]
-\end{align*}
-%
-with the degree of $\alpha_j$ upper bounded by
-%
-\begin{align*}
-    &\left(\prod_{l=1}^{n-i+1} \deg_{\Xb,T} g_l\right)\deg_{\A} (1-T\pjb)\\ 
-    + ~~~~~&(n-i+1)\left(\deg_{\Xb,T}\pjb\right)\left(\prod_{l=1}^{n-i+1}\deg_{\Xb,T} g_l \right)\deg_{\A} g_l\\
-    \leq ~~~~~&D^{n-i+1}\left( (D+1)^{n-i+1}\right)\\
-    +~~~~~&(n-i+1)\left( (D+1)^{n-i+1}+1\right)D^{n-i+2}.
-\end{align*}
-%
-Now substitute $T \leftarrow 1/\pjb$ so that 
+\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T],
+\end{align*}
+%
+and with the degree of $\alpha_j$ upper bounded by
+%
+\begin{align*}
+    &\left(\prod_{k=1}^{n-i+1} D\right)\Dt_j 
+    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}D \right)D\\
+    = &\left(D^{n-i+1}\right)\Dt_j+
+    (n-i+1)\left(\Dt_j+1\right)\left(D^{n-i+1} \right)\\
+    &\leq D^{n}\Dt_j + n\left(\Dt_j+1\right)D^{n}\\
+    &=D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+\end{align*}
+%
+Now we will show that $\alpha_j$ is the only remaining denominator whose degree we need to bound. Substitute $T \leftarrow 1/\pjb$ so that 
 \[
@@
 A_{j,l}(\A,\textit{\textbf{X}},1/\pjb) 
-&= \sum_{i=1}^{n_l} A(\A,\Xb,1/\pjb)\\
-&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_l}}\right)\At_{j,l,i}(\A,\textit{\textbf{X}}), ~k_l \in \mathbb{Z}.
-\end{align*}
-%
-Now let $K := \max\{k_l\}$ so that 
+&= \sum_{i=1}^{n_l} A_{j,l,i}(\A,\Xb,1/\pjb)\\
+&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\textit{\textbf{X}}), ~k_i \in \mathbb{Z}.
+\end{align*}
+%
+Let $K := \max\{k_l\}$ so that 
 %
@@
     \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},1/\pjb)g_l\right)\\
-    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{n_l}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb],
-\end{align*}
-%
-which shows that $\alpha_j$ is the only remaining denominator (i.e.\ the only denominators are $d_j$ and $\alpha_j$).
-We know that $\alpha_j$ is not zero, we know the leading coefficient of $\overline{P_j}$ is $d_j$ which is not zero, we have an upper bound for the degrees of $\alpha_j$, and we know $\deg d \leq \deg P_j = (D+1)^{n-i+1}$, where $\pjb=d_jP_j.$ By making $\pjb$ monic (this is just $P_j$?), the integrality of
-%
-\begin{align*}
-\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}]/\I^{\A}
-\end{align*}
-%
-holds with $\pjb(X_j)\in \I^{\A}.$
-%
-\subsection{Proof of Theorem 5.1?}
-%
-There is a Zariski-open subset $\Gamma \subset \GL(n,\C)$ such that for $A \in \Gamma$, the entries of $A$ cancel none of the denominators of the coefficients of the generators of $\I(\pi_i,V^{A}).$ Thus, we set
-\[
-\Xi := \C^{n^2} - \Gamma = V(h),
-\]
-with $h \in \Q[\A_{i,j}]$ defined as the least common multiple of the denominators of the generators of $\I^\A.$ Since $\pjb^k \in \I^\A$ and since
-\[
-\pjb^k = \frac{1}{\alpha}\left( Q(\A_{i,j},\Xb) \right), Q \in \Q[\A_{i,j}][\Xb],
-\]
-it follows that 
-\[
-\deg \Xi = \deg h \leq \deg \alpha \leq D^{\frac{3}{2} n \ln n+1}.
-\]
-Furthermore, since $\pjb^k \in \I^\A,$ it follows from by proposition 5.2 that, if $A \in \C^{n^2} - \Xi$ then the extension  
-\[
-\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}^\A
-\]
-is integral, and thus $V(\I^A)=W^\A$ is in Noether position for $\pi_{i-1}.$ Therefore, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i^{'}(4)$.
+    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{i}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb].
+\end{align*}
+%
+which shows that $\alpha_j$ is the only remaining denominator whose degree we need to bound other than $d_j$. Note as well that
+\[
+\pjb^K \in \I^{\A}.
+\]
+Therefore 
+%
+\begin{align*}
+\deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
+    &\leq \left(D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
+    &=D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+\end{align*}
+%
+\subsection{Proof of Theorem 8.1}
+%
+We can apply B\'ezout and obtain
+%
+\begin{align*}
+    \deg \Xi_i = \deg V(h_i,\hdots,h_n)
+    &\leq \prod_{j=i}^n \deg h_j\\
+    &\leq  \prod_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
+    &=  \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n-i+1}\\
+    &\leq  \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n}.
+\end{align*}
+%
+And therefore, by another application of B\'ezout, 
+%
+\begin{align*}
+    \deg& \Delta_3 \leq \prod_{i=1}^n \deg \Xi_i\\
+    &\leq \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n^2},
+    &(=D^{O(n^3 \log n)}\textrm{?})
+\end{align*}
+%
+where if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in \{1,\hdots,n\},$ the extension 
+\[
+\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
+\]
+is integral.
 %

### 2020-02-02 main.tex
Thom

--- 2020-02-01 main.tex
@@
 
+% test 
 \usepackage{mathrsfs}
+\usepackage{bm}
 % new commands and shortcuts
+\def\td{{\bf todo}}
 \def\bs{\textit{\textbf{s}}}
@@
 \def\Xb{\textit{\textbf{X}}}
+\def\Lambdab{\bm{\Lambda}}
+\def\Thetab{\bm{\Theta}}
+\def\thetab{\bm{\vartheta}}
 \def\xb{\textit{\textbf{x}}}
@@
 \def\Yt{\widetilde{Y}}
-\def\dt{\widetilde{d}}
+\def\dt{s}
+%% \def\dt{\widetilde{d}}
 \def\Dt{\widetilde{D}}
@@
 
-  % Furthermore, as bit complexity provides a far more realistic model
-  % of computation compared to arithmetic complexity, which only
-  % counts each operation at unit cost whereas bit complexity provide
-  % more information for both time and space resources that are needed
-  % in practice, it is important that this missing gap is filled.
-  % As bit complexity provides a far more realistic model of
-  % computation compared to arithmetic complexity, which only counts
-  % each operation at unit cost, our contribution is necessary and
-  % important. Indeed, bit estimates provide more information for both
-  % time and space resources that are needed in practice.
 \end{abstract}
@@
 \section{Weak Transversality}
-Write more about transversality? Provide an example?
-%
-\subsection{Extending Thom's weak transversality}
-%
-We prove a quantitative extension of Thom's weak transversality \cite{TWT} specialized to the particular case of transversality to a point, which can be rephrased entirely in terms of critical / regular values.
-\par 
-Denote by $\Phi :\C^n \times \C^{\dt} ~ \rightarrow \C^{m}$
-a polynomial mapping, where $n,\dt,$ and $m$ are positive integers (assume $m \leq n$?).
-Assume the total degree of $\Phi$ is bounded by an integer $d$.
-For $\vt$ in $\C^{\dt}$, let $\Phi_{\vt} : \C^n \rightarrow \C^{m}$ be the induced mapping $x\mapsto \Phi(x,\vt)$.
-%
-\begin{theorem} (Weak transversality)
-Suppose that $0$ is a regular value of $\Phi$.
-Then there exists a hypersurface $\Delta \subset \C^{\dt}$ of degree at most $d^n$ for which, if $\vt \in \C^{\dt}-\Delta$ then $0$ is a regular value of $\Phi_{\vt}$.
-\end{theorem}
-%
-\subsection{Genericity and Sard's lemma}
-%
-It will sometimes be useful for us to let the matrix $A$ represent new indeterminates: let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ It follows from Proposition 4.2 that for a generic $A \in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.
-The proof of \cite[Theorem B.3]{NO}, which shows the existence of $\Delta \subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the critical values of a polynomial mapping are contained in a hypersurface.
-It follows from Sard's lemma that for the matrix of indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise it could not be that $0$ is a regular value of $\Phi_A,$ for a generic $A\in \C^{n^2}.$ Therefore,
-\[
-\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(x),\frac{\pa f^{\A}(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(x)}{\pa X_n}\right)
-\]
-has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$. We will rely on this fact in Section 5. 
-%
-\subsection{Proof of Proposition 5.1}
-% 
-The proof of \cite[Theorem B.3]{TWT} shows the existence of $\Delta.$ We extend the theorem by showing that the degree of $\Delta$ is upper bounded by $d^n.$ 
-%
-\subsubsection{More notation and setup}
-%
-Put $X = \Phi^{-1}(0)$ and consider the projection $\pi:(x, \vt) \in \C^n \times \C^{\dt} \mapsto \vt \in\C^{\dt}$.
-The proof of \cite[Theorem B.3]{NO} also shows that $X$ is $(n+ \dt -m)$-equidimensional, and that if $\vt \in \C^{\dt}$
-is such that $0$ is a critical value of $\Phi_{\vt}$, then $\vt$ is a critical value of the restriction of $\pi$ to $X.$ We show that the critical points of $\pi|_X$ are contained in an algebraic set
-$\Delta^{'}$. We then show that 
-\[
-\deg \Delta \leq \deg \Delta^{'} \leq d^n.
-\] 
-%
-\subsubsection{Explicitly characterizing $\Delta^{'}$.} 
-%
-We will use \cite[Lemma B.4]{NO}:
-\begin{lemma}
-Let $A=\bbm A_1 \\ A_2 \ebm$ be a matrix. Then, 
-\[ 
-\textup{rank}(A) = 
-\textup{rank}(A_1) + \textup{rank}(A_2|\ker(A_1)),
-\]
-where $A_2|\ker(A_1)$ is the restriction of the linear map defined by $A_2$ to the kernel of $A_1$. 
-\end{lemma}
-Let $M$ denote the matrix
-%
-\begin{align*}
-M(\xb,\vt)&:= \jac_{(\xb,\vt)}(\Phi;X)\\
-&= 
+
+Sard's lemma states that the set of critical values of a smooth
+function $\R^n \to \R^m$ has measure zero. One can give ``algebraic''
+versions of it, for semi-algebraic mappings $\R^n \to \R^m$ as
+in~\cite[Chapter~9]{bochnak1998real} or polynomial mappings $\C^n \to
+\C^m$ as in~\cite[Chapter~3]{Mumford76}, for which the sets of critical
+values are contained in strict semi-algebraic, resp.\ algebraic sets
+in the codomain. Thom's weak transversality lemma, as given for
+instance in~\cite{demazure2000bifurcations}, generalizes Sard's
+lemma. In this section, we consider a particular case of this result
+(transversality to a point), and establish a quantitative version of
+it. Our presentation is inspired by that in~\cite{TWT}.
+
+%% ; it states that if a smooth function
+%% $F(\Xb,\Lambda)$, depending on parameters $\Lamdba$ in $\C^s$ is
+%% ``transverse'' to a certain submanifold in its domain space, then for
+%% most values $\lambda \in \C^s$, $F(\Xb,\lambda)$ remains
+
+Transversality to a point can be rephrased entirely in terms of
+critical and regular values. Recall that if $\bm \Psi$ is a mapping
+from a smooth algebraic set $Y$ to $\C^t$, with $t\le \dim(Y)$, a {\em
+  critical point} of $\bm \Psi$ is a point $\bm y \in Y$ such that the
+image of the tangent space $T_{\bm y} Y$ by the differential $d_{\bm
+  Y} \bm \Psi$ has dimension less than $t$. When for instance
+$Y=\C^v$, we have $T_{\bm y} Y=\C^v$ and this condition is equivalent
+to the Jacobian of $\bm \Psi$ having rank less than $t$ at $\bm y$.  A
+{\em regular point} of $\bm \Psi$ is a point on $Y$ that is not
+critical. {\em Critical values} are the images of critical points; the
+complement of this set are the {\em regular values} (so a regular
+value is not necessarily in the image of $\bm\Psi$).
+
+Let $n,\dt,$ and $m$ be positive integers, with $m \le n$, and denote
+by $\bm\Phi :\C^n \times \C^{\dt} ~ \rightarrow \C^{m}$ a mapping
+defined by polynomials in $\C[\Xb,\Thetab]$, where $\Xb$,
+resp.\ $\Thetab$, is a set of $n$, resp.\ $\dt$, indeterminates.  For
+$\thetab$ in $\C^{\dt}$, let $\bm\Phi_{\thetab} : \C^n \rightarrow
+\C^{m}$ be the induced mapping $\xb\mapsto \bm\Phi(\xb,\thetab)$.  The
+transversality result we will need is the following.
+
+\begin{proposition} [Weak transversality]\label{prop:weak_t}
+  Suppose that $\bm 0$ is a regular value of $\bm\Phi$. Then there
+  exists a hypersurface $\Delta \subset \C^{\dt}$ of degree at most
+  \td for which, if $\thetab \in \C^{\dt}-\Delta$, then $\bm 0$ is a
+  regular value of~$\bm\Phi_{\thetab}$.
+\end{proposition}
+
+Here is a simple example that shows this result at work. Consider a
+squarefree $f$ in $\C[X_1,X_2]$, such that $V(f)$ is a smooth curve in
+$\C^2$, and let the mapping $\bm\Phi:\C^2\times \C \to \C^2$ be defined
+by $\bm\Phi(X_1,X_2,\Lambda) = (f(X_1,X_2), X_1-\Lambda)$. One checks
+that the Jacobian of $\bm\Phi$ with respect to $(X_1,X_2,\Lambda)$ has
+rank two at any point in $\bm\Phi^{-1}(\bm 0)$, so the assumptions of the
+proposition apply. We deduce that for a generic $\lambda$ in $\C$,
+that is, for all $\lambda$ in $\C$ except a finite number, the ideal
+$(f(X_1,X_2), X_1-\lambda)$ is radical in $\C[X_1,X_2]$; equivalently,
+$f(\lambda, X_2)$ is squarefree. We will revisit this example in
+Section~\td.
+
+The rest of the section is devoted to the proof of the proposition.
+The proof of \cite[Theorem B.3]{TWT} already shows the existence of
+$\Delta$; it is essentially the classical proof for smooth
+mappings~\cite[Section~3.7]{demazure2000bifurcations}, written in an
+algebraic context. In what follows, we revisit this proof,
+establishing a bound on the degree of $\Delta$.
+
+We will reuse the following fact proved in~\cite{TWT}.  Put $V =
+\bm\Phi^{-1}(0)$ and consider the projection $\pi:(\xb, \thetab) \in
+\C^n \times \C^{\dt} \mapsto \thetab \in\C^{\dt}$.  If $V$ is empty,
+there is nothing to do, since all values $\thetab$ in $\C^\dt$ satisfy
+the conclusion of the theorem. Thus, we assume that $V$ is not
+empty. Then, the Jacobian criterion shows that $V$ is
+smooth and $(n+ \dt -m)$-equidimensional.
+
+Let $Z$ be the set of critical points of $\pi_{|V}$, and consider its
+projection $\pi(Z)$ in $\C^s$. This is the set of critical values of
+$\pi_{|V}$; hence, by the algebraic form of Sard's lemma (see
+\cite[Theorem~3.7]{Mumford76} for irreducible $V$
+and~\cite[Proposition~B.2]{TWT} for general $V$), its Zariski closure
+$\overline{\pi(Z)}$ is a strict closed subset of $\C^s$. Now, the
+proof of \cite[Theorem B.3]{TWT} shows that if $\thetab \in \C^{\dt}$
+is not in $\overline{\pi(Z)}$, then $\bm 0$ is a critical value of
+$\bm\Phi_{\thetab}$. Hence, it suffices to prove that $Z$ has degree
+at most $d^{m+n}$; this will imply the same degree bound for
+$\overline{\pi(Z)}$, and prove our propositon.
+
+We first describe the set $Z$ of critical points of $\pi_{|V}$.  Let
+$M$ denote the $(s+m) \times (s+n)$ matrix with entries in
+$\C[\Xb,\Thetab]$ given by $M = \jac_{\Xb,\Thetab}(\pi,\bm\Phi)$, that
+is,
+\begin{align*}
+M &= 
 \bbm 
-\jac_{(\xb,\vt)}(\pi)\\
-\jac_{(\xb,\vt)}(\Phi) 
+\jac_{\Xb,\Thetab}(\pi)\\
+\jac_{\Xb,\Thetab}(\bm\Phi) 
 \ebm 
@@
 \textbf{0}_{\dt \times n}\hspace{5mm}\textbf{I}_{\dt} \\
-\jac_{(\xb,\vt)}(\Phi)
+\jac_{(\Xb,\Thetab)}(\bm\Phi)
 \ebm.
 \end{align*}
-%
-\begin{proposition} 
-$M(\xb,\vt)$ has full rank $m+\dt$ if and only if $(\xb,\vt)$ is a regular point on $\pi|_X.$ 
-\end{proposition}
-%
+
+\begin{lemma} 
+  For $(\xb,\thetab)$ in $V$, the matrix $M$ has full rank $\dt+m$ at
+  $(\xb,\thetab)$ if and only if $(\xb,\thetab)$ is a regular point of
+  $\pi_{|V}.$
+\end{lemma}
 \begin{proof}
-The dimension of the source $\pi|_X$ is $\dim X = n + \dt - m.$ The dimension of the target space is $\dim \C^{\dt} = \dt.$ Now, if $(\xb,\vt)$ is a regular point of $\pi|_{X}$ then $\dim \textrm{Im}(d\pi|_X(T_{\xb}X)) = \dt$.
-When $\xb$ is regular on $X$, by Proposition 2.3, $\jac_{(\xb,\vt)} (\Phi) = T_{(\xb,\vt)}X$ and has full $\rk n + \dt - \dim X = n + \dt - (n + \dt - m) = m$.
-By applying Lemma 4.3 we have
-%
-\begin{align*}
-\rank ~M(\xb,\vartheta) &= 
-\rank ~
-\bbm 
-\jac_{(\xb,\vartheta)}(\pi|_X)\\
-\jac_{(\xb,\vartheta)}(\Phi) 
-\ebm \\
-&= \rank~ \jac_{(\xb,\vartheta)}(\pi|_X) + \rank ~\jac_{(\xb,\vartheta)}(\Phi)|_{T_{(x,\vartheta)}X} \\
-&= m + \dim \textrm{Im}(d\pi|_{\Xb}(T_xX)) \\
-&= m + \dt 
-\end{align*}
-%
-Otherwise, if $(\xb,\vt)$ is not a regular point of $\pi|_X,$ then \[\dim \textrm{Im}(d\pi|_X(T_{\xb}X)) < \dt\]  and therefore $\rank ~M(\xb,\dt) < m+\dt.$ 
+  Take $(\xb,\thetab)$ on $V$, and let $K(\xb,\thetab)$ be the
+  Jacobian matrix $\jac_{(\Xb,\Thetab)}(\bm\Phi)$ at $(\xb,\thetab)$.
+  Then, the rank of $M(\xb,\thetab)$ can be written as
+  $\textup{rank}(K(\xb,\thetab)) + \textup{rank}([\textbf{0}_{\dt
+      \times n}~\textbf{I}_{\dt}] \mid \ker K(\xb,\thetab))$, where
+  the latter is the rank of the restriction of $[\textbf{0}_{\dt
+      \times n}~\textbf{I}_{\dt}]$ to the nullspace of
+  $K(\xb,\thetab)$.
+
+  Since $V$ is smooth, $K(\xb,\thetab)$ has full rank ${\rm codim} (V)
+  = m$. On the other hand, the nullspace of $K(\xb,\thetab)$ is the
+  tangent space $T_{\xb,\thetab} V$, and
+  $\textup{rank}([\textbf{0}_{\dt \times n}~\textbf{I}_{\dt}] \mid
+  \ker K(\xb,\thetab))$ is the dimension of $\pi(T_{\xb,\thetab} V)$.
+  In other words, the rank of $M(\xb,\thetab)$ is equal to
+  $m+\dim(\pi(T_{\xb,\thetab} V))$; this implies the claim in the lemma.
 \end{proof}
-Therefore if $M(x,\vt)$ does not have full rank $\dt+m$ then $(x,\vt)$ is a critical point of $\pi|_X$.
-Since the minors of order $\dt+m$ vanish when $(x,\vt)$ is a critical point, the algebraic set defined by the vanishing of the minors of $M$ of order $\dt + m$ describe the critical points:
-\[
-\Delta^{'} = V(\textrm{minors of }M\textrm{ of order }\dt + m).
-\]
-Furthermore, we can characterize $\Delta^{'}$ with fewer equations by discarding those that evaluate to zero.
-Indeed, the first $\dt$ rows of $M(x,\vt)$ is the Jacobian matrix of the projection mapping $\pi|_X,$ which consists of a sub-matrix of zeros followed by an identity sub-matrix.
-Hence, we can discard several minors that evaluate to zero.
-Let $J$ denote the sub-matrix of the Jacobian of $\Phi$ consisting of the first $n$ columns:
- \[
- J := \jac_{(\xb,\vt)}(\Phi)[-;1,n].
- \]
-%
-\begin{proposition} 
-$J(\xb,\vt)$ has full rank $\min\{m,n\}$ if and only if $M(\xb,\vt)$ has full rank $\dt+m.$ 
-\end{proposition}
-%
+
+Therefore, we can characterize the set $Z$ of critical points of
+$\pi_{|V}$ as those points satisfying $\bm\Phi(\xb,\thetab)=\bm 0$ and
+where all minors of $M$ of order $\dt+m$ vanish. We can describe this
+set using fewer equations, by discarding certain minors that are
+identically zero. Let indeed $J$ denote the $m \times n$ submatrix of
+the Jacobian of $\bm\Phi$ consisting of the first $n$ columns.
+\begin{lemma} 
+  For $(\xb,\thetab)$ in $V$, $(\xb,\thetab)$ is in $Z$ if and only if
+  $J(\xb,\thetab)$ has rank less than $m$.
+\end{lemma}
 \begin{proof}
@@
 \begin{align*}
-M(\xb,\vt)&= 
-\bbm 
-\jac_{(\xb,\vt)}(\pi)\\
-\jac_{(\xb,\vt)}(\Phi) 
-\ebm \\
-&=
-\bbm 
-\textbf{0}_{\dt \times n}\hspace{5mm}\textbf{I}_{\dt} \\
-\jac_{(\xb,\vt)}(\Phi)
-\ebm\\
-&=
+M(\xb,\thetab)&= 
 \bbm 
 \textbf{0}_{\dt \times n} &\textbf{I}_{\dt} \\
-J(\xb,\vt)     &\jac_{(\xb,\vt)}(\Phi)[-;n+1,\dt]
-\ebm.
-\end{align*}
-%
-The first $n$ columns of $M(\xb,\vt)$ must all be different from the remaining $\dt$ columns. Therefore $J(\xb,\vt)$ has full rank $\min\{n,m\}$ if and only if $M(\xb,\vt)$ has full rank $\dt+m.$
+J(\xb,\thetab)     &J'(\xb,\thetab)
+\ebm,
+\end{align*}
+where $J'$ consists of the remaining columns of the Jacobian matrix of
+$\bm\Phi$.  Then, the rank of the former matrix is equal to the rank
+of
+\begin{align*}
+M(\xb,\thetab)&= 
+\bbm 
+\textbf{0}_{\dt \times n} &\textbf{I}_{\dt} \\
+J(\xb,\thetab)     & \bm 0_{m \times s}
+\ebm,
+\end{align*}
+and the conclusion follows.
 \end{proof}
-%
-Therefore $\Delta^{'} = V(\textrm{minors of }J\textrm{ of order }\min\{m,n\}).$
-%
-\subsubsection{Bounding the degree of $\Delta^{'}$.}
-% 
-Let $\textit{\textbf{L}}=[L_1,\hdots,L_m]$ be Lagrange multipliers, and consider the Lagrange system 
-\[
-\textit{\textbf{L}}\cdot J(x,A)=[\mathscr{L}_1,\hdots,\mathscr{L}_{n}]=[0,\hdots,0].
-\] 
-Denote by $\frak{Z}$ the algebraic set defined by the vanishing of $\mathscr{L}_1,\hdots,\mathscr{L}_{n},$ and consider the projection 
-%
-\begin{align*} 
-\pi_{n+\dt} :~ \C^{n+\dt+m} &\rightarrow \C^{n+\dt}\\
-(\textit{\textbf{x}},\vt,\textit{\textbf{L}})~ &\mapsto (\textit{\textbf{x}},\vt).
-\end{align*}
-%
-Denote by $\frak{Z}^{'}$ the algebraic set
-\[
-\frak{Z}^{'} := \overline{\frak{Z} - \{(\textit{\textbf{x}},\vt,0,\hdots,0) \in \C^{n+\dt+m}~|~(\textit{\textbf{x}},\vt,0\hdots,0) \in \frak{Z}\}}.
-\]
-%
-\begin{proposition}  
-The projection $\pi_{n+\dt}$ on $\frak{Z}^{'}$ is equal to $\Delta^{'}$.
-\end{proposition}
-%
-We will use the following lemma to prove Proposition 4.6.
-%
+Therefore, the set $Z$ can be defined as the set of all
+$(\xb,\thetab)$ in $\C^{n+\dt}$ satisfying $\bm\Phi(\xb,\thetab)=\bm
+0$ and where all minors of $J$ of order $m$ vanish. Our next step is
+to bound the degree of $Z$. For this, rather than considering minors
+of $J$, we will rewrite the condition that $J(\xb,\thetab)$ has rank
+less than $m$ as the existence of a non-trivial left kernel element.
+
+For this, we let $\textit{\textbf{L}}=[L_1,\hdots,L_m]$ be new
+variables, thought of as Lagrange multipliers, and consider the
+``Lagrange polynomials'' $\mathscr{L}_1,\dots,\mathscr{L}_{n}$, with
+\[
+[\mathscr{L}_1 \cdots \mathscr{L}_{n}]=\textit{\textbf{L}}\cdot J(\xb,\thetab).
+\] 
+Denote by $\frak{Z} \subset \C^{n+\dt+m}$ the algebraic set defined by
+the vanishing of $\mathscr{L}_1,\hdots,\mathscr{L}_{n},$ and
+$\bm\Psi$, and by $\frak{Z}'$ the algebraic set
+\[
+\frak{Z}' := \overline{\frak{Z} - \{(\textit{\textbf{x}},\thetab,0,\hdots,0) \in \C^{n+\dt+m}~|~(\textit{\textbf{x}},\thetab,0\hdots,0) \in \frak{Z}\}},
+\]
+where the bar denotes Zariski closure (we have to remove such points,
+since $L_1=\cdots=L_m=0$ is always a trivial solution to the Lagrange
+equations). Finally, consider the projection
+\begin{align*} 
+\mu :~ \C^{n+\dt+m} &\rightarrow \C^{n+\dt}\\
+(\textit{\textbf{x}},\thetab,\bm \ell)~ &\mapsto (\textit{\textbf{x}},\thetab).
+\end{align*}
+
 \begin{lemma}  
-For an irreducible component $Z$ of $\Z^{'},$ there exists a Zariski open subset $Z^o \subset Z$ with \[\pi_{n+\dt}~(Z^{o}) \subset \D^{'}~(\textrm{why?})\]
-and
-\[
-\overline{\pi_{n+\dt}~(\overline{Z^o})} = \overline{\pi_{n+\dt}~(Z^o)}.
-\] 
+  The algebraic set $Z$ is equal to the projection $\mu(\frak{Z}')$.
 \end{lemma}
-%
 \begin{proof}
-There exists a Zariski open subset $Z^o \subset Z$ with 
-\[
-\pi_{n+\dt}~(Z^{o}) \subset \D^{'}~(\textrm{why?}).
-\] 
-Since $Z^o \subset \overline{Z^o}$, we have $\pi_{n+\dt}~(Z^o) \subset \pi_{n+\dt}~(\overline{Z^o})$ and thus 
-\[
-\overline{\pi_{n+\dt}~(Z^o)} \subset \overline{\pi_{n+\dt}~(\overline{Z^o})}.
-\]   
-Since closed sets are by definition varieties in the Zariski topology, \[\overline{\pi_{n+\dt}~(\overline{Z^o})} = V\left( I(\overline{Z^o}) \cap \mathbb{C}[\textit{\textbf{X}},\vt]\right),
-\] 
-so let 
-\[
-\overline{\pi_{n+\dt}~(\overline{Z^o})} = V(\mathscr{I}),
-\] 
-for some ideal $\mathscr{I} \subset \C[\Xb,\vt].$ Take $f$ in $\mathscr{I}$ so that $f$ vanishes on 
-\[
-\overline{\pi_{n+\dt}~(Z^o)}\subset \overline{\pi_{n+\dt}~(\overline{Z^o})}
-\]
-Then $f$ must also vanish on the subset 
-\[
-\pi_{n+\dt}~(Z^o)\subset \overline{\pi_{n+\dt}~(Z^o)}\subset \overline{\pi_{n+\dt}~(\overline{Z^o})}
-\]
-and $Z^o,$ and hence also on $\overline{Z^o}.$ Therefore, 
-\[
-f \in I(\overline{Z^o}) \cap \mathbb{}[\textit{\textbf{X}},\vt]
-\]
-and  $\mathscr{I} \subset I(\overline{Z^o}) \cap \mathbb{Q}[\textit{\textbf{X}},\vt]$ (why?), and it then follows that 
-%
-\begin{align*}
-\overline{\pi_{n+\dt}~(\overline{Z^o})}&=V\left(I(\overline{Z^o})\cap \mathbb{C}[\textit{\textbf{X}},\vt]\right) \\&\subset V(\mathscr{I})\\&\subset \overline{\pi_{n + \dt}~(Z^o)}\textrm{ (why?)}.
-\end{align*}
-%
+  Take $(\xb,\thetab)$ in $Z$. Then, $(\xb,\thetab)$ cancels all
+  polynomials $\bm \Phi$, and there exists $\bm
+  \ell=(\ell_1,\dots,\ell_m)$, not identically zero, such that
+  $(\xb,\thetab,\bm \ell)$ cancels the Lagrange polynomials. This
+  implies that $(\xb,\thetab,\bm \ell)$ is in $\frak{Z} -
+  \{(\textit{\textbf{x}}',\thetab',0,\hdots,0) \in
+  \C^{n+\dt+m}~|~(\textit{\textbf{x}}',\thetab',0\hdots,0) \in
+  \frak{Z}\}$, and thus in $\frak{Z}'$. This proves the inclusion
+  $Z \subset \mu(\frak{Z}')$.
+
+  Conversely, take an irreducible component $Y$ of $\frak Z'$. We prove 
+  that $\mu(Y)$ is contained in $Z$.
+  By construction, there exists an open dense subset $Y^o \subset Y$
+  such that for any $(\xb,\thetab,\bm \ell)$ in $Y^o$, $\bm \ell$ is
+  not identically zero. As a result, $(\xb,\thetab)$ is in $Z$, that
+  is, $\mu(Y^o)$ is in $Z$. This implies that its Zariski closure
+  $\overline{\mu(Y^o)}$ is in $Z$. Since $\mu(Y)$ is contained in
+  $\overline{\mu(Y^o)}$, we have $\mu(Y) \subset Z$. Taking 
+  the union over all $Y$, we get $\mu(\frak Z') \subset Z$, as claimed.
 \end{proof}
 %
-Now we prove Proposition 4.7.
-%
+\begin{corollary} 
+  The degree of $Z$ is at most $d^{m+n}.$
+\end{corollary}
 \begin{proof}
-For all $(\textit{\textbf{x}},\vt) \in \D^{'}, $ there exists $\textit{\textbf{L}}^{'} \not = (0,\hdots,0)$ with $(\textit{\textbf{x}},\vt,\textit{\textbf{L}}^{'}) \in \Z.$ Thus, $(\textit{\textbf{x}},\vt,\textit{\textbf{L}}^{'})$ is in
-\[
-     \Z - \left\{(x,\vt,0,\hdots,0) \in \C^{n+\dt+m}~|~(x,\vt,0\hdots,0) \in \Z\right\}, 
-\]
-which implies that $(x,\vt,\textit{\textbf{L}}^{'}) \in \Z^{'}$, which then in turn implies that
-\[
-    (x,\vt) \in \Pi_{n + \dt}~(\Z^{'}).
-\]
-Therefore $\D^{'} \subset \pi_{n+\dt}~(\Z^{'}).$
-\newline \indent 
-Now let $Z$ be an irreducible component of $\Z^{'}.$ By Lemma 4.7 there exists a Zariski open subset $Z^o \subset Z$ with $\pi_{n+\dt}~(Z^{o}) \subset \D^{'}$, and
-%
-\begin{align*}
- \Pi_{n+\dt}~(Z) = 
-  \Pi_{n+\dt}~(\overline{Z^o})
-  &\subset 
-  \overline{\pi_{n+\dt}~(\overline{Z^o})}\\
-  &=
-  \overline{\Pi_{n+\dt}~(Z^o)}, &\textrm{by Lemma 4.7,}\\
-  &\subset \overline{\D^{'}}=\D^{'}.
-\end{align*}
-%
-   Therefore $\Pi_{n+\dt}~(\Z^{'}) \subset \D^{'}.$
+  The algebraic set $\frak Z$ is defined by $m+n$ equations, all of
+  them having degree at most $d$. It follows from B\'ezout's
+  Theorem~\cite{H} that $\deg(\frak{Z}) \leq d^{m+n}$, and the same
+  upper bound holds for $\deg(\frak{Z}')$. Applying the projection
+  $\mu$ yields the result.
 \end{proof}
-%
-\begin{proposition} 
-The degree of $\D^{'}$ is at most $d^n.$
-\end{proposition} 
-%
-\begin{proof}
-It follows from B\'ezout's Theorem that 
-\[
-\deg \frak{Z} \leq (d-1+1)^n=d^n.
-\]
-From \cite[Lemma 2]{H} we have 
-\[
-\deg(\pi_{n+\dt}(\Z^{'})) \leq \deg(\Z^{'}).
-\]
-Therefore 
-%
-\begin{align*}
-\deg(\D^{'}) &= \deg(\pi_{n+\dt}~(\Z^{'})),&\textrm{by Proposition 4.6,}\\ 
-            &\leq \deg(\Z^{'}),\\ 
-            &\leq \deg(\Z), &\textrm{by ?,}\\ 
-            &\leq d^n.
-\end{align*}
-%
-\end{proof}
-%
-%
-%
-%
-\section{Proof of $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$}
+
+\subsection{Genericity and Sard's lemma}
+%
+It will sometimes be useful for us to let the matrix $A$ represent new
+indeterminates: let $\A$ be an $n \times n$ matrix of new
+indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in
+\mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and
+$V^\A=V(f^\A).$ It follows from Proposition 4.2 that for a generic $A
+\in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.  The proof of
+\cite[Theorem B.3]{NO}, which shows the existence of $\Delta \subset
+\C^{n^2},$ applies \textit{Sard's lemma}, which shows that the
+critical values of a polynomial mapping are contained in a
+hypersurface. It follows from Sard's lemma that for the matrix of
+indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise
+it could not be that $0$ is a regular value of $\Phi_A,$ for a generic
+$A\in \C^{n^2}.$ Therefore,
+\[
+\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(x),\frac{\pa f^{\A}(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(x)}{\pa X_n}\right)
+\]
+has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$. We will rely on this fact in Section 5. 
+%
+\section{Proof of $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$}
 %
@@
 Thus, by Proposition 2.4,  $W(\pi_i,V(f))$ is defined by the vanishing of \[\fb := \left(f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right).\]
-If the Jacobian of $\fb$ has full rank at all $x \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion [4, Theorem 16.19] that $f$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+If the Jacobian of $\fb$ has full rank at all $x \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion [4, Theorem 16.19] that $f$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
 %
 \begin{theorem}
-There exists a Zariski closed set $\Delta \subset \C^{n^2}$ of degree at most $D^n$ with the property that, if $A \in \C^{n^2} - \Delta$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+There exists a Zariski closed set $\Delta \subset \C^{n^2}$ of degree at most $D^n$ with the property that, if $A \in \C^{n^2} - \Delta$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
 \end{theorem}
@@
 \]
-has full rank for all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+has full rank for all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
 \subsection{Proof of Theorem 6.1}
@@
 has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
-Therefore, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$, for each $i \in \{1,\hdots,n\}.$
-%
-%
-%
-%
-\section{Proof of $\textbf{H}_i^{'}(4),\textbf{H}_i^{'}(5)$ and $\textbf{H}_i^{'}(6)$}
+Therefore, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$, for each $i \in \{1,\hdots,n\}.$
+%
+%
+%
+%
+\section{Proof of $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$}
 %
 \begin{theorem}
-There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $D^{\textrm{?}}$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(4),\textbf{H}_i^{'}(5)$ and $\textbf{H}_i^{'}(6)$.
+There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $D^{\textrm{?}}$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
 \end{theorem}
@@
 $\hdots$ It then follows that for all $A \in \C^{n^2}-\Delta_2, \jac_{\xb}\Phi_A$ also has full rank.
-Therefore, by the Jacobian criterion, $f^A$ satisfies  $\textbf{H}_i^{'}(4),\textbf{H}_i^{'}(5)$ and $\textbf{H}_i^{'}(6)$.
-%
-%
-%
-%
-\section{Proof of $\textbf{H}_i^{'}(7)$}
-%
-Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To increase readability and simplify notation, we often do not specify $i$, as it is fixed.
+Therefore, by the Jacobian criterion, $f^A$ satisfies  $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
+%
+%
+%
+%
+\section{Proof of $\textbf{H}_i'(7)$}
+%
+Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2),$ and $\textbf{H}_i'(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To increase readability and simplify notation, we often do not specify $i$, as it is fixed.
 \subsection{Sketch of the proof}
 Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
-For $i \in \{1,\hdots,n\}$, recall $\textbf{H}_i^{'}(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
+For $i \in \{1,\hdots,n\}$, recall $\textbf{H}_i'(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
 \[
@@
 \begin{theorem}
-There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $D^{?}$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i^{'}(7)$.
+There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $D^{?}$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(7)$.
 \end{theorem}
@@
 \]
-is integral, and thus $V(\I^A)=W^\A$ is in Noether position for $\pi_{i-1}.$ Therefore, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i^{'}(4)$.
+is integral, and thus $V(\I^A)=W^\A$ is in Noether position for $\pi_{i-1}.$ Therefore, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(4)$.
 %

### 2020-02-02 main.tex

@@
 %
-Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2),$ and $\textbf{H}_i'(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To increase readability and simplify notation, we often do not specify $i$, as it is fixed.
+%% <<<<<<< HEAD
+%% Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2),$ and $\textbf{H}_i'(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To increase readability and simplify notation, we often do not specify $i$, as it is fixed.
+%% \subsection{Sketch of the proof}
+%% Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
+For $i \in \{1,\hdots,n\}$, recall $\textbf{H}_i'(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
+%% =======
+Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, to simplify notation, let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore, throughout this section, consider that $i \in \{1,\hdots,n\}$ is fixed.
+We will avoid writing $i$ where the context is clear.
+%
 \subsection{Sketch of the proof}
-Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
-For $i \in \{1,\hdots,n\}$, recall $\textbf{H}_i'(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
-\[
-\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
+%
+Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ have total degree $D$.
+Assume $f$ satisfies \textbf{H}, so that $f$ is squarefree with $V(f)$ smooth.
+Recall $\textbf{H}_i^{'}(7):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
+%% >>>>>>> f9eb2445ca6e153d1e49c3d2767097d331dbcbee
+\[
+\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
 \]
@@
 %
+Section 8 is devoted to proving Theorem 8.1.
+It has already been shown in \cite{EMP} that $f^A$ satisfies $\textbf{H}_i^{'}$ for a generic change of variables.
+The new contribution is in upper bounding the degree of $\Delta_3.$
+%
 \begin{proposition} 
@@
 For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $A \in \Gamma_j$,
-then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$. Define 
-\[
-\Xi_j:=V(h_j), 
-\]
-where $h_j$ is the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$, so that when $A \not \in \Xi_j$ then $A$ cancels none of the denominators $a_{j}$ or $b_{j,l}$ which provide the integral dependence relation.
-For each $j$, we want a bound on the degree of $\Xi_j$.
-We can obtain bounds by applying an effective Nullstellensatz theorem.
+then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$.
+Define $h_j \in \Q[\A]$ to be the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$.
+Hence, if $A \in \Q^{n^2}-V(h_j)$ then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l},$ which are providing the integral dependence relation.
+Now we define
+\[
+\Xi_i := V(h_i,\hdots,h_n), 
+\]
+and we obtain a bound on the degree of $\Xi_i$ by applying Bezout's theorem. Hence, if $A\in \Q^{n^2}-\Xi_i$ then
+\[
+P_j(X_j) \in \I^A,  
+\]
+for each $j \in \{i,\hdots,n\},$ and therefore the extension 
+\[
+\mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{A})
+\]
+is integral.
+We can obtain bounds for $h_j$ by applying an effective Nullstellensatz theorem.
 However, the theorem requires $P_{j}$ to be a polynomial.
 We can obtain a polynomial from $P_{j}$ by clearing denominators.
-We can multiply $P_{j}$ by $d_j \in \Q[\A_{i,j}]$ equal to the least common multiple of the denominators of $P_{j}.$ Put
-\[
-\overline{P_{j}} := dP_{j}\in \Q[\A][\textit{\textbf{X}}],
+We can multiply $P_{j}$ by the least common multiple of its denominators, which we will denote by $d_j \in \Q[\A_{i,j}]$.
+Put
+\[
+\overline{P_{j}} := d_jP_{j}\in \Q[\A][\textit{\textbf{X}}],
 \]
@@
 \[
-\deg d \leq \deg \pjb \leq (D+1)^{n-i+1}.
-\]
-%
-%
-%
+\deg d_j \leq \deg \pjb \leq \Dt_j.
+\]
 %
@@
 \begin{align*}
-\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\textit{\textbf{X}},T)g_l + B_j(\textit{\textbf{X}},T)(1-\pjb T), \\ g_l \in 
+\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},T)g_l + B_j(\A,\textit{\textbf{X}},T)(1-\pjb T), \\ g_l \in 
 \left\{ 
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T]
-\end{align*}
-%
-with the degree of $\alpha_j$ upper bounded by
-%
-\begin{align*}
-    &\left(\prod_{l=1}^{n-i+1} \deg_{\Xb,T} g_l\right)\deg_{\A} (1-T\pjb)\\ 
-    + ~~~~~&(n-i+1)\left(\deg_{\Xb,T}\pjb\right)\left(\prod_{l=1}^{n-i+1}\deg_{\Xb,T} g_l \right)\deg_{\A} g_l\\
-    \leq ~~~~~&D^{n-i+1}\left( (D+1)^{n-i+1}\right)\\
-    +~~~~~&(n-i+1)\left( (D+1)^{n-i+1}+1\right)D^{n-i+2}.
-\end{align*}
-%
-Now substitute $T \leftarrow 1/\pjb$ so that 
-\[
-\alpha_i = \sum_{l=1}^{n-i+1} A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb)g_l + 0
+\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T],
+\end{align*}
+%
+and with the degree of $\alpha_j$ upper bounded by
+%
+\begin{align*}
+    &\left(\prod_{k=1}^{n-i+1} D\right)\Dt_j 
+    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}D \right)D\\
+    = &\left(D^{n-i+1}\right)\Dt_j+
+    (n-i+1)\left(\Dt_j+1\right)\left(D^{n-i+1} \right)\\
+    &\leq D^{n}\Dt_j + n\left(\Dt_j+1\right)D^{n}\\
+    &=D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+\end{align*}
+%
+Now we will show that $\alpha_j$ is the only remaining denominator whose degree we need to bound. Substitute $T \leftarrow 1/\pjb$ so that 
+\[
+\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},1/\pjb)g_l + 0
 \]
@@
 \begin{align*}
-A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb) &= \sum_{i=1}^{n_l} A_{l,i}(\A_{i,j},\Xb,1/\pjb)\\
-&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_l}}\right)\At_{l,i}(\A_{i,j},\textit{\textbf{X}}), ~k_l \in \mathbb{Z}.
-\end{align*}
-%
-Now let $k := \max\{k_l\}$ so that 
-%
-\begin{align*}
-    \pjb^k \alpha &= \pjb^k\left(\sum_{l=1}^{n-i+1} A_l(\A_{i,j},\textit{\textbf{X}},1/\pjb)g_l\right)\\
-    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{k-k_{n_l}}\right)\At_l(\A_{i,j},\Xb) \right)g_l \in \Q[\A_{i,j}][\Xb],
-\end{align*}
-%
-which shows that $\alpha$ is the only remaining denominator.
-We know that $\alpha$ is not zero, we know the leading coefficient of $\overline{P_j}$ is not zero, we have an upper bound for the degree of $\alpha$, and we know $\deg d \leq \deg P_j = (D+1)^{n-i+1}$, where $\pjb=dP_j.$ By making $\pjb$ monic, the integrality of
-\begin{align*}\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A}_{i,j})[\textbf{X}]/\I_i^{\A}
-\end{align*}
-holds with $\pjb(X_j)\in \I_i^{\A}.$
-%
-\subsection{Proof of Theorem 5.1?}
-%
-There is a Zariski-open subset $\Gamma \subset \GL(n,\C)$ such that for $A \in \Gamma$, the entries of $A$ cancel none of the denominators of the coefficients of the generators of $\I(\pi_i,V^{A}).$ Thus, we set
-\[
-\Xi := \C^{n^2} - \Gamma = V(h),
-\]
-with $h \in \Q[\A_{i,j}]$ defined as the least common multiple of the denominators of the generators of $\I^\A.$ Since $\pjb^k \in \I^\A$ and since
-\[
-\pjb^k = \frac{1}{\alpha}\left( Q(\A_{i,j},\Xb) \right), Q \in \Q[\A_{i,j}][\Xb],
-\]
-it follows that 
-\[
-\deg \Xi = \deg h \leq \deg \alpha \leq D^{\frac{3}{2} n \ln n+1}.
-\]
-Furthermore, since $\pjb^k \in \I^\A,$ it follows from by proposition 5.2 that, if $A \in \C^{n^2} - \Xi$ then the extension  
-\[
-\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}^\A
-\]
-is integral, and thus $V(\I^A)=W^\A$ is in Noether position for $\pi_{i-1}.$ Therefore, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(4)$.
+A_{j,l}(\A,\textit{\textbf{X}},1/\pjb) 
+&= \sum_{i=1}^{n_l} A_{j,l,i}(\A,\Xb,1/\pjb)\\
+&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\textit{\textbf{X}}), ~k_i \in \mathbb{Z}.
+\end{align*}
+%
+Let $K := \max\{k_l\}$ so that 
+%
+\begin{align*}
+    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},1/\pjb)g_l\right)\\
+    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{i}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb].
+\end{align*}
+%
+which shows that $\alpha_j$ is the only remaining denominator whose degree we need to bound other than $d_j$. Note as well that
+\[
+\pjb^K \in \I^{\A}.
+\]
+Therefore 
+%
+\begin{align*}
+\deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
+    &\leq \left(D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
+    &=D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+\end{align*}
+%
+\subsection{Proof of Theorem 8.1}
+%
+We can apply B\'ezout and obtain
+%
+\begin{align*}
+    \deg \Xi_i = \deg V(h_i,\hdots,h_n)
+    &\leq \prod_{j=i}^n \deg h_j\\
+    &\leq  \prod_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
+    &=  \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n-i+1}\\
+    &\leq  \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n}.
+\end{align*}
+%
+And therefore, by another application of B\'ezout, 
+%
+\begin{align*}
+    \deg& \Delta_3 \leq \prod_{i=1}^n \deg \Xi_i\\
+    &\leq \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n^2},
+    &(=D^{O(n^3 \log n)}\textrm{?})
+\end{align*}
+%
+where if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in \{1,\hdots,n\},$ the extension 
+\[
+\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
+\]
+%% <<<<<<< HEAD
+%% is integral, and thus $V(\I^A)=W^\A$ is in Noether position for $\pi_{i-1}.$ Therefore, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(4)$.
+%% =======
+is integral.
+%% >>>>>>> f9eb2445ca6e153d1e49c3d2767097d331dbcbee
 %

### 2020-02-02 main.tex
Update main.tex
Updated Section 6

@@
 %
-It will sometimes be useful for us to let the matrix $A$ represent new
-indeterminates: let $\A$ be an $n \times n$ matrix of new
-indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in
-\mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and
-$V^\A=V(f^\A).$ It follows from Proposition 4.2 that for a generic $A
-\in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.  The proof of
-\cite[Theorem B.3]{NO}, which shows the existence of $\Delta \subset
-\C^{n^2},$ applies \textit{Sard's lemma}, which shows that the
-critical values of a polynomial mapping are contained in a
-hypersurface. It follows from Sard's lemma that for the matrix of
-indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise
-it could not be that $0$ is a regular value of $\Phi_A,$ for a generic
-$A\in \C^{n^2}.$ Therefore,
-\[
-\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(x),\frac{\pa f^{\A}(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(x)}{\pa X_n}\right)
-\]
-has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$. We will rely on this fact in Section 5. 
+It will sometimes be useful for us use in replace of the matrix $A$, a matrix representing indeterminants: let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ It follows from Proposition 5.1, that for a generic $A \in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.
+The proof of \cite[Theorem B.3]{TWT}, which establishes the existence of $\Delta \subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the critical values of a polynomial mapping are contained in a hypersurface.
+It follows from Sard's lemma that, for the matrix of indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise it could not be that $0$ is a regular value of $\Phi_A,$ for a generic $A\in \C^{n^2}.$ The proof is routine and we omit details.
+It then follows that
+\[
+\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(\xb),\frac{\pa f^{\A}(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(\xb)}{\pa X_n}\right)
+\]
+has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}.
+We will rely on this fact in Section 8.
 %
@@
 We assume our input polynomial $f$ satisfies \textbf{H} so that $f$ is squarefree with $V(f) \cap \mathbb{R}^n$ smooth.
-Thus, by Proposition 2.4,  $W(\pi_i,V(f))$ is defined by the vanishing of \[\fb := \left(f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right).\]
-If the Jacobian of $\fb$ has full rank at all $x \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion [4, Theorem 16.19] that $f$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
+Thus, by Proposition 2.4,  $W(\pi_i,V(f))$ is defined by the vanishing of $f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.$ If the Jacobian of this set of polynomials has full rank at all $\xb \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion \cite[Theorem 16.19]{ECA} that $f$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
 %
 \begin{theorem}
-There exists a Zariski closed set $\Delta \subset \C^{n^2}$ of degree at most $D^n$ with the property that, if $A \in \C^{n^2} - \Delta$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
+There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $D^n$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
 \end{theorem}
@@
 \]
-Then we show that $0$ is a regular value of $\Phi$, so that, by Proposition 4.2, $\Delta \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta$ then $0$ is a regular value of $\Phi_A.$ It then follows that
+We want to apply Theorem 5.1, and thus we show that $0$ is a regular value of $\Phi$, where then it follows that $\Delta_1 \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta_1$ then $0$ is a regular value of $\Phi_A,$ which means that
 \[
@@
 \]
-has full rank for all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
+has full rank for all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
 \subsection{Proof of Theorem 6.1}
-Now, with $i \in \{1,\hdots,n\}$, let $\Phi$ be the mapping \[(\xb,A) \mapsto (f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,
-\frac{\partial f^A}{\partial X_n}(\xb))\] so that 
-\[
-\Phi^{-1}(0)= W(\pi_i,V^A).
-\]
+With $i \in \{1,\hdots,n\}$, let $\Phi$ be as stated above.
 %
@@
 \begin{proof}
-Put
-\[
-G_0 = f(Ax), 
-G_1 = \frac{\partial (f(Ax))}{\partial X_{i+1}},\hdots,G_{n-i} = \frac{\partial (f(Ax))}{\partial X_n},
-\] 
-and assume that $G_0(\xb,A)=G_1(\xb,A)=\hdots =G_{n-i}(\xb,A)=0.$ We can simplify by removing $Ax$ from the system because  
-\[
-(f(Ax),(\grad(f)\cdot 
-\bbm 
-a_{i+1,1} \\
-\vdots \\
-a_{i+1,n} 
-\ebm)(Ax),\hdots, 
+Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that \[
+f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=0.
+\] 
+We want to show that the system
+\[
+f(Ax),(\grad(f)\cdot 
+A_{i+1})(Ax),\hdots, 
 (\grad(f)\cdot 
-\bbm 
-a_{n,1} \\
-\vdots \\
-a_{n,n} 
-\ebm)(Ax)
-\] 
-defines a radical ideal of dimension ? whose variety is smooth if and only if 
-\[
-(f,\grad(f)\cdot 
-\bbm 
-a_{i+1,1} \\
-\vdots \\
-a_{i+1,n} 
-\ebm),\hdots, 
+A_n)(Ax)
+\]
+defines a radical ideal of dimension ? whose variety is smooth, which holds if and only if 
+\[
+f,\grad(f)\cdot 
+A_{i+1},\hdots, 
 \grad(f)\cdot 
-\bbm 
-a_{n1} \\
-\vdots \\
-a_{nn} 
-\ebm)
-\]
-defines a radical ideal of dimension ? whose variety is smooth. Now, let $g$ be the following:
-%
-\begin{align*}
-    g: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
+A_n
+\]
+defines a radical ideal of dimension ? whose variety is smooth. Now, let $\Psi$ be the mapping
+%
+\begin{align*}
+    \Psi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
        (\xb,A) &\mapsto 
        \left(f(\xb),\grad(f(\xb))\cdot 
-A_{i+1},\hdots, 
+A_{i+1},\hdots. 
 \grad(f(\xb))\cdot 
 A_{n}
-\right)
-\end{align*}
-%
-I claim that for all $(\xb,A) \in g^{-1}(0),$ the Jacobian matrix of $g$ at $(\xb,A)$ has full rank $n-i+1$ (i.e. $g$ is transverse to $\{0\}).$ The Jacobian of 
-%
-\begin{align*}
-       & \left(f,\grad(f)\cdot 
-\bbm 
-a_{i+1,1} \\
-\vdots \\
-a_{i+1,n} 
-\ebm,\hdots, 
-\grad(f)\cdot 
-\bbm 
-a_{n,1} \\
-\vdots \\
-a_{n,n} 
-\ebm\right) \\
-&= \left(f, \frac{\pa f}{\pa X_1} a_{i+1,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+1,n}, \hdots, \frac{\pa f}{\pa X_1} a_{n,1} + \hdots + \frac{\pa f}{\pa X_n}a_{n,n}\right) \\
-&= (f,F_{1},\hdots,F_{n-i}),  
-\end{align*} 
-%
-where 
-\[
-F_j = \frac{\pa f}{\pa X_1} a_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+j,n}, 1 \leq j \leq n-i,\]
-is
+\right),
+\end{align*}
+%
+For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
+\[
+F_j = \frac{\pa f}{\pa X_1} a_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+j,n}, ~1 \leq j \leq n-i,
+\]
+The Jacobian of the system of polynomials $f,F_{1},\hdots,F_{n-i}$ is
 \[
@@
 \] 
-Since $f$ is square-free, \[I(V(f)) = \langle f \rangle,\]  and thus for all $\xb \in V(f)$, 
+Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
 \[
@@
 %
-Since $\deg \Phi \leq D,$ it follows by Theorem 4.2 that a hypersurface $\Delta \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta,$ then $0$ is a regular value of $\Phi_{A}$, which means that
+Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Phi_{A}$, which means that
 \[
@@
 has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
-Therefore, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$, for each $i \in \{1,\hdots,n\}.$
-%
+Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%
 %

### 2020-02-02 main.tex
Update main.tex
Updated Section 4

@@
 \nl \For{$i\gets1$ \KwTo $n$}{
-Apply the symbolic homotopy algorithm from \cite{SH} with input $\{X_1,\hdots,X_i,f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$ and $D$ to obtain a zero dimensional parameterization of $W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(0)$.;
+Apply the symbolic homotopy algorithm from \cite{SH} with input $\{X_1,\hdots,X_i,f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$ and $D$ to obtain a zero dimensional parameterization of $W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(0)$;
 } 
@@
 %
-Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ squarefree with total degree $D$ and $V(f)$ smooth. We say that $V$ is in \textit{Noether position} for $\pi_D$ when the extension 
-\[
-\C[X_1,\hdots,X_D] \rightarrow \C[X_1,\hdots,X_n]/I(V)
-\] 
-is injective and integral.  Then, for any $\xb \in \C^D,$ the fiber 
-$V \cap \pi_D^{-1}(\xb)$ has dimension zero. 
+Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ with total degree $D$.  
 We say that $f$ satisfies $\textbf{H}$ if 
@@
 %
-For $i\in\{1,\hdots,n\}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
+An equidimensional algebraic set $X$ of dimension $d$ is in \textit{Noether position} for $\pi_d$ when the extension 
+\[
+\C[X_1,\hdots,X_d] \rightarrow \C[X_1,\hdots,X_n]/I(V)
+\] 
+is injective and integral.  Then, for any $\xb \in \C^d,$ the fiber 
+$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
 %
@@
 \begin{theorem}
-Suppose that $f$ satisfies \textbf{H}.
-Then there exists a Zariski closed set $\frak{X} \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{?}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\frak{X}$ then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
+Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
+Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{?}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
 \end{theorem}

### 2020-02-02 main.tex
Updated Section 6

@@
 %
-Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Phi_{A}$, which means that
-\[
-\jac_\textit{\textbf{x}} \Phi_A 
+Since $\deg \Psi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Psi_{A}$, which means that
+\[
+\jac_\textit{\textbf{x}} \Psi_A 
 = \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)

### 2020-02-02 main.tex
Updated Section 6
Abstract references

@@
   geometry have been developed in a series of papers
-  \cite{a,b,c,d}. However, these algorithms are based in the
+  \cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}. However, these algorithms are based in the
   arithmetic complexity model, and analyses of the bit complexity
@@
 \subsubsection{Bit-complexity}
-Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{a,b,c,d}.
+Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}.
 However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work.

### 2020-02-03 main.tex
Updated Section 6

@@
 %
-We will let $\Phi$ be the mapping 
+We will let $\Phi$ be a mapping essentiall equal to 
 \[
@@
 \]
-defines a radical ideal of dimension ? whose variety is smooth. Now, let $\Psi$ be the mapping
-%
-\begin{align*}
-    \Psi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
+defines a radical ideal of dimension ? whose variety is smooth. Now, let $\Phi$ be the mapping
+%
+\begin{align*}
+    \Phi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
        (\xb,A) &\mapsto 
@@
 %
-For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
+For all $(\xb,A) \in \Phi^{-1}(0),$ the Jacobian matrix of $\Phi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
 \[
@@
 \]
-The Jacobian of the system of polynomials $f,F_{1},\hdots,F_{n-i}$ is
+so that the Jacobian is equal to
 \[
@@
 %
-Since $\deg \Psi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Psi_{A}$, which means that
-\[
-\jac_\textit{\textbf{x}} \Psi_A 
-= \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
-\] 
-has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
+Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $\td$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Phi_{A}$, which means that
+%
+\begin{align*}
+\jac_\textit{\textbf{x}} \Phi_A &=\left(f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots. \grad(f(\xb))\cdot A_{n} \right) 
+\end{align*}
+%
+has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). It follows that 
+\[
+ \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
+\]
+also has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
 Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%

### 2020-02-03 main.tex
Updated Section 3

@@
 \def\ab{\textit{\textbf{a}}}
+\def\pb{\textit{\textbf{p}}}
 \def\ajb{\overline{a_j}}
@@
 %
-\section{The Main Algorithm}
+\section{The Algorithm}
+%
+For a matrix $A \in \GL(n,\Q),$ let 
+\[
+Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
+\]
+where $b_i$ is the i-th row of $A^{-1}$.
 %
@@
 \KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq $?\;
+\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \td$\;
 \nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
@@
 \nl \For{$i\gets1$ \KwTo $n$}{
-Apply the symbolic homotopy algorithm from \cite{SH} with input $\{X_1,\hdots,X_i,f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$ and $D$ to obtain a zero dimensional parameterization of $W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(0)$;
+Randomly choose a point $p_{i-1}=(x_1,\hdots,x_{i-1}) \in \Q^{i-1}~(p_0$?) and apply the symbolic homotopy algorithm from \cite{SH} with input $\{Y_1-x_1,\hdots,Y_{i-1}-x_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$ and $D$, to obtain a zero dimensional parameterization of $W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(p_{i-1})$;
 } 
-\nl \Return $\cup_{i=1}^n W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(0)$;
+\nl \Return $\bigcup_{i=1}^n W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(p_{i-1})$.
 \end{algorithm}

### 2020-02-03 main.tex
Updated Section 6

@@
 \def\bs{\textit{\textbf{s}}}
+\def\bz{\textit{\textbf{0}}}
 \def\Lb{\textit{\textbf{L}}}
@@
 %
-We will let $\Phi$ be a mapping essentiall equal to 
+Let $\Phi$ be the polynomiall mapping 
 \[
@@
 \] 
-so that 
-\[
-\Phi_A^{-1}(0)= W(\pi_i,V^A).
-\]
-We want to apply Theorem 5.1, and thus we show that $0$ is a regular value of $\Phi$, where then it follows that $\Delta_1 \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta_1$ then $0$ is a regular value of $\Phi_A,$ which means that
-\[
-\jac_{\xb}(\Phi_A) = \jac_{\xb}\left(f^A(x),\frac{\pa f^A(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(x)}{\pa X_n}\right)
-\]
-has full rank for all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+so that $\Phi_A^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $0$ is a regular value of $\Phi$, where then it follows that $\Delta_1 \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta_1$ then
+\[
+\jac_{\xb}(\Phi_A) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)
+\]
+has full rank at all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
 \subsection{Proof of Theorem 6.1}
@@
 \begin{proposition} 
-0 is a regular value of $\Phi$.
+$\bz$ is a regular value of $\Phi$.
 \end{proposition}
@@
 \begin{proof}
-Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that \[
-f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=0.
-\] 
-We want to show that the system
-\[
-f(Ax),(\grad(f)\cdot 
-A_{i+1})(Ax),\hdots, 
-(\grad(f)\cdot 
-A_n)(Ax)
-\]
-defines a radical ideal of dimension ? whose variety is smooth, which holds if and only if 
-\[
-f,\grad(f)\cdot 
-A_{i+1},\hdots, 
-\grad(f)\cdot 
-A_n
-\]
-defines a radical ideal of dimension ? whose variety is smooth. Now, let $\Phi$ be the mapping
-%
-\begin{align*}
-    \Phi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
+Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that 
+$f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=\bz.$
+We want to show that the system of polynomials 
+\[
+f(Ax),(\grad(f)\cdot A_{i+1})(Ax),\hdots, (\grad(f)\cdot A_n)(Ax)
+\]
+defines a radical ideal of dimension ? whose variety is smooth (we just want the Jacobian of the system to have full rank?), which holds if and only if 
+\[
+f,\grad(f)\cdot A_{i+1},\hdots, \grad(f)\cdot A_n
+\]
+defines a radical ideal of dimension ? whose variety is smooth. Let $\Psi$ be the mapping
+%
+\begin{align*}
+    \Psi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
        (\xb,A) &\mapsto 
@@
 %
-For all $(\xb,A) \in \Phi^{-1}(0),$ the Jacobian matrix of $\Phi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
+For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
 \[
@@
 %
-Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $\td$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Phi_{A}$, which means that
-%
-\begin{align*}
-\jac_\textit{\textbf{x}} \Phi_A &=\left(f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots. \grad(f(\xb))\cdot A_{n} \right) 
-\end{align*}
-%
-has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). It follows that 
+Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $\td$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then 
+%
 \[
@@
 \]
-also has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
+has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
 Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%

### 2020-02-03 main.tex
Updated Section 9

@@
 is injective and integral.  Then, for any $\xb \in \C^d,$ the fiber 
-$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
+$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (x_1,\hdots,x_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
 %
@@
 \item $W(\pi_i,V)$ is smooth;
-\item $\langle X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
-\item $V(X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ has dimension $0$;
-\item $V(X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
+\item $\langle X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
+\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
+\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
 \item either $W(\pi_i,V)$ is empty or in Noether position for $\pi_{i-1}$.
@@
 Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
-Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{?}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
+Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
 \end{theorem}
@@
 \begin{corollary} 
-Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{?}}$ and $\epsilon > 0$.
+Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
 Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
@@
 %
-\section{Proof of Theorem 3.1}
-%
-Assume that $f\in \Q[X_1,\hdots,X_n]$ satisfies $\textbf{H}.$
+\section{Proof of Theorem 4.1}
+%
+Recall Theorem 4.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
+Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$}
+%
+\begin{proof}
+Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 6.1, there exists a zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 7.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
+Clearly then, if
+\[
+A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
+\]
+then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
+\[
+\Delta = \prod_{i=1}^3 \D_i,
+\]
+and note that 
+\[
+\deg \D \leq  \prod_{i=1}^3 \deg \D_i.
+\]
+\end{proof}
+%
+Recall Corollary 4.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
+Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
+%
+\begin{proof}
+\[
+Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
+\]
+\end{proof}
 %

### 2020-02-03 main.tex
Moved pseudo code to the proof of Theorem 1.1

@@
 \def\Yt{\widetilde{Y}}
+\def\kt{\widetilde{k}}
 \def\dt{s}
@@
 \begin{theorem}
-Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $\hdots$.
-Otherwise the algorithm either produces a subset of the critical points or FAIL.
+Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1/2$.
+Otherwise the algorithm either produces a subset of the points or FAIL.
 In any case, the algorithm uses
 \[
-\hdots  
-\]
-boolean operations.
+O^{\sim}(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
+\]
+boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. 
 \end{theorem}
 %
-The algorithm is Monte Carlo and can error on one side by producing a proper subset of the points.
-Running the algorithm $k$ times gives a list of outputs among which the highest cardinality set includes at least one point in each connected component with probability at least $\hdots.$
+The algorithm can error on one side by producing a proper subset of the points.
+Running the algorithm $\kt$ times gives a list of $n$ zero-dimensional parameterizations, among which the highest cardinality output includes at least one point in each connected component with probability at least $1-(1/2)^{\kt}.$
 %
@@
 %
-\section{The Algorithm}
-%
-For a matrix $A \in \GL(n,\Q),$ let 
-\[
-Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
-\]
-where $b_i$ is the i-th row of $A^{-1}$.
-%
-\begin{algorithm}
-\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $D=\deg(f)$}
-\KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \td$\;
-\nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
-\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
-    \caption{{Main Algorithm} \label{}}
-\nl \For{$i\gets1$ \KwTo $n$}{
-Randomly choose a point $p_{i-1}=(x_1,\hdots,x_{i-1}) \in \Q^{i-1}~(p_0$?) and apply the symbolic homotopy algorithm from \cite{SH} with input $\{Y_1-x_1,\hdots,Y_{i-1}-x_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$ and $D$, to obtain a zero dimensional parameterization of $W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(p_{i-1})$;
-} 
-\nl \Return $\bigcup_{i=1}^n W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(p_{i-1})$.
-\end{algorithm}
 %
@@
 %
-\subsection{Sketch of the proof of Theorem 6.1}
+\subsection{Sketch of the proof of Theorem 5.1}
 %
@@
 has full rank at all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
-\subsection{Proof of Theorem 6.1}
+%
+\subsection{Proof of Theorem 5.1}
+%
 With $i \in \{1,\hdots,n\}$, let $\Phi$ be as stated above.
@@
 %
-\subsection{Sketch of the proof of Theorem 7.1}
+\subsection{Sketch of the proof of Theorem 6.1}
 %
@@
 %
-\subsection{Proof of Theorem 8.1}
+\subsection{Proof of Theorem 7.1}
 %
@@
 %
-\section{Proof of Theorem 4.1}
-%
-Recall Theorem 4.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
+\section{Proof of Theorem 3.1}
+%
+Recall Theorem 3.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
 Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$}
@@
 \begin{proof}
-Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 6.1, there exists a zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 7.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
+Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
 Clearly then, if
@@
 %
-Recall Corollary 4.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
+Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
 Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
@@
 %
-%
+Recall Theorem 1.1: \textit{Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1/2$.
+Otherwise the algorithm either produces a subset of the points or FAIL.
+In any case, the algorithm uses
+\[
+O^{\sim}(k(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
+\]
+boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. }
+%
+\subsection{The Algorithm}
+%
+For a matrix $A \in \GL(n,\Q),$ let 
+\[
+Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
+\]
+where $b_i$ is the i-th row of $A^{-1}$.
+%
+\begin{algorithm}
+\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $D=\deg(f)$}
+\KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
+\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \td$\;
+\nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
+\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
+    \caption{{Main Algorithm} \label{}}
+\nl \For{$i\gets1$ \KwTo $n$}{
+\nl Randomly choose a point $p_{i-1}=(x_1,\hdots,x_{i-1}) \in \Q^{i-1}~(p_0$?)\; 
+\nl Run the symbolic homotopy algorithm from \cite{SH} $k \geq -\lg(1-2^{(-1/n)})$ times with input 
+\[
+\{Y_1-x_1,\hdots,Y_{i-1}-x_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } D\;
+\]
+\nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 6 \;
+} 
+\nl \Return $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$.
+\end{algorithm}
 

### 2020-02-03 main.tex
Proof of Theorem 1.1

@@
 
-% test 
+% packages 
+%\usepackage[options ]{algorithm2e}
+\usepackage[ruled,vlined]{algorithm2e}
+%\usepackage{algorithm,algpseudocode,float}
 \usepackage{mathrsfs}
 \usepackage{bm}
+\usepackage{enumitem}
 % new commands and shortcuts
@@
 \def\C{\mathbb{C}}
+\def\pr{\mathbb{P}}
 \def\vt{\vartheta}
@@
 
-%\usepackage[options ]{algorithm2e}
-\usepackage[ruled,vlined]{algorithm2e}
-
 \begin{document}
@@
 \]
-boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. 
+boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
+\[
+O^{\sim}((s+D)D^n + nD^n).
+\]
 \end{theorem}
@@
 %
-\section{Proof of Theorem 1.1}
+\section{Bit complexity}
 %
@@
 \[
-O^{\sim}(k(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
-\]
-boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. }
+O^{\sim}(nk(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
+\]
+boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
+\[
+O^{\sim}((s+D)D^n + nD^n).
+\]
+}
+Recall as well that the algorithm can error on one side by producing a proper subset of the points.
+Running the algorithm $\kt$ times gives a list of $n$ zero-dimensional parameterizations, among which the highest cardinality output includes at least one point in each connected component with probability at least $1-(1/2)^{\kt}.$
 %
@@
 %
-\begin{algorithm}
+\begin{algorithm}[hbt!]
 \KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $D=\deg(f)$}
 \KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \td$\;
+\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \epsilon^{-1}D^{\td}$, where $\epsilon < 5/21$\;
 \nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
-\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
+\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
     \caption{{Main Algorithm} \label{}}
@@
 \nl Randomly choose a point $p_{i-1}=(x_1,\hdots,x_{i-1}) \in \Q^{i-1}~(p_0$?)\; 
-\nl Run the symbolic homotopy algorithm from \cite{SH} $k \geq -\lg(1-2^{(-1/n)})$ times with input 
-\[
-\{Y_1-x_1,\hdots,Y_{i-1}-x_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } D\;
-\]
+\nl Run \cite[Algorithm 2]{SH} $k > -\lg(1-2^{(-1/n)})$ times with input 
+$\{Y_1-x_1,\hdots,Y_{i-1}-x_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } D$\;
 \nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 6 \;
@@
 \end{algorithm}
-
+ \clearpage
+%
+\subsection{Proof of Theorem 1.1}
+%
+\textbf{The boolean cost:} The following lists the costs for each step of Algorithm 1:
+%
+\begin{enumerate}
+    \item By our assumption on the size of $S$ we know that $|S| = \log (\epsilon^{-1}D^{\td}) \leq \td.$ Thus for $a_{ij} \in S$ we know that $|a_{ij}| \leq \td.$
+    \item 
+    \begin{enumerate}[label=\roman*.]
+        \item $O(L)$ operations are required to compute $f$ from its straight line program $\Gamma.$
+        \item After applying the change of variables obtaining $f(A x)=f^A(x)$ the height grows at most by a factor of
+        \begin{align*}
+        \log(n!\cdot \max_{\frac{1\leq i\leq n}{1\leq j\leq n}}\{a_{ij}\}) &= 
+        O(n\log n + n\log(D+1)) \\
+        &= 
+        O^\sim(\log(D+1)).
+        \end{align*}
+    \end{enumerate}
+    \item After computing the partial derivatives the height grows by at most another factor of $\log D$.
+Furthermore, preparing the straight line program for the gradient of $f$ does not introduce large integers.
+The integers in $\grad (f)$ are of the same magnitude as in $\Gamma$.
+    \item 
+    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the following upper bound on the total boolean cost of the algorithm:
+    \[
+    O^\sim(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4))),
+    \]
+    where it also follows from \cite[Algorithm 2]{SH} that the polynomials in the output have degree at most $D^n,$ and height at most
+    \[
+    O^{\sim}((s+D)D^n + nD^n).
+    \]
+\end{enumerate}
+%
+\par \noindent 
+\textbf{Probability of success:} Note that when $\epsilon < 5/21$ (as stated in step 1 of Algorithm 1), then
+\[
+\pr[A \not \in \D] = 1-\epsilon > \frac{16}{21},
+\]
+so that after a single run of \cite[Algorithm 2]{SH}, the probability of success (ensuring all genericity properties and obtaining all points) is at least 
+\[
+\left( \frac{16}{21} \right) \left( \frac{21}{32} \right) = \frac{1}{2}.
+\]
+Thus, running \cite[Algorithm 2]{SH} $k$ times gives a list of outputs among which the highest cardinality set includes all points with probability at least $1-(1/2)^k$.
+We repeat this $n$ times to obtain $n$ zero-dimensional parameterizations.
+Thus, the probability that we have every point in each parameterization is $(1-(1/2)^k)^n$.
+We want
+\[
+(1-(1/2)^k)^n>\frac{1}{2},
+\]
+which holds if and only if 
+\[
+k > -\lg(1-2^{(-1/n)}),
+\]
+thus proving Theorem 1.1.
+We can boost our success probability by running the main algorithm $\kt$ times, so that we obtain parameterizations whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1 - (1/2)^{\kt}$.
 %%

### 2020-02-04 main.tex
Updated Section 5

@@
 \begin{theorem}
-There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $D^n$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $D^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
 \end{theorem}
@@
 %
-Let $\Phi$ be the polynomiall mapping 
-\[
-(\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),
-\] 
-so that $\Phi_A^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $0$ is a regular value of $\Phi$, where then it follows that $\Delta_1 \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta_1$ then
-\[
-\jac_{\xb}(\Phi_A) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)
-\]
-has full rank at all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+For each $i \in \{1,\hdots,n\}$, let $\Phi_i$ be the polynomial mapping 
+\[
+\Phi_i : (\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),
+\] 
+so that $\Phi_{i,A}^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $\bz$ is a regular value of $\Phi_i$, where then it follows that $\Xi_i \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Xi_i$ then
+\[
+\jac_{\xb}(\Phi_{i,A}) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)
+\]
+has full rank at all $\xb \in V(f^A)~(\cap\R^n$?).
+Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+To obtain the result for all $i \in \{1,\hdots,n\}$, we take
+\[
+\Delta_1 = \bigcup_{i=1}^n \Xi_i 
+\]
+where we can bound the degree by observing that 
+\[
+\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i.
+\]
 %
@@
 %
-With $i \in \{1,\hdots,n\}$, let $\Phi$ be as stated above.
+Fix $i \in \{1,\hdots,n\}$, and let $\Phi_i$ be as stated above.
 %
 \begin{proposition} 
-$\bz$ is a regular value of $\Phi$.
+$\bz$ is a regular value of $\Phi_i$.
 \end{proposition}
@@
 $f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=\bz.$
-We want to show that the system of polynomials 
-\[
-f(Ax),(\grad(f)\cdot A_{i+1})(Ax),\hdots, (\grad(f)\cdot A_n)(Ax)
-\]
-defines a radical ideal of dimension ? whose variety is smooth (we just want the Jacobian of the system to have full rank?), which holds if and only if 
+We want to show that the Jacobian of the system of polynomials 
+\[
+f(A\xb),(\grad(f)\cdot A_{i+1})(A\xb),\hdots, (\grad(f)\cdot A_n)(A\xb)
+\]
+at $(\xb,A)$ has full rank, which holds if and only if the Jacobian of the system of polynomials 
 \[
@@
 \]
-defines a radical ideal of dimension ? whose variety is smooth. Let $\Psi$ be the mapping
-%
-\begin{align*}
-    \Psi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
+at $(\xb,A)$ has full rank. Let $\Psi_i$ be the mapping
+%
+\begin{align*}
+    \Psi_i: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
        (\xb,A) &\mapsto 
        \left(f(\xb),\grad(f(\xb))\cdot 
-A_{i+1},\hdots. 
+A_{i+1},\hdots
 \grad(f(\xb))\cdot 
 A_{n}
-\right),
-\end{align*}
-%
-For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
+\right).
+\end{align*}
+%
+For all $(\xb,A) \in \Psi_i^{-1}(0),$ the Jacobian matrix of $\Psi_i$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
 \[
@@
 At least one partial of $f$ must be non-zero.
-Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i$ rows, the matrix has full rank $n-i$.
+Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
 \end{proof}
 %
-Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $\td$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then 
+Since $\deg \Phi_i \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $D^{n+(n-i+1)}=D^{2n-i+1}\leq D^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
 %
@@
 \]
-has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
-Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%
+has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}.
+Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
+\[
+\Delta_1 := \bigcup_{i=1}^n \Xi_i,
+\]
+where we have the following bound on the degree which proves the claim:
+\[
+\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq D^{2n^2}.
+\] 
+%
 %

### 2020-02-04 main.tex
Updated Section 7 - Noether N

@@
 \begin{theorem}
-There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $D^{?}$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(7)$.
+There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(7)$.
 \end{theorem}
 %
-Section 8 is devoted to proving Theorem 8.1.
-It has already been shown in \cite{EMP} that $f^A$ satisfies $\textbf{H}_i^{'}$ for a generic change of variables.
+Section 7 is devoted to proving Theorem 7.1.
+It has already been shown in \cite{EMP} that $f^A$ satisfies $\textbf{H}_i^{'}(7)$ for a generic change of variables.
 The new contribution is in upper bounding the degree of $\Delta_3.$
@@
 %
-Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 8.2.
+Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 7.2.
 Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$
@@
 \[
-\Xi_i := V(h_i,\hdots,h_n), 
-\]
-and we obtain a bound on the degree of $\Xi_i$ by applying Bezout's theorem. Hence, if $A\in \Q^{n^2}-\Xi_i$ then
+\Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 
+\]
+and we obtain a bound on the degree of $\Xi_i$ by observing that
+\[
+\deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
+\]
+Hence, if $A\in \Q^{n^2}-\Xi_i$ then
 \[
@@
 %
-We can apply B\'ezout and obtain
-%
-\begin{align*}
-    \deg \Xi_i = \deg V(h_i,\hdots,h_n)
-    &\leq \prod_{j=i}^n \deg h_j\\
-    &\leq  \prod_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
-    &=  \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n-i+1}\\
-    &\leq  \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n}.
-\end{align*}
-%
-And therefore, by another application of B\'ezout, 
-%
-\begin{align*}
-    \deg& \Delta_3 \leq \prod_{i=1}^n \deg \Xi_i\\
-    &\leq \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n^2},
-    &(=D^{O(n^3 \log n)}\textrm{?})
+Now we obtain
+%
+\begin{align*}
+    \deg \Xi_i 
+    &\leq \sum_{j=i}^n \deg h_j\\
+    &\leq  \sum_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
+    &=  (n-i+1)\left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
+    &\leq  n D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
+\end{align*}
+%
+And therefore,  
+%
+\begin{align*}
+    \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
+    &\leq n^2 D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
 \end{align*}

### 2020-02-04 main.tex
minor tweaks

@@
 \def\Z{\frak{Z}}
+\newcommand{\ZZ}{{\mathbb{Z}}}
+\newcommand{\softO}{{O^{\sim}}}
 \def\I{\frak{I}}
@@
 Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
-We provide bit-complexity estimates for computing one point in each connected component of $V(f)\cap \R^n.$ Its boolean complexity is $\hdots$.
+We provide bit-complexity estimates for computing one point in each connected component of $V(f)\cap \R^n.$ Its bit complexity is $\hdots$.
 %
@@
 For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface, and it is used in determining whether or not a complex hypersurface has real solutions.
+
 \subsubsection{Bit-complexity}
-Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}.
-However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work.
-As bit complexity provides a far more realistic model of computation compared to arithmetic complexity,  which only counts each operation at unit cost, our results therefore begin to fill an important missing gap in the research.
+Algorithms for deciding connectivity queries in real algebraic geometry
+have been developed in a series of papers
+\cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}. However,
+these algorithms are based in the arithmetic complexity model, and bit
+complexity questions have been left for future work. As bit complexity
+provides a far more realistic model of computation compared to arithmetic
+complexity,  which only counts each operation at unit cost and does not
+account for coefficient size, our results therefore address an important
+missing aspect of previous research.
+
+Note that by the bit complexity we mean to count the number of all machine
+operations require on a standard computer in terms of the length of a
+standard representation (accounting for coefficient size, etc.).  In
+particular, we assume that an integer $a\in\ZZ$ is represented with
+$O(\log|a|)$ bits, and operations on integers with $\ell$ bits require
+$\softO(\ell)$ bit operations.
+
 \subsubsection{Quantitative genericity statements}
@@
 \]
-boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
+bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
 \[
@@
 %
-\textbf{The boolean cost:} The following lists the costs for each step of Algorithm 1:
+\textbf{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
 %
@@
     \item 
-    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the following upper bound on the total boolean cost of the algorithm:
+    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the
+    following upper bound on the total number of bit operations required by the algorithm:
     \[

### 2020-02-04 main.tex
minor
intro

--- 2020-02-04 main.tex
@@
-%%
-%% This is file `sample-xelatex.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigconf')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-xelatex.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
 \documentclass[sigconf]{acmart}
 
-% packages 
-%\usepackage[options ]{algorithm2e}
-\usepackage[ruled,vlined]{algorithm2e}
-%\usepackage{algorithm,algpseudocode,float}
+% test 
 \usepackage{mathrsfs}
 \usepackage{bm}
-\usepackage{enumitem}
 % new commands and shortcuts
@@
 \def\bs{\textit{\textbf{s}}}
-\def\bz{\textit{\textbf{0}}}
 \def\Lb{\textit{\textbf{L}}}
@@
 \def\ab{\textit{\textbf{a}}}
-\def\pb{\textit{\textbf{p}}}
 \def\ajb{\overline{a_j}}
@@
 \def\C{\mathbb{C}}
-\def\pr{\mathbb{P}}
 \def\vt{\vartheta}
 \def\Q{\mathbb{Q}}
+\def\ZZ{\mathbb{Z}}
 \def\R{\mathbb{R}}
@@
 \def\Yt{\widetilde{Y}}
-\def\kt{\widetilde{k}}
 \def\dt{s}
@@
 % matrices 
+\def\scrQ{\ensuremath{\mathscr{Q}}}
 \def\bbm{\begin{bmatrix}}
@@
 
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
+\usepackage[ruled,vlined]{algorithm2e}
+\usepackage{chngcntr}
+\usepackage{titlesec}
 
@@
 
-\author{Eric Schost}
+\author{\'Eric Schost}
 \affiliation{%
@@
 
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
 \begin{abstract}
-  We present a full analysis of an efficient algorithm for the
-  computation of at least one point in each connected component of a
-  smooth real hypersurface, taking into account bit complexity and
-  all coefficient growth.  This problem is a basic and important
-  subroutine used in semi-algebraic geometry. For instance, it is used
-  in determining an upper bound on the number of connected components
-  of a real hypersurface. The algorithm requires some genericity
-  properties, which we ensure through random changes of variables that
-  produce generic coordinate systems. In order to ensure these
-  properties with arbitrarily high probability, we developed a new
-  quantitative extension of Thom's weak transversality theorem, and a
-  new quantitative Noether normalization statement for polar
-  varieties. These statements enable us to give a precise probability
-  analysis of a monte carlo algorithm, where we can guarantee
-  correctness with arbitrarily high probability.
-
-  Algorithms for deciding connectivity queries in real algebraic
-  geometry have been developed in a series of papers
-  \cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}. However, these algorithms are based in the
-  arithmetic complexity model, and analyses of the bit complexity
-  questions were left for future work.  Our results are an important
-  first step in this analysis.
-
+  We present a full analysis of the bit complexity of an efficient
+  algorithm for the computation of at least one point in each
+  connected component of a smooth real hypersurface. This is a basic
+  and important operation in semi-algebraic geometry: it gives an
+  upper bound on the number of connected components of a real
+  hypersurface, and is also used in many higher level algorithms.
+
+  Our starting point is an algorithm by Safey El Din and Schost ({\em
+    Polar varieties and computation of one point in each connected
+    component of a smooth real algebraic set}, ISSAC'03). This
+  algorithm uses random changes of variables, that are proved to
+  generically ensure certain desirable geometric properties. The
+  complexity of the algorithm was given in an algebraic complexity
+  model; the analysis of the bit complexity and the error probability
+  were left for future work.
+
+  Our paper answer these questions. Our main contribution is a
+  quantitative analysis of several genericity statements, such as
+  Thom's weak transversality theorem or Noether normalization
+  properties for polar varieties.
 \end{abstract}
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
 \begin{CCSXML}
@@
 
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{Real algebraic geometry, transversality, Noether normalization, bit complexity}
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
+\setcounter{secnumdepth}{4}
+\renewcommand{\theparagraph}{\thesubsection.\arabic{paragraph}}
+\counterwithin{paragraph}{subsection} % makes paragraph depend on subsection
+\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries}{\theparagraph.}{1em}{}
+\titlespacing*{\paragraph}{0em}{1ex}{1em}
+\newcommand{\pref}[1]{{\bf\ref{#1}}}
+
+\keywords{Real algebraic geometry, transversality, Noether
+  normalization, bit complexity}
+
 \maketitle
-%
-%
-%
-%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
-%
-\subsection{Problem statement}
-%
-Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
-We provide bit-complexity estimates for computing one point in each connected component of $V(f)\cap \R^n.$ Its boolean complexity is $\hdots$.
-%
-\subsection{Motivation}
-%
-\subsubsection{Applications}
-%
-Computing one point in each connected component of the real part of a hypersurface is a basic and important subroutine used in semi-algebraic geometry.
-For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface, and it is used in determining whether or not a complex hypersurface has real solutions.
+
+\paragraph*{Background and problem statement.}
+Computing one point in each connected component of a real algebraic
+set $S$ is a basic subroutine in real alebraic and semi-algebraic
+geometry; it is also useful in its own right, since it allows one to
+decide if $S$ is empty or not. In this paper, we consider only the
+case where $S$ is given as $S=V \cap \R^n$, where $V=V(f) \subset
+\C^n$ is a complex hypersurface defined by a squarefree polynomial $f
+\in \ZZ[X_1,\dots,X_n]$.
+
+Algorithms for this task have been known for decades, and their
+complexity is to some extent well understood. Suppose that $f$ has
+degree $d$, and coefficients of bit-size $h$. Without making any
+assumption on $f$, the algorithm given
+in~\cite[Section~13.1]{BaPoRo03} solves our problem using $d^{O(n)}$
+operations in $\Q$; in addition, the output of the algorithm is
+represented by polynomials of degree $d^{O(n)}$, with coefficients of
+bit-size $hd^{O(n)}$.  The key idea behind this algorithm goes back
+to~\cite{GrVo88}: sample points are found through the computation of
+critical points of well-chosen functions on $V(f)$.
+
+The number of connected components of $V(f)$ admits the lower bound
+$d^{\Omega(n)}$, so up to polynomial factors, this result is
+optimal. However, due to the generality of the algorithm, the constant
+hidden in the exponent $O(n)$ in its runtime turns out to be rather
+large: the algorithm relies on infinitesimal deformations, that affect
+runtime non-trivially.
+
+In this paper, we will work under the additional assumption that
+$V=V(f)$ is a {\em smooth} complex hypersurface. We place ourselves in
+the continuation of the line of work initiated by~\cite{BaGiHeMb97}:
+that reference deals with cases where $V$ is smooth and $V \cap \R^n$
+is compact, pointing out how {\em polar varieties} (that were
+introduced in the 1930's in order to define characteristic
+classes~\cite{Piene78,Teissier88}) can play a role in effective real
+geometry. This paper was extended in several directions: to $V$ being
+a smooth complete intersection, still with $V\cap \R^n$
+compact~\cite{BaGiHeMb01}, then without the compactness
+assumption~\cite{EMP,BaGiHePa05}; the smoothness assumption was then partly
+dropped in~\cite{BaGiHe14,BaGiHeLePa12}.
+
+The starting point in our paper is the algorithm in~\cite{EMP}. In the
+hypersurface case, its runtime is $d^{(4+o(1))n}$ operations in $\Q$;
+as with many results in this line of work, the algorithm is
+randomized: the algorithm needs to assume that we are in generic
+coordinates; this is done by applying a random change of coordinates
+prior to all computations. In addition, it relies on algorithms for
+solving systems of polynomial equations that are themselves
+randomized.  Altogether, this procedure chooses $n^{O(1)}$ random
+vectors, each of them in an affine space of dimension $n^{O(1)}$;
+every time a choice is made, failure corresponds to our chosen vector
+lying in a hypersurface of the parameter space.
+
+This paper revisits the algorithm in~\cite{EMP} (in the hypersurface
+case) and gives a complete analysis of its probality of success and
+its bit complexity.
+
+\paragraph*{Data structures.} As in references such
+as~\cite{GiHeMoPa95,GiHaHeMoMoPa97,GiHeMoMoPa98,BaGiHeMb97,EMP}, the
+input polynomial $f$ is given by means of a {\em straight-line
+  program}, that is, a sequence of operations $+,-,\times$ that
+evaluates $f$, on the input variables $X_1,\dots,X_n$; the {\em
+  length} of a straight-line program of such an objet is simply the
+number of operations it performs. Any polynomial of degree $d$ in $n$
+variables can be computed by a straight-line program of length $O\big
+({{d+n} \choose n}\big)$ (evaluate all monomials of degree up to $d$
+in $n$ variables, multiply them by their respective coefficients and
+sum the result). However, some inputs may be given by shorter
+straight-line program, and the algorithm is able to benefit from it.
+
+The output of the algorithm is a finite set in $\C^n$ defined over
+$\Q$. To represent it, we rely on a widely used data structure based
+on univariate
+polynomials~\cite{Kronecker82,Macaulay16,GiMo89,GiHeMoPa95,ABRW,GiHaHeMoMoPa97,GiHeMoMoPa98,Rouillier99}.
+Consider a zero-dimensional algebraic set $S \subset \C^n$ defined
+over $\Q$. A {\em zero-dimensional parametrization}
+$\scrQ=((q,v_1,\dots,v_n),\lambda)$ of $S$ consists in polynomials
+$(q,v_1,\dots,v_n)$, such that $q\in \Q[T]$ is monic and squarefree,
+all $v_i$'s are in $\Q[T]$ and satisfy $\deg(v_i) < \deg(q)$, and in a
+$\Q$-linear form $\lambda$ in variables $X_1,\dots,X_n$, such that
+\begin{itemize}
+\item $\lambda(v_1,\dots,v_N)=T q' \bmod q$, where $q'=\frac{\partial
+  q}{\partial T}$;
+\item we have the equality
+  $S=\left \{\left(
+      \frac{v_1(\tau)}{q'(\tau)},\dots,\frac{v_N(\tau)}{q'(\tau)}\right
+    ) \ \mid \ q(\tau)=0 \right \}.$
+\end{itemize}
+The constraint on $\lambda$ says that the roots of $q$ are the values
+taken by $\lambda$ on $S$. The parametrization of the coordinates by
+rational functions having $q'$ as a denominator goes back
+to~\cite{Kronecker82,Macaulay16}: as pointed out in~\cite{ABRW}, it
+allows one to control precisely the size of the coefficients of
+$v_1,\dots,v_n$.
+
+\paragraph*{Main result.} To state our main result, we need to define 
+the {\em height} of rationals, and polynomials with rational
+coefficients.
+
+The {\em height} of a non-zero rational $a=u/v$ is the maximum of
+$\ln(|u|)$ and $\ln(|v|),$ where $u \in \mathbb{Z}$ and $v \in
+\mathbb{N}$ are coprime. For a polynomial $f$ with rational
+coefficients, if $v \in \mathbb N$ is the minimal common denominator
+of all non-zero coefficients of $f$, then the \textit{height}
+$\htt(f)$ of $f$ is defined as the maximum of the logarithms of $v$
+and of the absolute values of the coefficients of $vf$.
+
+\begin{theorem}
+  Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, of degree
+  at most $d$ and height at most $s$; assume that $f$ is given by a
+  straight-line program $\Gamma$ of size $L$ with integer constants of
+  height at most $b.$ There exists a randomized algorithm that takes
+  $\Gamma, d,$ and $s$ as input and produces a zero-dimensional
+  parameterization of a set that contains at least one point in each
+  connected component of $V(f) \cap \R^n$ with probability at least
+  $\hdots$. Otherwise the algorithm either produces a subset of the
+  critical points or FAIL. In any case, the algorithm uses
+  \[
+  \hdots  
+  \]
+  boolean operations.
+\end{theorem}
+
+The algorithm is Monte Carlo and can error on one side by producing a
+proper subset of the points. Running the algorithm $k$ times gives a
+list of outputs among which the highest cardinality set includes at
+least one point in each connected component with probability at least
+$\hdots.$
+
+%% Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree
+%% $d$, and such that $V(f)$ smooth. We provide bit-complexity estimates
+%% for computing one point in each connected component of $V(f)\cap
+%% \R^n.$ Its boolean complexity is $\hdots$.
+
 \subsubsection{Bit-complexity}
-Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}.
-However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work.
-As bit complexity provides a far more realistic model of computation compared to arithmetic complexity,  which only counts each operation at unit cost, our results therefore begin to fill an important missing gap in the research.
-\subsubsection{Quantitative genericity statements}
-%
-\subsection{Main result}
-%
-\begin{theorem}
-Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1/2$.
-Otherwise the algorithm either produces a subset of the points or FAIL.
-In any case, the algorithm uses
-\[
-O^{\sim}(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
-\]
-boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
-\[
-O^{\sim}((s+D)D^n + nD^n).
-\]
-\end{theorem}
-%
-The algorithm can error on one side by producing a proper subset of the points.
-Running the algorithm $\kt$ times gives a list of $n$ zero-dimensional parameterizations, among which the highest cardinality output includes at least one point in each connected component with probability at least $1-(1/2)^{\kt}.$
-%
-%
-%
-%
-\section{Notation and preliminaries}
-%
-\subsection{Algebraic sets}
-%
+
+Algorithms for deciding connectivity queries in real algebraic
+geometry have been developed in a series of papers
+\cite{a,b,c,d}. However, these algorithms are based in the arithmetic
+complexity model, and bit complexity questions have been left for
+future work. As bit complexity provides a far more realistic model of
+computation compared to arithmetic complexity, which only counts each
+operation at unit cost, our results therefore begin to fill an
+important missing gap in the research.
+
+%
+%
+%
+
 An \textit{algebraic set} $V \subset \C^n$ is the set of common zeros of a set of polynomials $\textit{\textbf{f}}=(f_1,\hdots,f_s)$ in $\C[X_1,\hdots,X_n].$
-\subsubsection{Dimension and degree}
+
 The \textit{dimension} of an algebraic set $V \subset \C^n$, denoted $\dim V,$ can be defined in the following ways:
@@
 %
-\subsection{Bit-size, height and degree}
-%
-For $r \leq n,$ $\textit{\textbf{X}}_{\leq r}$ denotes $[X_1,\hdots,X_r]$ and $\textit{\textbf{X}}$ denotes $[X_1,\hdots,X_n]$. 
-\par 
-For $a=\frac{u}{v}$ in $\mathbb{Q}-\{0\},$ the  \textit{height} of $a,$ $\htt(a),$ is the maximum of $\log(|u|)$ and $\log(|v|),$ where $u \in \mathbb{Z}$ and $v \in \mathbb{N}$ are coprime.
-If $v$ is the minimal common denominator of all non zero coefficients of $f$, then the \textit{height} of $f, \htt(f),$ is defined as the maximum of the logarithms of $v$ and of the absolute values of the coefficients of $vf$.
-%
-\par
-We write $\htt(\textit{\textbf{f}})=(\htt(f_1),\hdots,\htt(f_N))$ and assume that $\htt(\textit{\textbf{f}}) \leq \textit{\textbf{s}} = (S_1,\hdots,s_N),$  with $\htt(f_i) \leq s_i$ for all $i \in \{ 1,\hdots,N\}.$
-%
-\subsection{Data structures}
-%
-\subsubsection{Strait-line programs}
-%
-\subsubsection{Zero-dimensional parameterizations}
+%
 %
@@
 %
+\section{The Main Algorithm}
+%
+\begin{algorithm}
+\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $D=\deg(f)$}
+\KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
+\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq $?\;
+\nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
+\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
+    \caption{{Main Algorithm} \label{}}
+\nl \For{$i\gets1$ \KwTo $n$}{
+Apply the symbolic homotopy algorithm from \cite{SH} with input $\{X_1,\hdots,X_i,f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$ and $D$ to obtain a zero dimensional parameterization of $W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(0)$.;
+} 
+\nl \Return $\cup_{i=1}^n W(\pi_i,V^A) \cap \pi_{i-1}^{-1}(0)$;
+\end{algorithm}
 %
@@
 %
-Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ with total degree $D$.  
+Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ squarefree with total degree $D$ and $V(f)$ smooth. We say that $V$ is in \textit{Noether position} for $\pi_D$ when the extension 
+\[
+\C[X_1,\hdots,X_D] \rightarrow \C[X_1,\hdots,X_n]/I(V)
+\] 
+is injective and integral.  Then, for any $\xb \in \C^D,$ the fiber 
+$V \cap \pi_D^{-1}(\xb)$ has dimension zero. 
 We say that $f$ satisfies $\textbf{H}$ if 
@@
 %
-An equidimensional algebraic set $X$ of dimension $d$ is in \textit{Noether position} for $\pi_d$ when the extension 
-\[
-\C[X_1,\hdots,X_d] \rightarrow \C[X_1,\hdots,X_n]/I(V)
-\] 
-is injective and integral.  Then, for any $\xb \in \C^d,$ the fiber 
-$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (x_1,\hdots,x_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
+For $i\in\{1,\hdots,n\}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
 %
@@
 \item $W(\pi_i,V)$ is smooth;
-\item $\langle X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
-\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
-\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
+\item $\langle X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
+\item $V(X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ has dimension $0$;
+\item $V(X_1,\hdots,X_i, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
 \item either $W(\pi_i,V)$ is empty or in Noether position for $\pi_{i-1}$.
@@
 \begin{theorem}
-Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
-Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
+Suppose that $f$ satisfies \textbf{H}.
+Then there exists a Zariski closed set $\frak{X} \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{?}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\frak{X}$ then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
 \end{theorem}
@@
 \begin{corollary} 
-Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
+Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{?}}$ and $\epsilon > 0$.
 Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
@@
 %
-It will sometimes be useful for us use in replace of the matrix $A$, a matrix representing indeterminants: let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ It follows from Proposition 5.1, that for a generic $A \in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.
-The proof of \cite[Theorem B.3]{TWT}, which establishes the existence of $\Delta \subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the critical values of a polynomial mapping are contained in a hypersurface.
-It follows from Sard's lemma that, for the matrix of indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise it could not be that $0$ is a regular value of $\Phi_A,$ for a generic $A\in \C^{n^2}.$ The proof is routine and we omit details.
-It then follows that
-\[
-\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(\xb),\frac{\pa f^{\A}(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(\xb)}{\pa X_n}\right)
-\]
-has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}.
-We will rely on this fact in Section 8.
+It will sometimes be useful for us to let the matrix $A$ represent new
+indeterminates: let $\A$ be an $n \times n$ matrix of new
+indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in
+\mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and
+$V^\A=V(f^\A).$ It follows from Proposition 4.2 that for a generic $A
+\in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.  The proof of
+\cite[Theorem B.3]{NO}, which shows the existence of $\Delta \subset
+\C^{n^2},$ applies \textit{Sard's lemma}, which shows that the
+critical values of a polynomial mapping are contained in a
+hypersurface. It follows from Sard's lemma that for the matrix of
+indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise
+it could not be that $0$ is a regular value of $\Phi_A,$ for a generic
+$A\in \C^{n^2}.$ Therefore,
+\[
+\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(x),\frac{\pa f^{\A}(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(x)}{\pa X_n}\right)
+\]
+has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$. We will rely on this fact in Section 5. 
 %
@@
 We assume our input polynomial $f$ satisfies \textbf{H} so that $f$ is squarefree with $V(f) \cap \mathbb{R}^n$ smooth.
-Thus, by Proposition 2.4,  $W(\pi_i,V(f))$ is defined by the vanishing of $f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.$ If the Jacobian of this set of polynomials has full rank at all $\xb \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion \cite[Theorem 16.19]{ECA} that $f$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+Thus, by Proposition 2.4,  $W(\pi_i,V(f))$ is defined by the vanishing of \[\fb := \left(f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right).\]
+If the Jacobian of $\fb$ has full rank at all $x \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion [4, Theorem 16.19] that $f$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
 %
 \begin{theorem}
-There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $D^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+There exists a Zariski closed set $\Delta \subset \C^{n^2}$ of degree at most $D^n$ with the property that, if $A \in \C^{n^2} - \Delta$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
 \end{theorem}
 %
-\subsection{Sketch of the proof of Theorem 5.1}
-%
-For each $i \in \{1,\hdots,n\}$, let $\Phi_i$ be the polynomial mapping 
-\[
-\Phi_i : (\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),
-\] 
-so that $\Phi_{i,A}^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $\bz$ is a regular value of $\Phi_i$, where then it follows that $\Xi_i \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Xi_i$ then
-\[
-\jac_{\xb}(\Phi_{i,A}) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)
-\]
-has full rank at all $\xb \in V(f^A)~(\cap\R^n$?).
-Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
-To obtain the result for all $i \in \{1,\hdots,n\}$, we take
-\[
-\Delta_1 = \bigcup_{i=1}^n \Xi_i 
-\]
-where we can bound the degree by observing that 
-\[
-\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i.
-\]
-%
-\subsection{Proof of Theorem 5.1}
-%
-Fix $i \in \{1,\hdots,n\}$, and let $\Phi_i$ be as stated above.
+\subsection{Sketch of the proof of Theorem 6.1}
+%
+We will let $\Phi$ be the mapping 
+\[
+(\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),
+\] 
+so that 
+\[
+\Phi_A^{-1}(0)= W(\pi_i,V^A).
+\]
+Then we show that $0$ is a regular value of $\Phi$, so that, by Proposition 4.2, $\Delta \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta$ then $0$ is a regular value of $\Phi_A.$ It then follows that
+\[
+\jac_{\xb}(\Phi_A) = \jac_{\xb}\left(f^A(x),\frac{\pa f^A(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(x)}{\pa X_n}\right)
+\]
+has full rank for all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$.
+\subsection{Proof of Theorem 6.1}
+Now, with $i \in \{1,\hdots,n\}$, let $\Phi$ be the mapping \[(\xb,A) \mapsto (f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,
+\frac{\partial f^A}{\partial X_n}(\xb))\] so that 
+\[
+\Phi^{-1}(0)= W(\pi_i,V^A).
+\]
 %
 \begin{proposition} 
-$\bz$ is a regular value of $\Phi_i$.
+0 is a regular value of $\Phi$.
 \end{proposition}
@@
 \begin{proof}
-Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that 
-$f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=\bz.$
-We want to show that the Jacobian of the system of polynomials 
-\[
-f(A\xb),(\grad(f)\cdot A_{i+1})(A\xb),\hdots, (\grad(f)\cdot A_n)(A\xb)
-\]
-at $(\xb,A)$ has full rank, which holds if and only if the Jacobian of the system of polynomials 
-\[
-f,\grad(f)\cdot A_{i+1},\hdots, \grad(f)\cdot A_n
-\]
-at $(\xb,A)$ has full rank. Let $\Psi_i$ be the mapping
-%
-\begin{align*}
-    \Psi_i: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
+Put
+\[
+G_0 = f(Ax), 
+G_1 = \frac{\partial (f(Ax))}{\partial X_{i+1}},\hdots,G_{n-i} = \frac{\partial (f(Ax))}{\partial X_n},
+\] 
+and assume that $G_0(\xb,A)=G_1(\xb,A)=\hdots =G_{n-i}(\xb,A)=0.$ We can simplify by removing $Ax$ from the system because  
+\[
+(f(Ax),(\grad(f)\cdot 
+\bbm 
+a_{i+1,1} \\
+\vdots \\
+a_{i+1,n} 
+\ebm)(Ax),\hdots, 
+(\grad(f)\cdot 
+\bbm 
+a_{n,1} \\
+\vdots \\
+a_{n,n} 
+\ebm)(Ax)
+\] 
+defines a radical ideal of dimension ? whose variety is smooth if and only if 
+\[
+(f,\grad(f)\cdot 
+\bbm 
+a_{i+1,1} \\
+\vdots \\
+a_{i+1,n} 
+\ebm),\hdots, 
+\grad(f)\cdot 
+\bbm 
+a_{n1} \\
+\vdots \\
+a_{nn} 
+\ebm)
+\]
+defines a radical ideal of dimension ? whose variety is smooth. Now, let $g$ be the following:
+%
+\begin{align*}
+    g: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
        (\xb,A) &\mapsto 
        \left(f(\xb),\grad(f(\xb))\cdot 
-A_{i+1},\hdots
+A_{i+1},\hdots, 
 \grad(f(\xb))\cdot 
 A_{n}
-\right).
-\end{align*}
-%
-For all $(\xb,A) \in \Psi_i^{-1}(0),$ the Jacobian matrix of $\Psi_i$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
-\[
-F_j = \frac{\pa f}{\pa X_1} a_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+j,n}, ~1 \leq j \leq n-i,
-\]
-so that the Jacobian is equal to
+\right)
+\end{align*}
+%
+I claim that for all $(\xb,A) \in g^{-1}(0),$ the Jacobian matrix of $g$ at $(\xb,A)$ has full rank $n-i+1$ (i.e. $g$ is transverse to $\{0\}).$ The Jacobian of 
+%
+\begin{align*}
+       & \left(f,\grad(f)\cdot 
+\bbm 
+a_{i+1,1} \\
+\vdots \\
+a_{i+1,n} 
+\ebm,\hdots, 
+\grad(f)\cdot 
+\bbm 
+a_{n,1} \\
+\vdots \\
+a_{n,n} 
+\ebm\right) \\
+&= \left(f, \frac{\pa f}{\pa X_1} a_{i+1,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+1,n}, \hdots, \frac{\pa f}{\pa X_1} a_{n,1} + \hdots + \frac{\pa f}{\pa X_n}a_{n,n}\right) \\
+&= (f,F_{1},\hdots,F_{n-i}),  
+\end{align*} 
+%
+where 
+\[
+F_j = \frac{\pa f}{\pa X_1} a_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+j,n}, 1 \leq j \leq n-i,\]
+is
 \[
@@
 \] 
-Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
+Since $f$ is square-free, \[I(V(f)) = \langle f \rangle,\]  and thus for all $\xb \in V(f)$, 
 \[
@@
 At least one partial of $f$ must be non-zero.
-Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
+Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i$ rows, the matrix has full rank $n-i$.
 \end{proof}
 %
-Since $\deg \Phi_i \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $D^{n+(n-i+1)}=D^{2n-i+1}\leq D^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
-%
-\[
- \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
-\]
-has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}.
-Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
-\[
-\Delta_1 := \bigcup_{i=1}^n \Xi_i,
-\]
-where we have the following bound on the degree which proves the claim:
-\[
-\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq D^{2n^2}.
-\] 
+Since $\deg \Phi \leq D,$ it follows by Theorem 4.2 that a hypersurface $\Delta \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta,$ then $0$ is a regular value of $\Phi_{A}$, which means that
+\[
+\jac_\textit{\textbf{x}} \Phi_A 
+= \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
+\] 
+has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?).
+Therefore, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$, for each $i \in \{1,\hdots,n\}.$
 %
@@
 %
-\subsection{Sketch of the proof of Theorem 6.1}
+\subsection{Sketch of the proof of Theorem 7.1}
 %
@@
 \[
-\mathbb{Q}(\frak{A})[\textit{\textbf{X}}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textit{\textbf{X}}]/\fp_l^{\A}
+\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\Xb]/\fp_l^{\A}
 \] 
@@
 \[
-\mathbb{Q}(\frak{A})[\textit{\textbf{X}}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textit{\textbf{X}}]/\I^{\A}
+\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\Xb]/\I^{\A}
 \] 
@@
 \[
-\overline{P_{j}} := d_jP_{j}\in \Q[\A][\textit{\textbf{X}}],
+\overline{P_{j}} := d_jP_{j}\in \Q[\A][\Xb],
 \]
@@
 \begin{align*}
-\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},T)g_l + B_j(\A,\textit{\textbf{X}},T)(1-\pjb T), \\ g_l \in 
+\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,T)g_l + B_j(\A,\Xb,T)(1-\pjb T), \\ g_l \in 
 \left\{ 
@@
 \[
-\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},1/\pjb)g_l + 0
+\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l + 0
 \]
@@
 \begin{align*}
-A_{j,l}(\A,\textit{\textbf{X}},1/\pjb) 
+A_{j,l}(\A,\Xb,1/\pjb) 
 &= \sum_{i=1}^{n_l} A_{j,l,i}(\A,\Xb,1/\pjb)\\
-&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\textit{\textbf{X}}), ~k_i \in \mathbb{Z}.
+&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\Xb), ~k_i \in \mathbb{Z}.
 \end{align*}
@@
 \begin{align*}
-    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\textit{\textbf{X}},1/\pjb)g_l\right)\\
+    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l\right)\\
     &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{i}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb].
@@
 %
-\subsection{Proof of Theorem 7.1}
+\subsection{Proof of Theorem 8.1}
 %
@@
 %
-Recall Theorem 3.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
-Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$}
-%
-\begin{proof}
-Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
-Clearly then, if
-\[
-A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
-\]
-then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
-\[
-\Delta = \prod_{i=1}^3 \D_i,
-\]
-and note that 
-\[
-\deg \D \leq  \prod_{i=1}^3 \deg \D_i.
-\]
-\end{proof}
-%
-Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
-Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
-%
-\begin{proof}
-\[
-Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
-\]
-\end{proof}
-%
-%
-%
-%
-\section{Bit complexity}
-%
-Recall Theorem 1.1: \textit{Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1/2$.
-Otherwise the algorithm either produces a subset of the points or FAIL.
-In any case, the algorithm uses
-\[
-O^{\sim}(nk(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
-\]
-boolean operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
-\[
-O^{\sim}((s+D)D^n + nD^n).
-\]
-}
-Recall as well that the algorithm can error on one side by producing a proper subset of the points.
-Running the algorithm $\kt$ times gives a list of $n$ zero-dimensional parameterizations, among which the highest cardinality output includes at least one point in each connected component with probability at least $1-(1/2)^{\kt}.$
-%
-\subsection{The Algorithm}
-%
-For a matrix $A \in \GL(n,\Q),$ let 
-\[
-Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
-\]
-where $b_i$ is the i-th row of $A^{-1}$.
-%
-\begin{algorithm}[hbt!]
-\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $D=\deg(f)$}
-\KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \epsilon^{-1}D^{\td}$, where $\epsilon < 5/21$\;
-\nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
-\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
-    \caption{{Main Algorithm} \label{}}
-\nl \For{$i\gets1$ \KwTo $n$}{
-\nl Randomly choose a point $p_{i-1}=(x_1,\hdots,x_{i-1}) \in \Q^{i-1}~(p_0$?)\; 
-\nl Run \cite[Algorithm 2]{SH} $k > -\lg(1-2^{(-1/n)})$ times with input 
-$\{Y_1-x_1,\hdots,Y_{i-1}-x_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } D$\;
-\nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 6 \;
-} 
-\nl \Return $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$.
-\end{algorithm}
- \clearpage
-%
-\subsection{Proof of Theorem 1.1}
-%
-\textbf{The boolean cost:} The following lists the costs for each step of Algorithm 1:
-%
-\begin{enumerate}
-    \item By our assumption on the size of $S$ we know that $|S| = \log (\epsilon^{-1}D^{\td}) \leq \td.$ Thus for $a_{ij} \in S$ we know that $|a_{ij}| \leq \td.$
-    \item 
-    \begin{enumerate}[label=\roman*.]
-        \item $O(L)$ operations are required to compute $f$ from its straight line program $\Gamma.$
-        \item After applying the change of variables obtaining $f(A x)=f^A(x)$ the height grows at most by a factor of
-        \begin{align*}
-        \log(n!\cdot \max_{\frac{1\leq i\leq n}{1\leq j\leq n}}\{a_{ij}\}) &= 
-        O(n\log n + n\log(D+1)) \\
-        &= 
-        O^\sim(\log(D+1)).
-        \end{align*}
-    \end{enumerate}
-    \item After computing the partial derivatives the height grows by at most another factor of $\log D$.
-Furthermore, preparing the straight line program for the gradient of $f$ does not introduce large integers.
-The integers in $\grad (f)$ are of the same magnitude as in $\Gamma$.
-    \item 
-    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the following upper bound on the total boolean cost of the algorithm:
-    \[
-    O^\sim(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4))),
-    \]
-    where it also follows from \cite[Algorithm 2]{SH} that the polynomials in the output have degree at most $D^n,$ and height at most
-    \[
-    O^{\sim}((s+D)D^n + nD^n).
-    \]
-\end{enumerate}
-%
-\par \noindent 
-\textbf{Probability of success:} Note that when $\epsilon < 5/21$ (as stated in step 1 of Algorithm 1), then
-\[
-\pr[A \not \in \D] = 1-\epsilon > \frac{16}{21},
-\]
-so that after a single run of \cite[Algorithm 2]{SH}, the probability of success (ensuring all genericity properties and obtaining all points) is at least 
-\[
-\left( \frac{16}{21} \right) \left( \frac{21}{32} \right) = \frac{1}{2}.
-\]
-Thus, running \cite[Algorithm 2]{SH} $k$ times gives a list of outputs among which the highest cardinality set includes all points with probability at least $1-(1/2)^k$.
-We repeat this $n$ times to obtain $n$ zero-dimensional parameterizations.
-Thus, the probability that we have every point in each parameterization is $(1-(1/2)^k)^n$.
-We want
-\[
-(1-(1/2)^k)^n>\frac{1}{2},
-\]
-which holds if and only if 
-\[
-k > -\lg(1-2^{(-1/n)}),
-\]
-thus proving Theorem 1.1.
-We can boost our success probability by running the main algorithm $\kt$ times, so that we obtain parameterizations whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1 - (1/2)^{\kt}$.
+Assume that $f\in \Q[X_1,\hdots,X_n]$ satisfies $\textbf{H}.$
+%
+%
+%
+%
+\section{Proof of Theorem 1.1}
+%
+%
+
 %%

### 2020-02-04 main.tex
typo

--- 2020-02-04 main.tex
@@
-%%
-%% This is file `sample-xelatex.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigconf')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-xelatex.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
 \documentclass[sigconf]{acmart}
@@
 % packages 
-%\usepackage[options ]{algorithm2e}
 \usepackage[ruled,vlined]{algorithm2e}
-%\usepackage{algorithm,algpseudocode,float}
 \usepackage{mathrsfs}
@@
 \def\Q{\mathbb{Q}}
+\def\ZZ{\mathbb{Z}}
 \def\R{\mathbb{R}}
@@
 
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{Real algebraic geometry, transversality, Noether normalization, bit complexity}
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
+\setcounter{secnumdepth}{4}
+\renewcommand{\theparagraph}{\thesubsection.\arabic{paragraph}}
+\counterwithin{paragraph}{subsection} % makes paragraph depend on subsection
+\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries}{\theparagraph.}{1em}{}
+\titlespacing*{\paragraph}{0em}{1ex}{1em}
+\newcommand{\pref}[1]{{\bf\ref{#1}}}
+
+\keywords{Real algebraic geometry, transversality, Noether
+  normalization, bit complexity}
+
 \maketitle
-%
-%
-%
-%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
-%
-\subsection{Problem statement}
-%
-Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
-We provide bit-complexity estimates for computing one point in each connected component of $V(f)\cap \R^n.$ Its bit complexity is $\hdots$.
-%
-\subsection{Motivation}
-%
-\subsubsection{Applications}
-%
-Computing one point in each connected component of the real part of a hypersurface is a basic and important subroutine used in semi-algebraic geometry.
-For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface, and it is used in determining whether or not a complex hypersurface has real solutions.
-
-\subsubsection{Bit-complexity}
+
+\paragraph*{Background and problem statement.}
+Computing one point in each connected component of a real algebraic
+set $S$ is a basic subroutine in real alebraic and semi-algebraic
+geometry; it is also useful in its own right, since it allows one to
+decide if $S$ is empty or not. In this paper, we consider only the
+case where $S$ is given as $S=V \cap \R^n$, where $V=V(f) \subset
+\C^n$ is a complex hypersurface defined by a squarefree polynomial $f
+\in \ZZ[X_1,\dots,X_n]$.
+
+Algorithms for this task have been known for decades, and their
+complexity is to some extent well understood. Suppose that $f$ has
+degree $d$, and coefficients of bit-size $h$. Without making any
+assumption on $f$, the algorithm given
+in~\cite[Section~13.1]{BaPoRo03} solves our problem using $d^{O(n)}$
+operations in $\Q$; in addition, the output of the algorithm is
+represented by polynomials of degree $d^{O(n)}$, with coefficients of
+bit-size $hd^{O(n)}$.  The key idea behind this algorithm goes back
+to~\cite{GrVo88}: sample points are found through the computation of
+critical points of well-chosen functions on $V(f)$.
+
+The number of connected components of $V(f)$ admits the lower bound
+$d^{\Omega(n)}$, so up to polynomial factors, this result is
+optimal. However, due to the generality of the algorithm, the constant
+hidden in the exponent $O(n)$ in its runtime turns out to be rather
+large: the algorithm relies on infinitesimal deformations, that affect
+runtime non-trivially.
+
+In this paper, we will work under the additional assumption that
+$V=V(f)$ is a {\em smooth} complex hypersurface. We place ourselves in
+the continuation of the line of work initiated by~\cite{BaGiHeMb97}:
+that reference deals with cases where $V$ is smooth and $V \cap \R^n$
+is compact, pointing out how {\em polar varieties} (that were
+introduced in the 1930's in order to define characteristic
+classes~\cite{Piene78,Teissier88}) can play a role in effective real
+geometry. This paper was extended in several directions: to $V$ being
+a smooth complete intersection, still with $V\cap \R^n$
+compact~\cite{BaGiHeMb01}, then without the compactness
+assumption~\cite{EMP,BaGiHePa05}; the smoothness assumption was then partly
+dropped in~\cite{BaGiHe14,BaGiHeLePa12}.
+
+The starting point in our paper is the algorithm in~\cite{EMP}. In the
+hypersurface case, its runtime is $d^{(4+o(1))n}$ operations in $\Q$;
+as with many results in this line of work, the algorithm is
+randomized: the algorithm needs to assume that we are in generic
+coordinates; this is done by applying a random change of coordinates
+prior to all computations. In addition, it relies on algorithms for
+solving systems of polynomial equations that are themselves
+randomized.  Altogether, this procedure chooses $n^{O(1)}$ random
+vectors, each of them in an affine space of dimension $n^{O(1)}$;
+every time a choice is made, failure corresponds to our chosen vector
+lying in a hypersurface of the parameter space.
+
+This paper revisits the algorithm in~\cite{EMP} (in the hypersurface
+case) and gives a complete analysis of its probality of success and
+its bit complexity.
+
+\paragraph*{Data structures.} As in references such
+as~\cite{GiHeMoPa95,GiHaHeMoMoPa97,GiHeMoMoPa98,BaGiHeMb97,EMP}, the
+input polynomial $f$ is given by means of a {\em straight-line
+  program}, that is, a sequence of operations $+,-,\times$ that
+evaluates $f$, on the input variables $X_1,\dots,X_n$; the {\em
+  length} of a straight-line program of such an objet is simply the
+number of operations it performs. Any polynomial of degree $d$ in $n$
+variables can be computed by a straight-line program of length $O\big
+({{d+n} \choose n}\big)$ (evaluate all monomials of degree up to $d$
+in $n$ variables, multiply them by their respective coefficients and
+sum the result). However, some inputs may be given by shorter
+straight-line program, and the algorithm is able to benefit from it.
+
+The output of the algorithm is a finite set in $\C^n$ defined over
+$\Q$. To represent it, we rely on a widely used data structure based
+on univariate
+polynomials~\cite{Kronecker82,Macaulay16,GiMo89,GiHeMoPa95,ABRW,GiHaHeMoMoPa97,GiHeMoMoPa98,Rouillier99}.
+Consider a zero-dimensional algebraic set $S \subset \C^n$ defined
+over $\Q$. A {\em zero-dimensional parametrization}
+$\scrQ=((q,v_1,\dots,v_n),\lambda)$ of $S$ consists in polynomials
+$(q,v_1,\dots,v_n)$, such that $q\in \Q[T]$ is monic and squarefree,
+all $v_i$'s are in $\Q[T]$ and satisfy $\deg(v_i) < \deg(q)$, and in a
+$\Q$-linear form $\lambda$ in variables $X_1,\dots,X_n$, such that
+\begin{itemize}
+\item $\lambda(v_1,\dots,v_N)=T q' \bmod q$, where $q'=\frac{\partial
+  q}{\partial T}$;
+\item we have the equality
+  $S=\left \{\left(
+      \frac{v_1(\tau)}{q'(\tau)},\dots,\frac{v_N(\tau)}{q'(\tau)}\right
+    ) \ \mid \ q(\tau)=0 \right \}.$
+\end{itemize}
+The constraint on $\lambda$ says that the roots of $q$ are the values
+taken by $\lambda$ on $S$. The parametrization of the coordinates by
+rational functions having $q'$ as a denominator goes back
+to~\cite{Kronecker82,Macaulay16}: as pointed out in~\cite{ABRW}, it
+allows one to control precisely the size of the coefficients of
+$v_1,\dots,v_n$.
+
+\paragraph*{Main result.} To state our main result, we need to define 
+the {\em height} of rationals, and polynomials with rational
+coefficients.
+
+The {\em height} of a non-zero rational $a=u/v$ is the maximum of
+$\ln(|u|)$ and $\ln(|v|),$ where $u \in \mathbb{Z}$ and $v \in
+\mathbb{N}$ are coprime. For a polynomial $f$ with rational
+coefficients, if $v \in \mathbb N$ is the minimal common denominator
+of all non-zero coefficients of $f$, then the \textit{height}
+$\htt(f)$ of $f$ is defined as the maximum of the logarithms of $v$
+and of the absolute values of the coefficients of $vf$.
+
+\begin{theorem}
+Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree and satisfies $\deg
+f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a
+straight-line program $\Gamma$ of size $L$ with integer constants of
+height at most $b.$ There exists a randomized algorithm that takes
+$\Gamma, d,$ and $s$ as input and produces a zero-dimensional
+parameterization of a set that contains at least one point in each
+connected component of $V(f) \cap \R^n$ with probability at least
+$1/2$. Otherwise the algorithm either produces a subset of the points
+or FAIL. In any case, the algorithm uses
+\[
+O^{\sim}(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
+\]
+bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
+\[
+O^{\sim}((s+D)D^n + nD^n).
+\]
+\end{theorem}
+
 Algorithms for deciding connectivity queries in real algebraic geometry
@@
 operations require on a standard computer in terms of the length of a
-standard representation (accounting for coefficient size, etc.).  In
-particular, we assume that an integer $a\in\ZZ$ is represented with
-$O(\log|a|)$ bits, and operations on integers with $\ell$ bits require
-$\softO(\ell)$ bit operations.
-
-\subsubsection{Quantitative genericity statements}
-%
-\subsection{Main result}
-%
-\begin{theorem}
-Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1/2$.
-Otherwise the algorithm either produces a subset of the points or FAIL.
-In any case, the algorithm uses
-\[
-O^{\sim}(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
-\]
-bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
-\[
-O^{\sim}((s+D)D^n + nD^n).
-\]
-\end{theorem}
-%
-The algorithm can error on one side by producing a proper subset of the points.
-Running the algorithm $\kt$ times gives a list of $n$ zero-dimensional parameterizations, among which the highest cardinality output includes at least one point in each connected component with probability at least $1-(1/2)^{\kt}.$
-%
-%
-%
-%
-\section{Notation and preliminaries}
-%
-\subsection{Algebraic sets}
-%
+standard representation (accounting for coefficient size, etc.). See below
+for formal definitions.
+
+The algorithm is Monte Carlo and can error on one side by producing a
+proper subset of the points. Running the algorithm $k$ times gives a
+list of outputs among which the highest cardinality set includes at
+least one point in each connected component with probability at least
+$\hdots.$
+
 An \textit{algebraic set} $V \subset \C^n$ is the set of common zeros of a set of polynomials $\textit{\textbf{f}}=(f_1,\hdots,f_s)$ in $\C[X_1,\hdots,X_n].$
-\subsubsection{Dimension and degree}
+
 The \textit{dimension} of an algebraic set $V \subset \C^n$, denoted $\dim V,$ can be defined in the following ways:
@@
 \section{Proof of $\textbf{H}_i'(7)$}
-%
-%% <<<<<<< HEAD
-%% Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i'(1),\textbf{H}_i'(2),$ and $\textbf{H}_i'(3).$ Throughout this section, for simplicity let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ To increase readability and simplify notation, we often do not specify $i$, as it is fixed.
-%% \subsection{Sketch of the proof}
-%% Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ be squarefree with total degree $D$ and $V(f)$ smooth.
-For $i \in \{1,\hdots,n\}$, recall $\textbf{H}_i'(4):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
-%% =======
 Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, to simplify notation, let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore, throughout this section, consider that $i \in \{1,\hdots,n\}$ is fixed.
@@
 \]
-%% <<<<<<< HEAD
-%% is integral, and thus $V(\I^A)=W^\A$ is in Noether position for $\pi_{i-1}.$ Therefore, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(4)$.
-%% =======
+
 is integral.
-%% >>>>>>> f9eb2445ca6e153d1e49c3d2767097d331dbcbee
 %

### 2020-02-04 main.tex
typo
intro

@@
 \def\Q{\mathbb{Q}}
-\def\ZZ{\mathbb{Z}}
 \def\R{\mathbb{R}}
@@
 geometry; it is also useful in its own right, since it allows one to
-decide if $S$ is empty or not. In this paper, we consider only the
-case where $S$ is given as $S=V \cap \R^n$, where $V=V(f) \subset
-\C^n$ is a complex hypersurface defined by a squarefree polynomial $f
-\in \ZZ[X_1,\dots,X_n]$.
-
+decide if $S$ is empty or not.
+
+In this paper, we consider the case where $S$ is given as $S=V \cap
+\R^n$, where $V=V(f) \subset \C^n$ is a complex hypersurface defined
+by a squarefree polynomial $f \in \ZZ[X_1,\dots,X_n]$.
 Algorithms for this task have been known for decades, and their
@@
 
-The starting point in our paper is the algorithm in~\cite{EMP}. In the
-hypersurface case, its runtime is $d^{(4+o(1))n}$ operations in $\Q$;
-as with many results in this line of work, the algorithm is
-randomized: the algorithm needs to assume that we are in generic
-coordinates; this is done by applying a random change of coordinates
-prior to all computations. In addition, it relies on algorithms for
-solving systems of polynomial equations that are themselves
-randomized.  Altogether, this procedure chooses $n^{O(1)}$ random
-vectors, each of them in an affine space of dimension $n^{O(1)}$;
-every time a choice is made, failure corresponds to our chosen vector
-lying in a hypersurface of the parameter space.
-
-This paper revisits the algorithm in~\cite{EMP} (in the hypersurface
-case) and gives a complete analysis of its probality of success and
-its bit complexity.
+Our starting point is the algorithm in~\cite{EMP}. In the hypersurface
+case, its runtime is $d^{(4+o(1))n}$ operations in $\Q$.  As with many
+results in this vein, the algorithm is randomized: we need to assume
+that we are in generic coordinates; this is done by applying a random
+change of coordinates prior to all computations. In addition, the
+algorithm relies on procedures for solving systems of polynomial
+equations that are themselves randomized.  Altogether, we choose
+$n^{O(1)}$ random vectors, each of them in an affine space of
+dimension $n^{O(1)}$; every time a choice is made, there exists a
+hypersurface of the parameter space that one has to avoid in order to
+guarantee success. In this paper, we revisit this algorithm and give a
+complete analysis of its probality of success and its bit complexity.
 
@@
 input polynomial $f$ is given by means of a {\em straight-line
-  program}, that is, a sequence of operations $+,-,\times$ that
-evaluates $f$, on the input variables $X_1,\dots,X_n$; the {\em
-  length} of a straight-line program of such an objet is simply the
-number of operations it performs. Any polynomial of degree $d$ in $n$
-variables can be computed by a straight-line program of length $O\big
-({{d+n} \choose n}\big)$ (evaluate all monomials of degree up to $d$
-in $n$ variables, multiply them by their respective coefficients and
-sum the result). However, some inputs may be given by shorter
-straight-line program, and the algorithm is able to benefit from it.
-
-The output of the algorithm is a finite set in $\C^n$ defined over
-$\Q$. To represent it, we rely on a widely used data structure based
-on univariate
+  program}, that is, a sequence of operations $+,-,\times$ that takes
+as input $X_1,\dots,X_n$ and evaluates $f$; the {\em length} of a
+straight-line program is simply the number of operations it performs.
+
+Any polynomial of degree $d$ in $n$ variables can be computed by a
+straight-line program of length $O\big ({{d+n} \choose n}\big)$:
+evaluate all monomials of degree up to $d$ in $n$ variables, multiply
+them by their respective coefficients and sum the result. However,
+some inputs may be given by shorter straight-line program, and the
+algorithm is able to benefit from it.
+
+The output of the algorithm is a finite set in $\overline{\Q}{}^n$. To
+represent it, we rely on a widely used data structure based on
+univariate
 polynomials~\cite{Kronecker82,Macaulay16,GiMo89,GiHeMoPa95,ABRW,GiHaHeMoMoPa97,GiHeMoMoPa98,Rouillier99}.
@@
 \begin{itemize}
-\item $\lambda(v_1,\dots,v_N)=T q' \bmod q$, where $q'=\frac{\partial
-  q}{\partial T}$;
+\item $\lambda(v_1,\dots,v_n)=T q' \bmod q$;
 \item we have the equality
   $S=\left \{\left(
-      \frac{v_1(\tau)}{q'(\tau)},\dots,\frac{v_N(\tau)}{q'(\tau)}\right
+      \frac{v_1(\tau)}{q'(\tau)},\dots,\frac{v_n(\tau)}{q'(\tau)}\right
     ) \ \mid \ q(\tau)=0 \right \}.$
@@
 \paragraph*{Main result.} To state our main result, we need to define 
-the {\em height} of rationals, and polynomials with rational
-coefficients.
-
-The {\em height} of a non-zero rational $a=u/v$ is the maximum of
-$\ln(|u|)$ and $\ln(|v|),$ where $u \in \mathbb{Z}$ and $v \in
+the {\em height} of a rational number, and of a polynomial with
+rational coefficients.
+
+The {\em height} of a non-zero $a=u/v \in \Q$ is the maximum of
+$\ln(|u|)$ and $\ln(v),$ where $u \in \mathbb{Z}$ and $v \in
 \mathbb{N}$ are coprime. For a polynomial $f$ with rational
@@
 \begin{theorem}
-Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree and satisfies $\deg
-f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a
-straight-line program $\Gamma$ of size $L$ with integer constants of
-height at most $b.$ There exists a randomized algorithm that takes
-$\Gamma, d,$ and $s$ as input and produces a zero-dimensional
-parameterization of a set that contains at least one point in each
-connected component of $V(f) \cap \R^n$ with probability at least
-$1/2$. Otherwise the algorithm either produces a subset of the points
-or FAIL. In any case, the algorithm uses
-\[
-O^{\sim}(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
-\]
-bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
-\[
-O^{\sim}((s+D)D^n + nD^n).
-\]
+  Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
+  $\deg(f) \leq d, \htt(f) \leq s$, and that $V(f) \subset \C^n$ is
+  smooth.  Assume also that $f$ is given by a straight-line program
+  $\Gamma$ of size $L$ with integer constants of height at most $b.$
+
+  There exists a randomized algorithm that takes $\Gamma, d,$ and $s$
+  as input and produces a zero-dimensional parameterization of a set
+  that contains at least one point in each connected component of
+  $V(f) \cap \R^n$ with probability at least $1/2$. Otherwise the
+  algorithm either produces a subset of the points or FAIL. In any
+  case, the algorithm uses
+  \[
+  O^{\sim}(k(Lb+d^{2n}(s+d)(L+d)))
+  \]
+  bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in
+  the output have degree at most $d^n,$ and height $
+  O^{\sim}((s+d)d^n).$
 \end{theorem}
-
-Algorithms for deciding connectivity queries in real algebraic geometry
-have been developed in a series of papers
-\cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}. However,
-these algorithms are based in the arithmetic complexity model, and bit
-complexity questions have been left for future work. As bit complexity
-provides a far more realistic model of computation compared to arithmetic
-complexity,  which only counts each operation at unit cost and does not
-account for coefficient size, our results therefore address an important
-missing aspect of previous research.
-
-Note that by the bit complexity we mean to count the number of all machine
-operations require on a standard computer in terms of the length of a
-standard representation (accounting for coefficient size, etc.). See below
-for formal definitions.
-
-The algorithm is Monte Carlo and can error on one side by producing a
-proper subset of the points. Running the algorithm $k$ times gives a
-list of outputs among which the highest cardinality set includes at
-least one point in each connected component with probability at least
-$\hdots.$
-
-An \textit{algebraic set} $V \subset \C^n$ is the set of common zeros of a set of polynomials $\textit{\textbf{f}}=(f_1,\hdots,f_s)$ in $\C[X_1,\hdots,X_n].$
-
-The \textit{dimension} of an algebraic set $V \subset \C^n$, denoted $\dim V,$ can be defined in the following ways:
-%
-\begin{enumerate}
-    \item The number of generic hyperplanes needed to intersect with $V$ to obtain a finite set. 
-    \item The Krull Dimension of $\C[X_1,\hdots,X_n]/I(V)$.
-\end{enumerate}
-%
-The \textit{codimension} of $V$ is $n - \dim V$.
+The algorithm itself is rather simple. To describe it, we need to
+define {\em polar varieties}, which will play a crucial role in this
+paper. Let $V=V(f)$, for $f$ as in the theorem. For $i \in
+\{1,\hdots,n-1\},$ denote by $\pi_i:\C^n \rightarrow \C^i$ the
+projection $(x_1,\hdots,x_n) \mapsto (x_1,\hdots,x_i)$.  The $i$-th
+\textit{polar variety} \[W(\pi_i,V) := \{\xb \in V~|~\dim \pi_i(T_\xb
+V) < i\}\] is the set of critical points of $\pi_i$ on $V$.  It is
+thus defined by the vanishing of \[f,\frac{\pa f}{\pa
+  X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.\]
+
+In general, we cannot say much about the geometric properties of
+$W(\pi_i,V)$, but if we apply a generic change of coordinates $\bm A$,
+$W(\pi_i,V)$ is then known to be equidimensional of dimension $(i-1)$
+or empty~\cite{BaGiHeMb97}, and to be in so-called {\em Noether
+  position}~\cite{EMP} (background notions in algebraic geometry are
+in~\cite{Mumford76,Shafarevich77,Eisenbud96}; we will recall key
+definitions). If this is case, it suffices to choose arbitrary
+$\alpha_1,\dots,\alpha_{n-1}$ in $\Q$, and solve the systems defined
+by
+\begin{equation}\label{eq:syst}
+X_1-\alpha_1,\dots,X_{i-1}-\alpha_{i-1}, f, \frac{\pa f}{\pa
+  X_{i+1}} ,\dots,\frac{\pa f}{\pa X_n},  
+\end{equation}
+for $i=1,\dots,n$.  They all admit finitely many solutions, and
+Theorem~2 in~\cite{EMP} proves that the union of their solution sets
+contains one point on each connected component of $V \cap \R^n$.
+
+Our main contribution is to analyse precisely what conditions on our
+change of coordinates $\bm A$ guarantee success. This is done by
+revisiting the key ingredients in the proofs given
+in~\cite{BaGiHeMb97} and~\cite{EMP} and giving quantitative versions
+of these results, bounding the degree of the hypersurfaces we have to
+avoid.  To solve the equations~\eqref{eq:syst}, we use the algorithm
+in~\cite{SH}, for which a complete bit complexity analysis is
+available.
+
+This work should be seen as a first step toward the analysis of
+randomized algorithms in real algebraic geometry. An immediate
+follow-up question would be to handle the case of algebraic sets
+defined by {\em regular sequences}: the algorithm in~\cite{EMP} still
+applies, but the modifications needed would take us to far for the
+current format. Further yet, randomized algorithms for deciding {\em
+  connectivity queries} on smooth, compact algebraic sets have been
+developed in a series of papers
+\cite{SchostMohabBabySteps2011,SchostMohabBabySteps2014}, and could be
+revisited using the techniques introduced here.
+
+%% The \textit{dimension} of an algebraic set $V \subset \C^n$, denoted $\dim V,$ can be defined in the following ways:
+%% %
+%% \begin{enumerate}
+%%     \item The number of generic hyperplanes needed to intersect with $V$ to obtain a finite set. 
+%%     \item The Krull Dimension of $\C[X_1,\hdots,X_n]/I(V)$.
+%% \end{enumerate}
+%% %
+%% The \textit{codimension} of $V$ is $n - \dim V$.
 An algebraic set is \textit{equidimensional} if each irreducible component has the same dimension.
 If each component has dimension $d$ then we say it is $d-$equidimensional.
-The \textit{degree} of an algebraic set is the number of intersection points between itself and $\dim V$ generic hyperplanes.
-%
-\begin{example} 
-An algebraic set of dimension zero is a finite set, with degree equal to its cardinality.
-\end{example}
-%
-\begin{example}
-An algebraic set of dimension 1 is a curve, with degree equal to the number of intersection points with a generic hyperplane.
-\end{example}
-%
-%
-%
-\subsection{Critical / singular points}
-%
-\subsubsection{Regular and singular points of varieties}
-%
-Let $V \subset \C^n$ be a $d$-equidimensional algebraic set. 
-The point $x \in V$ is a \textit{regular point} if $\dim (T_xV) = d.$ Otherwise $x$ is a \textit{singular point}.
-We let $\reg(V)$ and $\sing(V)$ respectively denote the regular and singular points of $V$.
-\par 
-We assume that $V$ is smooth so that $V=\reg(V).$
-%
-\subsubsection{Critical points of polynomial mappings}
-%
-Let $\phi : V \rightarrow \C^m$ be a polynomial mapping.
+%% The \textit{degree} of an algebraic set is the number of intersection points between itself and $\dim V$ generic hyperplanes.
+%% %
+%% \begin{example} 
+%% An algebraic set of dimension zero is a finite set, with degree equal to its cardinality.
+%% \end{example}
+%% %
+%% \begin{example}
+%% An algebraic set of dimension 1 is a curve, with degree equal to the number of intersection points with a generic hyperplane.
+%% \end{example}
+%% %
+%% %
+%% %
+
+%% Let $V \subset \C^n$ be a $d$-equidimensional algebraic set.  The
+%% point $x \in V$ is a \textit{regular point} if $\dim (T_xV) = d.$
+%% Otherwise $x$ is a \textit{singular point}. We let $\reg(V)$ and
+%% $\sing(V)$ respectively denote the regular and singular points of $V$.
+
+%% %
+%% \subsubsection{Critical points of polynomial mappings}
+%% %
+%% Let $\phi : V \rightarrow \C^m$ be a polynomial mapping.
 A \textit{critical point} of $\phi$ is a regular point of $V$ with $d_x \phi(T_xV) \not = \C^m,$ where $d_x \phi$ is the differential of $\phi$ at $x.$ A \textit{critical} value of $\phi$ is the image of a critical point by $\phi$.
-%
-\subsection{The zariski-tangent space}
-%
-Denote by $\grad_{\xb}(f)$ the evaluation of the gradient vector of $f$ in $\C[X_1,\hdots,X_n]$ at $\textit{\textbf{x}}$ in $\C$.
-The \textit{Zariski-tangent space} to $V$ at $\textit{\textbf{x}} \in V$ is the vector space $T_{\xb}V$ defined by the equations $\grad_{\xb}(f) \cdot \textit{\textbf{v}}=0$ for all polynomials $f$ that vanish on $V$.
+%% %
+%% \subsection{The zariski-tangent space}
+%% %
+%% Denote by $\grad_{\xb}(f)$ the evaluation of the gradient vector of $f$ in $\C[X_1,\hdots,X_n]$ at $\xb$ in $\C$.
+%% The \textit{Zariski-tangent space} to $V$ at $\xb \in V$ is the vector space $T_{\xb}V$ defined by the equations $\grad_{\xb}(f) \cdot \textit{\textbf{v}}=0$ for all polynomials $f$ that vanish on $V$.
 For a polynomial system $\textit{\textbf{f}}=(f_1,\hdots,f_N)$ in $\C[X_1,\hdots,X_n]$, denote by $\jac(\textit{\textbf{f}})$ the Jacobian matrix.
-The following is a direct consequence of \cite[Corollary 16.20]{ECA}.
-%
-\begin{proposition}
-If $V \subset \C^n$ is a $d$-equidimensional algebraic set with ideal $I(V)=\langle f_1,\hdots,f_N \rangle$, then at any point $\textbf{x}$ of $\reg(V),$ $\jac_\textbf{x}(\textbf{f})$ has full rank $n - \dim(V)$ and the kernel of $\jac_\textbf{x}(\textbf{f})$ is equal to $T_\textbf{x}V.$
-\end{proposition}
-%
-\subsection{Polar varieties}
-%
-Let $V\subset \C^n$ be a smooth $d$-equidimensional variety. For $i \in \{1,\hdots,d\},$ denote by $\pi_i:\C^n \rightarrow \C^i$ the projection
-$(x_1,\hdots,x_n) \mapsto  (x_1,\hdots,x_i)$.
-A \textit{critical point} $\textit{\textbf{x}}$ in $V$ is a singular point on $\pi_i.$ In other words, the point $\textit{\textbf{x}} \in V$ is a critical point if $\dim \pi_i( T_\textit{\textbf{x}}V) < i$.
-The $i$-th  \textit{polar variety} \[W(\pi_i,V) := \{\textit{\textbf{x}} \in V~|~\dim \pi_i(T_xV) < i\}\] is the set of critical points of $\pi_i$ on $V$.
-Denote by $\I$ the ideal \[\frak{I}(\pi_i,V) := I(W(\pi_i,V)).\]
-%
-\begin{proposition} 
-Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ squarefree with $V(f)$ smooth.
-Then, for $i \in \{1,\hdots,n\}$, the polar variety $W(\pi_i,V)$ is defined by the vanishing of \[f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.\]
-\end{proposition}
-%
-\begin{proof}
-We have a proof but maybe we should reference it?
-\end{proof}
-%
-\subsection{Changes of variables}
-%
-Consider $A \in \C^{n^2}, f \in \C[X_1,\hdots,X_n], \textit{\textbf{x}} \in \mathbb{C}^n,$ and $V \subset \C^n$. We denote by 
+%% The following is a direct consequence of \cite[Corollary 16.20]{ECA}.
+%% %
+%% \begin{proposition}
+%% If $V \subset \C^n$ is a $d$-equidimensional algebraic set with ideal $I(V)=\langle f_1,\hdots,f_N \rangle$, then at any point $\textbf{x}$ of $\reg(V),$ $\jac_\textbf{x}(\textbf{f})$ has full rank $n - \dim(V)$ and the kernel of $\jac_\textbf{x}(\textbf{f})$ is equal to $T_\textbf{x}V.$
+%% \end{proposition}
+%% %
+%% \subsection{Polar varieties}
+%% %
+%% %
+%% \subsection{Changes of variables}
+%
+Consider $A \in \C^{n^2}, f \in \C[X_1,\hdots,X_n], \xb \in \mathbb{C}^n,$ and $V \subset \C^n$. We denote by 
 $V^A$ the set $\{x^A~|~\xb \in V\}, f^A$ the polynomial $f(A \xb)$ and $\xb^A$ denotes $A^{-1}\xb$. Notice $f^A(\xb^A) = f(A A^{-1}\xb)=f(\xb).$
@@
 \[
-\frak{Z}' := \overline{\frak{Z} - \{(\textit{\textbf{x}},\thetab,0,\hdots,0) \in \C^{n+\dt+m}~|~(\textit{\textbf{x}},\thetab,0\hdots,0) \in \frak{Z}\}},
+\frak{Z}' := \overline{\frak{Z} - \{(\xb,\thetab,0,\hdots,0) \in \C^{n+\dt+m}~|~(\xb,\thetab,0\hdots,0) \in \frak{Z}\}},
 \]
@@
 \mu :~ \C^{n+\dt+m} &\rightarrow \C^{n+\dt}\\
-(\textit{\textbf{x}},\thetab,\bm \ell)~ &\mapsto (\textit{\textbf{x}},\thetab).
+(\xb,\thetab,\bm \ell)~ &\mapsto (\xb,\thetab).
 \end{align*}
@@
   implies that $(\xb,\thetab,\bm \ell)$ is in $\frak{Z} -
-  \{(\textit{\textbf{x}}',\thetab',0,\hdots,0) \in
-  \C^{n+\dt+m}~|~(\textit{\textbf{x}}',\thetab',0\hdots,0) \in
+  \{(\xb',\thetab',0,\hdots,0) \in
+  \C^{n+\dt+m}~|~(\xb',\thetab',0\hdots,0) \in
   \frak{Z}\}$, and thus in $\frak{Z}'$. This proves the inclusion
@@
 \end{algorithm}
- \clearpage
+
 %

### 2020-02-04 main.tex
Update main.tex
Some corrections

@@
 %
-Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ with total degree $D$.  
+Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ with total degree $d$.  
 We say that $f$ satisfies $\textbf{H}$ if 
@@
     \item $f$ is squarefree;
-    \item $V(f)$ is smooth.
+    \item $V(f) \cap \R^n$ is smooth.
 \end{enumerate}
 %
-An equidimensional algebraic set $X$ of dimension $d$ is in \textit{Noether position} for $\pi_d$ when the extension 
-\[
-\C[X_1,\hdots,X_d] \rightarrow \C[X_1,\hdots,X_n]/I(V)
-\] 
-is injective and integral.  Then, for any $\xb \in \C^d,$ the fiber 
-$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (x_1,\hdots,x_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
+An equidimensional algebraic set $X$ of dimension $r$ is in \textit{Noether position} for $\pi_r$ when the extension 
+\[
+\C[X_1,\hdots,X_r] \rightarrow \C[X_1,\hdots,X_n]/I(V)
+\] 
+is injective and integral.  Then, for any $\xb \in \C^r,$ the fiber 
+$V \cap \pi_r^{-1}(\xb)$ has dimension zero.
+For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (\alpha_1,\hdots,\alpha_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if
 %
@@
 \item $W(\pi_i,V)$ is smooth;
-\item $\langle X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
-\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
-\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
+\item $\langle X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
+\item $V(X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
+\item $V(X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
 \item either $W(\pi_i,V)$ is empty or in Noether position for $\pi_{i-1}$.
@@
 \begin{theorem}
-There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $D^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $d^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
 \end{theorem}
 %
-\subsection{Sketch of the proof of Theorem 5.1}
+\subsection{Sketch of the proof of Theorem 4.1}
 %
@@
 %
-\subsection{Proof of Theorem 5.1}
+\subsection{Proof of Theorem 4.1}
 %
@@
 %
-Since $\deg \Phi_i \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $D^{n+(n-i+1)}=D^{2n-i+1}\leq D^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
+Since $\deg \Phi_i \leq d,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $d^{n+(n-i+1)}=d^{2n-i+1}\leq d^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
 %
@@
 \[
+\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
+\] 
+%
+%
+%
+%
+\section{Proof of $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$}
+%
+\begin{theorem}
+There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
+\end{theorem}
+%
+\subsection{Sketch of the proof of Theorem 5.1}
+%
+Let $p_{n-1} = (x_1,\hdots,x_{n-1}) \in \Q^{n-1}$ be a randomly chosen point. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
+\[
+X_1(\xb)-x_1,\hdots,X_{i-1}(\xb)-x_{i-1}, f(\xb),  \frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}
+\]
+has full rank, at all points $(\xb,A) \in \C^n \times \C^{n^2}$ in the zero set of this system. It would then follow from Theorem 5.1 that a hypersurface  exists with the desired properties. 
+%
+\subsection{Proof of Theorem 5.1}
+%
+Let $\Phi_i$ be the mapping 
+%
+\begin{align*}
+    \Phi_i: \C^n \times \C^{i-1} &\rightarrow \C^{n} \\
+           (\xb,\alpha_1,\hdots,\alpha_{i-1}) &\mapsto 
+       (X_1(\xb)-\alpha_1,\hdots \\
+       \hdots &,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),\frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n} ).
+\end{align*}
+%
+\begin{proposition}
+$\bz$ is a regular value of $\Phi_i.$
+\end{proposition} 
+\begin{proof}
+For all $(\xb,A) \in \Phi_i^{-1}(0),$ the Jacobian matrix of $\Phi_i$ at $(\xb,A)$ has full rank $\td$. Indeed, the Jacobian is equal to
+\[
+\left[ 
+\begin{array}{cccccc}
+\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
+\frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
+\ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
+\frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
+\end{array}
+\right]. 
+\] 
+Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
+\[
+T_{\xb} V(f) = \textrm{Nullspace}(\grad_{\xb} f).
+\]
+Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes.
+At least one partial of $f$ must be non-zero.
+Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
+\end{proof}
+%
+Since $\deg \Phi_i \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $D^{n+(n-i+1)}=D^{2n-i+1}\leq D^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
+%
+\[
+ \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
+\]
+has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}.
+Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
+\[
+\Delta_1 := \bigcup_{i=1}^n \Xi_i,
+\]
+where we have the following bound on the degree which proves the claim:
+\[
 \deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq D^{2n^2}.
 \] 
-%
-%
-%
-%
-\section{Proof of $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$}
-%
-\begin{theorem}
-There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $D^{\textrm{?}}$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
-\end{theorem}
-%
-\subsection{Sketch of the proof of Theorem 6.1}
-%
-Let 
-\[
-Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
-\]
-where $b_i$ is the i-th row of $A^{-1}$. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
-\[
-Y_1(\xb),\hdots,Y_{i-1}(\xb), f(\xb),  \frac{\pa f(A\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(A\xb)}{\pa X_n}
-\]
-has full rank, at all points $\xb \in \C^n$ with 
-\[
-X_1(\xb)=\hdots,X_{i-1}(\xb)=f(\xb)= \frac{\pa f(xb)}{\pa X_{i+1}}=\hdots = \frac{\pa f(\xb)}{\pa X_{n}}=0.
-\]
-Then we could use Theorem 5.1 to obtain a hypersurface with the desired properties. Let $\Phi$ be the mapping 
-%
-\begin{align*}
-    \Phi: \C^n \times \C^{n^2} &\rightarrow \C^{n+1} \\
-           (\xb,A) &\mapsto 
-       (Y_1,\hdots,Y_i,f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots \\
-       \hdots&~,\grad(f(\xb))\cdot A_{n})),
-\end{align*}
-%
-We cannot directly define the appropriate polynomial mapping, as $Y_j(A\xb)$ is rational in $A^{-1}.$ To circumvent this issue, we can alternativly define a polynomial mapping $\Psi$ as  
-%
-\begin{align*}
-    \Psi: \C^n \times \C^{n^2} \times \C &\rightarrow \C^{n+2} \\
-           (\xb,A,T) &\mapsto 
-       (\Yt_1,\hdots,\Yt_i,f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots \\
-\hdots,\grad(f(\xb))\cdot A_{n}),&~T\cdot \det (A) - 1),
-\end{align*}
-%
-where $\Yt_j=TY_j$ with denominators cleared.
-Now, look at the points in $\Psi^{-1}(0).$ Here, $\det A \not = 0$ and therefore invertible, and therefore at all points in $\Psi^{-1}(0)$ the Jacobian matrix has full rank?
-%
-\begin{proposition}
-For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank (i.e. $\Psi$ is transverse to $\{0\}).$
-\end{proposition}
-%
-\begin{proof}
-\end{proof}
-%
-Thus, by Theorem 5.1, there exists a hypersurface $\Delta_2 \subset \C^{n^2}$, of degree at most $D^{n+1}$ with the property that if $A \in \C^{n^2}-\Delta_2$ then $\jac_{\xb}\Psi_A$ has full rank.
-$\hdots$ It then follows that for all $A \in \C^{n^2}-\Delta_2, \jac_{\xb}\Phi_A$ also has full rank.
-Therefore, by the Jacobian criterion, $f^A$ satisfies  $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
 %
@@
 \[
-\Delta = \prod_{i=1}^3 \D_i,
+\Delta = \bigcup_{i=1}^3 \D_i,
 \]
@@
 \[
-\deg \D \leq  \prod_{i=1}^3 \deg \D_i.
+\deg \D \leq  \sum_{i=1}^3 \deg \D_i.
 \]
@@
 %
-Recall Theorem 1.1: \textit{Suppose that $f\in\Q[X_1\hdots,X_n]$ is squarefree and satisfies $\deg f \leq D, \htt(f) \leq s,$ and assume that $f$ is given by a straight-line program $\Gamma$ of size $L$ with integer constants of height at most $b.$ There exists a randomized algorithm that takes $\Gamma, d,$ and $s$ as input and produces a zero-dimensional parameterization of a set that contains at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1/2$.
-Otherwise the algorithm either produces a subset of the points or FAIL.
-In any case, the algorithm uses
-\[
-O^{\sim}(nk(Lb+D^{2n}(s+D)(L+n^3D+n^4)))
-\]
-bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in the output have degree at most $D^n,$ and height at most
-\[
-O^{\sim}((s+D)D^n + nD^n).
-\]
-}
+Recall Theorem 1.1: Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
+  $\deg(f) \leq d, \htt(f) \leq s$, and that $V(f) \subset \C^n$ is
+  smooth.  Assume also that $f$ is given by a straight-line program
+  $\Gamma$ of size $L$ with integer constants of height at most $b.$
+
+  There exists a randomized algorithm that takes $\Gamma, d,$ and $s$
+  as input and produces a zero-dimensional parameterization of a set
+  that contains at least one point in each connected component of
+  $V(f) \cap \R^n$ with probability at least $1/2$. Otherwise the
+  algorithm either produces a subset of the points or FAIL. In any
+  case, the algorithm uses
+  \[
+  O^{\sim}(k(Lb+d^{2n}(s+d)(L+d)))
+  \]
+  bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in
+  the output have degree at most $d^n,$ and height $
+  O^{\sim}((s+d)d^n).$
+
 Recall as well that the algorithm can error on one side by producing a proper subset of the points.
@@
 \begin{algorithm}[hbt!]
-\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $D=\deg(f)$}
+\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
 \KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \epsilon^{-1}D^{\td}$, where $\epsilon < 5/21$\;
+\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \epsilon^{-1}d^{\td}$, where $\epsilon < 5/21$\;
 \nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
@@
     \caption{{Main Algorithm} \label{}}
+\nl Randomly choose a point $p_{n-1}=(\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}~(p_0$?)\; 
 \nl \For{$i\gets1$ \KwTo $n$}{
-\nl Randomly choose a point $p_{i-1}=(x_1,\hdots,x_{i-1}) \in \Q^{i-1}~(p_0$?)\; 
 \nl Run \cite[Algorithm 2]{SH} $k > -\lg(1-2^{(-1/n)})$ times with input 
-$\{Y_1-x_1,\hdots,Y_{i-1}-x_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } D$\;
+$\{Y_1-\alpha_1,\hdots,Y_{i-1}-\alpha_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } d$\;
 \nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 6 \;
@@
         \log(n!\cdot \max_{\frac{1\leq i\leq n}{1\leq j\leq n}}\{a_{ij}\}) &= 
-        O(n\log n + n\log(D+1)) \\
+        O(n\log n + n\log(d+1)) \\
         &= 
-        O^\sim(\log(D+1)).
+        O^\sim(\log(d+1)).
         \end{align*}
     \end{enumerate}
-    \item After computing the partial derivatives the height grows by at most another factor of $\log D$.
+    \item After computing the partial derivatives the height grows by at most another factor of $\log d$.
 Furthermore, preparing the straight line program for the gradient of $f$ does not introduce large integers.
 The integers in $\grad (f)$ are of the same magnitude as in $\Gamma$.
+    \item $\td$
     \item 
@@
     \[
-    O^\sim(kn(Lb+D^{2n}(s+D)(L+n^3D+n^4))),
-    \]
-    where it also follows from \cite[Algorithm 2]{SH} that the polynomials in the output have degree at most $D^n,$ and height at most
-    \[
-    O^{\sim}((s+D)D^n + nD^n).
+    O^\sim(kn(Lb+d^{2n}(s+d)(L+d))),
+    \]
+    where it also follows from \cite[Algorithm 2]{SH} that the polynomials in the output have degree at most $d^n,$ and height at most
+    \[
+    O^{\sim}((s+d)d^n).
     \]

### 2020-02-04 main.tex
More corrections
secn 2

--- 2020-02-04 main.tex
@@
 \def\thetab{\bm{\vartheta}}
+\def\mA{{\bm A}}
+\def\fA{{\frak A}}
 \def\xb{\textit{\textbf{x}}}
@@
 \def\R{\mathbb{R}}
+\def\K{\mathbb{K}}
 \def\rs{\mathscr{R}}
@@
 \def\codim{ \textrm{codim}}
-\def\jac{ \textrm{jac}}
+\def\jac{ \textbf{jac}}
 \def\exp{\textrm{exp}}
@@
 
-\begin{theorem}
+\begin{theorem}\label{theo:main}
   Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
@@
 
-In general, we cannot say much about the geometric properties of
-$W(\pi_i,V)$, but if we apply a generic change of coordinates $\bm A$,
+In general, we cannot say much about the geometry of
+$W(\pi_i,V)$, but if we apply a generic change of coordinates $\mA$,
 $W(\pi_i,V)$ is then known to be equidimensional of dimension $(i-1)$
@@
   position}~\cite{EMP} (background notions in algebraic geometry are
-in~\cite{Mumford76,Shafarevich77,Eisenbud96}; we will recall key
+in~\cite{Mumford76,Shafarevich77,ECA}; we will recall key
 definitions). If this is case, it suffices to choose arbitrary
@@
 Our main contribution is to analyse precisely what conditions on our
-change of coordinates $\bm A$ guarantee success. This is done by
+change of coordinates $\mA$ guarantee success. This is done by
 revisiting the key ingredients in the proofs given
@@
 This work should be seen as a first step toward the analysis of
-randomized algorithms in real algebraic geometry. An immediate
+further randomized algorithms in real algebraic geometry. An immediate
 follow-up question would be to handle the case of algebraic sets
@@
 %% \end{proposition}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Genericity properties}
+
+Consider $f \in \ZZ[X_1,\hdots,X_n]$ with total degree $d$, and assume
+that $f$ is squarefree and that $V(f) \subset \C^n$ is smooth. The key
+to the proof of Theorem~\ref{theo:main} is the following quantitative
+version of facts we stated above, namely that in generic coordinates,
+polar varieties are smooth, equidimensional, and in Noether position.
+
+We recall that an equidimensional algebraic set $X \subset \C^n$ of
+dimension $d$ is in \textit{Noether position} for the projection
+$\pi_d$ when the extension $\C[X_1,\hdots,X_d] \rightarrow
+\C[X_1,\hdots,X_n]/I(X)$ is injective and integral; here, $I(X)
+\subset \C[X_1,\dots,X_n]$ is the defining ideal of $X$. In this case,
+for any $\xb \in \C^d,$ the fiber $X \cap \pi_d^{-1}(\xb)$ has
+dimension zero (so it is finite and not empty).
+
+For $i$ in $\{1,\dots,n-1\}$ and $f$ as above, we will let $\I(i, f)$
+denote the sequence of $n-(i-1)$ polynomials $(f, {\pa f}/{\pa
+  X_{i+1}},\dots,{\pa f}/{\pa X_n})$. As we pointed out in the
+introduction, their zero-set is the $i$th polar variety $W(\pi,V(f))$.
+Then, we say that $f$ satisfies $\textbf{H}_i$ if
+\begin{enumerate}
+\item For any $\xb$ in $W(\pi,V(f))$, the Jacobian matrix
+  $\jac(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.
+
+  {\em By the Jacobian Criterion~\cite[Corollary 16.20]{ECA}, this
+  implies that $W(\pi_i,V(f))$ is either empty or $(i-1)$-equidimensional.}
+
+\smallskip
+
+\item $W(\pi_i,V(f))$ is either empty or in Noether position for
+  $\pi_{i-1}$.
+\end{enumerate}
+When this holds, given $\bm \alpha = (\alpha_1,\hdots,\alpha_{i-1})$
+in $\C^{i-1}$, we further say that $f$ and $\bm \alpha$ satisfy
+$\textbf{H}'_i$ if
+\begin{enumerate}
+\item the $n$ equations
+  $(X_1-\alpha_1,\dots,X_{i-1}-\alpha_{i-1}),\I(i, f))$ generate a
+  radical ideal.
+
+  {\em By point (2) above, we know that there are finitely many solutions 
+    to these equations.}
+\end{enumerate}
+
+Even if $f$ does not satisfy $\textbf{H}_i$, we mentioned that it does
+after applying a change of variables. The precise statement is the
+following; to state it, we use the following notation. For a matrix
+$\mA$ in $\C^{n^2}$ and $g$ in $\C[X_1,\hdots,X_n]$ we write
+$g^\mA:=g(\mA \Xb) \in \C[X_1,\dots,X_n]$.
+
+%% , $\xb \in
+%% \mathbb{C}^n$ and $X \subset \C^n$. We write $\xb^\mA:=\mA^{-1}\xb$,
+%% $X^\mA:=\{x^\mA~|~\xb \in V\}$ and $g^\mA:=g(\mA \Xb) \in
+%% \C[X_1,\dots,X_n]$. In particular, we have $g^\mA(\xb^\mA) =g(\xb)$,
+%% and $V(f)^\mA=V(f^\mA)$.
+
+\begin{theorem}
+  There exists a hypersurface $\D \subset \mathbb{C}^{n^2}$ of degree
+  at most $\td$ such that, if $\mA$ is chosen from $\C^{n^2}-\Delta$
+  then $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for
+  all $i \in \{1,\hdots,n-1\}.$
+\end{theorem}
 %% %
-%% \subsection{Polar varieties}
-%% %
-%% %
-%% \subsection{Changes of variables}
-%
-Consider $A \in \C^{n^2}, f \in \C[X_1,\hdots,X_n], \xb \in \mathbb{C}^n,$ and $V \subset \C^n$. We denote by 
-$V^A$ the set $\{x^A~|~\xb \in V\}, f^A$ the polynomial $f(A \xb)$ and $\xb^A$ denotes $A^{-1}\xb$. Notice $f^A(\xb^A) = f(A A^{-1}\xb)=f(\xb).$
-%
-%
-%
-%
-%
-%
-%
-%
-\section{Genericity properties}
-%
-Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ with total degree $D$.  
-We say that $f$ satisfies $\textbf{H}$ if 
-%
-\begin{enumerate}
-    \item $f$ is squarefree;
-    \item $V(f)$ is smooth.
-\end{enumerate}
-%
-An equidimensional algebraic set $X$ of dimension $d$ is in \textit{Noether position} for $\pi_d$ when the extension 
-\[
-\C[X_1,\hdots,X_d] \rightarrow \C[X_1,\hdots,X_n]/I(V)
-\] 
-is injective and integral.  Then, for any $\xb \in \C^d,$ the fiber 
-$V \cap \pi_d^{-1}(\xb)$ has dimension zero. For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (x_1,\hdots,x_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if 
-%
-\begin{enumerate}
-\item $\I(\pi_i,V)$ is radical;
-\item either $W(\pi_i,V)$ is empty or $(i-1)$-equidimensional;
-\item $W(\pi_i,V)$ is smooth;
-\item $\langle X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
-\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
-\item $V(X_1-x_1,\hdots,X_{i-1}-x_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
-\item either $W(\pi_i,V)$ is empty or in Noether position for $\pi_{i-1}$.
-\end{enumerate}
-%
-\begin{theorem}
-Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
-Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
-\end{theorem}
-%
-\begin{corollary} 
-Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
-Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
-\end{corollary}
-%
-%
-%
-%
+%% \begin{corollary} 
+%%   Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1}
+%%   D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen
+%%   randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i
+%%   \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
+%% \end{corollary}
+
+We will also work with change of variables with ``generic entries''.
+For this, we will introduce $n^2$ new indeterminates $(\frak
+A_{i,j})_{1\le i,j \le n^2}$, we will let $\K$ be the field $\C(\frak
+A_{i,j})_{1\le i,j \le n^2})$, and use the corresponding matrix $ \fA$
+over $\K$. For $g$ as above, we will then define the polynomial 
+$g^\fA:=g(\fA \Xb) \in \K[X_1,\dots,X_n]$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Weak Transversality}
@@
 in~\cite[Chapter~9]{bochnak1998real} or polynomial mappings $\C^n \to
-\C^m$ as in~\cite[Chapter~3]{Mumford76}, for which the sets of critical
-values are contained in strict semi-algebraic, resp.\ algebraic sets
-in the codomain. Thom's weak transversality lemma, as given for
-instance in~\cite{demazure2000bifurcations}, generalizes Sard's
-lemma. In this section, we consider a particular case of this result
-(transversality to a point), and establish a quantitative version of
-it. Our presentation is inspired by that in~\cite{TWT}.
+\C^m$ as in~\cite[Chapter~3]{Mumford76}, for which the sets of
+critical values are contained in strict semi-algebraic,
+resp.\ algebraic sets in the codomain. Thom's weak transversality
+lemma, as given for instance in~\cite{demazure2000bifurcations},
+generalizes Sard's lemma. In this section, we consider a particular
+case of this result (transversality to a point), and establish a
+quantitative version of it; this will allow us to establish the first
+item in property ${\bf H}_i$, as well as property ${\bf H}'_i$. Our
+presentation is inspired by that in~\cite{TWT}.
 

### 2020-02-04 main.tex

--- 2020-02-04 main.tex
@@
 %% \end{proposition}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Genericity properties}
+
+Consider $f \in \ZZ[X_1,\hdots,X_n]$ with total degree $d$, and assume
+that $f$ is squarefree and that $V(f) \subset \C^n$ is smooth. The key
+to the proof of Theorem~\ref{theo:main} is the following quantitative
+version of facts we stated above, namely that in generic coordinates,
+polar varieties are smooth, equidimensional, and in Noether position.
+
+We recall that an equidimensional algebraic set $X \subset \C^n$ of
+dimension $d$ is in \textit{Noether position} for the projection
+$\pi_d$ when the extension $\C[X_1,\hdots,X_d] \rightarrow
+\C[X_1,\hdots,X_n]/I(X)$ is injective and integral; here, $I(X)
+\subset \C[X_1,\dots,X_n]$ is the defining ideal of $X$. In this case,
+for any $\xb \in \C^d,$ the fiber $X \cap \pi_d^{-1}(\xb)$ has
+dimension zero (so it is finite and not empty).
+
+For $i$ in $\{1,\dots,n-1\}$ and $f$ as above, we will let $\I(i, f)$
+denote the sequence of $n-(i-1)$ polynomials $(f, {\pa f}/{\pa
+  X_{i+1}},\dots,{\pa f}/{\pa X_n})$. As we pointed out in the
+introduction, their zero-set is the $i$th polar variety $W(\pi,V(f))$.
+Then, we say that $f$ satisfies $\textbf{H}_i$ if
+\begin{enumerate}
+\item For any $\xb$ in $W(\pi,V(f))$, the Jacobian matrix
+  $\jac(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.
+
+  {\em By the Jacobian Criterion~\cite[Corollary 16.20]{ECA}, this
+  implies that $W(\pi_i,V(f))$ is either empty or $(i-1)$-equidimensional.}
+
+\smallskip
+
+\item $W(\pi_i,V(f))$ is either empty or in Noether position for
+  $\pi_{i-1}$.
+\end{enumerate}
+When this holds, given $\bm \alpha = (\alpha_1,\hdots,\alpha_{i-1})$
+in $\C^{i-1}$, we further say that $f$ and $\bm \alpha$ satisfy
+$\textbf{H}'_i$ if
+\begin{enumerate}
+\item the $n$ equations
+  $(X_1-\alpha_1,\dots,X_{i-1}-\alpha_{i-1}),\I(i, f))$ generate a
+  radical ideal.
+
+  {\em By point (2) above, we know that there are finitely many solutions 
+    to these equations.}
+\end{enumerate}
+
+Even if $f$ does not satisfy $\textbf{H}_i$, we mentioned that it does
+after applying a change of variables. The precise statement is the
+following; to state it, we use the following notation. For a matrix
+$\mA$ in $\C^{n^2}$ and $g$ in $\C[X_1,\hdots,X_n]$ we write
+$g^\mA:=g(\mA \Xb) \in \C[X_1,\dots,X_n]$.
+
+%% , $\xb \in
+%% \mathbb{C}^n$ and $X \subset \C^n$. We write $\xb^\mA:=\mA^{-1}\xb$,
+%% $X^\mA:=\{x^\mA~|~\xb \in V\}$ and $g^\mA:=g(\mA \Xb) \in
+%% \C[X_1,\dots,X_n]$. In particular, we have $g^\mA(\xb^\mA) =g(\xb)$,
+%% and $V(f)^\mA=V(f^\mA)$.
+
+\begin{theorem}
+  There exists a hypersurface $\D \subset \mathbb{C}^{n^2}$ of degree
+  at most $\td$ such that, if $\mA$ is chosen from $\C^{n^2}-\Delta$
+  then $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for
+  all $i \in \{1,\hdots,n-1\}.$
+\end{theorem}
 %% %
-%% \subsection{Polar varieties}
-%% %
-%% %
-%% \subsection{Changes of variables}
-%
-Consider $A \in \C^{n^2}, f \in \C[X_1,\hdots,X_n], \xb \in \mathbb{C}^n,$ and $V \subset \C^n$. We denote by 
-$V^A$ the set $\{x^A~|~\xb \in V\}, f^A$ the polynomial $f(A \xb)$ and $\xb^A$ denotes $A^{-1}\xb$. Notice $f^A(\xb^A) = f(A A^{-1}\xb)=f(\xb).$
-%
-%
-%
-%
-%
-%
-%
-%
-\section{Genericity properties}
-%
-Consider $f \in \mathbb{Q}[X_1,\hdots,X_n]$ with total degree $d$.  
-We say that $f$ satisfies $\textbf{H}$ if 
-%
-\begin{enumerate}
-    \item $f$ is squarefree;
-    \item $V(f) \cap \R^n$ is smooth.
-\end{enumerate}
-%
-An equidimensional algebraic set $X$ of dimension $r$ is in \textit{Noether position} for $\pi_r$ when the extension 
-\[
-\C[X_1,\hdots,X_r] \rightarrow \C[X_1,\hdots,X_n]/I(V)
-\] 
-is injective and integral.  Then, for any $\xb \in \C^r,$ the fiber 
-$V \cap \pi_r^{-1}(\xb)$ has dimension zero.
-For $i\in\{1,\hdots,n\}$, and for a randomly chosen point $p_{i-1} = (\alpha_1,\hdots,\alpha_{i-1}) \in \Q^{i-1}$, we say that $f$ satisfies $\textbf{H}_i^{'}$ if
-%
-\begin{enumerate}
-\item $\I(\pi_i,V)$ is radical;
-\item either $W(\pi_i,V)$ is empty or $(i-1)$-equidimensional;
-\item $W(\pi_i,V)$ is smooth;
-\item $\langle X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\rangle $ is radical; 
-\item $V(X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is finite;
-\item $V(X_1-\alpha_1,\hdots,X_{i-1}-\alpha_{i-1}, f,  \frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n})$ is smooth;
-\item either $W(\pi_i,V)$ is empty or in Noether position for $\pi_{i-1}$.
-\end{enumerate}
-%
-\begin{theorem}
-Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
-Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
-\end{theorem}
-%
-\begin{corollary} 
-Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
-Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
-\end{corollary}
-%
-%
-%
-%
+%% \begin{corollary} 
+%%   Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1}
+%%   D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen
+%%   randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i
+%%   \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
+%% \end{corollary}
+
+We will also work with change of variables with ``generic entries''.
+For this, we will introduce $n^2$ new indeterminates $(\frak
+A_{i,j})_{1\le i,j \le n^2}$, we will let $\K$ be the field $\C(\frak
+A_{i,j})_{1\le i,j \le n^2})$, and use the corresponding matrix $ \fA$
+over $\K$. For $g$ as above, we will then define the polynomial 
+$g^\fA:=g(\fA \Xb) \in \K[X_1,\dots,X_n]$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Weak Transversality}
@@
 %
-Let $p_{n-1} = (x_1,\hdots,x_{n-1}) \in \Q^{n-1}$ be a randomly chosen point. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
-\[
-X_1(\xb)-x_1,\hdots,X_{i-1}(\xb)-x_{i-1}, f(\xb),  \frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}
+Let $p_{n-1} = (\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}$ be a randomly chosen point. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
+\[
+X_1(\xb)-\alpha_1,\hdots,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),  \frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}
 \]

### 2020-02-04 main.tex
changed sections/subsections

@@
 
-\section{Weak Transversality}
+\section{Weak Transversality and Applications}
 
@@
 %% most values $\lambda \in \C^s$, $F(\Xb,\lambda)$ remains
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Weak Transversality}
 
@@
 
-\subsection{Genericity and Sard's lemma}
-%
-It will sometimes be useful for us use in replace of the matrix $A$, a matrix representing indeterminants: let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ It follows from Proposition 5.1, that for a generic $A \in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.
-The proof of \cite[Theorem B.3]{TWT}, which establishes the existence of $\Delta \subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the critical values of a polynomial mapping are contained in a hypersurface.
-It follows from Sard's lemma that, for the matrix of indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise it could not be that $0$ is a regular value of $\Phi_A,$ for a generic $A\in \C^{n^2}.$ The proof is routine and we omit details.
-It then follows that
+It will sometimes be useful for us use in replace of the matrix $A$, a
+matrix representing indeterminants: let $\A$ be an $n \times n$ matrix
+of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define
+$f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and
+$V^\A=V(f^\A).$ It follows from Proposition 5.1, that for a generic $A
+\in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.  The proof of
+\cite[Theorem B.3]{TWT}, which establishes the existence of $\Delta
+\subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the
+critical values of a polynomial mapping are contained in a
+hypersurface. It follows from Sard's lemma that, for the matrix of
+indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise
+it could not be that $0$ is a regular value of $\Phi_A,$ for a generic
+$A\in \C^{n^2}.$ The proof is routine and we omit details. It then
+follows that
 \[
@@
 \]
-has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}.
-We will rely on this fact in Section 8.
-%
-\section{Proof of $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$}
-%
-We assume our input polynomial $f$ satisfies \textbf{H} so that $f$ is squarefree with $V(f) \cap \mathbb{R}^n$ smooth.
-Thus, by Proposition 2.4,  $W(\pi_i,V(f))$ is defined by the vanishing of $f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.$ If the Jacobian of this set of polynomials has full rank at all $\xb \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion \cite[Theorem 16.19]{ECA} that $f$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies
+$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by
+the Jacobian criterion \cite[Theorem 16.19]{ECA}. We will rely on this
+fact in Section 8.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Application: property $\textbf{H}_i(1)$}
+
+We assume our input polynomial $f$ satisfies \textbf{H} so that $f$ is
+squarefree with $V(f) \cap \mathbb{R}^n$ smooth. Thus, by Proposition
+2.4, $W(\pi_i,V(f))$ is defined by the vanishing of $f,\frac{\pa
+  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.$ If the Jacobian of
+this set of polynomials has full rank at all $\xb \in V(f) \cap
+\mathbb{R}^n,$ then it follows by the Jacobian criterion \cite[Theorem
+  16.19]{ECA} that $f$ satisfies
+$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
 %
@@
 \end{theorem}
-%
-\subsection{Sketch of the proof of Theorem 4.1}
-%
+
 For each $i \in \{1,\hdots,n\}$, let $\Phi_i$ be the polynomial mapping 
@@
 \]
-%
-\subsection{Proof of Theorem 4.1}
-%
+
 Fix $i \in \{1,\hdots,n\}$, and let $\Phi_i$ be as stated above.
@@
 \]
-%
-%
-%
-%
-\section{Proof of $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$}
-%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Application: property $\textbf{H}'_i$}
+
 \begin{theorem}
-There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
+  There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of
+  degree at most $\td$ with the property that, if $A \in \C^{n^2} -
+  \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies
+  $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
 \end{theorem}
-%
-\subsection{Sketch of the proof of Theorem 5.1}
-%
+
 Let $p_{n-1} = (\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}$ be a randomly chosen point. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
@@
 has full rank, at all points $(\xb,A) \in \C^n \times \C^{n^2}$ in the zero set of this system. It would then follow from Theorem 5.1 that a hypersurface  exists with the desired properties.
-%
-\subsection{Proof of Theorem 5.1}
-%
+
 Let $\Phi_i$ be the mapping 
@@
 For all $(\xb,A) \in \Phi_i^{-1}(0),$ the Jacobian matrix of $\Phi_i$ at $(\xb,A)$ has full rank $\td$. Indeed, the Jacobian is equal to
-\[
-\left[ 
-\begin{array}{cccccc}
-\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
-\frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
-\ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
-\frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
-\end{array}
-\right]. 
-\] 
+%% \[
+%% \left[ 
+%% \begin{array}{cccccc}
+%% \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
+%% \frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
+%% \ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
+%% \frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
+%% \end{array}
+%% \right]. 
+%% \] 
 Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
@@
 \]
-%
-%
-%
-%
-\section{Proof of $\textbf{H}_i'(7)$}
-Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, to simplify notation, let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore, throughout this section, consider that $i \in \{1,\hdots,n\}$ is fixed.
-We will avoid writing $i$ where the context is clear.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Property ${\bf H}_i(2)$ -- Noether position}
+
+Throughout this section, we consider that $i \in \{1,\hdots,n\}$ is
+fixed. We prove that there exists a hypersurface $\D_{3,i} \subset
+\C^{n^2}$ such that if $\mA$ is not in $\D_{3,i}$, then $\mA$ is
+invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.
+
+Let $\A$ be an $n \times n$ matrix of new indeterminates
+$(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in
+\mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$
+Recall from Section 4.1.4 that $f^\A$ satisfies
+$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$
+, to simplify notation, let $\I^\A$ denote
+$\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore,
+throughout this section, We will avoid writing $i$ where the context is clear.
 %
@@
 Recall $\textbf{H}_i^{'}(7):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
-%% >>>>>>> f9eb2445ca6e153d1e49c3d2767097d331dbcbee
+
 \[

### 2020-02-05 main.tex
Updated applications (Hi(1) and Hi') in Section 3

@@
 \def\dt{s}
+\def\bI{\textbf{I}}
 %% \def\dt{\widetilde{d}}
@@
   \[
-  O^{\sim}(k(Lb+d^{2n}(s+d)(L+d)))
+  O^{\sim}(nk(Lb+d^{2n}(s+d)(L+d)))
   \]
@@
   X_{i+1}},\dots,{\pa f}/{\pa X_n})$. As we pointed out in the
-introduction, their zero-set is the $i$th polar variety $W(\pi,V(f))$.
+introduction, their zero-set is the $i$th polar variety $W(\pi_i,V(f))$.
 Then, we say that $f$ satisfies $\textbf{H}_i$ if
 \begin{enumerate}
-\item For any $\xb$ in $W(\pi,V(f))$, the Jacobian matrix
+\item For any $\xb$ in $W(\pi_i,V(f))$, the Jacobian matrix
   $\jac(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.
@@
 
-We assume our input polynomial $f$ satisfies \textbf{H} so that $f$ is
-squarefree with $V(f) \cap \mathbb{R}^n$ smooth. Thus, by Proposition
-2.4, $W(\pi_i,V(f))$ is defined by the vanishing of $f,\frac{\pa
-  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.$ If the Jacobian of
-this set of polynomials has full rank at all $\xb \in V(f) \cap
-\mathbb{R}^n,$ then it follows by the Jacobian criterion \cite[Theorem
-  16.19]{ECA} that $f$ satisfies
-$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$ with $V(f) \subset \C^n$ smooth. 
 %
 \begin{theorem}
-There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $d^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
+There exists a hypersurface $\Delta_1 \subset \C^{n^2}$ of degree at most $d^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then, for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i(1)$.
 \end{theorem}
@@
 \] 
-so that $\Phi_{i,A}^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $\bz$ is a regular value of $\Phi_i$, where then it follows that $\Xi_i \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Xi_i$ then
-\[
-\jac_{\xb}(\Phi_{i,A}) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)
-\]
-has full rank at all $\xb \in V(f^A)~(\cap\R^n$?).
-Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
-To obtain the result for all $i \in \{1,\hdots,n\}$, we take
-\[
-\Delta_1 = \bigcup_{i=1}^n \Xi_i 
-\]
-where we can bound the degree by observing that 
-\[
-\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i.
-\]
-
-Fix $i \in \{1,\hdots,n\}$, and let $\Phi_i$ be as stated above.
+so that $\Phi_{i,A}^{-1}(0)= W(\pi_i,V^A).$
 %
@@
 %
-Since $\deg \Phi_i \leq d,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $d^{n+(n-i+1)}=d^{2n-i+1}\leq d^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
-%
-\[
- \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
-\]
-has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}.
-Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
+Since $\deg \Phi_i \leq d,$ it follows by Proposition 3.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $d^{n+(n-i+1)}=d^{2n-i+1}\leq d^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
+%
+\[
+ \jac_{\xb} (\Phi_{i,A})=\jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
+\]
+has full rank at all $\xb \in V(f^A)$, and therefore $f^A$ satisfies $\textbf{H}_i(1)$. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
 \[
@@
 \subsection{Application: property $\textbf{H}'_i$}
-
+%
+Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$ with $V(f) \subset \C^n$ smooth. 
+%
 \begin{theorem}
-  There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of
-  degree at most $\td$ with the property that, if $A \in \C^{n^2} -
-  \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies
-  $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
+  There exists a Zariski closed set $\Delta_2 \subset \C^{n-1}$ of
+  degree at most $d^{2n^2}$ with the property that, if $\bm\alpha \in \C^{n-1} - \Delta_2$, then, for each $i \in \{1,\hdots,n\},$ if $f$ satisfies $\textbf{H}_i$ then $f$ and $\bm \alpha$ satisfy
+  $\textbf{H}_i'$.
 \end{theorem}
-
-Let $p_{n-1} = (\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}$ be a randomly chosen point. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
-\[
-X_1(\xb)-\alpha_1,\hdots,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),  \frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}
-\]
-has full rank, at all points $(\xb,A) \in \C^n \times \C^{n^2}$ in the zero set of this system. It would then follow from Theorem 5.1 that a hypersurface  exists with the desired properties.
-
-Let $\Phi_i$ be the mapping 
+%
+Fix $i \in \{1,\hdots,n\}$ and let $\Phi_i$ be the mapping 
 %
@@
 \begin{proof}
-For all $(\xb,A) \in \Phi_i^{-1}(0),$ the Jacobian matrix of $\Phi_i$ at $(\xb,A)$ has full rank $\td$. Indeed, the Jacobian is equal to
-%% \[
-%% \left[ 
-%% \begin{array}{cccccc}
-%% \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
-%% \frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
-%% \ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
-%% \frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
-%% \end{array}
-%% \right]. 
-%% \] 
-Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
-\[
-T_{\xb} V(f) = \textrm{Nullspace}(\grad_{\xb} f).
-\]
-Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes.
-At least one partial of $f$ must be non-zero.
-Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
+At all $(\xb,\alpha_1,\hdots,\alpha_{i-1}) \in \Phi_i^{-1}(0),$ the Jacobian matrix of $\Phi_i$ has full rank. Indeed, the Jacobian is equal to
+\[
+\left[ 
+\begin{array}{cc}
+\hspace{-9mm}\bI_n\hspace{10mm}\hdots \hdots&\hspace{-10mm}-\bI_{i-1}\\
+\jac_{\xb}\left(f,\frac{\pa
+  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right)&\bz_{n-i+1\times i-1}
+\end{array}
+\right], 
+\] 
+and the Jacobian of $f,\frac{\pa
+  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}$ at $\xb$ is never singular because we are assuming that $f$ satisfies $\textbf{H}_i$.
+Therefore the entire matrix must have full rank, and $\bz$ is a regular value of $\Phi_i.$
 \end{proof}
 %
-Since $\deg \Phi_i \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $D^{n+(n-i+1)}=D^{2n-i+1}\leq D^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
-%
-\[
- \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
-\]
-has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}.
-Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
-\[
-\Delta_1 := \bigcup_{i=1}^n \Xi_i,
+Since $\deg \Phi_i \leq d,$ it follows by Proposition 3.1 that a hypersurface $\Xi_i \subset \C^{i-1}$ exists, of degree at most $d^{2n},$ with the property that, if $\bm \alpha_{i-1} \in \C^{i-1}-\Xi_i,$ then the Jacobian of $\Phi_{i,\alpha_{i-1}}$:
+%
+\[
+ \jac_{\xb} \left(X_1(\xb)-\alpha_1,\hdots 
+       ,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),\frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}\right)
+\]
+has full rank at all $\xb \in V(f)$, and therefore $f$ and $\bm \alpha_{i-1}$ satisfy $\textbf{H}_i^{'}$. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
+\[
+\Delta_2 := \bigcup_{i=1}^n \Xi_i,
 \]
@@
 \[
-\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq D^{2n^2}.
+\deg \Delta_2 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
 \]

### 2020-02-05 main.tex
stuff

--- 2020-02-04 main.tex
@@
 
-Throughout this section, we consider that $i \in \{1,\hdots,n\}$ is
+Throughout this section,  $i \in \{1,\hdots,n\}$ is
 fixed. We prove that there exists a hypersurface $\D_{3,i} \subset
 \C^{n^2}$ such that if $\mA$ is not in $\D_{3,i}$, then $\mA$ is
-invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.
-
-Let $\A$ be an $n \times n$ matrix of new indeterminates
-$(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in
+invertible and satisfies $\textbf{H}_i$ and $\textbf{H}_i$.
+
+Since $i$ is fixed, to simplify notation, let $\I^\A$ denote
+$\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$
+
+Consider again the matrix of indeterminates $\A$.  Define $f^{\A} \in
 \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$
-Recall from Section 4.1.4 that $f^\A$ satisfies
-$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$
-, to simplify notation, let $\I^\A$ denote
-$\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore,
-throughout this section, We will avoid writing $i$ where the context is clear.
-%
-\subsection{Sketch of the proof}
-%
-Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ have total degree $D$.
-Assume $f$ satisfies \textbf{H}, so that $f$ is squarefree with $V(f)$ smooth.
-Recall $\textbf{H}_i^{'}(7):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
+Recall from Section~\ref{xxx} that $f^\A$ satisfies
+$\textbf{H}_i^{'}(1)$, that is, \td.
 
@@
 %
-\begin{theorem}
-There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(7)$.
-\end{theorem}
-%
-Section 7 is devoted to proving Theorem 7.1.
-It has already been shown in \cite{EMP} that $f^A$ satisfies $\textbf{H}_i^{'}(7)$ for a generic change of variables.
-The new contribution is in upper bounding the degree of $\Delta_3.$
-%
-\begin{proposition} 
-The ring extension \[\mathbb{Q}(\frak{A})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textbf{X}]/\I^{\A}\] is integral.
-\end{proposition}
+
+It has already been shown in \cite{EMP} that $f^A$ satisfies
+$\textbf{H}_i^{'}(7)$ for a generic change of variables. The new
+contribution is in upper bounding the degree of $\Delta_3.$
+
+\begin{lemma} 
+The ring
+extension \[\mathbb{Q}(\frak{A})[X_1,\dots,X_{i-1}]\rightarrow\mathbb{Q}(\frak{A})[X_1,\dots,X_n]/\I^{\A}\]
+is integral.
+\end{lemma}
 %

### 2020-02-05 main.tex
Updated Section 4 - Noether position

@@
 \def\Yt{\widetilde{Y}}
+\def\dtt{\widetilde{d}}
 \def\kt{\widetilde{k}}
@@
 
-We will also work with change of variables with ``generic entries''.
+We will also work with changes of variables with ``generic entries''.
 For this, we will introduce $n^2$ new indeterminates $(\frak
 A_{i,j})_{1\le i,j \le n^2}$, we will let $\K$ be the field $\C(\frak
-A_{i,j})_{1\le i,j \le n^2})$, and use the corresponding matrix $ \fA$
+A_{i,j})_{1\le i,j \le n^2}$, and use the corresponding matrix $ \fA$
 over $\K$. For $g$ as above, we will then define the polynomial 
@@
 
-It will sometimes be useful for us use in replace of the matrix $A$, a
-matrix representing indeterminants: let $\A$ be an $n \times n$ matrix
-of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define
-$f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and
-$V^\A=V(f^\A).$ It follows from Proposition 5.1, that for a generic $A
-\in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.  The proof of
-\cite[Theorem B.3]{TWT}, which establishes the existence of $\Delta
-\subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the
-critical values of a polynomial mapping are contained in a
-hypersurface. It follows from Sard's lemma that, for the matrix of
-indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise
-it could not be that $0$ is a regular value of $\Phi_A,$ for a generic
-$A\in \C^{n^2}.$ The proof is routine and we omit details. It then
-follows that
-\[
-\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(\xb),\frac{\pa f^{\A}(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(\xb)}{\pa X_n}\right)
-\]
-has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies
-$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by
-the Jacobian criterion \cite[Theorem 16.19]{ECA}. We will rely on this
+Recall that we work with changes of variables with ``generic entries'' of new indeterminants $(\frak
+A_{i,j})_{1\le i,j \le n^2}$, and define the polynomial 
+$f^\fA:=f(\fA \Xb)$.
+Note that $f^\A$ satisfies $\textbf{H}_i(1).$ Indeed, otherwise it could not be that that the Jacobian of $f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$ has full rank at all $\xb \in V(f^A)$ for a generic $A \in \C^{n^2},$ which would contradict Popositon 3.1.
+The proof of this statement is routine and we omit details.
+We will rely on this
 fact in Section 8.
@@
 
-Throughout this section,  $i \in \{1,\hdots,n\}$ is
-fixed. We prove that there exists a hypersurface $\D_{3,i} \subset
+Fix $i \in \{1,\hdots,n\}$. Throughout this section, we will avoid writing $i$ where the context is clear. Let $\I^{\A}$ denote $\I(i,V^{\A}).$
+
+We prove that there exists a hypersurface $\D_{3,i} \subset
 \C^{n^2}$ such that if $\mA$ is not in $\D_{3,i}$, then $\mA$ is
-invertible and satisfies $\textbf{H}_i$ and $\textbf{H}_i$.
-
-Since $i$ is fixed, to simplify notation, let $\I^\A$ denote
-$\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$
-
-Consider again the matrix of indeterminates $\A$.  Define $f^{\A} \in
-\mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$
-Recall from Section~\ref{xxx} that $f^\A$ satisfies
-$\textbf{H}_i^{'}(1)$, that is, \td.
-
+invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.
+
+Recall that we work with changes of variables with ``generic entries'' of new indeterminants $(\frak
+A_{i,j})_{1\le i,j \le n^2}$, and define the polynomial 
+$f^\fA:=f(\fA \Xb)$. Recall as well that $f^\A$ satisfies $\textbf{H}_i(1),$ as was stated at the end of Section 3.1. 
+%
+\subsection{Sketch of the proof}
+%
+Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$ with $V(f) \subset \C^n$ smooth. Recall $\textbf{H}_i(2):$ \textit{$W(\pi_i,V(f))$ is either empty or in Noether position for
+  $\pi_{i-1}$}, which is equivalent to having the extension  
 \[
@@
 %
-
-It has already been shown in \cite{EMP} that $f^A$ satisfies
-$\textbf{H}_i^{'}(7)$ for a generic change of variables. The new
-contribution is in upper bounding the degree of $\Delta_3.$
-
-\begin{lemma} 
-The ring
-extension \[\mathbb{Q}(\frak{A})[X_1,\dots,X_{i-1}]\rightarrow\mathbb{Q}(\frak{A})[X_1,\dots,X_n]/\I^{\A}\]
-is integral.
-\end{lemma}
+\begin{theorem}
+There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, \mA$ is
+invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.
+\end{theorem}
+%
+\begin{proposition} 
+The ring extension \[\mathbb{Q}(\frak{A})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textbf{X}]/\I^{\A}\] is integral.
+\end{proposition}
 %
@@
 %
-Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 7.2.
+Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 4.2.
 Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$
@@
 \]
-For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $A \in \Gamma_j$,
-then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$.
+For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $\mA \in \Gamma_j$,
+then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$.
 Define $h_j \in \Q[\A]$ to be the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$.
-Hence, if $A \in \Q^{n^2}-V(h_j)$ then $A$ cancels none of the denominators of $a_{j}$ or $b_{j,l},$ which are providing the integral dependence relation.
+Hence, if $\mA \in \C^{n^2}-V(h_j)$ then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l},$ which are providing the integral dependence relation.
 Now we define
@@
 \]
-Hence, if $A\in \Q^{n^2}-\Xi_i$ then
+Hence, if $\mA\in \Q^{n^2}-\Xi_i$ then
 \[
@@
 \[
-\mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{A})
+\mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{\mA})
 \]
@@
 We can obtain a polynomial from $P_{j}$ by clearing denominators.
-We can multiply $P_{j}$ by the least common multiple of its denominators, which we will denote by $d_j \in \Q[\A_{i,j}]$.
+We can multiply $P_{j}$ by the least common multiple of its denominators, which we will denote by $d_j \in \Q[\A]$.
 Put
@@
 \begin{proposition} 
-$\deg \pjb\leq (D+1)^{n-i+1}.$ 
+$\deg \pjb\leq (d+1)^{n-i+1}.$ 
 \end{proposition} 
@@
 \begin{align*}
-&\deg \pjb \leq (D+1)^{n-i+1}.&(2D)^{n-i+1}\textrm{?} 
+&\deg \pjb \leq (d+1)^{n-i+1}.&(2d)^{n-i+1}\textrm{?} 
 \end{align*}
@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\}\leq D,
+\right\}\leq d,
 \]
@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\} \leq D,
+\right\} \leq d,
 \]
@@
 \begin{align*}
-    &\left(\prod_{k=1}^{n-i+1} D\right)\Dt_j 
-    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}D \right)D\\
-    = &\left(D^{n-i+1}\right)\Dt_j+
-    (n-i+1)\left(\Dt_j+1\right)\left(D^{n-i+1} \right)\\
-    &\leq D^{n}\Dt_j + n\left(\Dt_j+1\right)D^{n}\\
-    &=D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+    &\left(\prod_{k=1}^{n-i+1} d\right)\Dt_j 
+    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}d \right)d\\
+    = &\left(d^{n-i+1}\right)\Dt_j+
+    (n-i+1)\left(\Dt_j+1\right)\left(d^{n-i+1} \right)\\
+    &\leq d^{n}\Dt_j + n\left(\Dt_j+1\right)d^{n}\\
+    &=d^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
 \end{align*}
@@
 \deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
-    &\leq \left(D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
-    &=D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+    &\leq \left(d^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
+    &=d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
 \end{align*}
@@
     &\leq \sum_{j=i}^n \deg h_j\\
-    &\leq  \sum_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
-    &=  (n-i+1)\left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
-    &\leq  n D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
+    &\leq  \sum_{j=i}^n \left( d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
+    &=  (n-i+1)\left( d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
+    &\leq  n d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
 \end{align*}
@@
     \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
-    &\leq n^2 D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
+    &\leq n^2 d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
 \end{align*}

### 2020-02-05 main.tex
sec 4

@@
 \def\Yt{\widetilde{Y}}
-\def\dtt{\widetilde{d}}
 \def\kt{\widetilde{k}}
@@
 
-\section{Genericity properties}
+\section{Genericity properties}\label{sec:gen}
 
@@
 
-We will also work with changes of variables with ``generic entries''.
-For this, we will introduce $n^2$ new indeterminates $(\frak
-A_{i,j})_{1\le i,j \le n^2}$, we will let $\K$ be the field $\C(\frak
-A_{i,j})_{1\le i,j \le n^2}$, and use the corresponding matrix $ \fA$
-over $\K$. For $g$ as above, we will then define the polynomial 
-$g^\fA:=g(\fA \Xb) \in \K[X_1,\dots,X_n]$.
+It will on occasion be useful to work with change of variables with
+``generic'' entries. For this, we will introduce $n^2$ new indeterminates
+$(\frak A_{j,k})_{1\le j,k \le n^2}$, we will let $\K$ be the field
+$\C(\frak A_{i,j})$, and use the corresponding
+matrix $\A$ over $\K$. For $f$ as above, we will then define the
+polynomial $f^\A:=f(\A \Xb) \in \K[X_1,\dots,X_n]$.
 
@@
 versions of it, for semi-algebraic mappings $\R^n \to \R^m$ as
-in~\cite[Chapter~9]{bochnak1998real} or polynomial mappings $\C^n \to
+in~\cite[Chapter~9]{bochnak1998real}, or polynomial mappings $\C^n \to
 \C^m$ as in~\cite[Chapter~3]{Mumford76}, for which the sets of
@@
 
-Recall that we work with changes of variables with ``generic entries'' of new indeterminants $(\frak
-A_{i,j})_{1\le i,j \le n^2}$, and define the polynomial 
-$f^\fA:=f(\fA \Xb)$.
-Note that $f^\A$ satisfies $\textbf{H}_i(1).$ Indeed, otherwise it could not be that that the Jacobian of $f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$ has full rank at all $\xb \in V(f^A)$ for a generic $A \in \C^{n^2},$ which would contradict Popositon 3.1.
-The proof of this statement is routine and we omit details.
-We will rely on this
-fact in Section 8.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Application: property $\textbf{H}_i(1)$}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Application: property $\textbf{H}_i(1)$}\label{ssec:Hi1}
 
@@
 
+In Section~\ref{sec:Hi2}, we will need the following alternative form
+of this result: if we consider $f^\A \in \C(\frak
+A_{j,k})[X_1,\dots,X_n]$ as defined Section~\ref{sec:gen}, this
+polynomial satisfies the rank property $\textbf{H}_i(1)$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Property ${\bf H}_i(2)$ -- Noether position}
-
-Fix $i \in \{1,\hdots,n\}$. Throughout this section, we will avoid writing $i$ where the context is clear. Let $\I^{\A}$ denote $\I(i,V^{\A}).$
-
-We prove that there exists a hypersurface $\D_{3,i} \subset
-\C^{n^2}$ such that if $\mA$ is not in $\D_{3,i}$, then $\mA$ is
-invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.
-
-Recall that we work with changes of variables with ``generic entries'' of new indeterminants $(\frak
-A_{i,j})_{1\le i,j \le n^2}$, and define the polynomial 
-$f^\fA:=f(\fA \Xb)$. Recall as well that $f^\A$ satisfies $\textbf{H}_i(1),$ as was stated at the end of Section 3.1. 
-%
-\subsection{Sketch of the proof}
-%
-Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$ with $V(f) \subset \C^n$ smooth. Recall $\textbf{H}_i(2):$ \textit{$W(\pi_i,V(f))$ is either empty or in Noether position for
-  $\pi_{i-1}$}, which is equivalent to having the extension  
-\[
-\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
-\]
-injective and  integral.
-%
-\begin{theorem}
-There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, \mA$ is
-invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.
-\end{theorem}
-%
-\begin{proposition} 
-The ring extension \[\mathbb{Q}(\frak{A})[\textbf{X}_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\textbf{X}]/\I^{\A}\] is integral.
-\end{proposition}
-%
+\section{Property ${\bf H}_i(2)$ -- Noether position}\label{sec:Hi2}
+
+Throughout this section, $f$ and $i \in \{1,\hdots,n\}$ are fixed. We
+prove that there exists a hypersurface $\D_{3,i} \subset \C^{n\times
+  n}$ of degree at most \td{} such that if $\mA$ is not in $\D_{3,i}$,
+then $\mA$ is invertible and satisfies both conditions in
+$\textbf{H}_i$.
+
+Consider again the $n\times n$ matrix of indeterminates
+$\A=(\A_{j,k})_{1 \le j,k \le n}$ and the field $\C(\A)$,
+and define $f^{\A} \in \C(\A)[X_1,\dots,X_n]$.  Since $i$ is fixed, to
+simplify notation, let $\I^\A$ denote the following polynomials in
+$\C(\A)[X_1,\dots,X_n]$:
+$$\I(\pi_i,f^\A)= \big (f^\A, {\pa f^\A}/{\pa X_{i+1}},\dots,{\pa
+  f^\A}/{\pa X_n}) \big ),$$ and let $W^\A$ denote their zero-set,
+that is, $W(\pi_i,V(f^\A)).$ In Section~\ref{ssec:Hi1}, we saw that
+$f^\A$ satisfies $\textbf{H}_i(1)$, so that $\I^\A$ defines a
+radical ideal, and $W^\A$ is equidimensional of dimension $i-1$. We
+now point out that $f^\A$ also satisfies $\textbf{H}_i(2)$.
+
+\begin{lemma} 
+ The extension $\C(\A)[X_1,\dots,X_{i-1}]\rightarrow
+ \C(\A)[X_1,\dots,X_n]/\I^{\A}$ is integral.
+\end{lemma}
 \begin{proof}
-Let $(\frak{P}_l)_{l \leq L}$ be the prime components of the radical ideal $\I^\A$. By \cite[Proposition 1]{EMP}, 
-\[
-\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\Xb]/\fp_l^{\A}
-\] 
-is integral. Therefore polynomials $p_{l,j}\in\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ exist, monic in $T$, with $p_{l,j}(X_j)\in \frak{P}_l$ for each $j\in \{i,\hdots,n\}.$ Thence, 
-%
-\begin{align*}
-&P_{j}(X_j) := \prod_l p_{l,j}(X_j)\in\I^\A, 
-\end{align*}
-%
-for each $j \in \{i,\hdots,n\},$ and therefore 
-\[
-\mathbb{Q}(\frak{A})[\Xb_{\leq i-1}]\rightarrow\mathbb{Q}(\frak{A})[\Xb]/\I^{\A}
-\] 
-is integral.
+  Let $(\fp_\ell)_{1 \le \ell \leq L}$ be the prime components of
+  the radical ideal $\I^\A$. By \cite[Proposition 1]{EMP}, for all
+  $\ell$,
+  \[
+    \C(\A)[X_1,\dots,X_{i-1}]\rightarrow\C(\A)[X_1,\dots,X_n]/\fp_\ell
+  \] 
+  is integral. Therefore polynomials
+  $q_{\ell,j}\in\C(\A)[X_1,\dots,X_{i-1},X_j]$ exist, all monic in
+  $X_j$, with $q_{\ell,j}(X_j)\in \fp_\ell$ for each $j$ in
+  $\{i,\hdots,n\}.$ Thence, $ Q_{j} := \prod_{1 \le \ell\le L}
+  q_{\ell,j}$ is monic in $X_j$ and satisfies $ Q_{j} \in \I^\A$, for
+  each $j \in \{i,\hdots,n\}.$ This proves our claim.
 \end{proof}
-%
-Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 4.2.
-Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$
- we can write
-\[
-P_{j}(X_j) = a_j f^{\A} + \sum_{l=1}^{n-i}b_{j,l} \frac{\partial f^\A}{\partial X_{i+l}}, ~a_j,b_{j,l} \in \mathbb{Q}(\A)[\textbf{X}].
-\]
-For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $\mA \in \Gamma_j$,
-then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$.
-Define $h_j \in \Q[\A]$ to be the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$.
-Hence, if $\mA \in \C^{n^2}-V(h_j)$ then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l},$ which are providing the integral dependence relation.
-Now we define
-\[
-\Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 
-\]
-and we obtain a bound on the degree of $\Xi_i$ by observing that
-\[
-\deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
-\]
-Hence, if $\mA\in \Q^{n^2}-\Xi_i$ then
-\[
-P_j(X_j) \in \I^A,  
-\]
-for each $j \in \{i,\hdots,n\},$ and therefore the extension 
-\[
-\mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{\mA})
-\]
-is integral.
-We can obtain bounds for $h_j$ by applying an effective Nullstellensatz theorem.
-However, the theorem requires $P_{j}$ to be a polynomial.
-We can obtain a polynomial from $P_{j}$ by clearing denominators.
-We can multiply $P_{j}$ by the least common multiple of its denominators, which we will denote by $d_j \in \Q[\A]$.
-Put
-\[
-\overline{P_{j}} := d_jP_{j}\in \Q[\A][\Xb],
-\]
-and note that $\pjb(X_j) \in \I^{\A}$ with 
-\[
-\pjb(X_j) = \ajb f^{\A} + \sum_{l=1}^{n-i}\bjb \frac{\partial f^\A}{\partial X_{i+l}}, ~\ajb,\bjb \in \mathbb{Q}[\A][\textbf{X}].
-\]
-%
-\begin{proposition} 
-$\deg \pjb\leq (d+1)^{n-i+1}.$ 
-\end{proposition} 
-%
+
+\noindent
+If $P$ is any polynomial in $\C(\frak A)[X_1,\dots,X_n]$, we will let
+$D \in \C[\frak A]$ be the minimal common denominator of all its
+coefficients, and we will write $\overline P := D P$, so that
+$\overline P$ is in $\C[\A,X_1,\dots,X_{i-1},X_n]$.
+
+\begin{lemma} 
+  For $j=i,\dots,n$, there exists $P_j$ in $
+  \C(\A)[X_1,\dots,X_{i-1},X_j]$, monic in $X_j$, with $\pjb$ in
+  $\I^\A$, and such that $\deg(\pjb)\leq (2d)^{n-i+1}.$
+\end{lemma} 
 \begin{proof}
-\textbf{Eric and Mark}: I am unsure of how to do this part correctly, so I will assume 
-\[
-\deg \pjb\leq \Dt_j.
-\]
-Let $\Is \subset \Q[\A,\Xb]$ be the extension of $\I^{\A}$ in  $\Q[\A,\Xb],$ and consider the finite field extension
-%
-\begin{align*}
-    \Q(\A,\Xb_{i-1}) &\rightarrow \Q(\A,\Xb_{i-1})[X_i,\hdots,X_n]/\Is.
-\end{align*}
-%
-The minimal polynomial of the linear mapping defined by multiplication by $X_j$ in $\Q(\A,\Xb_{i-1})$ is \textbf{almost}(?) equal to $\pjb$ (the leading coefficient of $\pjb$ is $d_j$).
-It therefore follows by \cite[Proposition 1]{CGR} that
-%
-\begin{align*}
-&\deg \pjb \leq (d+1)^{n-i+1}.&(2d)^{n-i+1}\textrm{?} 
-\end{align*}
-%
+  We let $\frak L^\A$ denote the extension of $\I^\A$ given by $\frak
+  L^\A:=\I^\A\cdot \C(\frak A, X_1,\dots,X_{i-1})[X_i,\dots,X_n]$. Then,
+  \begin{equation}\label{eq:1}
+    \C(\frak A, X_1,\dots,X_{i-1}) \to \C(\frak A,
+    X_1,\dots,X_{i-1})[X_i,\dots,X_n]/\frak L^\A
+  \end{equation}
+  is an algebraic extension. On the other hand, 
+  the previous lemma states that 
+  \begin{equation}\label{eq:2}
+    \C(\A)[X_1,\dots,X_{i-1}]\rightarrow
+    \C(\A)[X_1,\dots,X_n]/\I^{\A}  
+  \end{equation}
+  is integral; from this, Proposition~3.3.1 in~\cite{GiHeSa93} implies
+  that it is actually a free module. Any basis of the latter is also a
+  basis of~\eqref{eq:1}; as a consequence, for $j$ in $i,\dots,n$, the
+  characteristic polynomials of $X_j$ in~\eqref{eq:1} or~\eqref{eq:2}
+  are the same. Let $P_j$ be the minimal polynomial of $X_j$
+  in~\eqref{eq:1}. The previous discussion implies that the
+  characteristic polynomial $\chi_j$ of $X_j$ in~\eqref{eq:1}, and
+  thus also $P_j$, are in $\C(\A)[X_1,\dots,X_{i-1},X_j]$ and monic in
+  $X_j$.
+
+  By definition, $\chi_{j}$ is in $\frak I^\A$ and since there exists
+  an integer $k$ such that $\chi_j$ divides $P_j{}^k$ in
+  $\C(\A)[X_1,\dots,X_{i-1}][X_j]$, $P_j{}^k$ is in $\frak
+  I^\A$. Since the latter ideal is radical, we conclude that $P_{j}$
+  is in $\frak I^\A$. This implies that $\pjb$ is in $\frak I^\A$ as
+  well.
+
+  Now, consider the polynomials $f^\A, {\pa f^\A}/{\pa
+    X_{i+1}}, \dots, {\pa f^\A}/{\pa X_n}$ in $\C[\A,X_1,\dots,X_n]$,
+  let $\frak W$ be their zero-set, and let $\deg(\frak W)$ be its
+  degree, in the sense of~\cite{H}. Proposition~1 in~\cite{CGR}
+  implies that $\pjb$ has degree at most $\deg(\frak W)$. Since all
+  polynomials defining $\frak W$, seen in $\C[\A,X_1,\dots,X_n]$, have
+  degree at most $2d$, the B\'ezout inequality of~\cite{H} gives
+  $\deg(\pjb) \le (2d)^{n-i+1}$.
 \end{proof}
-%
-Note that 
-\[
-\deg d_j \leq \deg \pjb \leq \Dt_j.
-\]
-%
-\subsection{Applying the effective Nullstellensatz}
-%
-To apply the effective Nullstellensatz theorem, we first need to determine degree bounds, separately in $\Xb$ and $\A,$ of the polynomials in the membership relationship. We have
+
+%% \[
+%% \C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
+%% \]
+%% injective and  integral.
+
+%%  Since $P_{j}(X_j) \in\I^{\A}= \langle
+%% f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial
+%%   f^\A}{\partial X_n} \rangle,$ we can write
+%% \[
+%% P_{j}(X_j) = a_j f^{\A} + \sum_{l=1}^{n-i}b_{j,l} \frac{\partial f^\A}{\partial X_{i+l}}, ~a_j,b_{j,l} \in \mathbb{Q}(\A)[\textbf{X}].
+%% \]
+%% For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset
+%% \C^{n^2}$ such that if $A \in \Gamma_j$, then $A$ cancels none of the
+%% denominators of $a_{j}$ or $b_{j,l}$. Define $h_j \in \Q[\A]$ to be
+%% the product of the denominators of the coefficients of $a_j$ and
+%% $b_{j,l}$. Hence, if $A \in \Q^{n^2}-V(h_j)$ then $A$ cancels none of
+%% the denominators of $a_{j}$ or $b_{j,l},$ which are providing the
+%% integral dependence relation. Now we define
+%% \[
+%% \Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 
+%% \]
+%% and we obtain a bound on the degree of $\Xi_i$ by observing that
+%% \[
+%% \deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
+%% \]
+%% Hence, if $A\in \Q^{n^2}-\Xi_i$ then
+%% \[
+%% P_j(X_j) \in \I^A,  
+%% \]
+%% for each $j \in \{i,\hdots,n\},$ and therefore the extension 
+%% \[
+%% \mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{A})
+%% \]
+%% is integral. We can obtain bounds for $h_j$ by applying an effective
+%% Nullstellensatz theorem.
+
+%% %
+%% Note that 
+%% \[
+%% \deg d_j \leq \deg \pjb \leq \Dt_j.
+%% \]
+%% %
+%% \subsection{Applying the effective Nullstellensatz}
+%% %
+
+To apply the effective Nullstellensatz theorem, we first need to
+determine degree bounds, separately in $\Xb$ and $\A,$ of the
+polynomials in the membership relationship. We have
 \[
@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\}\leq d,
+\right\}\leq D,
 \]
@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\} \leq d,
+\right\} \leq D,
 \]
@@
 \begin{align*}
-    &\left(\prod_{k=1}^{n-i+1} d\right)\Dt_j 
-    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}d \right)d\\
-    = &\left(d^{n-i+1}\right)\Dt_j+
-    (n-i+1)\left(\Dt_j+1\right)\left(d^{n-i+1} \right)\\
-    &\leq d^{n}\Dt_j + n\left(\Dt_j+1\right)d^{n}\\
-    &=d^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+    &\left(\prod_{k=1}^{n-i+1} D\right)\Dt_j 
+    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}D \right)D\\
+    = &\left(D^{n-i+1}\right)\Dt_j+
+    (n-i+1)\left(\Dt_j+1\right)\left(D^{n-i+1} \right)\\
+    &\leq D^{n}\Dt_j + n\left(\Dt_j+1\right)D^{n}\\
+    &=D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
 \end{align*}
@@
 \deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
-    &\leq \left(d^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
-    &=d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+    &\leq \left(D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
+    &=D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
 \end{align*}
@@
     &\leq \sum_{j=i}^n \deg h_j\\
-    &\leq  \sum_{j=i}^n \left( d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
-    &=  (n-i+1)\left( d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
-    &\leq  n d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
+    &\leq  \sum_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
+    &=  (n-i+1)\left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
+    &\leq  n D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
 \end{align*}
@@
     \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
-    &\leq n^2 d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
+    &\leq n^2 D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
 \end{align*}

### 2020-02-05 main.tex
sec 4

@@
 
+Our next step is to give degree bounds on the coefficients appearing
+in the membership equality $\pjb \in\I^\A$. This is done using
+Rabinovicz's trick. Let $T$ be a new variable; applying the
+Nullstellensatz in $\C(\A)[X_1,\dots,X_n,T]$, and clearing
+denominators, we obtain the existence of $\alpha_j$ in
+$\C[\A]\setminus\{0\}$ and $ A_{j,\ell},B_j$ in
+$\C[\A][X_1,\dots,X_n][T]$, such that
+\begin{align*}
+\alpha_j = \sum_{\ell=1}^{n-i+1} A_{j,\ell} g_\ell + B_j (1-\pjb T),\ \  g_\ell \in 
+\left\{ 
+f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
+\right\}.
+\end{align*}
+
 %% \[
@@
 \]
-For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, there exists $\alpha_j \in \mathbb{Q}[\A]\setminus\{0\}$ with 
-%
-\begin{align*}
-\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,T)g_l + B_j(\A,\Xb,T)(1-\pjb T), \\ g_l \in 
-\left\{ 
-f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T],
-\end{align*}
+For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, 
 %

### 2020-02-05 main.tex
Updates from Overleaf

--- 2020-02-05 main.tex
@@
 \keywords{Real algebraic geometry, transversality, Noether
-  normalization, bit complexity}
+  position, bit complexity}
 
@@
 \begin{theorem}
-There exists a hypersurface $\Delta_1 \subset \C^{n^2}$ of degree at most $d^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then, for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i(1)$.
+There exists a hypersurface $\Delta_1 \subset \C^{n^2}$ of degree at most $nd^{2n}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then, for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i(1)$.
 \end{theorem}
@@
 \[
-\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
+\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq nd^{2n}.
 \]
@@
   There exists a Zariski closed set $\Delta_2 \subset \C^{n-1}$ of
-  degree at most $d^{2n^2}$ with the property that, if $\bm\alpha \in \C^{n-1} - \Delta_2$, then, for each $i \in \{1,\hdots,n\},$ if $f$ satisfies $\textbf{H}_i$ then $f$ and $\bm \alpha$ satisfy
+  degree at most $nd^{2n}$ with the property that, if $\bm\alpha \in \C^{n-1} - \Delta_2$, then, for each $i \in \{1,\hdots,n\},$ if $f$ satisfies $\textbf{H}_i$ then $f$ and $\bm \alpha$ satisfy
   $\textbf{H}_i'$.
@@
 \[
-\deg \Delta_2 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
+\deg \Delta_2 \leq \sum_{i=1}^n \deg \Xi_i \leq n d^{2n}.
 \]
@@
 %
-\section{Proof of Theorem 3.1}
+\section{Proof of Theorem 2.1}
 %

### 2020-02-05 main.tex

--- 2020-02-05 main.tex
@@
 
+%% <<<<<<< HEAD
+%% =======
+%% Recall that we work with changes of variables with ``generic entries'' of new indeterminants $(\frak
+%% A_{i,j})_{1\le i,j \le n^2}$, and define the polynomial 
+%% $f^\fA:=f(\fA \Xb)$.
+Note that $f^\A$ satisfies $\textbf{H}_i(1).$ Indeed, otherwise it could not be that that the Jacobian of $f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$ has full rank at all $\xb \in V(f^A)$ for a generic $A \in \C^{n^2},$ which would contradict Popositon 3.1.
+The proof of this statement is routine and we omit details.
+We will rely on this
+%% fact in Section 8.
+
+%% >>>>>>> 3c8b7c51e8e3a65e188ffd3ac7465da21bedb71e
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%% =======
+%% %
+%% Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 4.2.
+Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$
+%%  we can write
+%% \[
+%% P_{j}(X_j) = a_j f^{\A} + \sum_{l=1}^{n-i}b_{j,l} \frac{\partial f^\A}{\partial X_{i+l}}, ~a_j,b_{j,l} \in \mathbb{Q}(\A)[\textbf{X}].
+%% \]
+%% For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $\mA \in \Gamma_j$,
+%% then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$.
+Define $h_j \in \Q[\A]$ to be the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$.
+Hence, if $\mA \in \C^{n^2}-V(h_j)$ then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l},$ which are providing the integral dependence relation.
+Now we define
+%% \[
+%% \Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 
+%% \]
+%% and we obtain a bound on the degree of $\Xi_i$ by observing that
+%% \[
+%% \deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
+%% \]
+%% Hence, if $\mA\in \Q^{n^2}-\Xi_i$ then
+%% \[
+%% P_j(X_j) \in \I^A,  
+%% \]
+%% for each $j \in \{i,\hdots,n\},$ and therefore the extension 
+%% \[
+%% \mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{\mA})
+%% \]
+%% is integral.
+We can obtain bounds for $h_j$ by applying an effective Nullstellensatz theorem.
+However, the theorem requires $P_{j}$ to be a polynomial.
+We can obtain a polynomial from $P_{j}$ by clearing denominators.
+We can multiply $P_{j}$ by the least common multiple of its denominators, which we will denote by $d_j \in \Q[\A]$.
+Put
+%% \[
+%% \overline{P_{j}} := d_jP_{j}\in \Q[\A][\Xb],
+%% \]
+%% and note that $\pjb(X_j) \in \I^{\A}$ with 
+%% \[
+%% \pjb(X_j) = \ajb f^{\A} + \sum_{l=1}^{n-i}\bjb \frac{\partial f^\A}{\partial X_{i+l}}, ~\ajb,\bjb \in \mathbb{Q}[\A][\textbf{X}].
+%% \]
+%% %
+%% \begin{proposition} 
+%% $\deg \pjb\leq (d+1)^{n-i+1}.$ 
+%% \end{proposition} 
+%% %
+%% \begin{proof}
+%% \textbf{Eric and Mark}: I am unsure of how to do this part correctly, so I will assume 
+%% \[
+%% \deg \pjb\leq \Dt_j.
+%% \]
+%% Let $\Is \subset \Q[\A,\Xb]$ be the extension of $\I^{\A}$ in  $\Q[\A,\Xb],$ and consider the finite field extension
+%% %
+%% \begin{align*}
+%%     \Q(\A,\Xb_{i-1}) &\rightarrow \Q(\A,\Xb_{i-1})[X_i,\hdots,X_n]/\Is.
+%% \end{align*}
+%% %
+%% The minimal polynomial of the linear mapping defined by multiplication by $X_j$ in $\Q(\A,\Xb_{i-1})$ is \textbf{almost}(?) equal to $\pjb$ (the leading coefficient of $\pjb$ is $d_j$).
+It therefore follows by \cite[Proposition 1]{CGR} that
+%% %
+%% \begin{align*}
+%% &\deg \pjb \leq (d+1)^{n-i+1}.&(2d)^{n-i+1}\textrm{?} 
+%% >>>>>>> 3c8b7c51e8e3a65e188ffd3ac7465da21bedb71e
+%% \end{align*}
+
 %% \[

### 2020-02-05 main.tex
things

@@
 \keywords{Real algebraic geometry, transversality, Noether
-  position, bit complexity}
+  normalization, bit complexity}
 
@@
 \begin{theorem}
-There exists a hypersurface $\Delta_1 \subset \C^{n^2}$ of degree at most $nd^{2n}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then, for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i(1)$.
+There exists a hypersurface $\Delta_1 \subset \C^{n^2}$ of degree at most $d^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then, for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i(1)$.
 \end{theorem}
@@
 \[
-\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq nd^{2n}.
+\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
 \]
@@
   There exists a Zariski closed set $\Delta_2 \subset \C^{n-1}$ of
-  degree at most $nd^{2n}$ with the property that, if $\bm\alpha \in \C^{n-1} - \Delta_2$, then, for each $i \in \{1,\hdots,n\},$ if $f$ satisfies $\textbf{H}_i$ then $f$ and $\bm \alpha$ satisfy
+  degree at most $d^{2n^2}$ with the property that, if $\bm\alpha \in \C^{n-1} - \Delta_2$, then, for each $i \in \{1,\hdots,n\},$ if $f$ satisfies $\textbf{H}_i$ then $f$ and $\bm \alpha$ satisfy
   $\textbf{H}_i'$.
@@
 \[
-\deg \Delta_2 \leq \sum_{i=1}^n \deg \Xi_i \leq n d^{2n}.
+\deg \Delta_2 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
 \]
@@
 $\C[\A][X_1,\dots,X_n][T]$, such that
-\begin{align*}
+\begin{align}\label{eq:nullst}
 \alpha_j = \sum_{\ell=1}^{n-i+1} A_{j,\ell} g_\ell + B_j (1-\pjb T),\ \  g_\ell \in 
@@
 \right\}.
-\end{align*}
+\end{align}
 
@@
 %% %
+
+Let us then define $\D_{3,i}:=\D_{2,i} \alpha_i \cdots \alpha_n$.
+This is a non-zero polynomial in $\C[\A]$; we will 
+estimate its degree below.
+
+\begin{lemma}
+  Suppose that $\mA \in \C^{n\times n}$ does not cancel
+  $\D_{3,i}$. Then $f^\mA$ satisfies ${\bf H}_i$.
+\end{lemma}
+\begin{proof}
+  By assumption, $\D_{2,i}(\mA)$ is non-zero, so that $\mA$ is invertible
+  and satisfies ${\bf H}_i(1)$.
+\end{proof}
 
@@
 %
-\section{Proof of Theorem 2.1}
+\section{Proof of Theorem 3.1}
 %

### 2020-02-05 main.tex
checked 2 and 3.1

--- 2020-02-05 main.tex
@@
 \usepackage[ruled,vlined]{algorithm2e}
+\usepackage[titles]{tocloft}%----------------------------------------
 \usepackage{mathrsfs}
@@
 version of facts we stated above, namely that in generic coordinates,
-polar varieties are smooth, equidimensional, and in Noether position.
+polar varieties are smooth, equidimensional, and in Noether position
+(or empty).
 
@@
 $\pi_d$ when the extension $\C[X_1,\hdots,X_d] \rightarrow
-\C[X_1,\hdots,X_n]/I(X)$ is injective and integral; here, $I(X)
-\subset \C[X_1,\dots,X_n]$ is the defining ideal of $X$. In this case,
-for any $\xb \in \C^d,$ the fiber $X \cap \pi_d^{-1}(\xb)$ has
-dimension zero (so it is finite and not empty).
-
-For $i$ in $\{1,\dots,n-1\}$ and $f$ as above, we will let $\I(i, f)$
+\C[X_1,\hdots,X_n]/I(X)$ is integral; here, $I(X) \subset
+\C[X_1,\dots,X_n]$ is the defining ideal of $X$. In this case, for any
+$\xb \in \C^d,$ the fiber $X \cap \pi_d^{-1}(\xb)$ has dimension zero
+(so it is finite and not empty).
+
+For $i$ in $\{1,\dots,n\}$ and $f$ as above, we will let $\I(i, f)$
 denote the sequence of $n-(i-1)$ polynomials $(f, {\pa f}/{\pa
-  X_{i+1}},\dots,{\pa f}/{\pa X_n})$. As we pointed out in the
-introduction, their zero-set is the $i$th polar variety $W(\pi_i,V(f))$.
-Then, we say that $f$ satisfies $\textbf{H}_i$ if
+  X_{i+1}},\dots,{\pa f}/{\pa X_n})$. As pointed out in the
+introduction, their zero-set is the $i$th polar variety
+$W(\pi_i,V(f))$.  Then, we say that $f$ satisfies $\textbf{H}_i$ if
 \begin{enumerate}
@@
   {\em By the Jacobian Criterion~\cite[Corollary 16.20]{ECA}, this
-  implies that $W(\pi_i,V(f))$ is either empty or $(i-1)$-equidimensional.}
+  implies that $W(\pi_i,V(f))$ is either empty or $(i-1)$-equidimensional,
+  and that $\I(i, f^\mA)$ is radical.}
 
@@
 \begin{enumerate}
-\item the $n$ equations
-  $(X_1-\alpha_1,\dots,X_{i-1}-\alpha_{i-1}),\I(i, f))$ generate a
+\item The $n$ polynomials
+  $(X_1-\alpha_1,\dots,X_{i-1}-\alpha_{i-1},\I(i, f))$ generate a
   radical ideal.
@@
 
-Even if $f$ does not satisfy $\textbf{H}_i$, we mentioned that it does
-after applying a change of variables. The precise statement is the
-following; to state it, we use the following notation. For a matrix
-$\mA$ in $\C^{n^2}$ and $g$ in $\C[X_1,\hdots,X_n]$ we write
-$g^\mA:=g(\mA \Xb) \in \C[X_1,\dots,X_n]$.
-
-%% , $\xb \in
-%% \mathbb{C}^n$ and $X \subset \C^n$. We write $\xb^\mA:=\mA^{-1}\xb$,
-%% $X^\mA:=\{x^\mA~|~\xb \in V\}$ and $g^\mA:=g(\mA \Xb) \in
-%% \C[X_1,\dots,X_n]$. In particular, we have $g^\mA(\xb^\mA) =g(\xb)$,
-%% and $V(f)^\mA=V(f^\mA)$.
-
-\begin{theorem}
-  There exists a hypersurface $\D \subset \mathbb{C}^{n^2}$ of degree
-  at most $\td$ such that, if $\mA$ is chosen from $\C^{n^2}-\Delta$
-  then $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for
-  all $i \in \{1,\hdots,n-1\}.$
+Even if $f$ does not satisfy $\textbf{H}_i$, we mentioned that it
+does, after applying a generic change of variables. The precise
+statement is the following; to state it, we use the following
+notation. For a matrix $\mA$ in $\C^{n\times n}$ and $g$ in
+$\C[X_1,\hdots,X_n]$ we write $g^\mA:=g(\mA \Xb) \in
+\C[X_1,\dots,X_n]$, where $\Xb$ is the column vector with entries
+$X_1,\dots,X_n$.
+
+We will also have to consider matrices with generic entries. For this,
+we introduce $n^2$ new indeterminates $(\frak A_{j,k})_{1\le j,k \le
+  n}$. Then, $\A$ will denote the matrix with entries $(\frak
+A_{j,k})_{1\le j,k \le n}$, $\C(\A)$ will denote the rational function
+field $\C((\frak A_{j,k})_{1\le j,k \le n})$ and $\C[\A]$ the
+polynomial ring $\C[(\frak A_{j,k})_{1\le j,k \le n}]$.  For $f$ as
+above, we will then define the polynomial $f^\A:=f(\A \Xb)$, 
+which we will consider in either
+$\C(\A)[X_1,\dots,X_n]$ or $\C[\A,X_1,\dots,X_n]$.
+
+\begin{theorem}\label{theo:gen}
+  For $i=1,\dots,n$, there exists a non-zero polynomial $\D_i$ in
+  $\C[\A]$ of degree at most $\td$ such that if $\mA \in \C^{n\times
+    n}$ does not cancel $\D_i$, then $\mA$ is invertible and $f^\mA$
+  satisfies $\textbf{H}_i$.
 \end{theorem}
-%% %
-%% \begin{corollary} 
-%%   Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1}
-%%   D^{\textrm{\td}}$ and $\epsilon > 0$. Then for $A\in S^{n^2}$ chosen
-%%   randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i
-%%   \in \{1,\hdots,n\}$ is at least $1-\epsilon.$
-%% \end{corollary}
-
-It will on occasion be useful to work with change of variables with
-``generic'' entries. For this, we will introduce $n^2$ new indeterminates
-$(\frak A_{j,k})_{1\le j,k \le n^2}$, we will let $\K$ be the field
-$\C(\frak A_{i,j})$, and use the corresponding
-matrix $\A$ over $\K$. For $f$ as above, we will then define the
-polynomial $f^\A:=f(\A \Xb) \in \K[X_1,\dots,X_n]$.
+\noindent The proof of this theorem occupies the next two sections.
 
@@
 quantitative version of it; this will allow us to establish the first
-item in property ${\bf H}_i$, as well as property ${\bf H}'_i$. Our
-presentation is inspired by that in~\cite{TWT}.
-
-%% ; it states that if a smooth function
-%% $F(\Xb,\Lambda)$, depending on parameters $\Lamdba$ in $\C^s$ is
-%% ``transverse'' to a certain submanifold in its domain space, then for
-%% most values $\lambda \in \C^s$, $F(\Xb,\lambda)$ remains
+item in property ${\bf H}_i$, as well as property ${\bf H}'_i$.
 
@@
 $Y=\C^v$, we have $T_{\bm y} Y=\C^v$ and this condition is equivalent
-to the Jacobian of $\bm \Psi$ having rank less than $t$ at $\bm y$.  A
-{\em regular point} of $\bm \Psi$ is a point on $Y$ that is not
-critical. {\em Critical values} are the images of critical points; the
+to the Jacobian of $\bm \Psi$ having rank less than $t$ at $\bm y$.
+{\em Critical values} are the images by $\Psi$ of critical points; the
 complement of this set are the {\em regular values} (so a regular
-value is not necessarily in the image of $\bm\Psi$).
-
-Let $n,\dt,$ and $m$ be positive integers, with $m \le n$, and denote
+value is not necessarily in the image of~$\bm\Psi$).
+
+Let then $n,\dt,$ and $m$ be positive integers, with $m \le n$, and denote
 by $\bm\Phi :\C^n \times \C^{\dt} ~ \rightarrow \C^{m}$ a mapping
@@
   Suppose that $\bm 0$ is a regular value of $\bm\Phi$. Then there
-  exists a hypersurface $\Delta \subset \C^{\dt}$ of degree at most
-  \td for which, if $\thetab \in \C^{\dt}-\Delta$, then $\bm 0$ is a
-  regular value of~$\bm\Phi_{\thetab}$.
+  exists a non-zero polynomial $\Gamma \in \C[\Thetab]$ of degree at
+  most $d^{m+n}$ such that for $\thetab$ in $\C^\dt$, if
+  $\Gamma(\thetab)\ne 0$, then $\bm 0$ is a regular value
+  of~$\bm\Phi_{\thetab}$.
 \end{proposition}
@@
 squarefree $f$ in $\C[X_1,X_2]$, such that $V(f)$ is a smooth curve in
-$\C^2$, and let the mapping $\bm\Phi:\C^2\times \C \to \C^2$ be defined
-by $\bm\Phi(X_1,X_2,\Lambda) = (f(X_1,X_2), X_1-\Lambda)$. One checks
-that the Jacobian of $\bm\Phi$ with respect to $(X_1,X_2,\Lambda)$ has
-rank two at any point in $\bm\Phi^{-1}(\bm 0)$, so the assumptions of the
-proposition apply. We deduce that for a generic $\lambda$ in $\C$,
-that is, for all $\lambda$ in $\C$ except a finite number, the ideal
-$(f(X_1,X_2), X_1-\lambda)$ is radical in $\C[X_1,X_2]$; equivalently,
-$f(\lambda, X_2)$ is squarefree. We will revisit this example in
-Section~\td.
-
-The rest of the section is devoted to the proof of the proposition.
+$\C^2$, and let the mapping $\bm\Phi:\C^2\times \C \to \C^2$ be
+defined by $\bm\Phi(X_1,X_2,\Theta) = (f(X_1,X_2), X_1-\Theta)$. One
+checks that the Jacobian of $\bm\Phi$ with respect to
+$(X_1,X_2,\Theta)$ has rank two at any point in $\bm\Phi^{-1}(\bm 0)$,
+so the assumptions of the proposition apply. We deduce that for a
+generic $\vartheta$ in $\C$, that is, for all $\vartheta$ in $\C$
+except a finite number, the ideal $(f(X_1,X_2), X_1-\vartheta)$ is
+radical in $\C[X_1,X_2]$; equivalently, $f(\vartheta, X_2)$ is
+squarefree. We will revisit this example in Section~\ref{ssec:fiber}.
+
+The rest of the subsection is devoted to the proof of the proposition.
 The proof of \cite[Theorem B.3]{TWT} already shows the existence of
-$\Delta$; it is essentially the classical proof for smooth
+$\Gamma$; it is essentially the classical proof for smooth
 mappings~\cite[Section~3.7]{demazure2000bifurcations}, written in an
 algebraic context. In what follows, we revisit this proof,
-establishing a bound on the degree of $\Delta$.
-
-We will reuse the following fact proved in~\cite{TWT}.  Put $V =
-\bm\Phi^{-1}(0)$ and consider the projection $\pi:(\xb, \thetab) \in
-\C^n \times \C^{\dt} \mapsto \thetab \in\C^{\dt}$.  If $V$ is empty,
-there is nothing to do, since all values $\thetab$ in $\C^\dt$ satisfy
-the conclusion of the theorem. Thus, we assume that $V$ is not
-empty. Then, the Jacobian criterion shows that $V$ is
-smooth and $(n+ \dt -m)$-equidimensional.
-
-Let $Z$ be the set of critical points of $\pi_{|V}$, and consider its
-projection $\pi(Z)$ in $\C^s$. This is the set of critical values of
-$\pi_{|V}$; hence, by the algebraic form of Sard's lemma (see
-\cite[Theorem~3.7]{Mumford76} for irreducible $V$
+establishing a bound on the degree of $\Gamma$.
+
+Put $V = \bm\Phi^{-1}(\bm 0)$. If $V$ is empty, there is nothing to do,
+since all values $\thetab$ in $\C^\dt$ satisfy the conclusion of the
+proposition. Thus, we assume that $V$ is not empty. Then, the Jacobian
+criterion shows that $V$ is smooth and $(n+ \dt -m)$-equidimensional.
+
+We will reuse the following fact, proved in~\cite{TWT}.  Consider the
+projection $\pi:(\xb, \thetab) \in \C^n \times \C^{\dt} \mapsto
+\thetab \in\C^{\dt}$.  Let $Z$ be the set of critical points of
+$\pi_{|V}$, and consider its projection $\pi(Z)$ in $\C^s$. This is
+the set of critical values of $\pi_{|V}$; hence, by the algebraic form
+of Sard's lemma (see \cite[Theorem~3.7]{Mumford76} for irreducible $V$
 and~\cite[Proposition~B.2]{TWT} for general $V$), its Zariski closure
-$\overline{\pi(Z)}$ is a strict closed subset of $\C^s$. Now, the
-proof of \cite[Theorem B.3]{TWT} shows that if $\thetab \in \C^{\dt}$
-is not in $\overline{\pi(Z)}$, then $\bm 0$ is a critical value of
-$\bm\Phi_{\thetab}$. Hence, it suffices to prove that $Z$ has degree
-at most $d^{m+n}$; this will imply the same degree bound for
-$\overline{\pi(Z)}$, and prove our propositon.
-
-We first describe the set $Z$ of critical points of $\pi_{|V}$.  Let
-$M$ denote the $(s+m) \times (s+n)$ matrix with entries in
-$\C[\Xb,\Thetab]$ given by $M = \jac_{\Xb,\Thetab}(\pi,\bm\Phi)$, that
-is,
+$\overline{\pi(Z)}$ is a strict closed subset of $\C^s$. As we will
+see below, if $\thetab \in \C^{\dt}$ is not in $\overline{\pi(Z)}$,
+then $\bm 0$ is a regular value of $\bm\Phi_{\thetab}$.
+
+% Now, the proof of \cite[Theorem B.3]{TWT} shows that if $\thetab \in
+% \C^{\dt}$ is not in $\overline{\pi(Z)}$, then $\bm 0$ is a regular
+% value of $\bm\Phi_{\thetab}$.
+
+To describe the set $Z$ of critical points of $\pi_{|V}$, let $\bm M$
+denote the $(s+m) \times (s+n)$ Jacobian matrix with entries in
+$\C[\Xb,\Thetab]$ given by $\bm M = \jac_{\Xb,\Thetab}(\pi,\bm\Phi)$,
+that is,
 \begin{align*}
-M &= 
+\bm M &= 
 \bbm 
@@
 \textbf{0}_{\dt \times n}\hspace{5mm}\textbf{I}_{\dt} \\
-\jac_{(\Xb,\Thetab)}(\bm\Phi)
+\jac_{\Xb,\Thetab}(\bm\Phi)
 \ebm.
@@
 \begin{lemma} 
-  For $(\xb,\thetab)$ in $V$, the matrix $M$ has full rank $\dt+m$ at
-  $(\xb,\thetab)$ if and only if $(\xb,\thetab)$ is a regular point of
-  $\pi_{|V}.$
+  For $(\xb,\thetab)$ in $V$, $(\xb,\thetab)$ is in $Z$ if and only if
+  the matrix $\bm M$ has rank less than $\dt+m$ at $(\xb,\thetab)$.
 \end{lemma}
 \begin{proof}
-  Take $(\xb,\thetab)$ on $V$, and let $K(\xb,\thetab)$ be the
-  Jacobian matrix $\jac_{(\Xb,\Thetab)}(\bm\Phi)$ at $(\xb,\thetab)$.
-  Then, the rank of $M(\xb,\thetab)$ can be written as
-  $\textup{rank}(K(\xb,\thetab)) + \textup{rank}([\textbf{0}_{\dt
-      \times n}~\textbf{I}_{\dt}] \mid \ker K(\xb,\thetab))$, where
+  Take $(\xb,\thetab)$ on $V$, and let $\bm K(\xb,\thetab)$ be the
+  Jacobian matrix $\jac_{\Xb,\Thetab}(\bm\Phi)$ taken at $(\xb,\thetab)$.
+  Then, the rank of $\bm M(\xb,\thetab)$ can be written as
+  $\textup{rank}(\bm K(\xb,\thetab)) + \textup{rank}([\textbf{0}_{\dt
+      \times n}~\textbf{I}_{\dt}] \mid \ker \bm K(\xb,\thetab))$, where
   the latter is the rank of the restriction of $[\textbf{0}_{\dt
       \times n}~\textbf{I}_{\dt}]$ to the nullspace of
-  $K(\xb,\thetab)$.
-
-  Since $V$ is smooth, $K(\xb,\thetab)$ has full rank ${\rm codim} (V)
-  = m$. On the other hand, the nullspace of $K(\xb,\thetab)$ is the
-  tangent space $T_{\xb,\thetab} V$, and
+  $\bm K(\xb,\thetab)$.
+
+  Since $V$ is smooth, $\bm K(\xb,\thetab)$ has full rank ${\rm codim}
+  (V) = m$. On the other hand, the nullspace of $\bm K(\xb,\thetab)$
+  is the tangent space $T_{\xb,\thetab} V$, and
   $\textup{rank}([\textbf{0}_{\dt \times n}~\textbf{I}_{\dt}] \mid
-  \ker K(\xb,\thetab))$ is the dimension of $\pi(T_{\xb,\thetab} V)$.
-  In other words, the rank of $M(\xb,\thetab)$ is equal to
-  $m+\dim(\pi(T_{\xb,\thetab} V))$; this implies the claim in the lemma.
+  \ker \bm K(\xb,\thetab))$ is the dimension of $\pi(T_{\xb,\thetab}
+  V)$.  In other words, the rank of $\bm M(\xb,\thetab)$ is equal to
+  $m+\dim(\pi(T_{\xb,\thetab} V))$; this implies the claim in the
+  lemma.
 \end{proof}
@@
 $\pi_{|V}$ as those points satisfying $\bm\Phi(\xb,\thetab)=\bm 0$ and
-where all minors of $M$ of order $\dt+m$ vanish. We can describe this
-set using fewer equations, by discarding certain minors that are
-identically zero. Let indeed $J$ denote the $m \times n$ submatrix of
-the Jacobian of $\bm\Phi$ consisting of the first $n$ columns.
+where all minors of $\bm M$ of order $\dt+m$ vanish. We can actually
+describe this set using a smaller matrix, by discarding certain minors
+that are identically zero. Let indeed $\bm J$ denote the $m \times n$
+submatrix of the Jacobian of $\bm\Phi$ consisting of the first $n$
+columns. This is the Jacobian matrix of $\bm \Phi$ with respect to $\Xb$.
 \begin{lemma} 
   For $(\xb,\thetab)$ in $V$, $(\xb,\thetab)$ is in $Z$ if and only if
-  $J(\xb,\thetab)$ has rank less than $m$.
+  $\bm J(\xb,\thetab)$ has rank less than $m$.
 \end{lemma}
@@
 \textbf{0}_{\dt \times n} &\textbf{I}_{\dt} \\
-J(\xb,\thetab)     &J'(\xb,\thetab)
+\bm J(\xb,\thetab)     &\bm J'(\xb,\thetab)
 \ebm,
 \end{align*}
-where $J'$ consists of the remaining columns of the Jacobian matrix of
+where $\bm J'$ consists of the remaining columns of the Jacobian matrix of
 $\bm\Phi$.  Then, the rank of the former matrix is equal to the rank
@@
 \textbf{0}_{\dt \times n} &\textbf{I}_{\dt} \\
-J(\xb,\thetab)     & \bm 0_{m \times s}
+\bm J(\xb,\thetab)     & \bm 0_{m \times s}
 \ebm,
@@
 \end{proof}
-Therefore, the set $Z$ can be defined as the set of all
-$(\xb,\thetab)$ in $\C^{n+\dt}$ satisfying $\bm\Phi(\xb,\thetab)=\bm
-0$ and where all minors of $J$ of order $m$ vanish. Our next step is
-to bound the degree of $Z$. For this, rather than considering minors
-of $J$, we will rewrite the condition that $J(\xb,\thetab)$ has rank
-less than $m$ as the existence of a non-trivial left kernel element.
+
+In particular, take $\thetab$ in $\C^\dt - \overline{\pi(Z)}$.
+Then for all $\xb$ in $\bm \Phi_{\thetab}^{-1}(\bm 0)$, $(\xb,\thetab)$
+is in $V$, so it is not in $Z$. The previous lemma then implies that
+the Jacobian matrix $\bm J$ of $\bm\Phi_{\thetab}$ has full rank $m$ at
+$(\xb,\thetab)$. In other words, $\bm 0$ is a regular value of $\bm
+\Phi_{\thetab}$, as claimed.
+
+Our next step is to bound the degree of $Z$.  In that, we use the
+definition of degree given in~\cite{H}: the degree of an irreducible
+algebraic set is the number of intersection points it has with a
+generic hyperplane of complementary dimension, and the degree of an
+arbitrary algebraic set is the sum of the degrees of its irreducible
+components.  To obtain an estimate on the degree of $Z$, rather than
+considering minors of $\bm J$, we will rewrite the condition that $\bm
+J(\xb,\thetab)$ has rank less than $m$ as the existence of a
+non-trivial left kernel element.
 
@@
 \[
-[\mathscr{L}_1 \cdots \mathscr{L}_{n}]=\textit{\textbf{L}}\cdot J(\xb,\thetab).
+[\mathscr{L}_1 \cdots \mathscr{L}_{n}]=\textit{\textbf{L}}\cdot \bm J(\xb,\thetab).
 \] 
@@
 the vanishing of $\mathscr{L}_1,\hdots,\mathscr{L}_{n},$ and
-$\bm\Psi$, and by $\frak{Z}'$ the algebraic set
+$\bm\Phi$, and by $\frak{Z}'$ the algebraic set
 \[
@@
 
-  Conversely, take an irreducible component $Y$ of $\frak Z'$. We prove 
-  that $\mu(Y)$ is contained in $Z$.
-  By construction, there exists an open dense subset $Y^o \subset Y$
-  such that for any $(\xb,\thetab,\bm \ell)$ in $Y^o$, $\bm \ell$ is
-  not identically zero. As a result, $(\xb,\thetab)$ is in $Z$, that
-  is, $\mu(Y^o)$ is in $Z$. This implies that its Zariski closure
-  $\overline{\mu(Y^o)}$ is in $Z$. Since $\mu(Y)$ is contained in
-  $\overline{\mu(Y^o)}$, we have $\mu(Y) \subset Z$. Taking 
-  the union over all $Y$, we get $\mu(\frak Z') \subset Z$, as claimed.
+  Conversely, take an irreducible component $Y$ of $\frak Z'$. We
+  prove that $\mu(Y)$ is contained in $Z$.  By construction, there
+  exists an open dense subset $Y^o \subset Y$ such that for any
+  $(\xb,\thetab,\bm \ell)$ in $Y^o$, $\bm \ell$ is not identically
+  zero. As a result, $(\xb,\thetab)$ is in $Z$, that is, $\mu(Y^o)$ is
+  in $Z$. This implies that its Zariski closure $\overline{\mu(Y^o)}$
+  is in $Z$. Since $\mu(Y)$ is contained in $\overline{\mu(Y^o)}$, we
+  deduce $\mu(Y) \subset Z$. Taking the union over all $Y$, we get
+  $\mu(\frak Z') \subset Z$, as claimed.
 \end{proof}
@@
   Theorem~\cite{H} that $\deg(\frak{Z}) \leq d^{m+n}$, and the same
-  upper bound holds for $\deg(\frak{Z}')$. Applying the projection
-  $\mu$ yields the result.
+  upper bound holds for $\deg(\frak{Z}')$, since it consists of
+  certain irreducible components of $\frak Z$. Applying the projection
+  $\mu$ yields the result, since degree cannot increase through
+  projection.
 \end{proof}
 
-%% <<<<<<< HEAD
-%% =======
-%% Recall that we work with changes of variables with ``generic entries'' of new indeterminants $(\frak
-%% A_{i,j})_{1\le i,j \le n^2}$, and define the polynomial 
-%% $f^\fA:=f(\fA \Xb)$.
-Note that $f^\A$ satisfies $\textbf{H}_i(1).$ Indeed, otherwise it could not be that that the Jacobian of $f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$ has full rank at all $\xb \in V(f^A)$ for a generic $A \in \C^{n^2},$ which would contradict Popositon 3.1.
-The proof of this statement is routine and we omit details.
-We will rely on this
-%% fact in Section 8.
-
-%% >>>>>>> 3c8b7c51e8e3a65e188ffd3ac7465da21bedb71e
+In particular, we obtain the same degree bound for
+$\overline{\pi(Z)}$.  It then suffices to take for $\Gamma$ any
+non-zero polynomial of degree at most $d^{m+n}$ that vanishes on
+$\overline{\pi(Z)}$; this proves Proposition~\ref{prop:weak_t}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Application: property $\textbf{H}'_i$}
+\subsection{Application: property $\textbf{H}'_i$}\label{ssec:fiber}
 %
@@
   \C(\A)[X_1,\dots,X_{i-1},X_j]$, monic in $X_j$, with $\pjb$ in
-  $\I^\A$, and such that $\deg(\pjb)\leq (2d)^{n-i+1}.$
+  $\I^\A$, and such that $\deg(\pjb)\leq (2d)^{n}.$
 \end{lemma} 
@@
   degree at most $2d$, the B\'ezout inequality of~\cite{H} gives
-  $\deg(\pjb) \le (2d)^{n-i+1}$.
+  $\deg(\pjb) \le (2d)^{n-i+1} \le (2d)^n$.
 \end{proof}
@@
 denominators, we obtain the existence of $\alpha_j$ in
-$\C[\A]\setminus\{0\}$ and $ A_{j,\ell},B_j$ in
+$\C[\A]-\{0\}$ and $ C_{j,\ell},B_j$ in
 $\C[\A][X_1,\dots,X_n][T]$, such that
-\begin{align*}
-\alpha_j = \sum_{\ell=1}^{n-i+1} A_{j,\ell} g_\ell + B_j (1-\pjb T),\ \  g_\ell \in 
+\begin{align}\label{eq:nullst}
+\alpha_j = \sum_{\ell=1}^{n-i+1} C_{j,\ell} G_\ell + B_j (1-\pjb T),\ \  G_\ell \in 
 \left\{ 
@@
 \right\}.
+\end{align}
+
+Let us then define 
+$$\D_{3,i}:=\D_{2,i} \alpha_i \cdots \alpha_n D_i \cdots D_n,$$
+where, for all $j$, $\alpha_j$ is as above and $D_j$ is the leading
+coefficient of $\pjb$ with respect to $X_j$. Thus, $\D_{3,i}$ is a
+non-zero polynomial in $\C[\A]$; we will estimate its degree below.
+
+\begin{lemma}
+  Suppose that $\mA \in \C^{n\times n}$ does not cancel
+  $\D_{3,i}$. Then $f^\mA$ satisfies ${\bf H}_i$.
+\end{lemma}
+\begin{proof}
+  By assumption, $\D_{2,i}(\mA)$ is non-zero, so that $\mA$ is
+  invertible and $f^\mA$ satisfies ${\bf H}_i(1)$. In particular, the
+  ideal $\I(i, f^\mA)$ is radical, and its zero-set
+  $W(\pi_i,V(f^\mA))$ is either empty or $(i-1)$-equidimensional. If it is 
+  empty, we are done.
+
+  Otherwise, for $j=i,\dots,n$, evaluate all indeterminates in $\A$ at the
+  corresponding entries of $\mA$ in~\eqref{eq:nullst}. This gives us
+  an equality in $\C[X_1,\dots,X_n,T]$ of the form
+  \begin{align*}
+    a_j = \sum_{\ell=1}^{n-i+1} c_{j,\ell} g_\ell + b_j (1-p_j T),\ \  g_\ell \in 
+    \left\{ 
+      f^\mA,\frac{\partial f^\mA}{\partial X_{i+1}},\hdots,\frac{\partial f^\mA}{\partial X_n}
+    \right\},
   \end{align*}
-
-%% =======
-%% %
-%% Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 4.2.
-Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$
-%%  we can write
-%% \[
-%% P_{j}(X_j) = a_j f^{\A} + \sum_{l=1}^{n-i}b_{j,l} \frac{\partial f^\A}{\partial X_{i+l}}, ~a_j,b_{j,l} \in \mathbb{Q}(\A)[\textbf{X}].
-%% \]
-%% For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset \C^{n^2}$ such that if $\mA \in \Gamma_j$,
-%% then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l}$.
-Define $h_j \in \Q[\A]$ to be the product of the denominators of the coefficients of $a_j$ and $b_{j,l}$.
-Hence, if $\mA \in \C^{n^2}-V(h_j)$ then $\mA$ cancels none of the denominators of $a_{j}$ or $b_{j,l},$ which are providing the integral dependence relation.
-Now we define
-%% \[
-%% \Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 
-%% \]
-%% and we obtain a bound on the degree of $\Xi_i$ by observing that
-%% \[
-%% \deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
-%% \]
-%% Hence, if $\mA\in \Q^{n^2}-\Xi_i$ then
-%% \[
-%% P_j(X_j) \in \I^A,  
-%% \]
-%% for each $j \in \{i,\hdots,n\},$ and therefore the extension 
-%% \[
-%% \mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{\mA})
-%% \]
-%% is integral.
-We can obtain bounds for $h_j$ by applying an effective Nullstellensatz theorem.
-However, the theorem requires $P_{j}$ to be a polynomial.
-We can obtain a polynomial from $P_{j}$ by clearing denominators.
-We can multiply $P_{j}$ by the least common multiple of its denominators, which we will denote by $d_j \in \Q[\A]$.
-Put
-%% \[
-%% \overline{P_{j}} := d_jP_{j}\in \Q[\A][\Xb],
-%% \]
-%% and note that $\pjb(X_j) \in \I^{\A}$ with 
-%% \[
-%% \pjb(X_j) = \ajb f^{\A} + \sum_{l=1}^{n-i}\bjb \frac{\partial f^\A}{\partial X_{i+l}}, ~\ajb,\bjb \in \mathbb{Q}[\A][\textbf{X}].
-%% \]
-%% %
-%% \begin{proposition} 
-%% $\deg \pjb\leq (d+1)^{n-i+1}.$ 
-%% \end{proposition} 
-%% %
-%% \begin{proof}
-%% \textbf{Eric and Mark}: I am unsure of how to do this part correctly, so I will assume 
-%% \[
-%% \deg \pjb\leq \Dt_j.
-%% \]
-%% Let $\Is \subset \Q[\A,\Xb]$ be the extension of $\I^{\A}$ in  $\Q[\A,\Xb],$ and consider the finite field extension
-%% %
-%% \begin{align*}
-%%     \Q(\A,\Xb_{i-1}) &\rightarrow \Q(\A,\Xb_{i-1})[X_i,\hdots,X_n]/\Is.
-%% \end{align*}
-%% %
-%% The minimal polynomial of the linear mapping defined by multiplication by $X_j$ in $\Q(\A,\Xb_{i-1})$ is \textbf{almost}(?) equal to $\pjb$ (the leading coefficient of $\pjb$ is $d_j$).
-It therefore follows by \cite[Proposition 1]{CGR} that
-%% %
-%% \begin{align*}
-%% &\deg \pjb \leq (d+1)^{n-i+1}.&(2d)^{n-i+1}\textrm{?} 
-%% >>>>>>> 3c8b7c51e8e3a65e188ffd3ac7465da21bedb71e
-%% \end{align*}
-
-%% \[
-%% \C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V)
-%% \]
-%% injective and  integral.
-
-%%  Since $P_{j}(X_j) \in\I^{\A}= \langle
-%% f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial
-%%   f^\A}{\partial X_n} \rangle,$ we can write
-%% \[
-%% P_{j}(X_j) = a_j f^{\A} + \sum_{l=1}^{n-i}b_{j,l} \frac{\partial f^\A}{\partial X_{i+l}}, ~a_j,b_{j,l} \in \mathbb{Q}(\A)[\textbf{X}].
-%% \]
-%% For each $P_j,$ there exists a Zariski open set $\Gamma_j \subset
-%% \C^{n^2}$ such that if $A \in \Gamma_j$, then $A$ cancels none of the
-%% denominators of $a_{j}$ or $b_{j,l}$. Define $h_j \in \Q[\A]$ to be
-%% the product of the denominators of the coefficients of $a_j$ and
-%% $b_{j,l}$. Hence, if $A \in \Q^{n^2}-V(h_j)$ then $A$ cancels none of
-%% the denominators of $a_{j}$ or $b_{j,l},$ which are providing the
-%% integral dependence relation. Now we define
-%% \[
-%% \Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 
-%% \]
-%% and we obtain a bound on the degree of $\Xi_i$ by observing that
-%% \[
-%% \deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
-%% \]
-%% Hence, if $A\in \Q^{n^2}-\Xi_i$ then
-%% \[
-%% P_j(X_j) \in \I^A,  
-%% \]
-%% for each $j \in \{i,\hdots,n\},$ and therefore the extension 
-%% \[
-%% \mathbb{C}[{\Xb}_{\leq i-1}]\rightarrow\mathbb{C}[\Xb]/\I(\pi_i,V^{A})
-%% \]
-%% is integral. We can obtain bounds for $h_j$ by applying an effective
-%% Nullstellensatz theorem.
-
-%% %
-%% Note that 
-%% \[
-%% \deg d_j \leq \deg \pjb \leq \Dt_j.
-%% \]
-%% %
-%% \subsection{Applying the effective Nullstellensatz}
-%% %
-
-To apply the effective Nullstellensatz theorem, we first need to
-determine degree bounds, separately in $\Xb$ and $\A,$ of the
-polynomials in the membership relationship. We have
-\[
-\deg_{\Xb}\left\{ 
+  for $a_j$ in $\C$, polynomials $c_{j,\ell}$ and $b_j$ in
+  $\C[X_1,\dots,X_n,T]$ and $p_j$ in
+  $\C[X_1,\dots,X_{i-1},X_j]$. Since neither $\alpha_j$ nor $D_j$
+  vanish at $\mA$, $a_j$ is non-zero and the leading coefficient of
+  $p_j$ in $X_j$ is a non-zero constant.
+
+  The conclusion is now routine. Replace $T$ by $1/p_j$ in the
+  previous equality; after clearing denominators, this gives a
+  membership equality of the form $p_j{}^k \in \I(i, f^\mA)$, for some
+  integer $k \ge 1$ (we cannot have $k=0$, since we assumed that
+  $W(\pi_i,V(f^\mA))$ is not empty). Since $\I(i, f^\mA)$ is radical,
+  $p_j$ is in $\I(i, f^\mA)$. Repeating this for all $j$ proves that 
+  $\C[X_1,\dots,X_{i-1}]\rightarrow\C[X_1,\dots,X_n]/\I(i, f^\mA)$
+  is integral.
+\end{proof}
+
+To estimate the degree of $\D_{3,i}$, what remains is to give an upper
+bound on the degree of $\alpha_i,\dots,\alpha_n$. This will come as an
+application of the effective Nullstellensatz given in~\cite{EN}, for
+which we first need to determine degree bounds, separately in $\Xb,T$
+and $\A,$ of the polynomials in the membership relationship. We have
+\begin{align*}
+\deg_{\Xb,T}\left\{ 
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\}\leq d,
-\]
-\[
+\right\}&\leq d\\
 \deg_{\A}  
@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\} \leq d,
-\]
-\[
-\deg_{\Xb,T}(1-T\pjb) \leq \Dt_j +1 
-\]
-and
-\[
-\deg_{\A}(1-T\pjb) \leq \Dt_j.
-\]
-For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, 
-%
-and with the degree of $\alpha_j$ upper bounded by
-%
-\begin{align*}
-    &\left(\prod_{k=1}^{n-i+1} d\right)\Dt_j 
-    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}d \right)d\\
-    = &\left(d^{n-i+1}\right)\Dt_j+
-    (n-i+1)\left(\Dt_j+1\right)\left(d^{n-i+1} \right)\\
-    &\leq d^{n}\Dt_j + n\left(\Dt_j+1\right)d^{n}\\
-    &=d^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
+\right\}& \leq d\\
+\deg_{\Xb,T}(1-T\pjb) &\leq (2d)^n +1 \\
+\deg_{\A}(1-T\pjb)& \leq (2d)^n.
 \end{align*}
-%
-Now we will show that $\alpha_j$ is the only remaining denominator whose degree we need to bound. Substitute $T \leftarrow 1/\pjb$ so that 
-\[
-\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l + 0
-\]
-and
-%
-\begin{align*}
-A_{j,l}(\A,\Xb,1/\pjb) 
-&= \sum_{i=1}^{n_l} A_{j,l,i}(\A,\Xb,1/\pjb)\\
-&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\Xb), ~k_i \in \mathbb{Z}.
-\end{align*}
-%
-Let $K := \max\{k_l\}$ so that 
-%
-\begin{align*}
-    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l\right)\\
-    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{i}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb].
-\end{align*}
-%
-which shows that $\alpha_j$ is the only remaining denominator whose degree we need to bound other than $d_j$. Note as well that
-\[
-\pjb^K \in \I^{\A}.
-\]
-Therefore 
-%
-\begin{align*}
-\deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
-    &\leq \left(d^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
-    &=d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
-\end{align*}
-%
-\subsection{Proof of Theorem 7.1}
-%
-Now we obtain
-%
-\begin{align*}
-    \deg \Xi_i 
-    &\leq \sum_{j=i}^n \deg h_j\\
-    &\leq  \sum_{j=i}^n \left( d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
-    &=  (n-i+1)\left( d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
-    &\leq  n d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
-\end{align*}
-%
-And therefore,  
-%
-\begin{align*}
-    \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
-    &\leq n^2 d^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
-\end{align*}
-%
-where if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in \{1,\hdots,n\},$ the extension 
-\[
-\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
-\]
-
-is integral.
-%
-%
-%
-%
-\section{Proof of Theorem 2.1}
-%
-Recall Theorem 3.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
+For each $j \in \{i,\hdots,n\},$ a direct application of \cite[Theorem
+0.5]{EN}, gives $\deg(\alpha_j) \le (n+1)d^n((2d)^n+1)$; we will use
+the slightly less precise bound $\deg(\alpha_j) \le 2n(2d)^{2n}$.
+
+\td finish the degree bound.
+
+% \section{Proof of Theorem 2.1}
+% %
+% Recall Theorem 3.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
 Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$}
-%
-\begin{proof}
-Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
+% %
+% \begin{proof}
+% Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
 Clearly then, if
-\[
-A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
-\]
-then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
-\[
-\Delta = \bigcup_{i=1}^3 \D_i,
-\]
-and note that 
-\[
-\deg \D \leq  \sum_{i=1}^3 \deg \D_i.
-\]
-\end{proof}
-%
-Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
+% \[
+% A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
+% \]
+% then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
+% \[
+% \Delta = \bigcup_{i=1}^3 \D_i,
+% \]
+% and note that 
+% \[
+% \deg \D \leq  \sum_{i=1}^3 \deg \D_i.
+% \]
+% \end{proof}
+% %
+% Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
 Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
-%
-\begin{proof}
-\[
-Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
-\]
-\end{proof}
-%
-%
-%
-%
+% %
+% \begin{proof}
+% \[
+% Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
+% \]
+% \end{proof}
+% %
+% %
+% %
+% %
 \section{Bit complexity}

### 2020-02-06 main.tex
Updates from Overleaf

--- 2020-02-05 main.tex
@@
   at most $\td$ such that, if $\mA$ is chosen from $\C^{n^2}-\Delta$
-  then $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for
+  then $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ and $\textbf{H}_i^{'}$ for
   all $i \in \{1,\hdots,n-1\}.$
@@
 %
-\section{Proof of Theorem 2.1}
-%
-Recall Theorem 3.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
-Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$}
-%
-\begin{proof}
-Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
-Clearly then, if
-\[
-A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
-\]
-then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
-\[
-\Delta = \bigcup_{i=1}^3 \D_i,
-\]
-and note that 
-\[
-\deg \D \leq  \sum_{i=1}^3 \deg \D_i.
-\]
-\end{proof}
-%
-Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
-Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
-%
-\begin{proof}
-\[
-Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
-\]
-\end{proof}
-%
-%
-%
-%
 \section{Bit complexity}
@@
     \caption{{Main Algorithm} \label{}}
-\nl Randomly choose a point $p_{n-1}=(\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}~(p_0$?)\; 
+\nl Choose $T \subset \mathbb{Q}$ and $\alpha_{n-1}=(\alpha_1,\hdots,\alpha_{n-1}) \in T^{n-1}$ with $|T| \geq \epsilon^{-1}d^{\td}$\; 
 \nl \For{$i\gets1$ \KwTo $n$}{
@@
 \end{algorithm}
-
+\clearpage 
 %
@@
 %
+Recall Theorem 2.1: \textit{  There exists a hypersurface $\D \subset \mathbb{C}^{n^2}$ of degree at most $\td$ such that, if $\mA$ is chosen from $\C^{n^2}-\Delta$ then $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ and $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n-1\}.$}
+%
+\begin{proof}
+Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
+Clearly then, if
+\[
+A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
+\]
+then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
+\[
+\Delta = \bigcup_{i=1}^3 \D_i,
+\]
+and note that 
+\[
+\deg \D \leq  \sum_{i=1}^3 \deg \D_i.
+\]
+\end{proof}
+%
+Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
+Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
+%
+\begin{proof}
+\[
+Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
+\]
+\end{proof}
 \textbf{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
@@
 \begin{enumerate}
-    \item By our assumption on the size of $S$ we know that $|S| = \log (\epsilon^{-1}D^{\td}) \leq \td.$ Thus for $a_{ij} \in S$ we know that $|a_{ij}| \leq \td.$
+    \item We assume that $S=\{1,2,\hdots,\epsilon^{-1}\td\}$. Therefore, the height of $a_{ij} \in S$ is bounded by $\log \td -\log \epsilon.$
     \item 
@@
         &= 
-        O^\sim(\log(d+1)).
+        O^\sim(n\log(d)- \log \epsilon).
         \end{align*}

### 2020-02-06 main.tex
sec 3

--- 2020-02-05 main.tex
@@
 \def\exp{\textrm{exp}}
-\def\grad{\textrm{grad}}
+\def\grad{\textbf{grad}}
 \def\rank{\textrm{rank}}
@@
 \item For any $\xb$ in $W(\pi_i,V(f))$, the Jacobian matrix
-  $\jac(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.
+  $\jac_\Xb(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.
 
@@
 \end{enumerate}
-When this holds, given $\bm \alpha = (\alpha_1,\hdots,\alpha_{i-1})$
-in $\C^{i-1}$, we further say that $f$ and $\bm \alpha$ satisfy
+When this holds, given $\bm \sigma = (\sigma_1,\hdots,\sigma_{i-1})$
+in $\C^{i-1}$, we further say that $f$ and $\bm \sigma$ satisfy
 $\textbf{H}'_i$ if
 \begin{enumerate}
-\item The $n$ polynomials
-  $(X_1-\alpha_1,\dots,X_{i-1}-\alpha_{i-1},\I(i, f))$ generate a
-  radical ideal.
+\item The ideal  $(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
+  X_{i+1}},\dots,{\pa f}/{\pa X_n})$ is
+  radical.
 
@@
 above, we will then define the polynomial $f^\A:=f(\A \Xb)$, 
-which we will consider in either
+which we may consider in either
 $\C(\A)[X_1,\dots,X_n]$ or $\C[\A,X_1,\dots,X_n]$.
 
+\smallskip
+
+This being said, our two key results are the following.
 \begin{theorem}\label{theo:gen}
@@
 \end{theorem}
-\noindent The proof of this theorem occupies the next two sections.
+
+\begin{theorem}
+  Suppose that $f$ satisfies $\textbf{H}_i$. There exists a non-zero
+  polynomial $\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ of degree at most
+  $d^{2n}$ such that if $\bm \sigma \in \C^{i-1}$ does not
+  cancel $\Xi_{i}$, then $f$ and $\bm \sigma$ satisfy $\textbf{H}_i'$.
+\end{theorem}
+\noindent 
+The proof of these theorems occupies the next two sections.
 
@@
 then $\bm 0$ is a regular value of $\bm\Phi_{\thetab}$.
-
-% Now, the proof of \cite[Theorem B.3]{TWT} shows that if $\thetab \in
-% \C^{\dt}$ is not in $\overline{\pi(Z)}$, then $\bm 0$ is a regular
-% value of $\bm\Phi_{\thetab}$.
 
@@
 
-Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$ with $V(f) \subset \C^n$ smooth. 
-%
-\begin{theorem}
-There exists a hypersurface $\Delta_1 \subset \C^{n^2}$ of degree at most $nd^{2n}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then, for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i(1)$.
-\end{theorem}
-
-For each $i \in \{1,\hdots,n\}$, let $\Phi_i$ be the polynomial mapping 
-\[
-\Phi_i : (\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),
-\] 
-so that $\Phi_{i,A}^{-1}(0)= W(\pi_i,V^A).$
-%
-\begin{proposition} 
-$\bz$ is a regular value of $\Phi_i$.
-\end{proposition}
-%
+Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$, with $V(f)
+\subset \C^n$ smooth. In what follows, we fix $i$ in $1,\dots,n$, and
+we prove the following: {\em there exists a non-zero polynomial
+  $\D_{i,1} \in \C[\A]$ of degree at most $2nd^{2n}$ such that if $\mA
+  \in \C^{n\times n}$ does not cancel $\D_{i,1}$, then $\mA$ is
+  invertible and $f^\mA$ satisfies $\textbf{H}_i(1)$.}
+
+The following construction is already in~\cite{BaGiHeMb97}; our
+contribution is the degree estimate. We let $\bm\Phi: \C^n \times
+\C^{n\times n} \to \C^{n-i+1}$ be the mapping defined by the
+polynomials 
+\[
+  \big( f,\,\grad(f)\cdot \A_{i+1},\,\hdots,\, \grad(f)\cdot \A_n \big ),
+\] 
+where $\A_1,\hdots,\A_n$ denote the columns of $\A$ and $\cdot$ is the dot-product.
+\begin{lemma} 
+  $\bz$ is a regular value of $\bm\Phi$.
+\end{lemma}
 \begin{proof}
-Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that 
-$f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=\bz.$
-We want to show that the Jacobian of the system of polynomials 
-\[
-f(A\xb),(\grad(f)\cdot A_{i+1})(A\xb),\hdots, (\grad(f)\cdot A_n)(A\xb)
-\]
-at $(\xb,A)$ has full rank, which holds if and only if the Jacobian of the system of polynomials 
-\[
-f,\grad(f)\cdot A_{i+1},\hdots, \grad(f)\cdot A_n
-\]
-at $(\xb,A)$ has full rank. Let $\Psi_i$ be the mapping
-%
-\begin{align*}
-    \Psi_i: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
-       (\xb,A) &\mapsto 
-       \left(f(\xb),\grad(f(\xb))\cdot 
-A_{i+1},\hdots
-\grad(f(\xb))\cdot 
-A_{n}
-\right).
-\end{align*}
-%
-For all $(\xb,A) \in \Psi_i^{-1}(0),$ the Jacobian matrix of $\Psi_i$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
-\[
-F_j = \frac{\pa f}{\pa X_1} a_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+j,n}, ~1 \leq j \leq n-i,
-\]
-so that the Jacobian is equal to
-\[
+Let $(\xb,\mA) \in \C^n \times \C^{n\times n}$ be a zero of $\bm\Phi$.
+We have to show that the Jacobian matrix of the equations defining
+$\bm \Phi$, taken with respect to $\Xb$ and $\A$, has full rank
+$n-i+1$ at $(\xb,\mA)$.
+If we set 
+\[
+F_j = \frac{\pa f}{\pa X_1} A_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}A_{i+j,n}, ~1 \leq j \leq n-i,
+\]
+this Jacobian matrix is equal to
+{\small \[
 \left[ 
 \begin{array}{cccccc}
-\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
-\frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
-\ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
-\frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
+\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}             &\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
+\frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}      &\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
+\ddots                                                         &\ddots&\ddots                                              & \ddots & \ddots \\
+\frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n}  &\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
+\end{array}
+\right],
+\]}
+where the first columns are indexed by $X_1,\dots,X_n$ and the further
+ones by $\A_{1,i+1},\dots,\A_{n,i+1},\dots,\A_{1,n},\dots,\A_{n,n}$.
+Since $f(\xb)=0$, our assumption on $f$ implies that at least one of
+its partial derivatives is non-zero at $\xb$, and the conclusion
+follows.
+\end{proof}
+Since all equations defining $\bm \Phi$ have degree at most $d,$ it
+follows by Proposition~\ref{prop:weak_t} that there exists a non-zero
+polynomial $\Gamma_i \in \C[\A]$ of degree at most $d^{2n-i+1}\leq
+d^{2n},$ with the property that, if $\mA \in \C^{n\times n}$ does not
+cancel $\Gamma_i$, then the Jacobian matrix of $$\bm\Phi_\mA=\big(
+f,\,\grad(f)\cdot \mA_{i+1},\,\hdots,\, \grad(f)\cdot \mA_n \big ),$$
+taken with respect to $\Xb$, has full rank $n-i+1$ at all $\xb$ that
+cancels equations. We then define $\Delta_{i,i}:=\Gamma_i
+\det(\A)$; this is a non-zero polynomial of degree at most $d^{2n}+n
+\le 2nd^{2n}$.
+
+Let us verify that $\Delta_{i,1}$ satisfies the claim in the preamble.
+Take $\mA$ in $\C^{n\times n}$, such that $\Delta_{i,i}(\mA)$ is
+non-zero. Clearly, $\mA$ is invertible; it remains to check that
+$f^\mA$ satisfies $\textbf{H}_i(1)$. Thus, we take $\xb$ that cancels
+$(f^\mA, {\pa f^\mA}/{\pa X_{i+1}},\dots,{\pa f^\mA}/{\pa X_n})$, and
+we prove that the Jacobian matrix of these equations, taken with
+respect to $\Xb$, has full rank $n-i+1$ at $\xb$. Using the chain
+rule, the equations above can be rewritten as $\bm\Phi_\mA(\mA \xb)$,
+so their Jacobian matrix at $\xb$ has the same rank as that of
+$\bm\Phi_\mA$ at $\mA \xb$, that is, $n-i+1$. Our claim is proved.
+
+In Section~\ref{sec:Hi2}, we will need the following by-product of
+this result: if we consider $f^\A \in \C(\frak
+A_{j,k})[X_1,\dots,X_n]$ as defined Section~\ref{sec:gen}, this
+polynomial satisfies the rank property $\textbf{H}_i(1)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Application: property $\textbf{H}'_i$}\label{ssec:fiber}
+
+Let $f \in \ZZ[X_1,\hdots,X_n]$ and $i$ be as before. We now assume
+that $f$ satisfies $\textbf{H}_i(1)$, and we prove the following: {\em
+  there exists a non-zero polynomial $\Xi_{i} \in
+  \C[S_1,\dots,S_{i-1}]$ of degree at most $d^{2n}$ such that if $\bm
+  \sigma =(\sigma_1,\dots,\sigma_{i-1})\in \C^{i-1}$ does not cancel
+  $\Xi_{i}$, the ideal
+  $$(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
+    X_{i+1}},\dots,{\pa f}/{\pa X_n})$$ is radical.}
+
+\smallskip
+
+Let $\bm\Psi: \C^n \times \C^{i-1} \rightarrow \C^{n}$ be the mapping defined by the polynomials
+\[
+  (X_1-S_1,\hdots,X_{i-1}-S_{i-1}, f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n} ).
+\]
+%
+\begin{lemma}
+  $\bz$ is a regular value of $\bm\Psi.$
+\end{lemma}
+\begin{proof}
+At all $(\xb,\bm\sigma)$ zeros of $\bm\Psi,$ the Jacobian matrix of
+$\bm\Psi$ has full rank $n$. Indeed, indexing columns 
+by $X_1,\dots,X_n,S_1,\dots,S_{i-1}$, this matrix is equal to
+\[
+\left[ 
+\begin{array}{cc}
+\bI_{i-1}\hspace{7mm} \bz_{(i-1)\times (n-i+1)}&\hspace{-10mm}-\bI_{i-1}\\
+\jac_{\xb}\left(f,\frac{\pa
+  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right)&\bz_{(n-i+1)\times (i-1)}
 \end{array}
@@
 \] 
-Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
-\[
-T_{\xb} V(f) = \textrm{Nullspace}(\grad_{\xb} f).
-\]
-Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes.
-At least one partial of $f$ must be non-zero.
-Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
+Since the Jacobian of $f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa
+  f}{\pa X_n}$ at $\xb$ is non-zero (by $\textbf{H}_i$), the entire
+matrix must have full rank $n$. Thus,  $\bz$ is a regular value of $\bm\Phi.$
 \end{proof}
 %
-Since $\deg \Phi_i \leq d,$ it follows by Proposition 3.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $d^{n+(n-i+1)}=d^{2n-i+1}\leq d^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then
-%
-\[
- \jac_{\xb} (\Phi_{i,A})=\jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
-\]
-has full rank at all $\xb \in V(f^A)$, and therefore $f^A$ satisfies $\textbf{H}_i(1)$. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
-\[
-\Delta_1 := \bigcup_{i=1}^n \Xi_i,
-\]
-where we have the following bound on the degree which proves the claim:
-\[
-\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq nd^{2n}.
-\]
-
-In Section~\ref{sec:Hi2}, we will need the following alternative form
-of this result: if we consider $f^\A \in \C(\frak
-A_{j,k})[X_1,\dots,X_n]$ as defined Section~\ref{sec:gen}, this
-polynomial satisfies the rank property $\textbf{H}_i(1)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Application: property $\textbf{H}'_i$}\label{ssec:fiber}
-%
-Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$ with $V(f) \subset \C^n$ smooth. 
-%
-\begin{theorem}
-  There exists a Zariski closed set $\Delta_2 \subset \C^{n-1}$ of
-  degree at most $nd^{2n}$ with the property that, if $\bm\alpha \in \C^{n-1} - \Delta_2$, then, for each $i \in \{1,\hdots,n\},$ if $f$ satisfies $\textbf{H}_i$ then $f$ and $\bm \alpha$ satisfy
-  $\textbf{H}_i'$.
-\end{theorem}
-%
-Fix $i \in \{1,\hdots,n\}$ and let $\Phi_i$ be the mapping 
-%
-\begin{align*}
-    \Phi_i: \C^n \times \C^{i-1} &\rightarrow \C^{n} \\
-           (\xb,\alpha_1,\hdots,\alpha_{i-1}) &\mapsto 
-       (X_1(\xb)-\alpha_1,\hdots \\
-       \hdots &,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),\frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n} ).
-\end{align*}
-%
-\begin{proposition}
-$\bz$ is a regular value of $\Phi_i.$
-\end{proposition} 
-\begin{proof}
-At all $(\xb,\alpha_1,\hdots,\alpha_{i-1}) \in \Phi_i^{-1}(0),$ the Jacobian matrix of $\Phi_i$ has full rank. Indeed, the Jacobian is equal to
-\[
-\left[ 
-\begin{array}{cc}
-\hspace{-9mm}\bI_n\hspace{10mm}\hdots \hdots&\hspace{-10mm}-\bI_{i-1}\\
-\jac_{\xb}\left(f,\frac{\pa
-  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right)&\bz_{n-i+1\times i-1}
-\end{array}
-\right], 
-\] 
-and the Jacobian of $f,\frac{\pa
-  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}$ at $\xb$ is never singular because we are assuming that $f$ satisfies $\textbf{H}_i$.
-Therefore the entire matrix must have full rank, and $\bz$ is a regular value of $\Phi_i.$
-\end{proof}
-%
-Since $\deg \Phi_i \leq d,$ it follows by Proposition 3.1 that a hypersurface $\Xi_i \subset \C^{i-1}$ exists, of degree at most $d^{2n},$ with the property that, if $\bm \alpha_{i-1} \in \C^{i-1}-\Xi_i,$ then the Jacobian of $\Phi_{i,\alpha_{i-1}}$:
-%
-\[
- \jac_{\xb} \left(X_1(\xb)-\alpha_1,\hdots 
-       ,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),\frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}\right)
-\]
-has full rank at all $\xb \in V(f)$, and therefore $f$ and $\bm \alpha_{i-1}$ satisfy $\textbf{H}_i^{'}$. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
-\[
-\Delta_2 := \bigcup_{i=1}^n \Xi_i,
-\]
-where we have the following bound on the degree which proves the claim:
-\[
-\deg \Delta_2 \leq \sum_{i=1}^n \deg \Xi_i \leq n d^{2n}.
-\]
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Property ${\bf H}_i(2)$ -- Noether position}\label{sec:Hi2}
+Since all polynomials defining $\bm\Psi$ have degree at most $d$, it
+follows by Proposition~\ref{prop:weak_t} that there exists a non-zero
+polynomial $\Xi_i$ in $\C[S_1,\dots,S_{i-1}]$ of degree at most
+$d^{2n},$ with the following property: at any root $\xb$ of
+$(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
+  X_{i+1}},\dots,{\pa f}/{\pa X_n})$, the Jacobian matrix of these
+equations has rank $n$. The conclusion follows.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Property ${\bf H}_i(2)$: Noether position}\label{sec:Hi2}
 
 Throughout this section, $f$ and $i \in \{1,\hdots,n\}$ are fixed. We
-prove that there exists a hypersurface $\D_{3,i} \subset \C^{n\times
-  n}$ of degree at most \td{} such that if $\mA$ is not in $\D_{3,i}$,
+prove that there exists a hypersurface $\D_{i} \subset \C^{n\times
+  n}$ of degree at most \td{} such that if $\mA$ is not in $\D_{i}$,
 then $\mA$ is invertible and satisfies both conditions in
@@
 \begin{lemma} 
- The extension $\C(\A)[X_1,\dots,X_{i-1}]\rightarrow
- \C(\A)[X_1,\dots,X_n]/\I^{\A}$ is integral.
+ The extension $$\C(\A)[X_1,\dots,X_{i-1}]\rightarrow
+ \C(\A)[X_1,\dots,X_n]/\I^{\A}$$ is integral.
 \end{lemma}
@@
 Let us then define 
-$$\D_{3,i}:=\D_{2,i} \alpha_i \cdots \alpha_n D_i \cdots D_n,$$
+$$\D_{i}:=\D_{1,i} \alpha_i \cdots \alpha_n D_i \cdots D_n,$$
 where, for all $j$, $\alpha_j$ is as above and $D_j$ is the leading
-coefficient of $\pjb$ with respect to $X_j$. Thus, $\D_{3,i}$ is a
+coefficient of $\pjb$ with respect to $X_j$. Thus, $\D_{i}$ is a
 non-zero polynomial in $\C[\A]$; we will estimate its degree below.
@@
   Suppose that $\mA \in \C^{n\times n}$ does not cancel
-  $\D_{3,i}$. Then $f^\mA$ satisfies ${\bf H}_i$.
+  $\D_{i}$. Then $f^\mA$ satisfies ${\bf H}_i$.
 \end{lemma}
@@
 
-To estimate the degree of $\D_{3,i}$, what remains is to give an upper
+To estimate the degree of $\D_{i}$, what remains is to give an upper
 bound on the degree of $\alpha_i,\dots,\alpha_n$. This will come as an

### 2020-02-06 main.tex
Update main.tex

@@
   that contains at least one point in each connected component of
-  $V(f) \cap \R^n$ with probability at least $1/2$. Otherwise the
-  algorithm either produces a subset of the points or FAIL. In any
-  case, the algorithm uses
-  \[
-  O^{\sim}(nk(Lb+d^{2n}(s+d)(L+d)))
-  \]
-  bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in
-  the output have degree at most $d^n,$ and height $
-  O^{\sim}((s+d)d^n).$
+  $V(f) \cap \R^n$.
+
+  As part of the randomization, the algorithm chooses a set 
+  \[
+  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}
+  \]
+  from which to sample from.
+
+  With probability at least $1-\epsilon$, the output is correct. Otherwise, either a proper subset of the points is produced, or FAIL.  In any case, the algorithm uses
+  \[
+  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))
+  \]
+  bit operations, with $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$. The polynomials in
+  the output have degree at most $d^n,$ and height 
+  \[
+  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
+  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).
+  \]
 \end{theorem}
+
+The runtime for cases without a strait-line program in the input are as follows.
+In these cases a polynomial $f$ of degree $d$ is given in the input, and a strait-line program is built for it by computing all the terms.
+In this case, $L \geq d^n$ and $b \geq \htt(f) = s,$ so that the number of bit operations becomes
+\begin{align*}
+      &O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))\\
+      &= 
+O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon^2+d)(d^n+d)\log(s + \log 1/\epsilon^2)))\\
+      &= 
+O^{\sim}(nk(d^ns+(d^{3n}+d^{2n+1})(s + \log 1/\epsilon^2+d)\log(s + \log 1/\epsilon^2)))\\
+     &= 
+O^{\sim}(nk(d^{3n}(s + \log 1/\epsilon^2+d)\log(s + \log 1/\epsilon^2)))\\
+     &= 
+O^{\sim}(nk(d^{3n+1}(s + \log 1/\epsilon^2)\log(s + \log 1/\epsilon^2))),
+\end{align*}
+and the degree and height of the output does not change.
+
 The algorithm itself is rather simple. To describe it, we need to

### 2020-02-06 main.tex
Update main.tex
Updated bit Section 5 and Theorem 1.1

@@
 \section{Bit complexity}
-%
-Recall Theorem 1.1: Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
+%Recall Theorem 1.1:   Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
   $\deg(f) \leq d, \htt(f) \leq s$, and that $V(f) \subset \C^n$ is
@@
   that contains at least one point in each connected component of
-  $V(f) \cap \R^n$ with probability at least $1/2$. Otherwise the
-  algorithm either produces a subset of the points or FAIL. In any
-  case, the algorithm uses
-  \[
-  O^{\sim}(k(Lb+d^{2n}(s+d)(L+d)))
-  \]
-  bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in
-  the output have degree at most $d^n,$ and height $
-  O^{\sim}((s+d)d^n).$
-
-Recall as well that the algorithm can error on one side by producing a proper subset of the points.
-Running the algorithm $\kt$ times gives a list of $n$ zero-dimensional parameterizations, among which the highest cardinality output includes at least one point in each connected component with probability at least $1-(1/2)^{\kt}.$
+  $V(f) \cap \R^n$.
+
+  As part of the randomization, the algorithm chooses a set 
+  \[
+  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}
+  \]
+  from which to sample from.
+
+  With probability at least $1-\epsilon$, the output is correct. Otherwise, either a proper subset of the points is produced, or FAIL.  In any case, the algorithm uses
+  \[
+  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))
+  \]
+  bit operations, with $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$. The polynomials in
+  the output have degree at most $d^n,$ and height 
+  \[
+  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
+  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).
+  \]
 %
@@
 \KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
-\KwOut{$n$ zero-dimensional parameterizations, whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Choose $S \subset \mathbb{Q}$ and $A \in S^{n^2}$ with $|S|\geq \epsilon^{-1}d^{\td}$, where $\epsilon < 5/21$\;
+\KwOut{$n$ zero-dimensional parameterizations, the union of which includes at least one point in each connected component of $V(f) \cap \R^n$}
+\nl Take  $S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}$
+ and randomly choose $A \in S^{n^2}$, and  $\alpha_{n-1}=(\alpha_1,\hdots,\alpha_{n-1}) \in S^{n-1}$\;
 \nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
@@
     \caption{{Main Algorithm} \label{}}
-\nl Randomly choose a point $p_{n-1}=(\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}~(p_0$?)\; 
 \nl \For{$i\gets1$ \KwTo $n$}{
-\nl Run \cite[Algorithm 2]{SH} $k > -\lg(1-2^{(-1/n)})$ times with input 
+\nl Run \cite[Algorithm 2]{SH} $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$ times with input 
 $\{Y_1-\alpha_1,\hdots,Y_{i-1}-\alpha_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } d$\;
@@
 \end{algorithm}
-
+\clearpage
 %
@@
 \begin{enumerate}
-    \item By our assumption on the size of $S$ we know that $|S| = \log (\epsilon^{-1}D^{\td}) \leq \td.$ Thus for $a_{ij} \in S$ we know that $|a_{ij}| \leq \td.$
+    \item We defined $S = \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}$ and therefore the height of $a_{i,j} \in S$ is at most 
+    \[
+    \log 1/{\epsilon^2} + \log(3n^2(2d)^{2n}) = O^{\sim}(\log 1/{\epsilon^2}).
+    \]
     \item 
@@
         \log(n!\cdot \max_{\frac{1\leq i\leq n}{1\leq j\leq n}}\{a_{ij}\}) &= 
-        O(n\log n + n\log(d+1)) \\
-        &= 
-        O^\sim(\log(d+1)).
+        O^{\sim}(n\log n + \log 1/{\epsilon^2})\\
+        &= O^{\sim}(\log 1/{\epsilon^2}).
         \end{align*}
@@
 The integers in $\grad (f)$ are of the same magnitude as in $\Gamma$.
-    \item $\td$
     \item 
@@
   \[
-    O^\sim(kn(Lb+d^{2n}(s+d)(L+d))),
+  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))
   \]
@@
   \[
-    O^{\sim}((s+d)d^n).
+  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
+  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).
   \]
@@
 \par \noindent 
-\textbf{Probability of success:} Note that when $\epsilon < 5/21$ (as stated in step 1 of Algorithm 1), then
-\[
-\pr[A \not \in \D] = 1-\epsilon > \frac{16}{21},
-\]
-so that after a single run of \cite[Algorithm 2]{SH}, the probability of success (ensuring all genericity properties and obtaining all points) is at least 
-\[
-\left( \frac{16}{21} \right) \left( \frac{21}{32} \right) = \frac{1}{2}.
-\]
-Thus, running \cite[Algorithm 2]{SH} $k$ times gives a list of outputs among which the highest cardinality set includes all points with probability at least $1-(1/2)^k$.
-We repeat this $n$ times to obtain $n$ zero-dimensional parameterizations.
-Thus, the probability that we have every point in each parameterization is $(1-(1/2)^k)^n$.
-We want
-\[
-(1-(1/2)^k)^n>\frac{1}{2},
-\]
-which holds if and only if 
-\[
-k > -\lg(1-2^{(-1/n)}),
-\]
-thus proving Theorem 1.1.
-We can boost our success probability by running the main algorithm $\kt$ times, so that we obtain parameterizations whose reunion includes at least one point in each connected component of $V(f) \cap \R^n$ with probability at least $1 - (1/2)^{\kt}$.
+\textbf{Probability of success:} Recall Theorem 2.1:   \textit{For $i=1,\dots,n$, there exists a non-zero polynomial $\D_i$ in
+  $\C[\A]$ of degree at most $3n(2d)^{2n}$ such that if $\mA \in \C^{n\times
+    n}$ does not cancel $\D_i$, then $\mA$ is invertible and $f^\mA$
+  satisfies $\textbf{H}_i$ and $\textbf{H}_i^{'}$.} 
+ Now, if we set
+\[
+ \Delta := \bigcup_{i=1}^n \Delta_i,
+\]
+then
+\[
+\deg \Delta \leq \sum_{i=1}^n \deg \Delta_i  \leq 3n^2(2d)^{2n},
+\] 
+and for $A \in \C^{n \times n}$ that does not cancel $\Delta,$  $\mA$ is invertible and $f^\mA$
+  satisfies $\textbf{H}_i$ and $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Let $\mathscr{E}$ denote the event that, with $k$ repetitions of \cite[Algorithm 2]{SH}, for each $i \in \{1,\hdots,n\}$, the result contains all points and is correct.
+Then,
+\begin{align*}
+\pr[\textrm{success}] = \pr[A \not\in \Delta] \times \pr[\mathscr{E}].  
+\end{align*}
+By construction of $S$,
+\[
+\pr[A \not\in \Delta] = 1-\pr[A \in \Delta] \geq
+1-\epsilon^2.
+\]
+Thus, 
+\begin{align*}
+\pr[\textrm{success}] &\geq  (1-\epsilon^2)\pr[\mathscr{E}]\\
+&\geq (1-\epsilon^2)(1-(11/32)^k)^n\\
+& \geq (1-\epsilon^2)(1-2^{-k})^n= 1-\epsilon
+\end{align*}
+if and only if 
+\[
+(1+\epsilon)(1-2^{-k})^n= 1,
+\]
+if and only if 
+\[
+k \geq -\lg\left ( 1 - (1+\epsilon)^{(-1/n)} \right ).
+\]
 %%

### 2020-02-07 main.tex
Update main.tex
typo
Update main.tex
Updated Section 5

@@
 \begin{align*}
-      &O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))\\
-      &= 
-O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon^2+d)(d^n+d)\log(s + \log 1/\epsilon^2)))\\
+&O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon^2+d)(d^n+d)\log(s + \log 1/\epsilon^2)))\\
       &= 
@@
 \section{Bit complexity}
-%Recall Theorem 1.1:   Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
+Recall Theorem 1.1:   Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
   $\deg(f) \leq d, \htt(f) \leq s$, and that $V(f) \subset \C^n$ is
@@
   \[
-  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}
+  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}
   \]
@@
 
-  With probability at least $1-\epsilon$, the output is correct. Otherwise, either a proper subset of the points is produced, or FAIL.  In any case, the algorithm uses
+  With probability at least $1-\epsilon$, the output is correct. Otherwise, the algorithm either returns a proper subset of the points or FAIL. In any case, the algorithm uses
   \[
@@
 \KwOut{$n$ zero-dimensional parameterizations, the union of which includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Take  $S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}$
- and randomly choose $A \in S^{n^2}$, and  $\alpha_{n-1}=(\alpha_1,\hdots,\alpha_{n-1}) \in S^{n-1}$\;
+\nl Take  $S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}$
+ and randomly choose $A \in S^{n^2}$, and  $\sigma_{n-1}=(\sigma_1,\hdots,\sigma_{n-1}) \in S^{n-1}$\;
 \nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
@@
 \nl \For{$i\gets1$ \KwTo $n$}{
-\nl Run \cite[Algorithm 2]{SH} $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$ times with input 
-$\{Y_1-\alpha_1,\hdots,Y_{i-1}-\alpha_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } d$\;
-\nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 6 \;
+\nl Run \cite[Algorithm 2]{SH} $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$ times with input (state this in terms of straight line programs?)
+$\{Y_1-\sigma_1,\hdots,Y_{i-1}-\sigma_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } d$\;
+\nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 5 \;
 } 
@@
 \begin{enumerate}
-    \item We defined $S = \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}$ and therefore the height of $a_{i,j} \in S$ is at most 
+    \item We defined $S = \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}$ and therefore the height of $a_{i,j} \in S$ is at most 
     \[
@@
 \par \noindent 
-\textbf{Probability of success:} Recall Theorem 2.1:   \textit{For $i=1,\dots,n$, there exists a non-zero polynomial $\D_i$ in
-  $\C[\A]$ of degree at most $3n(2d)^{2n}$ such that if $\mA \in \C^{n\times
-    n}$ does not cancel $\D_i$, then $\mA$ is invertible and $f^\mA$
-  satisfies $\textbf{H}_i$ and $\textbf{H}_i^{'}$.} 
- Now, if we set
-\[
- \Delta := \bigcup_{i=1}^n \Delta_i,
-\]
-then
-\[
-\deg \Delta \leq \sum_{i=1}^n \deg \Delta_i  \leq 3n^2(2d)^{2n},
-\] 
-and for $A \in \C^{n \times n}$ that does not cancel $\Delta,$  $\mA$ is invertible and $f^\mA$
-  satisfies $\textbf{H}_i$ and $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Let $\mathscr{E}$ denote the event that, with $k$ repetitions of \cite[Algorithm 2]{SH}, for each $i \in \{1,\hdots,n\}$, the result contains all points and is correct.
-Then,
+\textbf{Probability of success:} By Theorem 2.1, there exists $\Delta_i \in \C[\A]$ with $\deg \Delta_i \leq 2n^2(2d)^{3n}.$ By Theorem 2.2, there exists $\Xi_i \subset \C[\A]$ with $\deg \Xi_i \leq d^{2n}.$ Take $\Delta =  \prod_{i=1}^n\Delta_i  \Xi_i $ so that
+%
 \begin{align*}
-\pr[\textrm{success}] = \pr[A \not\in \Delta] \times \pr[\mathscr{E}].  
+    \deg \Delta &\leq \sum_{i=1}^n (\deg \Delta_i + \deg \Xi_i)\\
+    &\leq 2n^2(2d)^{3n} + nd^{2n}\\
+    &\leq 3n^2(2d)^{3n}, 
+\end{align*}
+%
+and note that, for $A \in \C^{n \times n}$ that does not cancel $\Delta,$  $\mA$ is then invertible and $f^\mA$ satisfies $\textbf{H}_i$ and $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
+
+Let $\mathscr{E}$ be the event that, the parameterizations $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 7 of Algorithm 1 contain all points and are correct. Then, 
+\begin{align*}
+\pr[\textrm{success}] = \pr[A \not\in \Delta] \times \pr[\mathscr{E}~|~A \not\in \Delta].  
 \end{align*}
@@
 \begin{align*}
-\pr[\textrm{success}] &\geq  (1-\epsilon^2)\pr[\mathscr{E}]\\
+\pr[\textrm{success}] &\geq  (1-\epsilon^2)\pr[\mathscr{E}~|~A \not\in \Delta]\\
 &\geq (1-\epsilon^2)(1-(11/32)^k)^n\\
@@
 %%
-%% End of file `sample-xelatex.tex'.
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2020-02-07 main.tex
Update main.tex
Bernoulli's inequality

@@
   \[
-  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}
+  S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{2n}\}
   \]
@@
   \[
-  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))
-  \]
-  bit operations, with $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$. The polynomials in
+  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon+d)(L+d)\log(s + \log 1/\epsilon)))
+  \]
+  bit operations, with $k \geq 1 + \lg n + \lg(1/\epsilon)$. The polynomials in
   the output have degree at most $d^n,$ and height 
   \[
-  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
-  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).
+  O^{\sim}((s+\lg 1/\epsilon + d)d^n)
+  =O^{\sim}((s+\lg 1/\epsilon)d^{n+1}).
   \]
@@
 \begin{align*}
-&O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon^2+d)(d^n+d)\log(s + \log 1/\epsilon^2)))\\
+&O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon+d)(d^n+d)\log(s + \log 1/\epsilon)))\\
       &= 
-O^{\sim}(nk(d^ns+(d^{3n}+d^{2n+1})(s + \log 1/\epsilon^2+d)\log(s + \log 1/\epsilon^2)))\\
+O^{\sim}(nk(d^ns+(d^{3n}+d^{2n+1})(s + \log 1/\epsilon+d)\log(s + \log 1/\epsilon)))\\
      &= 
-O^{\sim}(nk(d^{3n}(s + \log 1/\epsilon^2+d)\log(s + \log 1/\epsilon^2)))\\
+O^{\sim}(nk(d^{3n}(s + \log 1/\epsilon+d)\log(s + \log 1/\epsilon)))\\
      &= 
-O^{\sim}(nk(d^{3n+1}(s + \log 1/\epsilon^2)\log(s + \log 1/\epsilon^2))),
+O^{\sim}(nk(d^{3n+1}(s + \log 1/\epsilon)\log(s + \log 1/\epsilon))),
 \end{align*}
@@
   \[
-  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}
+  S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}
   \]
@@
   \[
-  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))
-  \]
-  bit operations, with $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$. The polynomials in
+  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon+d)(L+d)\log(s + \log 1/\epsilon)))
+  \]
+  bit operations, with $k \geq 1+\lg n + \lg(1/\epsilon)$. The polynomials in
   the output have degree at most $d^n,$ and height 
   \[
-  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
-  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).
+  O^{\sim}((s+\lg 1/\epsilon + d)d^n)
+  =O^{\sim}((s+\lg 1/\epsilon)d^{n+1}).
   \]
@@
 \KwOut{$n$ zero-dimensional parameterizations, the union of which includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Take  $S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}$
+\nl Take  $S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}$
  and randomly choose $A \in S^{n^2}$, and  $\sigma_{n-1}=(\sigma_1,\hdots,\sigma_{n-1}) \in S^{n-1}$\;
@@
 \nl \For{$i\gets1$ \KwTo $n$}{
-\nl Run \cite[Algorithm 2]{SH} $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$ times with input (state this in terms of straight line programs?)
+\nl Run \cite[Algorithm 2]{SH} $k \geq 1+\lg n + \lg(1/\epsilon)$ times with input (state this in terms of straight line programs?)
 $\{Y_1-\sigma_1,\hdots,Y_{i-1}-\sigma_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } d$\;
@@
 \begin{enumerate}
-    \item We defined $S = \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}$ and therefore the height of $a_{i,j} \in S$ is at most 
-    \[
-    \log 1/{\epsilon^2} + \log(3n^2(2d)^{2n}) = O^{\sim}(\log 1/{\epsilon^2}).
+    \item We defined $S = \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}$ and therefore the height of $a_{i,j} \in S$ is at most 
+    \[
+    \log 1/{\epsilon} + \log(3n^2(2d)^{2n}) = O^{\sim}(\log 1/{\epsilon}).
     \]
@@
         \log(n!\cdot \max_{\frac{1\leq i\leq n}{1\leq j\leq n}}\{a_{ij}\}) &= 
-        O^{\sim}(n\log n + \log 1/{\epsilon^2})\\
-        &= O^{\sim}(\log 1/{\epsilon^2}).
+        O^{\sim}(n\log n + \log 1/{\epsilon})\\
+        &= O^{\sim}(\log 1/{\epsilon}).
         \end{align*}
@@
   \[
-  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))
+  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon+d)(L+d)\log(s + \log 1/\epsilon)))
   \]
@@
   \[
-  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
-  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).
+  O^{\sim}((s+\lg 1/\epsilon + d)d^n)
+  =O^{\sim}((s+\lg 1/\epsilon)d^{n+1}).
   \]
@@
 \pr[A \not\in \Delta] = 1-\pr[A \in \Delta] \geq
-1-\epsilon^2.
-\]
-Thus, 
+1-\epsilon/2.
+\]
+Now set $k = \lg(2n/\epsilon)$ so that 
+\[
+(1-2^{-k})^n = (1 - \epsilon/(2n))^n \geq 1 - \epsilon/2,
+\]
+by Bernoulli's inequality. Therefore, 
 \begin{align*}
-\pr[\textrm{success}] &\geq  (1-\epsilon^2)\pr[\mathscr{E}~|~A \not\in \Delta]\\
-&\geq (1-\epsilon^2)(1-(11/32)^k)^n\\
-& \geq (1-\epsilon^2)(1-2^{-k})^n= 1-\epsilon
+\pr[\textrm{success}] &\geq  (1-\epsilon/2)\pr[\mathscr{E}~|~A \not\in \Delta]\\
+&\geq (1-\epsilon/2)(1-(11/32)^k)^n\\
+& \geq (1-\epsilon/2)(1-2^{-k})^n \\
+& \geq (1-\epsilon/2)(1-\epsilon/2)\\
+& = 1 - \epsilon + \epsilon^2/4 \geq 1- \epsilon.
 \end{align*}
-if and only if 
-\[
-(1+\epsilon)(1-2^{-k})^n= 1,
-\]
-if and only if 
-\[
-k \geq -\lg\left ( 1 - (1+\epsilon)^{(-1/n)} \right ).
-\]
 %%
@@
 \endinput
-%%

### 2020-02-07 main.tex
Degree bounds

@@
   For $i=1,\dots,n$, there exists a non-zero polynomial $\D_i$ in
-  $\C[\A]$ of degree at most $\td$ such that if $\mA \in \C^{n\times
-    n}$ does not cancel $\D_i$, then $\mA$ is invertible and $f^\mA$
-  satisfies $\textbf{H}_i$.
+  $\C[\A]$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA \in
+  \C^{n\times n}$ does not cancel $\D_i$, then $\mA$ is invertible and
+  $f^\mA$ satisfies $\textbf{H}_i$.
 \end{theorem}
 
-\begin{theorem}
+\begin{theorem}\label{theo:Hp}
   Suppose that $f$ satisfies $\textbf{H}_i$. There exists a non-zero
@@
 \end{proof}
-%
+
 Since all polynomials defining $\bm\Psi$ have degree at most $d$, it
@@
   X_{i+1}},\dots,{\pa f}/{\pa X_n})$, the Jacobian matrix of these
-equations has rank $n$. The conclusion follows.
+equations has rank $n$. Theorem~\ref{theo:Hp} is proved.
 
@@
 Let us then define 
-$$\D_{i}:=\D_{1,i} \alpha_i \cdots \alpha_n D_i \cdots D_n,$$
-where, for all $j$, $\alpha_j$ is as above and $D_j$ is the leading
-coefficient of $\pjb$ with respect to $X_j$. Thus, $\D_{i}$ is a
-non-zero polynomial in $\C[\A]$; we will estimate its degree below.
+$$\D_{i}:=\D_{i,1} \alpha_i \cdots \alpha_n D_i \cdots D_n,$$ where
+$\D_{i,1}$ was defined in Section~\ref{ssec:Hi1} and for all $j$,
+$\alpha_j$ is as above and $D_j$ is the leading coefficient of $\pjb$
+with respect to $X_j$. Thus, $\D_{i}$ is a non-zero polynomial in
+$\C[\A]$; we will estimate its degree below.
 
 \begin{lemma}
-  Suppose that $\mA \in \C^{n\times n}$ does not cancel
-  $\D_{i}$. Then $f^\mA$ satisfies ${\bf H}_i$.
+  Suppose that $\mA \in \C^{n\times n}$ does not cancel $\D_{i}$. Then
+  $f^\mA$ satisfies ${\bf H}_i$.
 \end{lemma}
 \begin{proof}
-  By assumption, $\D_{2,i}(\mA)$ is non-zero, so that $\mA$ is
+  By assumption, $\D_{i,1}(\mA)$ is non-zero, so that $\mA$ is
   invertible and $f^\mA$ satisfies ${\bf H}_i(1)$. In particular, the
   ideal $\I(i, f^\mA)$ is radical, and its zero-set
-  $W(\pi_i,V(f^\mA))$ is either empty or $(i-1)$-equidimensional. If it is 
-  empty, we are done.
+  $W(\pi_i,V(f^\mA))$ is either empty or $(i-1)$-equidimensional. If
+  it is empty, we are done.
 
@@
 
-\td finish the degree bound.
-
-% \section{Proof of Theorem 2.1}
-% %
-% Recall Theorem 3.1: \textit{Suppose that $f \in \Q[X_1,\hdots,X_n]$ satisfies \textbf{H}.
-Then there exists a Zariski closed set $\D \subset \mathbb{C}^{n^2}$ of degree at most $D^{\textrm{\td}}$ such that, if $\textbf{A}$ is chosen from  $\C^{n^2}-\Delta$ ( $\Q^{n^2}-\Delta$?) then $f^A$ satisfies $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$}
-% %
-% \begin{proof}
-% Assume that $f\in \Q[X_1,\hdots,X_n]$ has degree at most $D$ and satisfies $\textbf{H}.$ By Theorem 5.1, there exists a Zariski closed set $\D_1\subset \C^{n^2}$ with the property that, if $A \in \C^{n^2}-\D_1$ then, for $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1), \textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Likewise, by Theorem 6.1, we obtain $\D_2 \subset \C^{n^2}$ with the property that if $A \in \C^{n^2}-\D_2$ then $f^A$ satisfies $\textbf{H}_i^{'}(4), \textbf{H}_i^{'}(5),$ and $\textbf{H}_i^{'}(6).$ By Theorem 7.1, $\D_3 \subset \C^{n^2}$ exists with $f^A$ satisfying $\textbf{H}_i^{'}(7)$ when $A \in \C^{n^2}-\D_3$.
-Clearly then, if
-% \[
-% A \in \C^{n^2} - \bigcup_{i=1}^3 \D_i
-% \]
-% then $f^A$ satisfies  $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ Take 
-% \[
-% \Delta = \bigcup_{i=1}^3 \D_i,
-% \]
-% and note that 
-% \[
-% \deg \D \leq  \sum_{i=1}^3 \deg \D_i.
-% \]
-% \end{proof}
-% %
-% Recall Corollary 3.2: \textit{Fix $S \subset \mathbb{Q}$ with $|S| \geq \epsilon^{-1} D^{\textrm{\td}}$ and $\epsilon > 0$.
-Then for $A\in S^{n^2}$ chosen randomly, the probability that $f^A$ satisfies $H_i^{'}$ for all $i \in \{1,\hdots,n\}$ is at least $1-\epsilon.$}
-% %
-% \begin{proof}
-% \[
-% Pr[A \in \Delta] \leq \frac{\deg \Delta}{|S|} \leq \frac{D^{\td}}{\epsilon^{-1}D^{\td}} = \epsilon.
-% \]
-% \end{proof}
-% %
-% %
-% %
-% %
+We saw in Section~\ref{ssec:Hi1} that $\D_{i,1}$ has degree at most
+$2nd^{2n}$, and all $D_j$'s have degree at most $(2d)^n$. This gives
+the upper bound
+$$\deg(\D_i) \le 2nd^{2n} + 2n^2(2d)^{2n} + n(2d)^n \le 6n^2 (2d)^{2n}.$$
+This finishes the proof of Theorem~\ref{theo:gen}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Bit complexity}
@@
 \end{algorithm}
-\clearpage
+
 %

### 2020-02-07 main.tex
Minor intro updates

@@
   generically ensure certain desirable geometric properties. The
-  complexity of the algorithm was given in an algebraic complexity
+  cost of the algorithm was given in an algebraic complexity
   model; the analysis of the bit complexity and the error probability
@@
 The number of connected components of $V(f)$ admits the lower bound
-$d^{\Omega(n)}$, so up to polynomial factors, this result is
+$d^{\Omega(n)}$, so up to polynomial factors this result is
 optimal. However, due to the generality of the algorithm, the constant
@@
 some inputs may be given by shorter straight-line program, and the
-algorithm is able to benefit from it.
+algorithm is able to benefit from this.
 
@@
   \]
-  from which to sample from.
+  from which to sample.
 
@@
 
-The runtime for cases without a strait-line program in the input are as follows.
-In these cases a polynomial $f$ of degree $d$ is given in the input, and a strait-line program is built for it by computing all the terms.
+The runtime for cases without a straight-line program in the input are as follows.
+In these cases a polynomial $f$ of degree $d$ is given in the input, and a straight-line program is built for it by computing all the terms.
 In this case, $L \geq d^n$ and $b \geq \htt(f) = s,$ so that the number of bit operations becomes
@@
 revisiting the key ingredients in the proofs given
-in~\cite{BaGiHeMb97} and~\cite{EMP} and giving quantitative versions
+in~\cite{BaGiHeMb97} and~\cite{EMP}, and giving quantitative versions
 of these results, bounding the degree of the hypersurfaces we have to
@@
 defined by {\em regular sequences}: the algorithm in~\cite{EMP} still
-applies, but the modifications needed would take us to far for the
-current format. Further yet, randomized algorithms for deciding {\em
+applies, but the modifications needed are beyond the scope of this
+publication. Further still, randomized algorithms for deciding {\em
   connectivity queries} on smooth, compact algebraic sets have been
@@
 \begin{algorithm}[hbt!]
-\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
+\KwIn{a straight line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
 \KwOut{$n$ zero-dimensional parameterizations, the union of which includes at least one point in each connected component of $V(f) \cap \R^n$}
@@
 \end{document}
-\endinput
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2020-02-07 main.tex
Minor typos in S2

@@
 
-Even if $f$ does not satisfy $\textbf{H}_i$, we mentioned that it
-does, after applying a generic change of variables. The precise
-statement is the following; to state it, we use the following
+Even if $f$ does not initially satisfy $\textbf{H}_i$, it does after applying a generic change of variables. The precise
+statement is as follows, for which we use the following
 notation. For a matrix $\mA$ in $\C^{n\times n}$ and $g$ in

### 2020-02-07 main.tex
Minor

@@
 
-Here is a simple example that shows this result at work. Consider a
+The following simple example shows this result at work. Consider a
 squarefree $f$ in $\C[X_1,X_2]$, such that $V(f)$ is a smooth curve in
@@
 \right],
-\]}
+\]}%
 where the first columns are indexed by $X_1,\dots,X_n$ and the further

### 2020-02-07 main.tex
Minor S4 updates

@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\}&\leq d\\
+\right\}&\leq d,\\
 \deg_{\A}  
@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\}& \leq d\\
-\deg_{\Xb,T}(1-T\pjb) &\leq (2d)^n +1 \\
+\right\}& \leq d,\\
+\deg_{\Xb,T}(1-T\pjb) &\leq (2d)^n +1,\\
 \deg_{\A}(1-T\pjb)& \leq (2d)^n.
@@
 $$\deg(\D_i) \le 2nd^{2n} + 2n^2(2d)^{2n} + n(2d)^n \le 6n^2 (2d)^{2n}.$$
-This finishes the proof of Theorem~\ref{theo:gen}.
+This completes the proof of Theorem~\ref{theo:gen}.
 

### 2020-02-07 main.tex
Update main.tex
Section 5

@@
 
-\section{Bit complexity}
-Recall Theorem 1.1:   Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
-  $\deg(f) \leq d, \htt(f) \leq s$, and that $V(f) \subset \C^n$ is
-  smooth.  Assume also that $f$ is given by a straight-line program
-  $\Gamma$ of size $L$ with integer constants of height at most $b.$
-
-  There exists a randomized algorithm that takes $\Gamma, d,$ and $s$
-  as input and produces a zero-dimensional parameterization of a set
-  that contains at least one point in each connected component of
-  $V(f) \cap \R^n$.
-
-  As part of the randomization, the algorithm chooses a set 
-  \[
-  S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}
-  \]
-  from which to sample from.
-
-  With probability at least $1-\epsilon$, the output is correct. Otherwise, the algorithm either returns a proper subset of the points or FAIL. In any case, the algorithm uses
-  \[
-  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon+d)(L+d)\log(s + \log 1/\epsilon)))
-  \]
-  bit operations, with $k \geq 1+\lg n + \lg(1/\epsilon)$. The polynomials in
-  the output have degree at most $d^n,$ and height 
-  \[
-  O^{\sim}((s+\lg 1/\epsilon + d)d^n)
-  =O^{\sim}((s+\lg 1/\epsilon)d^{n+1}).
-  \]
-%
+\section{Bit complexity}%
 \subsection{The Algorithm}
@@
 \begin{algorithm}[hbt!]
-\KwIn{a straight line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
+\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
 \KwOut{$n$ zero-dimensional parameterizations, the union of which includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Take  $S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}$
- and randomly choose $A \in S^{n^2}$, and  $\sigma_{n-1}=(\sigma_1,\hdots,\sigma_{n-1}) \in S^{n-1}$\;
-\nl Compute $f$ and apply the change of variables to obtain $f(A x)=f^A(x)$\;
+\nl Take $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $A \in S^{n^2}$, and  $\sigma \in T^{n-1}$\;
+\nl Apply the change of variables to obtain $f(A x)=f^A(x)$\;
 \nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
@@
 \nl \For{$i\gets1$ \KwTo $n$}{
-\nl Run \cite[Algorithm 2]{SH} $k \geq 1+\lg n + \lg(1/\epsilon)$ times with input (state this in terms of straight line programs?)
-$\{Y_1-\sigma_1,\hdots,Y_{i-1}-\sigma_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \} \textrm{ and } d$\;
+\nl Run \cite[Algorithm 2]{SH} $k \geq \lg(3n/\epsilon)$ times with a straight-line program computed from 
+$\{Y_1-\sigma_1,\hdots,Y_{i-1}-\sigma_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$\;
 \nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 5 \;
@@
 \end{algorithm}
-
+%
 %
@@
     \[
-    \log 1/{\epsilon} + \log(3n^2(2d)^{2n}) = O^{\sim}(\log 1/{\epsilon}).
+    \log 1/{\epsilon} + \log(3n^2(2d)^{2n}) = O^{\sim}(n\log d + \log 1/{\epsilon}).
+    \]
+    \item  We can prepare a straight-line program $\Gamma$ for $f^A$ with length at most $d^n$, and 
+    by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, height of at most 
+    \[
+        O^{\sim}(b + d\log 1 / \epsilon + dn).
     \]
     \item 
-    \begin{enumerate}[label=\roman*.]
-        \item $O(L)$ operations are required to compute $f$ from its straight line program $\Gamma.$
-        \item After applying the change of variables obtaining $f(A x)=f^A(x)$ the height grows at most by a factor of
-        \begin{align*}
-        \log(n!\cdot \max_{\frac{1\leq i\leq n}{1\leq j\leq n}}\{a_{ij}\}) &= 
-        O^{\sim}(n\log n + \log 1/{\epsilon})\\
-        &= O^{\sim}(\log 1/{\epsilon}).
-        \end{align*}
-    \end{enumerate}
-    \item After computing the partial derivatives the height grows by at most another factor of $\log d$.
+    After computing the partial derivatives the height grows by at most another factor of $\log d$.
 Furthermore, preparing the straight line program for the gradient of $f$ does not introduce large integers.
@@
     \item 
-    After applying \cite[Algorithm 2]{SH} $kn$ times, we obtain the
-    following upper bound on the total number of bit operations required by the algorithm:
-  \[
-  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon+d)(L+d)\log(s + \log 1/\epsilon)))
-  \]
-    where it also follows from \cite[Algorithm 2]{SH} that the polynomials in the output have degree at most $d^n,$ and height at most
-  \[
-  O^{\sim}((s+\lg 1/\epsilon + d)d^n)
-  =O^{\sim}((s+\lg 1/\epsilon)d^{n+1}).
+    After applying \cite[Algorithm 2]{SH} $kn$ times with $k = O(\log n + \log 1 / \epsilon)$, the total boolean cost of the algorithm is
+  \[
+O^{\sim}(d^{3n+1}(\log1/\epsilon)(b + \log1/\epsilon))
+  \]
+    where the polynomials in the output have degree at most $d^n,$ and height at most
+  \[
+  O^{\sim}(d^{n+1}(b + \log 1 / \epsilon)).
   \]
@@
 \par \noindent 
-\textbf{Probability of success:} By Theorem 2.1, there exists $\Delta_i \in \C[\A]$ with $\deg \Delta_i \leq 2n^2(2d)^{3n}.$ By Theorem 2.2, there exists $\Xi_i \subset \C[\A]$ with $\deg \Xi_i \leq d^{2n}.$ Take $\Delta =  \prod_{i=1}^n\Delta_i  \Xi_i $ so that
-%
+\textbf{Probability of success:} Let $\Delta_i \in \C[\A]$ be the polynomials from Theorem 2.1. Denote by $\Delta$ the product $\Delta := \prod_{i=1}^n \D_i.$ Note that 
+\begin{align}
+    \deg \Delta \leq \sum_{i=1}^n \deg \Delta_i \leq 6n^3(2d)^{2n},
+\end{align}
+where then, if $\mA \in \C^{n \times n}$ does not cancel $\Delta,$ then  $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for all $i \in \{1,\hdots,n\}.$ Now, assuming that $\mA$ is such a matrix, let $\Xi_i\in \C[\A]$ be the polynomials from Theorem 2.2 and denote by $\Xi$ the product $\Xi := \prod_{i=1}^n \Xi_i.$ Note that
+\begin{align}
+    \deg \Xi \leq \sum_{i=1}^n \deg \Xi_i \leq nd^{2n},
+\end{align}
+where then, if $\sigma \in \C^{i-1}$ does not cancel $\Xi$ then $f^{\mA}$ and $\sigma$ satisfy $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ 
+Now, by construction of \[S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}\] and \[T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},\] where $A \in S^{n^2}$ and  $\sigma \in T^{n-1}$ are randomly chosen, we have
+%
+\[
+\pr[A \in \Delta] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3
+\]
+and
+\[
+\pr[\sigma \in \Xi] \leq \deg \frac{\deg\Xi}{|S|} = \epsilon/3.
+\]
+%
+Let $\mathscr{E}$ be the event that, the parameterizations $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 7 of Algorithm 1 contain all points and are correct.
+Then, the probability of success is equal to
 \begin{align*}
-    \deg \Delta &\leq \sum_{i=1}^n (\deg \Delta_i + \deg \Xi_i)\\
-    &\leq 2n^2(2d)^{3n} + nd^{2n}\\
-    &\leq 3n^2(2d)^{3n}, 
+ \pr[A \not\in \Delta] \times \pr[\sigma \not \in \Xi ~|~A \not\in \Delta] \times \pr[\mathscr{E}~|~A \not\in \Delta \textrm{ and } \sigma \not \in \Xi].
 \end{align*}
 %
-and note that, for $A \in \C^{n \times n}$ that does not cancel $\Delta,$  $\mA$ is then invertible and $f^\mA$ satisfies $\textbf{H}_i$ and $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$
-
-Let $\mathscr{E}$ be the event that, the parameterizations $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 7 of Algorithm 1 contain all points and are correct. Then, 
-\begin{align*}
-\pr[\textrm{success}] = \pr[A \not\in \Delta] \times \pr[\mathscr{E}~|~A \not\in \Delta].  
-\end{align*}
-By construction of $S$,
-\[
-\pr[A \not\in \Delta] = 1-\pr[A \in \Delta] \geq
-1-\epsilon/2.
-\]
-Now set $k = \lg(2n/\epsilon)$ so that 
-\[
-(1-2^{-k})^n = (1 - \epsilon/(2n))^n \geq 1 - \epsilon/2,
+Set $k = \lg(3n/\epsilon)$, with $\epsilon>0,$ so that 
+\[
+(1-2^{-k})^n = (1 - \epsilon/(3n))^n \geq 1 - \epsilon/3,
 \]
@@
 \begin{align*}
-\pr[\textrm{success}] &\geq  (1-\epsilon/2)\pr[\mathscr{E}~|~A \not\in \Delta]\\
-&\geq (1-\epsilon/2)(1-(11/32)^k)^n\\
-& \geq (1-\epsilon/2)(1-2^{-k})^n \\
-& \geq (1-\epsilon/2)(1-\epsilon/2)\\
-& = 1 - \epsilon + \epsilon^2/4 \geq 1- \epsilon.
+\pr[\textrm{success}] &\geq  (1- \epsilon/3)(1- \epsilon/3)\pr[\mathscr{E}~|~A \not\in \Delta \textrm{ and } \sigma \not \in \Xi]\\
+&\geq (1- \epsilon/3)(1- \epsilon/3)(1-(11/32)^k)^n\\
+& \geq (1- \epsilon/3)(1- \epsilon/3)(1-2^{-k})^n \\
+& \geq (1- \epsilon/3)(1- \epsilon/3)(1- \epsilon/3)\\
+& \geq 1 - \epsilon.
 \end{align*}

### 2020-02-07 main.tex
Update main.tex
Theorem 1.1

@@
   Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
-  $\deg(f) \leq d, \htt(f) \leq s$, and that $V(f) \subset \C^n$ is
-  smooth.  Assume also that $f$ is given by a straight-line program
-  $\Gamma$ of size $L$ with integer constants of height at most $b.$
-
-  There exists a randomized algorithm that takes $\Gamma, d,$ and $s$
+  $\deg(f) \leq d, \htt(f) \leq b$, and that $V(f) \subset \C^n$ is
+  smooth.
+
+  There exists a randomized algorithm that takes $f$
   as input and produces a zero-dimensional parameterization of a set
@@
 
-  As part of the randomization, the algorithm chooses a set 
-  \[
-  S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{2n}\}
-  \]
-  from which to sample.
-
-  With probability at least $1-\epsilon$, the output is correct. Otherwise, either a proper subset of the points is produced, or FAIL.  In any case, the algorithm uses
-  \[
-  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon+d)(L+d)\log(s + \log 1/\epsilon)))
-  \]
-  bit operations, with $k \geq 1 + \lg n + \lg(1/\epsilon)$. The polynomials in
+  As part of the randomization, the algorithm chooses sets 
+  \[
+  S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}
+  \]
+  and
+  \[
+  T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\}
+  \]
+  from which to sample from.
+
+  With probability at least $1-\epsilon$, the output is correct. Otherwise, 
+  the algorithm either returns a proper subset of the points, or FAIL.  In
+  any case, the algorithm uses
+  \[
+O^{\sim}(d^{3n+1}(\log1/\epsilon)(b + \log1/\epsilon))
+  \]
+  bit operations. The polynomials in
   the output have degree at most $d^n,$ and height 
-  \[
-  O^{\sim}((s+\lg 1/\epsilon + d)d^n)
-  =O^{\sim}((s+\lg 1/\epsilon)d^{n+1}).
-  \]
+  \begin{align*}
+  &O^{\sim}(d^{n+1}(b + \log 1 / \epsilon)). 
+  \end{align*}
 \end{theorem}
 
-The runtime for cases without a straight-line program in the input are as follows.
-In these cases a polynomial $f$ of degree $d$ is given in the input, and a straight-line program is built for it by computing all the terms.
-In this case, $L \geq d^n$ and $b \geq \htt(f) = s,$ so that the number of bit operations becomes
-\begin{align*}
-&O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon+d)(d^n+d)\log(s + \log 1/\epsilon)))\\
-      &= 
-O^{\sim}(nk(d^ns+(d^{3n}+d^{2n+1})(s + \log 1/\epsilon+d)\log(s + \log 1/\epsilon)))\\
-     &= 
-O^{\sim}(nk(d^{3n}(s + \log 1/\epsilon+d)\log(s + \log 1/\epsilon)))\\
-     &= 
-O^{\sim}(nk(d^{3n+1}(s + \log 1/\epsilon)\log(s + \log 1/\epsilon))),
-\end{align*}
-and the degree and height of the output does not change.
-
+Here we assume that $f$ is given as a dense polynomial. However, it 
+would be possible to take into account the runtime if $f$ was given 
+by a straight-line program $\Gamma,$ where the length of $\Gamma$ would
+be bounded by $d^n$ and would have integer constants of height at most
+$b$. Here, $\Gamma$ could be computed in the trivial way, by 
+computing the terms and summing them. 
 The algorithm itself is rather simple. To describe it, we need to

### 2020-02-07 main.tex
Update main.tex
Correction at the beginning of Section 4

@@
 prove that there exists a hypersurface $\D_{i} \subset \C^{n\times
-  n}$ of degree at most \td{} such that if $\mA$ is not in $\D_{i}$,
+  n}$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA$ is not in $\D_{i}$,
 then $\mA$ is invertible and satisfies both conditions in

### 2020-02-07 main.tex
Update main.tex
Updated Section 1 and Theorem 1.1

@@
 
-\paragraph*{Data structures.} As in references such
-as~\cite{GiHeMoPa95,GiHaHeMoMoPa97,GiHeMoMoPa98,BaGiHeMb97,EMP}, the
-input polynomial $f$ is given by means of a {\em straight-line
-  program}, that is, a sequence of operations $+,-,\times$ that takes
-as input $X_1,\dots,X_n$ and evaluates $f$; the {\em length} of a
-straight-line program is simply the number of operations it performs.
-
-Any polynomial of degree $d$ in $n$ variables can be computed by a
-straight-line program of length $O\big ({{d+n} \choose n}\big)$:
-evaluate all monomials of degree up to $d$ in $n$ variables, multiply
-them by their respective coefficients and sum the result. However,
-some inputs may be given by shorter straight-line program, and the
-algorithm is able to benefit from this.
-
+\paragraph*{Data structures.} 
 The output of the algorithm is a finite set in $\overline{\Q}{}^n$. To
@@
   $\deg(f) \leq d, \htt(f) \leq b$, and that $V(f) \subset \C^n$ is
-  smooth.
-
-  There exists a randomized algorithm that takes $f$
-  as input and produces a zero-dimensional parameterization of a set
-  that contains at least one point in each connected component of
-  $V(f) \cap \R^n$.
-
-  As part of the randomization, the algorithm chooses sets 
-  \[
-  S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}
-  \]
-  and
-  \[
-  T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\}
-  \]
-  from which to sample from.
-
-  With probability at least $1-\epsilon$, the output is correct. Otherwise, 
+  smooth. Also suppose that $0 < \epsilon < 1.$
+
+  There exists a randomized algorithm that takes $f$ and $\epsilon$
+  as input and produces $n$ zero-dimensional parameterizations whose reunion includes at least one point in each connected component of
+  $V(f) \cap \R^n$, with probability at least $1-\epsilon$. Otherwise, 
   the algorithm either returns a proper subset of the points, or FAIL.  In
@@
 would be possible to take into account the runtime if $f$ was given 
-by a straight-line program $\Gamma,$ where the length of $\Gamma$ would
+by a {\em straight-line
+  program}, that is, a sequence of operations $+,-,\times$ that takes
+as input $X_1,\dots,X_n$ and evaluates $f$; the {\em length} of a
+straight-line program is simply the number of operations it performs. Straigh-line programs are described in references such
+as~\cite{GiHeMoPa95,GiHaHeMoMoPa97,GiHeMoMoPa98,BaGiHeMb97,EMP}. The length of the straight-line program for $f$ would
 be bounded by $d^n$ and would have integer constants of height at most
-$b$. Here, $\Gamma$ could be computed in the trivial way, by 
-computing the terms and summing them. 
+$b$. Any polynomial of degree $d$ in $n$ variables can be computed by a
+straight-line program of length $O\big ({{d+n} \choose n}\big)$:
+evaluate all monomials of degree up to $d$ in $n$ variables, multiply
+them by their respective coefficients and sum the result. However,
+some inputs may be given by shorter straight-line program, and the
+algorithm is able to benefit from this.
+
 The algorithm itself is rather simple. To describe it, we need to
@@
 \begin{equation}\label{eq:syst}
-X_1-\alpha_1,\dots,X_{i-1}-\alpha_{i-1}, f, \frac{\pa f}{\pa
+X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1}, f, \frac{\pa f}{\pa
   X_{i+1}} ,\dots,\frac{\pa f}{\pa X_n},  

### 2020-02-07 main.tex
Update main.tex
Corrections in Section 5

@@
 
-\section{Bit complexity}%
+\section{Bit complexity}
+%
 \subsection{The Algorithm}
 %
-For a matrix $A \in \GL(n,\Q),$ let 
-\[
-Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
-\]
-where $b_i$ is the i-th row of $A^{-1}$.
+The following is our main algorithm.
+In step 5, we use  \cite[Algorithm 2]{SH} to solve a square system.
+This subroutine is randomized.
+In order to guarantee a higher probability of success, we repeat the calculation $k$ times.
+This subroutine also requires a straight-line program as input, which we compute from $f^\mA$ and its partial derivatives.
 %
 \begin{algorithm}[hbt!]
-\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
+\KwIn{$f \in \Q[X_1,\hdots,X_n]$ of degree $d$ and $0 < \epsilon < 1$}
 \KwOut{$n$ zero-dimensional parameterizations, the union of which includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Take $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $A \in S^{n^2}$, and  $\sigma \in T^{n-1}$\;
-\nl Apply the change of variables to obtain $f(A x)=f^A(x)$\;
-\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
+\nl Construct $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $\mA \in S^{n^2}$, and  $\bm \sigma \in T^{n-1}$\;
+\nl Apply the change of variables to obtain $f(\mA x)=f^{\mA}(x)$\;
+\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n}$\;
     \caption{{Main Algorithm} \label{}}
@@
 \nl Run \cite[Algorithm 2]{SH} $k \geq \lg(3n/\epsilon)$ times with a straight-line program computed from 
-$\{Y_1-\sigma_1,\hdots,Y_{i-1}-\sigma_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$\;
+$\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \}$\;
 \nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 5 \;
@@
 \end{algorithm}
+\clearpage 
 %
@@
     \]
-    \item  We can prepare a straight-line program $\Gamma$ for $f^A$ with length at most $d^n$, and 
-    by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, height of at most 
+    \item  We can prepare a straight-line program $\Gamma$ for $f^{\mA}$ with length at most $d^n$, and 
+    by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, height at most 
     \[
@@
 \par \noindent 
-\textbf{Probability of success:} Let $\Delta_i \in \C[\A]$ be the polynomials from Theorem 2.1. Denote by $\Delta$ the product $\Delta := \prod_{i=1}^n \D_i.$ Note that 
+\textbf{Probability of success:} Let $\Delta_i \in \C[\A]$ be the polynomials from Theorem 2.1. Denote by $\Delta := \prod_{i=1}^n \D_i,$ and note that 
 \begin{align}
@@
 \end{align}
-where then, if $\mA \in \C^{n \times n}$ does not cancel $\Delta,$ then  $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for all $i \in \{1,\hdots,n\}.$ Now, assuming that $\mA$ is such a matrix, let $\Xi_i\in \C[\A]$ be the polynomials from Theorem 2.2 and denote by $\Xi$ the product $\Xi := \prod_{i=1}^n \Xi_i.$ Note that
+where then, if $\mA \in \C^{n \times n}$ does not cancel $\Delta,$ then  $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for all $i \in \{1,\hdots,n\}.$ Now, assuming that $\mA$ is such a matrix, let $\Xi_i\in \C[\A]$ be the polynomials from Theorem 2.2 applied to $f^{\mA}.$ Denote by $\Xi := \prod_{i=1}^n \Xi_i,$ and note that
 \begin{align}
@@
 \end{align}
-where then, if $\sigma \in \C^{i-1}$ does not cancel $\Xi$ then $f^{\mA}$ and $\sigma$ satisfy $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ 
-Now, by construction of \[S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}\] and \[T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},\] where $A \in S^{n^2}$ and  $\sigma \in T^{n-1}$ are randomly chosen, we have
-%
-\[
-\pr[A \in \Delta] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3
+where then, if $\bm \sigma \in \C^{i-1}$ does not cancel $\Xi$ then $f^{\mA}$ and $\bm \sigma$ satisfy $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ 
+Now, by construction of 
+\[
+S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}
 \] 
@@
 \[
-\pr[\sigma \in \Xi] \leq \deg \frac{\deg\Xi}{|S|} = \epsilon/3.
+T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},
+\] 
+where $\mA \in S^{n^2}$ and  $\bm \sigma \in T^{n-1}$ are randomly chosen, we have 
+%
+\[
+\pr[\mA \in \Delta] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3
+\]
+and
+\[
+\pr[\bm \sigma \in \Xi] \leq \deg \frac{\deg\Xi}{|S|} = \epsilon/3.
 \]
@@
 \begin{align*}
- \pr[A \not\in \Delta] \times \pr[\sigma \not \in \Xi ~|~A \not\in \Delta] \times \pr[\mathscr{E}~|~A \not\in \Delta \textrm{ and } \sigma \not \in \Xi].
+ \pr[\mA \not\in \Delta] \times \pr[\bm \sigma \not \in \Xi ~|~\mA \not\in \Delta] \times \pr[\mathscr{E}~|~\mA \not\in \Delta \textrm{ and } \bm\sigma \not \in \Xi].
 \end{align*}
 %
-Set $k = \lg(3n/\epsilon)$, with $\epsilon>0,$ so that 
+Set $k = \lg(3n/\epsilon)$ so that 
 \[
@@
 \begin{align*}
-\pr[\textrm{success}] &\geq  (1- \epsilon/3)(1- \epsilon/3)\pr[\mathscr{E}~|~A \not\in \Delta \textrm{ and } \sigma \not \in \Xi]\\
+\pr[\textrm{success}] &\geq  (1- \epsilon/3)(1- \epsilon/3)\pr[\mathscr{E}~|~\mA \not\in \Delta \textrm{ and } \bm \sigma \not \in \Xi]\\
 &\geq (1- \epsilon/3)(1- \epsilon/3)(1-(11/32)^k)^n\\

### 2020-02-08 main.tex
Update main.tex
Updated algorithm, corrections

@@
 The following is our main algorithm.
-In step 5, we use  \cite[Algorithm 2]{SH} to solve a square system.
-This subroutine is randomized.
+In step 5, we use  \cite[Algorithm 2]{SH} to solve a square system, where this subroutine is randomized.
 In order to guarantee a higher probability of success, we repeat the calculation $k$ times.
-This subroutine also requires a straight-line program as input, which we compute from $f^\mA$ and its partial derivatives.
+This subroutine requires the input to be in the form of a straight-line program, which we compute from $f^\mA$ and its partial derivatives.
 %
@@
 \KwOut{$n$ zero-dimensional parameterizations, the union of which includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Construct $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $\mA \in S^{n^2}$, and  $\bm \sigma \in T^{n-1}$\;
+\nl Construct $S := \{1,2,\hdots,\lceil(3\epsilon^{-1})6n^3(2d)^{2n}\}\rceil$ and $T := \{1,2,\hdots,\lceil (3\epsilon^{-1})nd^{2n}\rceil\},$ and randomly choose $\mA \in S^{n^2}$, and  $\bm \sigma \in T^{n-1}$\;
 \nl Apply the change of variables to obtain $f(\mA x)=f^{\mA}(x)$\;
@@
 \nl \For{$i\gets1$ \KwTo $n$}{
-\nl Run \cite[Algorithm 2]{SH} $k \geq \lg(3n/\epsilon)$ times with a straight-line program computed from 
-$\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \}$\;
+\nl Prepare a straight-line program $\Gamma$ that computes the system of polynomials
+$\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \}$ and run \cite[Algorithm 2]{SH}, with input $\Gamma,$ and with $ k \geq \lg(3n/\epsilon)$ repetitions\;
 \nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 5 \;

### 2020-02-08 main.tex
clean up conclusion

--- 2020-02-07 main.tex
@@
   Suppose that $f\in\ZZ[X_1\hdots,X_n]$ is squarefree, satisfies
-  $\deg(f) \leq d, \htt(f) \leq b$, and that $V(f) \subset \C^n$ is
+  $\deg(f) \leq d$ and $\htt(f) \leq b$, and that $V(f) \subset \C^n$ is
   smooth. Also suppose that $0 < \epsilon < 1.$
 
-  There exists a randomized algorithm that takes $f$ and $\epsilon$
-  as input and produces $n$ zero-dimensional parameterizations whose reunion includes at least one point in each connected component of
-  $V(f) \cap \R^n$, with probability at least $1-\epsilon$. Otherwise, 
-  the algorithm either returns a proper subset of the points, or FAIL.  In
-  any case, the algorithm uses
+  There exists a randomized algorithm that takes $f$ and $\epsilon$ as
+  input and produces $n$ zero-dimensional parameterizations, the union
+  of whose zeros includes at least one point in each connected
+  component of $V(f) \cap \R^n$, with probability at least
+  $1-\epsilon$. Otherwise, the algorithm either returns a proper
+  subset of the points, or FAIL.  In any case, the algorithm uses
   \[
@@
 
-Here we assume that $f$ is given as a dense polynomial. However, it 
-would be possible to take into account the runtime if $f$ was given 
-by a {\em straight-line
-  program}, that is, a sequence of operations $+,-,\times$ that takes
-as input $X_1,\dots,X_n$ and evaluates $f$; the {\em length} of a
-straight-line program is simply the number of operations it performs. Straigh-line programs are described in references such
-as~\cite{GiHeMoPa95,GiHaHeMoMoPa97,GiHeMoMoPa98,BaGiHeMb97,EMP}. The length of the straight-line program for $f$ would
-be bounded by $d^n$ and would have integer constants of height at most
-$b$. Any polynomial of degree $d$ in $n$ variables can be computed by a
-straight-line program of length $O\big ({{d+n} \choose n}\big)$:
+Here we assume that $f$ is given as a dense polynomial.  Following
+references such
+as~\cite{GiHeMoPa95,GiHaHeMoMoPa97,GiHeMoMoPa98,BaGiHeMb97,EMP}, it
+would be possible to refine the runtime estimate by assuming that $f$
+is given by a {\em straight-line program} (that is, a sequence of
+operations $+,-,\times$ that takes as input $X_1,\dots,X_n$ and
+evaluates $f$). Any polynomial of degree $d$ in $n$ variables can be
+computed by a straight-line program that does $O(d^n)$ operations:
 evaluate all monomials of degree up to $d$ in $n$ variables, multiply
-them by their respective coefficients and sum the result. However,
+them by their respective coefficients and sum the results. However,
 some inputs may be given by shorter straight-line program, and the
-algorithm is able to benefit from this.
+algorithm would actually be able to benefit from this.
 
@@
 
-In general, we cannot say much about the geometry of
-$W(\pi_i,V)$, but if we apply a generic change of coordinates $\mA$,
-$W(\pi_i,V)$ is then known to be equidimensional of dimension $(i-1)$
-or empty~\cite{BaGiHeMb97}, and to be in so-called {\em Noether
+In general, we cannot say much about the geometry of $W(\pi_i,V)$, but
+if we apply a generic change of coordinates $\mA$, $W(\pi_i,V)$ is
+then known to be equidimensional of dimension $(i-1)$ or
+empty~\cite{BaGiHeMb97}, and to be in so-called {\em Noether
   position}~\cite{EMP} (background notions in algebraic geometry are
@@
 definitions). If this is case, it suffices to choose arbitrary
-$\alpha_1,\dots,\alpha_{n-1}$ in $\Q$, and solve the systems defined
+$\sigma_1,\dots,\sigma_{n-1}$ in $\Q$, and solve the systems defined
 by
@@
 
-\section{Bit complexity}%
-\subsection{The Algorithm}
-%
-For a matrix $A \in \GL(n,\Q),$ let 
-\[
-Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
-\]
-where $b_i$ is the i-th row of $A^{-1}$.
-%
-\begin{algorithm}[hbt!]
-\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}
-\KwOut{$n$ zero-dimensional parameterizations, the union of which includes at least one point in each connected component of $V(f) \cap \R^n$}
-\nl Take $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $A \in S^{n^2}$, and  $\sigma \in T^{n-1}$\;
-\nl Apply the change of variables to obtain $f(A x)=f^A(x)$\;
-\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;
+\section{Proof of the main result}
+
+The following is our main algorithm; it expands on the sketch given in
+the introduction, by quantifying the various random choices.
+
+In step 4, we use \cite[Algorithm 2]{SH} to solve a square
+system. This subroutine is randomized; in order to guarantee a higher
+probability of success, we repeat the calculation $k$ times, for a
+well-chosen parameter $k$.
+
+This subroutine also requires that the input system be given by a
+straight-line program. We build it (at Step 3) in the straightforward
+manner already suggested in the introduction: given $f$, we can build
+a straight-line program that evaluates $f$ in $O(d^n)$ operations, by
+computing all monomials of degree up to $d$, multiplying them by the
+corresponding coefficients in $f$, and adding results. To obtain a
+straight-line program for $f^\mA$, we add $O(n^2)$ steps corresponding
+to the application of the change of variables $\mA$. From this, we can
+compute the required partial derivatives of $f^\mA$ for the same asymptotic
+cost~\cite{BaSt83}. Finally, we add the linear equations
+$X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1}$; this gives $\Gamma_i$.
+
+\begin{algorithm}[!h]
+\KwIn{$f \in \ZZ[X_1,\hdots,X_n]$ of degree at most $d$ and height at most $b$, and $0 < \epsilon < 1$}
+\KwOut{$n$ zero-dimensional parameterizations, the union of whose zeros
+  includes at least one point in each connected component of $V(f)
+  \cap \R^n$}
+
+\nl Construct $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T :=
+\{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $\mA \in
+S^{n^2}$, and $\bm \sigma \in T^{n-1}$\;
+
 \caption{{Main Algorithm} \label{}}
+
 \nl \For{$i\gets1$ \KwTo $n$}{
-\nl Run \cite[Algorithm 2]{SH} $k \geq \lg(3n/\epsilon)$ times with a straight-line program computed from 
-$\{Y_1-\sigma_1,\hdots,Y_{i-1}-\sigma_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$\;
-\nl Let $\mathscr{Q}_i$ be the highest cardinality zero-dimensional parameterization returned in step 5 \;
+ \nl Build a straight-line program $\Gamma_i$ that computes the 
+ equations
+  $\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa
+    f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \}$\;
+
+  \nl Run \cite[Algorithm 2]{SH} $k \geq \lg(3n/\epsilon)$ times
+  with input $\Gamma_i$\;
+
+  \nl Let $\mathscr{Q}_i$ be the highest cardinality
+  zero-dimensional parameterization returned in step 5 \; 
 } 
@@
 \end{algorithm}
+
+If $f^\mA$ satisfies ${\bf H}_i$, and $f^\mA$ and
+$(\sigma_1,\dots,\sigma_{i-1})$ satisfy ${\bf H}'_i$ for all $i$, then
+Theorem~2 in~\cite{EMP} establishes correctness.
+
+\paragraph*{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
+\begin{enumerate}
+    \item We defined $S = \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}$
+      and therefore the height of any $a_{i,j} \in S$ is at most
+    \[
+    \log 1/{\epsilon} + \log(3n^2(2d)^{2n}) \in O^{\sim}(n\log d + \log 1/{\epsilon}).
+    \]
+    \item As a result, by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, all coefficients in 
+      $f^\mA$ have height $ O^{\sim}(b + d\log 1 / \epsilon + dn)$.
+    \item 
+    After computing the partial derivatives, the height grows by at
+    most another factor of $\log d$. Thus, all polynomials in the
+    system considered at Step 3 have height $ O^{\sim}(b + d\log 1 /
+    \epsilon + dn)$. All integer coefficients appearing in $\Gamma_i$ 
+    satisfy the same bound.    
+    %% Furthermore, preparing the
+    %% straight line program for the gradient of $f$ does not introduce
+    %% large integers. The integers in $\grad (f)$ are of the same
+    %% magnitude as in $\Gamma$.
+    \item As a result, after applying \cite[Algorithm 2]{SH} $k$ times
+      for each index $i$, with $k = O(\log n + \log 1 / \epsilon)$,
+      the total boolean cost of the algorithm is
+      \[
+      O^{\sim}(d^{3n+1}(\log1/\epsilon)(b + \log1/\epsilon))
+      \]
+      where the polynomials in the output have degree at most $d^n,$ and height at most
+      \[
+      O^{\sim}(d^{n+1}(b + \log 1 / \epsilon)).
+  \]
+\end{enumerate}
+
+This proves the runtime estimate, as well as our bounds on the height
+of the output.
+
+\paragraph*{Probability of success.} 
+Let $\Delta_i \in \C[\A]$ be the polynomials from
+Theorem~\ref{theo:gen}. Denote by $\Delta := \prod_{i=1}^n \D_i,$ and
+note that
+\begin{align}
+    \deg \Delta \leq \sum_{i=1}^n \deg \Delta_i \leq 6n^3(2d)^{2n}.
+\end{align}
+If $\mA \in \C^{n \times n}$ does not cancel $\Delta,$ then $\mA$ is
+invertible and $f^\mA$ satisfies $\textbf{H}_i$ for all $i \in
+\{1,\hdots,n\}.$ Now, assuming that $\mA$ is such a matrix, let
+$\Xi_i\in \C[\A]$ be the polynomials from Theorem 2.2 applied to
+$f^{\mA}.$ Denote by $\Xi := \prod_{i=1}^n \Xi_i,$ and note that
+\begin{align}
+    \deg \Xi \leq \sum_{i=1}^n \deg \Xi_i \leq nd^{2n}.
+\end{align}
+If $\bm \sigma \in \C^{i-1}$ does not cancel $\Xi$, then $f^{\mA}$ and
+$\bm \sigma$ satisfy $\textbf{H}_i^{'}$ for all $i \in
+\{1,\hdots,n\};$ as we argued above, the algorithm is guaranteed to
+succeed, as long as our call to Algorithm 2 in~\cite{SH} succeeds.
+That latter reference establishes that by repeating the calculation 
+$k$ times, and keeping the output of highest degree among those $k$
+results, we succeed with probability at least $1-(1/2)^k$.
+
+Now, by construction of
+\[
+S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}
+\] 
+and 
+\[
+T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},
+\] 
+where $\mA \in S^{n^2}$ and  $\bm \sigma \in T^{n-1}$ are randomly chosen, we have 
 %
+\[
+\pr[\Delta(\mA)=0] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3
+\]
+and
+\[
+\pr[\Xi(\bm \sigma)=0] \leq \deg \frac{\deg\Xi}{|T|} = \epsilon/3.
+\]
 %
-\subsection{Proof of Theorem 1.1}
-%
-\textbf{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
-%
-\begin{enumerate}
-    \item We defined $S = \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}$ and therefore the height of $a_{i,j} \in S$ is at most 
-    \[
-    \log 1/{\epsilon} + \log(3n^2(2d)^{2n}) = O^{\sim}(n\log d + \log 1/{\epsilon}).
-    \]
-    \item  We can prepare a straight-line program $\Gamma$ for $f^A$ with length at most $d^n$, and 
-    by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, height of at most 
-    \[
-        O^{\sim}(b + d\log 1 / \epsilon + dn).
-    \]
-    \item 
-    After computing the partial derivatives the height grows by at most another factor of $\log d$.
-Furthermore, preparing the straight line program for the gradient of $f$ does not introduce large integers.
-The integers in $\grad (f)$ are of the same magnitude as in $\Gamma$.
-    \item 
-    After applying \cite[Algorithm 2]{SH} $kn$ times with $k = O(\log n + \log 1 / \epsilon)$, the total boolean cost of the algorithm is
-  \[
-O^{\sim}(d^{3n+1}(\log1/\epsilon)(b + \log1/\epsilon))
-  \]
-    where the polynomials in the output have degree at most $d^n,$ and height at most
-  \[
-  O^{\sim}(d^{n+1}(b + \log 1 / \epsilon)).
-  \]
-\end{enumerate}
-%
-\par \noindent 
-\textbf{Probability of success:} Let $\Delta_i \in \C[\A]$ be the polynomials from Theorem 2.1. Denote by $\Delta$ the product $\Delta := \prod_{i=1}^n \D_i.$ Note that 
-\begin{align}
-    \deg \Delta \leq \sum_{i=1}^n \deg \Delta_i \leq 6n^3(2d)^{2n},
-\end{align}
-where then, if $\mA \in \C^{n \times n}$ does not cancel $\Delta,$ then  $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for all $i \in \{1,\hdots,n\}.$ Now, assuming that $\mA$ is such a matrix, let $\Xi_i\in \C[\A]$ be the polynomials from Theorem 2.2 and denote by $\Xi$ the product $\Xi := \prod_{i=1}^n \Xi_i.$ Note that
-\begin{align}
-    \deg \Xi \leq \sum_{i=1}^n \deg \Xi_i \leq nd^{2n},
-\end{align}
-where then, if $\sigma \in \C^{i-1}$ does not cancel $\Xi$ then $f^{\mA}$ and $\sigma$ satisfy $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ 
-Now, by construction of \[S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}\] and \[T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},\] where $A \in S^{n^2}$ and  $\sigma \in T^{n-1}$ are randomly chosen, we have
-%
-\[
-\pr[A \in \Delta] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3
-\]
-and
-\[
-\pr[\sigma \in \Xi] \leq \deg \frac{\deg\Xi}{|S|} = \epsilon/3.
-\]
-%
-Let $\mathscr{E}$ be the event that, the parameterizations $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 7 of Algorithm 1 contain all points and are correct.
-Then, the probability of success is equal to
+Let $\mathscr{E}$ be the event that the parametrizations
+$[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 6 of
+Algorithm~1 are correct. Then, the probability of success is equal to
 \begin{align*}
- \pr[A \not\in \Delta] \times \pr[\sigma \not \in \Xi ~|~A \not\in \Delta] \times \pr[\mathscr{E}~|~A \not\in \Delta \textrm{ and } \sigma \not \in \Xi].
+ \pr[\Delta(\mA)\ne 0] \times \pr[\Xi(\bm \sigma)\ne 0 ~|~\Delta(\mA) \ne 0] \times \pr[\mathscr{E}~|~
+   \Delta(\mA)\Xi(\bm\sigma) \ne 0].
 \end{align*}
 %
-Set $k = \lg(3n/\epsilon)$, with $\epsilon>0,$ so that 
+Set $k = \lg(3n/\epsilon)$ so that 
 \[
@@
 \begin{align*}
-\pr[\textrm{success}] &\geq  (1- \epsilon/3)(1- \epsilon/3)\pr[\mathscr{E}~|~A \not\in \Delta \textrm{ and } \sigma \not \in \Xi]\\
-&\geq (1- \epsilon/3)(1- \epsilon/3)(1-(11/32)^k)^n\\
-& \geq (1- \epsilon/3)(1- \epsilon/3)(1-2^{-k})^n \\
-& \geq (1- \epsilon/3)(1- \epsilon/3)(1- \epsilon/3)\\
-& \geq 1 - \epsilon.
+\pr[\textrm{success}] &\geq (1- \epsilon/3)(1-
+\epsilon/3)\pr[\mathscr{E}~|~   \Delta(\mA)\Xi(\bm\sigma) \ne 0]\\ 
+& \geq (1- \epsilon/3)(1-
+\epsilon/3)(1-2^{-k})^n \\ & \geq (1- \epsilon/3)(1- \epsilon/3)(1-
+\epsilon/3)\\ & \geq 1 - \epsilon.
 \end{align*}
+This finishes the proof our main theorem.
+
 %%

### 2020-02-08 main.tex
Update main.tex
Ceilings and step 5 in main alg

@@
 
-\nl Construct $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T :=
-\{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $\mA \in
+\nl Construct $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n} \rceil\}$ and $T :=
+\{1,2,\hdots,\lceil 3\epsilon^{-1}nd^{2n}\rceil\},$ and randomly choose $\mA \in
 S^{n^2}$, and $\bm \sigma \in T^{n-1}$\;
@@
   \nl Let $\mathscr{Q}_i$ be the highest cardinality
-  zero-dimensional parameterization returned in step 5 \; 
+  zero-dimensional parameterization returned in step 4 \; 
 } 
@@
 \begin{enumerate}
-    \item We defined $S = \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}$
+    \item We defined $S = \{1,2,\hdots,\lceil 3\epsilon^{-1}3n^2(2d)^{3n} \rceil \}$
       and therefore the height of any $a_{i,j} \in S$ is at most
@@
 \[
-S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}
+S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n}\rceil \}
 \] 
@@
 \[
-T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},
+T := \{1,2,\hdots,\lceil 3\epsilon^{-1}nd^{2n} \rceil \},
 \] 

### 2020-02-08 main.tex
Update main.tex
Bit operation cost, correction

@@
 \begin{enumerate}
-    \item We defined $S = \{1,2,\hdots,\lceil 3\epsilon^{-1}3n^2(2d)^{3n} \rceil \}$
+    \item We defined $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n} \rceil \}$
       and therefore the height of any $a_{i,j} \in S$ is at most
     \[
-    \log 1/{\epsilon} + \log(3n^2(2d)^{2n}) \in O^{\sim}(n\log d + \log 1/{\epsilon}).
-    \]
-    \item As a result, by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, all coefficients in 
-      $f^\mA$ have height $ O^{\sim}(b + d\log 1 / \epsilon + dn)$.
+    \log 3/{\epsilon} + \log(6n^3(2d)^{2n}) \in O^{\sim}(\log 1/{\epsilon} + n\log d).
+    \]
     \item 

### 2020-02-08 main.tex
Update main.tex
Some typos corrected
Update main.tex
More typos

@@
   X_{i+1}},\dots,{\pa f}/{\pa X_n})$. As pointed out in the
-introduction, their zero-set is the $i$th polar variety
+introduction, their zero-set is the $i$-th polar variety
 $W(\pi_i,V(f))$.  Then, we say that $f$ satisfies $\textbf{H}_i$ if
@@
   implies that $W(\pi_i,V(f))$ is either empty or $(i-1)$-equidimensional,
-  and that $\I(i, f^\mA)$ is radical.}
+  and that $\I(i, f)$ is radical.}
 
@@
 \begin{proof}
-At all $(\xb,\bm\sigma)$ zeros of $\bm\Psi,$ the Jacobian matrix of
+At all zeros $(\xb,\bm\sigma)$ of $\bm\Psi,$ the Jacobian matrix of
 $\bm\Psi$ has full rank $n$. Indeed, indexing columns 
@@
 $\C(\A)[X_1,\dots,X_n]$:
-$$\I(\pi_i,f^\A)= \big (f^\A, {\pa f^\A}/{\pa X_{i+1}},\dots,{\pa
+$$\I(i,f^\A)= \big (f^\A, {\pa f^\A}/{\pa X_{i+1}},\dots,{\pa
   f^\A}/{\pa X_n}) \big ),$$ and let $W^\A$ denote their zero-set,
@@
 \[
-\pr[\Xi(\bm \sigma)=0] \leq \deg \frac{\deg\Xi}{|T|} = \epsilon/3.
+\pr[\Xi(\bm \sigma)=0] \leq  \frac{\deg\Xi}{|T|} = \epsilon/3.
 \]
@@
 \end{align*}
-This finishes the proof our main theorem.
+This finishes the proof of our main theorem.
 
@@
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2020-04-27 main.tex
Update main.tex
Section capitalization
Updates from Overleaf
Typos and changes suggested from Review 2

@@
     component of a smooth real algebraic set}, ISSAC'03). This
-  algorithm uses random changes of variables, that are proved to
+  algorithm uses random changes of variables that are proved to
   generically ensure certain desirable geometric properties. The
@@
 
-  Our paper answer these questions. Our main contribution is a
+  Our paper answers these questions. Our main contribution is a
   quantitative analysis of several genericity statements, such as
@@
 in~\cite{Mumford76,Shafarevich77,ECA}; we will recall key
-definitions). If this is case, it suffices to choose arbitrary
+definitions). If this is the case, it suffices to choose arbitrary
 $\sigma_1,\dots,\sigma_{n-1}$ in $\Q$, and solve the systems defined
@@
 
-\section{Weak Transversality and Applications}
+\section{Weak transversality and applications}
 
@@
 
-\subsection{Weak Transversality}
+\subsection{Weak transversality}
 
@@
 taken with respect to $\Xb$, has full rank $n-i+1$ at all $\xb$ that
-cancels equations. We then define $\Delta_{i,i}:=\Gamma_i
+cancels equations. We then define $\Delta_{i,1}:=\Gamma_i
 \det(\A)$; this is a non-zero polynomial of degree at most $d^{2n}+n
@@
 Let us verify that $\Delta_{i,1}$ satisfies the claim in the preamble.
-Take $\mA$ in $\C^{n\times n}$, such that $\Delta_{i,i}(\mA)$ is
+Take $\mA$ in $\C^{n\times n}$, such that $\Delta_{i,1}(\mA)$ is
 non-zero. Clearly, $\mA$ is invertible; it remains to check that
@@
   f}{\pa X_n}$ at $\xb$ is non-zero (by $\textbf{H}_i$), the entire
-matrix must have full rank $n$. Thus,  $\bz$ is a regular value of $\bm\Phi.$
+matrix must have full rank $n$. Thus,  $\bz$ is a regular value of $\bm\Psi.$
 \end{proof}
@@
 polynomial $\Xi_i$ in $\C[S_1,\dots,S_{i-1}]$ of degree at most
-$d^{2n},$ with the following property: at any root $\xb$ of
-$(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
-  X_{i+1}},\dots,{\pa f}/{\pa X_n})$, the Jacobian matrix of these
+$d^{2n},$ with the following property:  if $\Xi_i(\bm \sigma)\neq 0$ then at any root $\xb$ of
+\[(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
+  X_{i+1}},\dots,{\pa f}/{\pa X_n}),\] the Jacobian matrix of these
 equations has rank $n$. Theorem~\ref{theo:Hp} is proved.
@@
 \KwOut{$n$ zero-dimensional parameterizations, the union of whose zeros
-  includes at least one point in each connected component of $V(f)
-  \cap \R^n$}
+  includes at least one point in each connected component of $V(f)\cap \R^n$, with probability of success at least $1-\epsilon$}
 
@@
 results, we succeed with probability at least $1-(1/2)^k$.
+In ~\cite{SH} the algorithm is shown to succeed in a single run with  probability at least $1-21/32$.
+We bound the probability of success with $1-1/2$ for simplicity.
 

### 2020-05-09 main.tex
Explained how the main algorithm is Monte Carlo

@@
 \item For any $\xb$ in $W(\pi_i,V(f))$, the Jacobian matrix
-  $\jac_\Xb(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.
+  $\jac_\xb(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.
 
@@
 succeed, as long as our call to Algorithm 2 in~\cite{SH} succeeds.
-That latter reference establishes that by repeating the calculation 
-$k$ times, and keeping the output of highest degree among those $k$
-results, we succeed with probability at least $1-(1/2)^k$.
-In ~\cite{SH} the algorithm is shown to succeed in a single run with  probability at least $1-21/32$.
-We bound the probability of success with $1-1/2$ for simplicity.
-
+That latter reference establishes that by repeating the calculation $k$ times, and keeping the output of highest degree among those $k$ results, we succeed with probability at least $1-(1/2)^k$.
+Hence, the algorithm is Monte Carlo because it can error on one side by possibly missing solutions.
+Note that Algorithm 2 is shown to succeed in a single run with  probability at least $1-11/32,$ and we bound the probability of success with $1-1/2$ for simplicity.
 Now, by construction of

### 2020-05-09 main.tex
Explaining how the algorithm can return FAIL

@@
 \KwOut{$n$ zero-dimensional parameterizations, the union of whose zeros
-  includes at least one point in each connected component of $V(f)\cap \R^n$, with probability of success at least $1-\epsilon$}
+  includes at least one point in each connected component of $V(f)\cap \R^n$, with probability of success at least $1-\epsilon$. }
 
@@
 That latter reference establishes that by repeating the calculation $k$ times, and keeping the output of highest degree among those $k$ results, we succeed with probability at least $1-(1/2)^k$.
-Hence, the algorithm is Monte Carlo because it can error on one side by possibly missing solutions.
+When Algorithm 2 does not succeed, it either returns a proper subset of the solutions, or FAIL.
 Note that Algorithm 2 is shown to succeed in a single run with  probability at least $1-11/32,$ and we bound the probability of success with $1-1/2$ for simplicity.

### 2020-05-14 main.tex
Explanation: W(\pi_i,V(f^A)) \not =W(\pi_i,V)^A

@@
 %\acmConference[ Kalamata, Messinia, Greece '20]{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation}{July 20--23, 2020}{ Kalamata, Messinia, Greece}
-\acmBooktitle{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation,  July 20--23, 2020,  Kalamata, Messinia, Greece}
+\acmBooktitle{Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation,  July 20--23, 2020,  Kalamata, Messinia, Greece}
 \acmPrice{15.00}
@@
 
-\keywords{Real algebraic geometry, transversality, Noether
-  position, bit complexity}
+\keywords{Real algebraic geometry; weak transversality; Noether
+  position; complexity }
 
@@
 In general, we cannot say much about the geometry of $W(\pi_i,V)$, but
-if we apply a generic change of coordinates $\mA$, $W(\pi_i,V)$ is
-then known to be equidimensional of dimension $(i-1)$ or
+if we apply a generic change of coordinates $\mA$ to $f$, then $W(\pi_i,V)$ is
+known to be equidimensional of dimension $(i-1)$ or
 empty~\cite{BaGiHeMb97}, and to be in so-called {\em Noether
@@
 $X_1,\dots,X_n$.
+
+Note that for a variety $Y \subset \C^n,$ we can define $Y^{\mA}$ as the image of $Y$ by the map $\phi_{\mA} : \xb \mapsto \mA^{-1}\xb.$ Note that $W(\pi_i,V(f^\mA))$ may not equal $W(\pi_i,V(f))^\mA$, as, for instance, their dimensions may vary.
 

### 2020-05-14 rebuttal.tex
Uploaded rebuttal

%\documentclass{acmart}
%\documentclass{amsart}
\documentclass{article}
%\documentclass{acmart}
\usepackage[utf8]{inputenc}

% packages 
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[titles]{tocloft}%----------------------------------------
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{enumerate}
\usepackage{chngcntr}
\usepackage{titlesec}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

% new commands and shortcuts

\def\sO{\mathscr{O}}
\def\gip{\Gamma_i^{'}}
\def\gi{\Gamma_i}
\def\td{{\bf todo}}
\def\bs{\textit{\textbf{s}}}
\def\ub{\textit{\textbf{u}}}
\def\bz{\textit{\textbf{0}}}
\def\Lb{\textit{\textbf{L}}}
\def\Ls{\mathscr{L}}
\def\Xb{\textit{\textbf{X}}}
\def\lb{\textit{\textbf{l}}}
\def\Lambdab{\bm{\Lambda}}
\def\Thetab{\bm{\Theta}}
\def\thetab{\bm{\vartheta}}
\def\mA{{\bm A}}
\def\fA{{\frak A}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\pb{\textit{\textbf{p}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\crit}{crit}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\pr{\mathbb{P}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\N{\mathbb{N}}
\def\R{\mathbb{R}}
\def\K{\mathbb{K}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\DeclareMathOperator{\jac}{jac}
\def\exp{\textrm{exp}}
\def\grad{\textbf{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\dtt{\widetilde{d}}
\def\kt{\widetilde{k}}
\def\dt{s}
\def\bI{\textbf{I}}
%% \def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\softO}{{O^{\sim}}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\scrQ{\ensuremath{\mathscr{Q}}}
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
% Theorems 
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}{Question}
%\newtheorem*{ex}{Example}
\newtheorem{cor}[theorem]{Corollary}

\begin{document}
\title{Rebuttal, Submission 98: On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface}
\author{}
\date{}

\maketitle
\noindent \textbf{Brief  review of notation.} 
Recall some of the notation from our paper, where we have $f\in\ZZ[X_1\hdots,X_n]$ squarefree, satisfying $\deg(f) \leq d$ and $\htt(f) \leq b$,
and $V=V(f) \subset \C^n$ smooth (note that we do not assume $V(f)$ is compact). Recall the notion of polar varieties, which are defined as follows. For $i \in
\{1,\hdots,n-1\},$ denote by $\pi_i:\C^n \rightarrow \C^i$ the
projection $(x_1,\hdots,x_n) \mapsto (x_1,\hdots,x_i)$.  The $i$-th
\textit{polar variety} \[W(\pi_i,V) := \{\xb \in V~|~\dim \pi_i(T_\xb
V) < i\}\] is the set of critical points of $\pi_i$ on $V$, which is
thus defined by the vanishing of 
\[
f,\frac{\pa f}{\pa
  X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.
\]
Consider again the $n\times n$ matrix of indeterminates $\A=(\A_{j,k})_{1 \le j,k \le n}$ where we define $f^\A := f(\A\xb).$ For a matrix $\mA \in \C^{n \times n}$ we define $f^\mA := f(\mA\xb),$ and for a variety $Y \subset \C^n,$  $Y^{\mA}$ is the image of $Y$ by the map $\phi_{\mA} : \xb \mapsto \mA^{-1}\xb.$
\vspace{2mm}
\par 
\noindent \textbf{Responding to questions.} 
In what follows, we address the main questions posed in the three reviews of our paper. There is some overlap between the ideas given in each review. To avoid repetition, we do not respond to each review individually.

\begin{enumerate}
    \item \textit{Can we replace each upper degree bound $d^n$ by $\deg W(\pi_i,V)$? }

    It is not straightforward to replace $d^n$ with degree bounds of polar varieties; we are not sure how to do it. In any case, we do not expect that it would improve our degree bounds.

    \item \textit{Can you explain the FAIL output in the main algorithm?}

    The main algorithm is guaranteed to succeed, as long as our call to Algorithm 2 in~\cite{SH} succeeds. That latter reference establishes that by repeating the calculation $k$ times, and keeping the output of highest degree among those $k$ results, we succeed with probability at least $1-(1/2)^k$. When Algorithm 2 does not succeed, it either returns a proper subset of the solutions, or FAIL. Note that Algorithm 2 is shown to succeed in a single run with  probability at least $1-11/32,$ and we bound the probability of success with $1-1/2$ for simplicity.

    \item\textit{ Is the quantitative Noether position statement a new result? }

    In Theorem 2.1, we show that, for $i=1,\dots,n$, there exists a non-zero polynomial $\D_i$ in $\C[\A]$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA \in \C^{n\times n}$ does not cancel $\D_i$, then $\mA$ is invertible and $f^\mA$ satisfies:
%
\begin{enumerate}[(i)]
\item For any $\xb$ in $W(\pi_i,V(f^{\mA}))$, the Jacobian matrix
  $\jac_\xb(f^{\mA},\frac{\pa f^{\mA}}{\pa
  X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n})$ has full rank $n-(i-1)$.

\smallskip

\item $W(\pi_i,V(f^{\mA}))$ is either empty or in Noether position for
  $\pi_{i-1}$.
\end{enumerate}

In the second review, it was pointed out that \cite[Lemma 5]{JeSa10} and \cite[Proposition 4.5]{SharpEstimatesForTheEffectiveN} are similar quantitative Noether position statements. Although the authors proceed in a way that is different from our approach, each of these statements show that a non-zero polynomial $g \in \C[\A]$ exists, with $\deg g \leq D,$ for some explicit degree bound $D \in \mathbb{N}-\{0\},$
such that if $\mA \in \C^{n \times n}$ does not cancel $g$, then $W(\pi_i,V(f))^A$ is in Noether position for $\pi_{i-1}.$ However, (ii) does not follow from these statements. Indeed, it is not necessarily the case that $W(\pi_i,V(f))^A$ is equal to $W(\pi_i,V(f^A))$. For instance, their dimensions may not be equal. This can be seen already for simple polynomials such as $f = x^2 + 2y^2-1$. 
\end{enumerate}

\newpage

\bibliographystyle{plain}
\bibliography{sample-base}
\end{document}

### 2020-05-15 main.tex
ACM reference format
Typos and minor stylistic changes

@@
 %\acmConference[ Kalamata, Messinia, Greece '20]{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation}{July 20--23, 2020}{ Kalamata, Messinia, Greece}
-\acmBooktitle{Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation,  July 20--23, 2020,  Kalamata, Messinia, Greece}
+\acmBooktitle{International Symposium on Symbolic and Algebraic Computation (ISSAC'20),  July 20--23, 2020,  Kalamata, Greece}
 \acmPrice{15.00}
@@
   implies that $W(\pi_i,V(f))$ is either empty or $(i-1)$-equidimensional,
-  and that $\I(i, f)$ is radical.}
+  and that $\I(i, f)$ defines a radical ideal.}
 
@@
 \[
-  (X_1-S_1,\hdots,X_{i-1}-S_{i-1}, f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n} ).
+  \left(X_1-S_1,\hdots,X_{i-1}-S_{i-1}, f,\pa f/\pa X_{i+1},\hdots,\pa f/\pa X_n \right).
 \]
@@
 \] 
-Since the Jacobian of $f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa
-  f}{\pa X_n}$ at $\xb$ is non-zero (by $\textbf{H}_i$), the entire
+Since the Jacobian of $f,\pa f/\pa X_{i+1},\hdots,\pa
+  f/\pa X_n$ at $\xb$ is non-zero (by $\textbf{H}_i$), the entire
 matrix must have full rank $n$. Thus,  $\bz$ is a regular value of $\bm\Psi.$
@@
 $$\I(i,f^\A)= \big (f^\A, {\pa f^\A}/{\pa X_{i+1}},\dots,{\pa
-  f^\A}/{\pa X_n}) \big ),$$ and let $W^\A$ denote their zero-set,
+  f^\A}/{\pa X_n} \big ),$$ and let $W^\A$ denote their zero-set,
 that is, $W(\pi_i,V(f^\A)).$ In Section~\ref{ssec:Hi1}, we saw that
@@
 which we first need to determine degree bounds, separately in $\Xb,T$
-and $\A,$ of the polynomials in the membership relationship. We have
+and $\A,$ of the polynomials in the membership relationship:
 \begin{align*}
@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\}&\leq d,\\
+\right\}&\leq d;\\
 \deg_{\A}  
@@
 f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
-\right\}& \leq d,\\
-\deg_{\Xb,T}(1-T\pjb) &\leq (2d)^n +1,\\
+\right\}& \leq d;\\
+\deg_{\Xb,T}(1-T\pjb) &\leq (2d)^n +1;\\
 \deg_{\A}(1-T\pjb)& \leq (2d)^n.
@@
  equations
-  $\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa
-    f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \}$\;
+  $\left\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa
+    f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \right\}$\;
 

### 2020-05-15 main.tex
More typos and stylistic changes

@@
 
-Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$, with $V(f)
-\subset \C^n$ smooth. In what follows, we fix $i$ in $1,\dots,n$, and
+Let $f \in \ZZ[X_1,\hdots,X_n]$ have total degree $d$, with $V(f)\subset \C^n$ smooth. In what follows, we fix $i$ in $\{1,\dots,n\}$, and
 we prove the following: {\em there exists a non-zero polynomial
@@
 
-Let $f \in \ZZ[X_1,\hdots,X_n]$ and $i$ be as before. We now assume
+Let $f \in \ZZ[X_1,\hdots,X_n]$ and $i \in \{1,\hdots,n\}$ be as before. We now assume
 that $f$ satisfies $\textbf{H}_i(1)$, and we prove the following: {\em
@@
   \sigma =(\sigma_1,\dots,\sigma_{i-1})\in \C^{i-1}$ does not cancel
-  $\Xi_{i}$, the ideal
+  $\Xi_{i}$, then the ideal
   $$(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
@@
 \section{Property ${\bf H}_i(2)$: Noether position}\label{sec:Hi2}
-
-Throughout this section, $f$ and $i \in \{1,\hdots,n\}$ are fixed. We
-prove that there exists a hypersurface $\D_{i} \subset \C^{n\times
-  n}$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA$ is not in $\D_{i}$,
-then $\mA$ is invertible and satisfies both conditions in
+Let $f\in \ZZ[X_1,\hdots,X_n]$, with total degree $d$ and $V(f)\subset \C^n$ smooth, and $i \in \{1,\hdots,n\}$ be fixed throughout this section. We
+prove that there exists a non-zero polynomial $\D_{i}$ in $\C[\A]$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA \in \C^{n \times n}$ does not cancel $\D_{i}$,
+then $\mA$ is invertible and $f^{\mA}$ satisfies both conditions in
 $\textbf{H}_i$.
@@
 $\A=(\A_{j,k})_{1 \le j,k \le n}$ and the field $\C(\A)$,
-and define $f^{\A} \in \C(\A)[X_1,\dots,X_n]$.  Since $i$ is fixed, to
+and define $f^{\A} \in \C(\A)[X_1,\dots,X_n]$.  Since $f$ and $i$ are fixed, to
 simplify notation, let $\I^\A$ denote the following polynomials in
@@
 coefficients, and we will write $\overline P := D P$, so that
-$\overline P$ is in $\C[\A,X_1,\dots,X_{i-1},X_n]$.
+$\overline P$ is in $\C[\A,X_1,\dots,X_n]$.
 

### 2020-05-15 main.tex
Updates from Overleaf

@@
   For $i=1,\dots,n$, there exists a non-zero polynomial $\D_i$ in
-  $\C[\A]$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA \in
+  $\C[\A]$ of degree at most $5n^2(2d)^{2n}$ such that if $\mA \in
   \C^{n\times n}$ does not cancel $\D_i$, then $\mA$ is invertible and
@@
 Let $f\in \ZZ[X_1,\hdots,X_n]$, with total degree $d$ and $V(f)\subset \C^n$ smooth, and $i \in \{1,\hdots,n\}$ be fixed throughout this section. We
-prove that there exists a non-zero polynomial $\D_{i}$ in $\C[\A]$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA \in \C^{n \times n}$ does not cancel $\D_{i}$,
+prove that there exists a non-zero polynomial $\D_{i}$ in $\C[\A]$ of degree at most $5n^2(2d)^{2n}$ such that if $\mA \in \C^{n \times n}$ does not cancel $\D_{i}$,
 then $\mA$ is invertible and $f^{\mA}$ satisfies both conditions in
@@
 the upper bound
-$$\deg(\D_i) \le 2nd^{2n} + 2n^2(2d)^{2n} + n(2d)^n \le 6n^2 (2d)^{2n}.$$
+$$\deg(\D_i) \le 2nd^{2n} + 2n^2(2d)^{2n} + n(2d)^n \le 5n^2 (2d)^{2n}.$$
 This completes the proof of Theorem~\ref{theo:gen}.
@@
 
-\nl Construct $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n} \rceil\}$ and $T :=
+\nl Construct $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}5n^3(2d)^{2n} \rceil\}$ and $T :=
 \{1,2,\hdots,\lceil 3\epsilon^{-1}nd^{2n}\rceil\},$ and randomly choose $\mA \in
@@
 \begin{enumerate}
-    \item We defined $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n} \rceil \}$
+    \item We defined $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}5n^3(2d)^{2n} \rceil \}$
       and therefore the height of any $a_{i,j} \in S$ is at most
     \[
-    \log 3/{\epsilon} + \log(6n^3(2d)^{2n}) \in O^{\sim}(\log 1/{\epsilon} + n\log d).
+    \log 3/{\epsilon} + \log(5n^3(2d)^{2n}) \in O^{\sim}(\log 1/{\epsilon} + n\log d).
     \]
@@
 \begin{align}
-    \deg \Delta \leq \sum_{i=1}^n \deg \Delta_i \leq 6n^3(2d)^{2n}.
+    \deg \Delta \leq \sum_{i=1}^n \deg \Delta_i \leq 5n^3(2d)^{2n}.
 \end{align}
@@
 \[
-S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n}\rceil \}
+S := \{1,2,\hdots,\lceil 3\epsilon^{-1}5n^3(2d)^{2n}\rceil \}
 \] 

### 2020-05-15 rebuttal.tex
Updates from Overleaf

@@
 \usepackage{enumitem}
-\usepackage{enumerate}
+%% \usepackage{enumerate}
 \usepackage{chngcntr}
@@
 \begin{document}
-\title{Rebuttal, Submission 98: On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface}
+
+\title{Answer to the reviews for Submission 98}
+
 \author{}
@@
 \maketitle
-\noindent \textbf{Brief  review of notation.} 
-Recall some of the notation from our paper, where we have $f\in\ZZ[X_1\hdots,X_n]$ squarefree, satisfying $\deg(f) \leq d$ and $\htt(f) \leq b$,
-and $V=V(f) \subset \C^n$ smooth (note that we do not assume $V(f)$ is compact). Recall the notion of polar varieties, which are defined as follows. For $i \in
-\{1,\hdots,n-1\},$ denote by $\pi_i:\C^n \rightarrow \C^i$ the
-projection $(x_1,\hdots,x_n) \mapsto (x_1,\hdots,x_i)$.  The $i$-th
-\textit{polar variety} \[W(\pi_i,V) := \{\xb \in V~|~\dim \pi_i(T_\xb
-V) < i\}\] is the set of critical points of $\pi_i$ on $V$, which is
-thus defined by the vanishing of 
-\[
-f,\frac{\pa f}{\pa
-  X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.
-\]
-Consider again the $n\times n$ matrix of indeterminates $\A=(\A_{j,k})_{1 \le j,k \le n}$ where we define $f^\A := f(\A\xb).$ For a matrix $\mA \in \C^{n \times n}$ we define $f^\mA := f(\mA\xb),$ and for a variety $Y \subset \C^n,$  $Y^{\mA}$ is the image of $Y$ by the map $\phi_{\mA} : \xb \mapsto \mA^{-1}\xb.$
-\vspace{2mm}
-\par 
-\noindent \textbf{Responding to questions.} 
-In what follows, we address the main questions posed in the three reviews of our paper.
-There is some overlap between the ideas given in each review.
-To avoid repetition, we do not respond to each review individually.
+
+\noindent \textbf{Responding to questions.} We take
+$f\in\ZZ[X_1\hdots,X_n]$ squarefree, satisfying $\deg(f) \leq d$ and
+$V=V(f) \subset \C^n$ smooth. For $i \in \{1,\hdots,n-1\},$ denote by
+$\pi_i:\C^n \rightarrow \C^i$ the projection $(x_1,\hdots,x_n) \mapsto
+(x_1,\hdots,x_i)$.  The $i$-th \textit{polar variety} \[W(\pi_i,V) :=
+\{\xb \in V~|~\dim \pi_i(T_\xb V) < i\}\] is the set of critical
+points of $\pi_i$ on $V$.
+For a matrix $\mA \in \C^{n \times n}$ we define $f^\mA := f(\mA\xb),$
+and for a variety $Y \subset \C^n,$ $Y^{\mA}$ is the image of $Y$ by
+the map $\phi_{\mA} : \xb \mapsto \mA^{-1}\xb.$
+
+There is some overlap between the questions in the reviews. To
+avoid repetition, we do not respond to each review individually.
 
 \begin{enumerate}
-    \item \textit{Can we replace each upper degree bound $d^n$ by $\deg W(\pi_i,V)$? }
+    \item \textit{Can we replace each upper degree bound $d^n$ by
+      $\deg W(\pi_i,V)$? }
 
-    It is not straightforward to replace $d^n$ with degree bounds of polar varieties; we are not sure how to do it. In any case, we do not expect that it would improve our degree bounds.
+    This is not straightforward to replace $d^n$; we are not sure how
+    to do it. In any case, we do not expect that it would improve the
+    worst-case bounds.
 
@@
 
-    The main algorithm is guaranteed to succeed, as long as our call to Algorithm 2 in~\cite{SH} succeeds.
-That latter reference establishes that by repeating the calculation $k$ times, and keeping the output of highest degree among those $k$ results, we succeed with probability at least $1-(1/2)^k$.
-When Algorithm 2 does not succeed, it either returns a proper subset of the solutions, or FAIL.
-Note that Algorithm 2 is shown to succeed in a single run with  probability at least $1-11/32,$ and we bound the probability of success with $1-1/2$ for simplicity.
+    The main algorithm is guaranteed to succeed as long as our call
+    to Algorithm 2 in [30] does. The latter is randomized; when it
+    does not succeed, it either returns a proper subset of the
+    solutions, or FAIL.
 
-    \item\textit{ Is the quantitative Noether position statement a new result? }
+    \item\textit{Is the quantitative Noether position statement a new result? }
 
-    In Theorem 2.1, we show that, for $i=1,\dots,n$, there exists a non-zero polynomial $\D_i$ in $\C[\A]$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA \in \C^{n\times n}$ does not cancel $\D_i$, then $\mA$ is invertible and $f^\mA$ satisfies:
-%
-\begin{enumerate}[(i)]
-\item For any $\xb$ in $W(\pi_i,V(f^{\mA}))$, the Jacobian matrix
-  $\jac_\xb(f^{\mA},\frac{\pa f^{\mA}}{\pa
-  X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n})$ has full rank $n-(i-1)$.
+    In Theorem 2.1, we show that, for $i=1,\dots,n$, there exists a
+    non-zero polynomial $\D_i$ of degree at most
+    $6n^2(2d)^{2n}$ such that if $\mA \in \C^{n\times n}$ does not
+    cancel $\D_i$, then $\mA$ is invertible and $W(\pi_i,V(f^{\mA}))$
+    is either empty or in Noether position for $\pi_{i-1}$.
 
-\smallskip
+    In the second review, it was pointed out that Lemma 5 in G. Jeronimo
+    and J. Sabia, {\em Effective equidimensional decomposition of affine
+      varieties} or Proposition 4.5 in T. Krick, L.-M. Pardo and
+    M. Sombra, {\em Sharp estimates for the arithmetic Nullstellensatz},
+    are quantitative Noether position statements. The question is  
+    whether our Theorem 2.1 is new.
 
-\item $W(\pi_i,V(f^{\mA}))$ is either empty or in Noether position for
-  $\pi_{i-1}$.
+    Our theorem does not follow from these previous results. Indeed,
+    results in the references above would allow us to quantify when
+    $W(\pi_i,V(f))^\mA$ is in Noether position, whereas we need to
+    understand when $W(\pi_i,V(f^\mA))$ is. These two sets are in general
+    different: the operations of computing the critical points of a
+    projection and changing variables do not commute (this can be seen
+    already for polynomials such as $f = X_1^2 + 2X_2^2-1$).
+    We should have made it clearer.
 \end{enumerate}
 
-In the second review, it was pointed out that \cite[Lemma 5]{JeSa10} and \cite[Proposition 4.5]{SharpEstimatesForTheEffectiveN} are similar quantitative Noether position statements.
-Although the authors proceed in a way that is different from our approach, each of these statements show that a non-zero polynomial $g \in \C[\A]$ exists, with $\deg g \leq D,$ for some explicit degree bound $D \in \mathbb{N}-\{0\},$
-such that if $\mA \in \C^{n \times n}$ does not cancel $g$, then $W(\pi_i,V(f))^A$ is in Noether position for $\pi_{i-1}.$ However, (ii) does not follow from these statements.
-Indeed, it is not necessarily the case that $W(\pi_i,V(f))^A$ is equal to $W(\pi_i,V(f^A))$.
-For instance, their dimensions may not be equal.
-This can be seen already for simple polynomials such as $f = x^2 + 2y^2-1$.
-\end{enumerate}
-
-\newpage
+\vspace{2mm}
+\par 
+\noindent \textbf{On the student author's contribution.}  Jesse
+Elliott is a Master's student, under the supervision of Mark
+Giesbrecht and \'Eric Schost; this paper will form the basis of his
+Master's thesis. Jesse was the main contributor to this submission. He
+came up with the idea of analyzing the bit-complexity of a former
+algorithm by Safey El Din and Schost, worked out most estimates, and
+wrote the bulk of the paper. He also wrote this rebuttal (except of
+course for this paragraph). We (MG and \'ES) would like to nominate
+him for a distinguished student paper award.
 

### 2020-05-15 main.tex
Updates from Overleaf

--- 2020-05-15 main.tex
@@
 Computing one point in each connected component of a real algebraic
-set $S$ is a basic subroutine in real alebraic and semi-algebraic
+set $S$ is a basic subroutine in real algebraic and semi-algebraic
 geometry; it is also useful in its own right, since it allows one to
@@
 guarantee success. In this paper, we revisit this algorithm and give a
-complete analysis of its probality of success and its bit complexity.
+complete analysis of its probability of success and its bit complexity.
 
@@
 polynomials~\cite{Kronecker82,Macaulay16,GiMo89,GiHeMoPa95,ABRW,GiHaHeMoMoPa97,GiHeMoMoPa98,Rouillier99}.
-Consider a zero-dimensional algebraic set $S \subset \C^n$ defined
-over $\Q$. A {\em zero-dimensional parametrization}
+For a zero-dimensional algebraic set $S \subset \C^n$ defined
+over $\Q$, a {\em zero-dimensional parameterization}
 $\scrQ=((q,v_1,\dots,v_n),\lambda)$ of $S$ consists in polynomials
@@
 The constraint on $\lambda$ says that the roots of $q$ are the values
-taken by $\lambda$ on $S$. The parametrization of the coordinates by
+taken by $\lambda$ on $S$. The parameterization of the coordinates by
 rational functions having $q'$ as a denominator goes back
@@
 
-Our main contribution is to analyse precisely what conditions on our
+Our main contribution is to analyze precisely what conditions on our
 change of coordinates $\mA$ guarantee success. This is done by
@@
 \begin{enumerate}
-\item The ideal  $(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
-  X_{i+1}},\dots,{\pa f}/{\pa X_n})$ is
+\item The ideal generated by polynomials $X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
+  X_{i+1}},\dots,{\pa f}/{\pa X_n}$ is
   radical.
@@
 prove that there exists a hypersurface $\D_{i} \subset \C^{n\times
-  n}$ of degree at most $6n^2(2d)^{2n}$ such that if $\mA$ is not in $\D_{i}$,
+  n}$ of degree at most $5n^2(2d)^{2n}$ such that if $\mA$ is not in $\D_{i}$,
 then $\mA$ is invertible and satisfies both conditions in
@@
 
-Consider again the $n\times n$ matrix of indeterminates
+Consider again the matrix of indeterminates
 $\A=(\A_{j,k})_{1 \le j,k \le n}$ and the field $\C(\A)$,
@@
 \begin{lemma} 
-  For $j=i,\dots,n$, there exists $P_j$ in $
-  \C(\A)[X_1,\dots,X_{i-1},X_j]$, monic in $X_j$, with $\pjb$ in
+  For $j=1,\dots,n$, there exists a polynomial $P_j$ in
+  $\C(\A)[X_1,\dots,X_{i-1},X_j]$, monic in $X_j$, with $\pjb$ in
   $\I^\A$, and such that $\deg(\pjb)\leq (2d)^{n}.$
@@
 %
-Let $\mathscr{E}$ be the event that the parametrizations
+Let $\mathscr{E}$ be the event that the parameterizations
 $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 6 of

### 2020-05-15 main.tex
typos

@@
 Throughout this section, $f$ and $i \in \{1,\hdots,n\}$ are fixed. We
-prove that there exists a hypersurface $\D_{i} \subset \C^{n\times
-  n}$ of degree at most $5n^2(2d)^{2n}$ such that if $\mA$ is not in $\D_{i}$,
-then $\mA$ is invertible and satisfies both conditions in
-$\textbf{H}_i$.
+prove that there exists a non-zero polynomial $\D_{i}$ in $n^2$
+variables and of degree at most $5n^2(2d)^{2n}$ such that if $\mA$ does
+not cancel $\D_{i}$, then $\mA$ is invertible and satisfies both
+conditions in $\textbf{H}_i$.
 

### 2020-05-15 main.tex
typos

@@
 \noindent 
-The proof of these theorems occupies the next two sections.
+The proof of these theorems occupies the next two sections. Some
+related results appear in the literature; for instance, Lemma 5
+in~\cite{JeSa10} or Proposition 4.5
+in~\cite{SharpEstimatesForTheEffectiveN} are quantitative Noether
+position statements. However, Theorem~\ref{theo:gen} does not follow
+from these previous results. Indeed, those references would allow us
+to quantify when $W(\pi_i,V(f))^\mA$ is in Noether position, whereas
+we need to understand when $W(\pi_i,V(f^\mA))$ is. As we pointed out
+before, these two sets are in general different.
 

### 2020-05-15 main.tex
typos
XML stuff

@@
 <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+<concept_id>10010147.10010148.10010149.10010150</concept_id>
+<concept_desc>Computing methodologies~Algebraic algorithms</concept_desc>
 <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
 </concept>
@@
 \]
-%
 Let $\mathscr{E}$ be the event that the parameterizations
@@
 \end{align*}
-%
 Set $k = \lg(3n/\epsilon)$ so that 

### 2020-06-09 main.tex
corrections, minor changes, and typos

@@
 \usepackage{enumitem}
+\makeatletter
+\newcommand{\skipitems}[1]{%
+  \addtocounter{\@enumctr}{#1}%
+}
+\makeatother
 % new commands and shortcuts
@@
 \end{enumerate}
-When this holds, given $\bm \sigma = (\sigma_1,\hdots,\sigma_{i-1})$
+When $\textbf{H}_i(1)$ holds, given $\bm \sigma = (\sigma_1,\hdots,\sigma_{i-1})$
 in $\C^{i-1}$, we further say that $f$ and $\bm \sigma$ satisfy
@@
 \begin{enumerate}
-\item The ideal generated by polynomials $X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
-  X_{i+1}},\dots,{\pa f}/{\pa X_n}$ is
-  radical.
-
-  {\em By point (2) above, we know that there are finitely many solutions 
+\item For any root $\xb$ of 
+\[
+(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
+  X_{i+1}},\dots,{\pa f}/{\pa X_n}),
+\]
+  the Jacobian matrix of these equations at $\xb$ has full rank $n.$
+
+{\em By point (1) above, we know that there are finitely many solutions 
     to these equations.}
+%\item The ideal generated by polynomials $X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
+%  X_{i+1}},\dots,{\pa f}/{\pa X_n}$ is
+%  radical.
+%  
+%  {\em By point (2) above, we know that there are finitely many solutions 
+%    to these equations.}
 \end{enumerate}
@@
 \begin{theorem}\label{theo:gen}
-  For $i=1,\dots,n$, there exists a non-zero polynomial $\D_i$ in
-  $\C[\A]$ of degree at most $5n^2(2d)^{2n}$ such that if $\mA \in
+  For $i=1,\dots,n$, there exists a non-zero polynomial $\D_i \in
+  \C[\A]$ of degree at most $5n^2(2d)^{2n}$ such that if $\mA \in
   \C^{n\times n}$ does not cancel $\D_i$, then $\mA$ is invertible and
@@
 \begin{theorem}\label{theo:Hp}
-  Suppose that $f$ satisfies $\textbf{H}_i$. There exists a non-zero
+  Suppose that $f$ satisfies $\textbf{H}_i$. Then for  $i=1,\dots,n$, there exists a non-zero
   polynomial $\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ of degree at most
@@
   \sigma =(\sigma_1,\dots,\sigma_{i-1})\in \C^{i-1}$ does not cancel
-  $\Xi_{i}$, the ideal
-  $$(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
-    X_{i+1}},\dots,{\pa f}/{\pa X_n})$$ is radical.}
+  $\Xi_{i}$, then for any root $\xb$ of 
+$$(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
+  X_{i+1}},\dots,{\pa f}/{\pa X_n}),$$ the Jacobian matrix of these equations at $\xb$ has full rank $n.$}
+ % the ideal
+ % $$(X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f, {\pa f}/{\pa
+ %   X_{i+1}},\dots,{\pa f}/{\pa X_n})$$ is radical.}
 
@@
   X_{i+1}},\dots,{\pa f}/{\pa X_n}),\] the Jacobian matrix of these
-equations has rank $n$. Theorem~\ref{theo:Hp} is proved.
+equations has full rank $n$. Theorem~\ref{theo:Hp} is proved.
 
@@
 
-\paragraph*{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
+\paragraph*{Bit operation cost.} The following lists the costs for each step of Algorithm 1:
 \begin{enumerate}
-    \item We defined $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}5n^3(2d)^{2n} \rceil \}$
+    \item \skipitems{1} We defined $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}5n^3(2d)^{2n} \rceil \}$
       and therefore the height of any $a_{i,j} \in S$ is at most
@@
     \]
+    Since $|T| < |S|,$ the height of any $\sigma_{j} \in T$ is at most the same.
     \item 
@@
 \end{enumerate}
-
+\noindent 
 This proves the runtime estimate, as well as our bounds on the height
@@
 \{1,\hdots,n\}.$ Now, assuming that $\mA$ is such a matrix, let
-$\Xi_i\in \C[\A]$ be the polynomials from Theorem 2.2 applied to
+$\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ be the polynomials from Theorem 2.2 applied to
 $f^{\mA}.$ Denote by $\Xi := \prod_{i=1}^n \Xi_i,$ and note that
@@
 If $\bm \sigma \in \C^{i-1}$ does not cancel $\Xi$, then $f^{\mA}$ and
-$\bm \sigma$ satisfy $\textbf{H}_i^{'}$ for all $i \in
-\{1,\hdots,n\};$ as we argued above, the algorithm is guaranteed to
+$\bm \sigma$ satisfy $\textbf{H}_i^{'}$ for all $i\in\{1,\hdots,n\}.$ As we argued above, the algorithm is guaranteed to
 succeed, as long as our call to Algorithm 2 in~\cite{SH} succeeds.

### 2020-06-12 main.tex
ACM rights review

@@
 %% complete the rights form.
-\setcopyright{acmcopyright}
+
+%% These commands are for a PROCEEDINGS abstract or paper.
+%\acmConference[ Kalamata, Messinia, Greece '20]{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation}{July 20--23, 2020}{ Kalamata, Messinia, Greece}
 \copyrightyear{2020}
 \acmYear{2020}
-\acmDOI{10.1145/1122445.1122456}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-%\acmConference[ Kalamata, Messinia, Greece '20]{ Kalamata, Messinia, Greece '20: ACM International Symposium on Symbolic and Algebraic Computation}{July 20--23, 2020}{ Kalamata, Messinia, Greece}
-\acmBooktitle{International Symposium on Symbolic and Algebraic Computation (ISSAC'20),  July 20--23, 2020,  Kalamata, Greece}
+\setcopyright{acmlicensed}\acmConference[ISSAC '20]{International Symposium on Symbolic and Algebraic Computation}{July 20--23, 2020}{Kalamata, Greece}
+\acmBooktitle{International Symposium on Symbolic and Algebraic Computation (ISSAC '20), July 20--23, 2020, Kalamata, Greece}
 \acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+\acmDOI{10.1145/3373207.3404058}
+\acmISBN{978-1-4503-7100-1/20/07}
 

### 2020-06-12 main.tex
Corrections in Theorem 2.2 and the genericity assumptions

@@
 \end{enumerate}
-When $\textbf{H}_i(1)$ holds, given $\bm \sigma = (\sigma_1,\hdots,\sigma_{i-1})$
+Given $\bm \sigma = (\sigma_1,\hdots,\sigma_{i-1})$
 in $\C^{i-1}$, we further say that $f$ and $\bm \sigma$ satisfy
@@
   the Jacobian matrix of these equations at $\xb$ has full rank $n.$ 
-
-{\em By point (1) above, we know that there are finitely many solutions 
-    to these equations.}
+{\em By the Jacobian Criterion~\cite[Corollary 16.20]{ECA}, this
+  implies that there are finitly many solutions to these equations.}
 %\item The ideal generated by polynomials $X_1-\sigma_1,\dots,X_{i-1}-\sigma_{i-1},f,{\pa f}/{\pa
@@
 \begin{theorem}\label{theo:Hp}
-  Suppose that $f$ satisfies $\textbf{H}_i$. Then for  $i=1,\dots,n$, there exists a non-zero
-  polynomial $\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ of degree at most
-  $d^{2n}$ such that if $\bm \sigma \in \C^{i-1}$ does not
+  For $i=1,\dots,n$, suppose that $f$ satisfies $\textbf{H}_i$, then there exists a non-zero polynomial $\Xi_{i} \in \C[S_1,\dots,S_{i-1}]$ of degree at most $d^{2n}$ such that if $\bm \sigma \in \C^{i-1}$ does not
   cancel $\Xi_{i}$, then $f$ and $\bm \sigma$ satisfy $\textbf{H}_i'$.

### 2020-06-13 main.tex
minor typos

@@
 
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10010147.10010148.10010149.10010150</concept_id>
+<concept_desc>Computing methodologies~Algebraic algorithms</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Computing methodologies~Algebraic algorithms}
 \begin{document}
@@
 
-Put $V = \bm\Phi^{-1}(\bm 0)$. If $V$ is empty, there is nothing to do,
+Put $V := \bm\Phi^{-1}(\bm 0)$. If $V$ is empty, there is nothing to do,
 since all values $\thetab$ in $\C^\dt$ satisfy the conclusion of the
@@
 denote the $(s+m) \times (s+n)$ Jacobian matrix with entries in
-$\C[\Xb,\Thetab]$ given by $\bm M = \jac_{\Xb,\Thetab}(\pi,\bm\Phi)$,
+$\C[\Xb,\Thetab]$ given by $\bm M := \jac_{\Xb,\Thetab}(\pi,\bm\Phi)$,
 that is,
@@
 \[
-[\mathscr{L}_1 \cdots \mathscr{L}_{n}]=\textit{\textbf{L}}\cdot \bm J(\xb,\thetab).
+[\mathscr{L}_1 \cdots \mathscr{L}_{n}]:=\textit{\textbf{L}}\cdot \bm J(\xb,\thetab).
 \] 
@@
 this result: if we consider $f^\A \in \C(\frak
-A_{j,k})[X_1,\dots,X_n]$ as defined Section~\ref{sec:gen}, this
+A_{j,k})[X_1,\dots,X_n]$ as defined in Section~\ref{sec:gen}, this
 polynomial satisfies the rank property $\textbf{H}_i(1)$.
@@
 \begin{lemma} 
-  For $j=1,\dots,n$, there exists a polynomial $P_j$ in
+  For $j=i,\dots,n$, there exists a polynomial $P_j$ in
   $\C(\A)[X_1,\dots,X_{i-1},X_j]$, monic in $X_j$, with $\pjb$ in
@@
 $\C[\A][X_1,\dots,X_n][T]$, such that
+%
 \begin{align}\label{eq:nullst}
@@
 \end{align}
-
+%
 Let us then define 
